### 2017-03-29 main.tex

\documentclass{article}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\title{Big Literature in Climate Change}
\begin{document}
\maketitle
\begin{abstract}
Where are the topics?
\end{abstract}

\section{Introduction}
\begin{itemize}

	\item Science policy, assessments - challenges of explosion.

\end{itemize}

\section{Topics}

\end{document}

### 2017-04-04 main.tex
Update on Overleaf.

@@
 \usepackage{todonotes}
-\title{Big Literature in Climate Change}
+\title{A Topic Model of Climate Change Literature}
 \begin{document}
@@
 \begin{abstract}
-Where are the topics?
+IPCC motivation, assessment making
 \end{abstract}
@@
 \begin{itemize}
+	\item Literature exploding, IPCC not keeping up \citep{minx2016learning}
+    \item No systematic way of selecting references, no comprehensive assessment
+    \item First step towards this is a map provided by topic models
+    \item What is the topic structure of climate change research? How has it changed over time?
+\end{itemize}
 
-	\item Science policy, assessments - challenges of explosion.
+\section{Methodology}
+
+\begin{itemize}
+\item Model selection: NMF
+\item How does it work?
+Advantages: Simple, scalable: better results than with other solutions, if only because it was possible to iterate with large document collections.
+LDA can be better but relies on tuning hyperparameters, hard to do with such big corpus
+\item Topic model browser \citet{Chaney2012}
+\item Human Validation: 
+\item Compare topic space to keyword space. Reduces dimensionality, ignores non-standardisation
 
@@
 
-\section{Topics}
+\section{Data}
+\begin{itemize}
+	\item Queries: use \citet{Grieneisen2011}, or take the best bits of \citet{Grieneisen2011} and other?
+    \item Sources: WoS, Scopus or both?
+\end{itemize}
+
+\section{Results}
+\begin{itemize}
+	\item The biggest topics are x and y
+	\item These topics have grown, these have decreased
+    \item X keywords fit into Y topics like so...
+    \item Finding similar documents works across topics, rather than just by keywords, so better.
+    \item Similar documents more or less likely to be across disciplinary boundaries ??
+    \item Model selection validated by these measurements.
+\end{itemize}
+
+\section{Conclusion}
+\begin{itemize}
+	\item A very simple topic model provides an overview of the whole landscape.
+    \item This allows researchers / assessment makers to identify areas that have grown recently
+    \item Topic models aid document discovery, have the potential to contribute to more comprehensive assessments.
+    \item Next steps for research: using topic models to assess the assessment process: find gaps etc.
+\end{itemize}
+
+\begin{figure}
+	%\includegraphics{}
+    \caption{Topic structure of climate change literature [network plot]}
+\end{figure}
+
+\begin{figure}
+	%\includegraphics{}
+    \caption{5 topics with most growth and 5 topics with biggest decline}
+\end{figure}
+
+\begin{figure}
+	%\includegraphics{}
+    \caption{Focus on [biochar?] showing document with highlighted words}
+\end{figure}
+
+\begin{figure}
+	%\includegraphics{}
+    \caption{Model validation graph, showing error for different topic numbers, feature numbers}
+\end{figure}
+
+\begin{figure}
+	%\includegraphics{}
+    \caption{Some relation of topics to other features of dataset: e.g. most interdisciplinary journals and least, or so...}
+\end{figure}
+
+\listoffigures
+
+\bibliography{Mendeley.bib}
+\bibliographystyle{apalike}
 

### 2017-05-02 code/do_runs.sh
new plots

@@ -1,0 +1,17 @@
+topics=(10 20 40 60 80 100)
+features=(5000 10000 50000)
+ngrams=(1 2)
+
+for t in "${topics[@]}"
+do
+    :
+    for f in "${features[@]}"
+    do
+      :
+      for n in "${ngrams[@]}"
+      do
+        :
+        python3 /home/galm/projects/cc-topography/code/nmf.py $t $n $f
+      done
+    done
+done

### 2017-05-02 code/merge_scopus.py

@@ -1,0 +1,151 @@
+import os, sys, time, resource, re, gc, shutil
+from multiprocess import Pool
+from functools import partial
+from mongoengine import *
+from urllib.parse import urlparse, parse_qsl
+connect('mongoengine_documents')
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+from mongoengine.queryset.visitor import Q
+import django
+sys.path.append('/home/galm/software/tmv/BasicBrowser/')
+os.environ.setdefault("DJANGO_SETTINGS_MODULE", "BasicBrowser.settings")
+django.setup()
+from monary import Monary
+mon = Monary()
+
+from scoping.models import *
+
+class scopus_doc(DynamicDocument):
+    scopus_id = StringField(required=True, max_length=50, unique=True)
+    PY = IntField(required=True)
+
+class scopus_ref(Document):
+    text = StringField(required=True, unique=True)
+    ti = StringField()
+    PY = IntField()
+    extra = StringField()
+    doi = StringField()
+    url = URLField()
+
+class similarity(Document):
+    wos_ut = StringField(required=True, max_length=50)
+    scopus_id = StringField(required=True, max_length=50,unique_with='wos_ut')
+    scopus_do = BooleanField(required=True, max_length=50)
+    wos_do = BooleanField(required=True, max_length=50)
+    do_match = BooleanField()
+    t_match = BooleanField()
+    jaccard = FloatField()
+    py_diff = IntField()
+    wc_diff = IntField()
+    wc = IntField()
+
+class match(Document):
+    scopus_id = StringField(required=True, max_length=50,unique_with='wos_ut')
+    wos_ut = StringField(required=True, max_length=50)
+    py_diff = IntField()
+    jaccard = FloatField()
+    wc_diff = IntField()
+
+def get(r, k):
+    try:
+        x = r[k]
+    except:
+        x = ""
+    return(x)
+
+def add_doc(r):
+    scopus2WoSFields = {
+        'TY': 'dt',
+        'TI': 'ti',
+        'T2': '',
+        'C3': '',
+        'J2': 'so',
+        'VL': 'vl',
+        'IS': '',
+        'SP': 'bp',
+        'EP': 'ep',
+        'PY': 'py',
+        'DO': 'di',
+        'SN': 'sn',
+        'AU': 'au',
+        'AD': 'ad',
+        'AB': 'ab',
+        'KW': 'kwp',
+        'Y2': '',
+        'CY': '',
[…]

### 2017-05-02 code/nmf.py

@@ -44,6 +44,7 @@ sys.path.append('/home/galm/software/tmv/BasicBrowser/')
 # sys.path.append('/home/max/Desktop/django/BasicBrowser/')
 import db3 as db
 from tmv_app.models import *
+from scoping.models import Doc
 
 
 def main():
@@ -57,11 +58,16 @@ def main():
     # The n in ngram
     try:
         ng = int(sys.argv[2])
-        print(K)
+        print(ng)
     except:
         ng = 1
+    try:
+        n_features = int(sys.argv[3])
+        print(n_features)
+    except:
+        n_features = 50000
 
-    n_features = 50000
+
     n_samples = 1000
 
     #############################################
@@ -75,10 +81,11 @@ def main():
     stoplist.add('sons')
     stoplist.add('copyright')
 
-    docs = Doc.objects.all().exclude(UT__contains='WOS2:').exclude(UT__contains='2WOS').filter(content__iregex='\w').values('UT','title','content')
+    docs = Doc.objects.filter(query=365,content__iregex='\w').values('UT','title','content')
+    #docs = docs
 
     print(len(docs))
-    abstracts = [re.split("\(C\) [1-2][0-9]{3} Elsevier",x['content'])[0] for x in docs]
+    abstracts = [re.split("\([C-c]\) [1-2][0-9]{3} Elsevier",x['content'])[0] for x in docs]
     abstracts = [x.split("Published by Elsevier")[0] for x in abstracts]
     abstracts = [x.split("Copyright (C)")[0] for x in abstracts]
     abstracts = [re.split("\. \(C\) [1-2][0-9]{3} ",x)[0] for x in abstracts]
@@ -89,22 +96,22 @@ def main():
         transtable = {ord(c): None for c in string.punctuation + string.digits}
         tokens = nltk.word_tokenize(text.translate(transtable))
         tokens = [i for i in tokens if len(i) > 2]
-        return tokens        
+        return tokens
 
     class snowball_stemmer(object):
         def __init__(self):
             self.stemmer = SnowballStemmer("english")
         def __call__(self, doc):
             return [self.stemmer.stem(t) for t in tokenize(doc)]
-    
 
 
-    run_id = db.init()
-    
+
+    run_id = db.init(n_features,ng)
+
     #############################################
     # Use tf-idf features for NMF.
     print("Extracting tf-idf features for NMF...")
[…]

### 2017-05-02 main.tex

@@
 \title{A Topic Model of Climate Change Literature}
+\title{Words, words, words: Mapping the Matter of Climate Change Literature}
+\title{A Topography of Climate Change Research}
+\author{Max Callaghan}
 \begin{document}
@@
 \begin{abstract}
-IPCC motivation, assessment making
+To contribute to evidence-based policies on tackling climate change, the IPCC aims to comprehensively assess the relevant scientific literature \citep{IPCC2013}.
+With the size of this literature currently at least [x] times larger than at the time of the IPCC's first assessment report \citep{Houghton1990ClimateAssessment}, this task has become impossible without the aid of machine-reading.
+We collect over 300,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to allow an overview of this unmanageably large corpus.
+We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of further IPCC reports.
 \end{abstract}
@@
     \item No systematic way of selecting references, no comprehensive assessment
-    \item First step towards this is a map provided by topic models
+    \item First step towards this is a map provided by topic models. 
+    \item A map shows the places which the assessment makers need to navigate, leaving them to decide course. Computer assisted not computer decided.
     \item What is the topic structure of climate change research? How has it changed over time?
@@
 \begin{itemize}
-\item Model selection: NMF
+\item Model selection: NMF \citep{Lee1999}
 \item How does it work?
@@
 \item Human Validation: 
-\item Compare topic space to keyword space. Reduces dimensionality, ignores non-standardisation
+\item Compare topic space to keyword space. Reduces dimensionality, overcomes non-standardisation
+\item Which topics get the most citations?
 
@@
 \begin{itemize}
-	\item Queries: use \citet{Grieneisen2011}, or take the best bits of \citet{Grieneisen2011} and other?
+	\item Queries: use \citet{Grieneisen2011}, or take the best bits of \citet{Grieneisen2011} and \citet{Haunschild2016}?
     \item Sources: WoS, Scopus or both?
+    \item Preprocessing: Remove punctuation, numbers, common, uncommon words, stemming
 \end{itemize}

### 2017-05-02 main.tex
Update on Overleaf.

@@
 \maketitle
-\begin{abstract}
+\textbf{
 To contribute to evidence-based policies on tackling climate change, the IPCC aims to comprehensively assess the relevant scientific literature \citep{IPCC2013}.
 With the size of this literature currently at least [x] times larger than at the time of the IPCC's first assessment report \citep{Houghton1990ClimateAssessment}, this task has become impossible without the aid of machine-reading.
-We collect over 300,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to allow an overview of this unmanageably large corpus.
+We collect over 300,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to give an overview of this unmanageably large corpus.
 We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of further IPCC reports.
-\end{abstract}
+}
+
+The size of the scientific literature on climate change has expanded rapidly over the lifetime of the IPCC.
+While the first assessment report had around 7,000 articles to assess, 5,000 new articles are now published every month, bringing the total size of the literature to well over half a million papers, (Figure \ref{growth}).
+The increase in volume, velocity, and variety of content to be assessed has turned the task of the IPCC into a `Big Literature` challenge.
+To ask questions about the literature \textit{at scale}, we now need to employ computational techniques involving natural language processing.
+
+Topic models are one such technique.
+A topic model learns the latent topics that structure a large corpus of documents, by leveraging the systematic co-occurrence of words across documents.
+Topics are distributions of words, and the topic mixture of each document explains the words observed in that document.
+This means that topic models can aid the understanding of large corpuses, and of the place of individual documents within them, by showing a document or corpus as a combination of 100 or so intelligible topics, rather than combinations of thousands of words.
+
+The topic model presented here is a rough map of climate change research since 1985.
+It shows the topics that make up this research and how they relate to each other, and demonstrates how this has changed over time.
+
+\begin{figure}
+	\includegraphics[width=\linewidth]{plots/wos_scopus_docs_time}
+    \caption{Growth in relevant literature in WoS and Scopus}
+    \label{growth}
+\end{figure}
 

### 2017-05-02 main.tex

@@
 The topic model presented here is a rough map of climate change research since 1985.
-It shows the topics that make up this research and how they relate to each other, and demonstrates how this has changed over time.
+It shows a broad outline of the topics that make up this research and how they relate to each other, and demonstrates how this has changed over time.
+This relief map does not replace the maps drawn by assessment-makers-as-cartographers for policymakers described in \citet{Edenhofer2015}.
+Rather, it supplements it by reducing the exploration time necessary and acting as a reference, to compare how the assessment reflects the literature.
+[Rather, it provides a vital anchor.]
+
+While topic modelling has been employed to answer specific questions about small aspects of climate literature, e.g.
+\citep[e.g.][]{minx2016negative,Sleeman2016}, this is the first application of topic models to gain an overview of the entire field.
 

### 2017-05-03 code/nmf.py
hot topics graph

@@ -42,7 +42,7 @@ sys.stdout.flush()
 sys.path.append('/home/galm/software/tmv/BasicBrowser/')
 
 # sys.path.append('/home/max/Desktop/django/BasicBrowser/')
-import db3 as db
+import db as db
 from tmv_app.models import *
 from scoping.models import Doc
 

### 2017-05-03 main.tex
Update on Overleaf.

@@
 While topic modelling has been employed to answer specific questions about small aspects of climate literature, e.g.
-\citep[e.g.][]{minx2016negative,Sleeman2016}, this is the first application of topic models to gain an overview of the entire field.
+\citep[e.g.][]{minx2016negative,Grubert2016}, this is the first application of topic models to gain an overview of the entire field.
 
@@
 \begin{figure}
-	%\includegraphics{}
-    \caption{5 topics with most growth and 5 topics with biggest decline}
+	\includegraphics[width=\linewidth]{plots/hot_topics}
+    \caption{Topic growth over time. The 3 topics in each assessment period that grew by the largest amount are labelled}
 \end{figure}

### 2017-05-03 main.tex
Update on Overleaf.

@@
 \documentclass{article}
+\usepackage[a4paper, total={7in, 8in}]{geometry}
 \usepackage{graphicx}
@@
 \usepackage{todonotes}
+\usepackage{booktabs}
 \title{A Topic Model of Climate Change Literature}
@@
 \end{figure}
+
+\begin{figure}
+	\includegraphics[width=\linewidth]{plots/hot_topics}
+    \caption{Topic growth over time. The 3 topics in each assessment period that grew by the largest amount are labelled}
+\end{figure}
+
+\begin{table}
+\small
+\setlength\tabcolsep{0.1cm}
+\begin{tabular}{cccccc}
+AR1 & AR2 & AR3 & AR4 & AR5 & AR6 \\
+\midrule \\
+\input{tables/topAR1} & \input{tables/topAR2}  & \input{tables/topAR3}
+ & \input{tables/topAR4}  & \input{tables/topAR5}  & \input{tables/topAR6}
+\end{tabular}
+\caption{The top 5 topics in each assessment period by percentage growth since the last assessment period}
+\end{table}
 
@@
 \begin{figure}
-	\includegraphics[width=\linewidth]{plots/hot_topics}
-    \caption{Topic growth over time. The 3 topics in each assessment period that grew by the largest amount are labelled}
-\end{figure}
-
-\begin{figure}
 	%\includegraphics{}

### 2017-05-04 code/do_runs.sh
more efficient

@@ -1,6 +1,7 @@
-topics=(10 20 40 60 80 100)
+topics=(20 40 75 100)
 features=(5000 10000 50000)
 ngrams=(1 2)
+
 
 for t in "${topics[@]}"
 do

### 2017-05-04 code/nmf.py

@@ -18,7 +18,7 @@
 # You should have received a copy of the GNU General Public License
 # along with this program.  If not, see <http://www.gnu.org/licenses/>.
 
-import pickle, string, numpy, getopt, sys, random, time, re, pprint, gc
+import pickle, string, numpy, getopt, sys, random, time, re, pprint, gc, resource
 import pandas as pd
 import onlineldavb
 import scrapeWoS
@@ -46,6 +46,62 @@ import db as db
 from tmv_app.models import *
 from scoping.models import Doc
 
+def flatten(container):
+    for i in container:
+        if isinstance(i, (list,tuple)):
+            for j in flatten(i):
+                yield j
+        else:
+            yield i
+
+def f_gamma(d,gamma,docsizes,docUTset,topic_ids):
+    dts = []
+    django.db.connections.close_all()
+    doc_size = docsizes[d]
+    doc_id = docUTset[d]
+    for k in range(len(gamma[d])):
+        if gamma[d][k] > 0.001:
+            doc = Doc.objects.get(UT=doc_id)
+            topic = Topic.objects.get(pk=topic_ids[k])
+            dt = DocTopic(
+                doc=doc, topic=topic, score=gamma[d][k],
+                scaled_score=gamma[d][k]/doc_size,
+                run_id=run_id
+            )
+            dts.append(dt)
+        # db.add_doc_topic_sk(doc_id, topic_ids[k], gamma[d][k], gamma[d][k]/doc_size)
+    return dts
+    django.db.connections.close_all()
+
+def f_lambda(topic_no,ldalambda,vocab_ids,topic_ids):
+    tts = []
+    django.db.connections.close_all()
+    lambda_sum = sum(ldalambda[topic_no])
+    db.clear_topic_terms(topic_no)
+    for term_no in range(len(ldalambda[topic_no])):
+        if ldalambda[topic_no][term_no]/lambda_sum >= .0005:
+            topic = Topic.objects.get(pk=topic_ids[topic_no])
+            term = Term.objects.get(pk=vocab_ids[term_no])
+            tt = TopicTerm(topic=topic,term=term,
+                score=ldalambda[topic_no][term_no]/lambda_sum,run_id=run_id
+            )
+            tts.append(tt)
+    return tts
+    django.db.connections.close_all()
+
+def tokenize(text):
[…]

### 2017-05-11 code/do_runs.sh
do-over without duplicate docs

@@ -1,18 +1,14 @@
-topics=(20 40 75 100)
+
 features=(5000 10000 50000)
 ngrams=(1 2)
 
 
-for t in "${topics[@]}"
-do
+  for f in "${features[@]}"
+  do
     :
-    for f in "${features[@]}"
+    for n in "${ngrams[@]}"
     do
       :
-      for n in "${ngrams[@]}"
-      do
-        :
-        python3 /home/galm/projects/cc-topography/code/nmf.py $t $n $f
-      done
+      python3 /home/galm/projects/cc-topography/code/nmf_multi.py 20 $n $f
     done
-done
+  done

### 2017-05-11 code/nmf.py

@@ -35,6 +35,11 @@ from sklearn.feature_extraction.text import TfidfVectorizer, CountVectorizer
 from sklearn.decomposition import NMF, LatentDirichletAllocation
 from time import time
 from django.utils import timezone
+from scipy.sparse import csr_matrix, find
+import numpy as np
+import psycopg2
+
+#conn = psycopg2.connect("dbname=tmv_app user=tmv password=topicmodels")
 
 sys.stdout.flush()
 
@@ -45,6 +50,8 @@ sys.path.append('/home/galm/software/tmv/BasicBrowser/')
 import db as db
 from tmv_app.models import *
 from scoping.models import Doc
+from django.db import connection, transaction
+cursor = connection.cursor()
 
 def flatten(container):
     for i in container:
@@ -54,40 +61,62 @@ def flatten(container):
         else:
             yield i
 
-def f_gamma(d,gamma,docsizes,docUTset,topic_ids):
-    dts = []
-    django.db.connections.close_all()
-    doc_size = docsizes[d]
-    doc_id = docUTset[d]
-    for k in range(len(gamma[d])):
-        if gamma[d][k] > 0.001:
-            doc = Doc.objects.get(UT=doc_id)
-            topic = Topic.objects.get(pk=topic_ids[k])
-            dt = DocTopic(
-                doc=doc, topic=topic, score=gamma[d][k],
-                scaled_score=gamma[d][k]/doc_size,
-                run_id=run_id
-            )
-            dts.append(dt)
-        # db.add_doc_topic_sk(doc_id, topic_ids[k], gamma[d][k], gamma[d][k]/doc_size)
-    return dts
-    django.db.connections.close_all()
+# def f_gamma(d,gamma,docsizes,docUTset,topic_ids):
+#     dts = []
+#     django.db.connections.close_all()
+#     doc_size = docsizes[d]
+#     doc_id = docUTset[d]
+#     row = gamma[d]
+#     nzs = find(row)
+#     for nz in range(len(nzs[1])):
+#         k = nzs[1][nz]
+#         score = nzs[2][nz]
+#         doc = Doc.objects.get(UT=doc_id)
+#         topic = Topic.objects.get(pk=topic_ids[k])
+#         dt = DocTopic(
+#             doc=doc, topic=topic, score=score,
+#             scaled_score=score,
+#             run_id=run_id
+#         )
+#         dts.append(dt)
[…]

### 2017-05-11 code/nmf_multi.py

@@ -1,0 +1,397 @@
+#!/usr/bin/env python3
+
+# onlinewikipedia.py: Demonstrates the use of online VB for LDA to
+# analyze a bunch of random Wikipedia articles.
+#
+# Copyright (C) 2010  Matthew D. Hoffman
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+
+import pickle, string, numpy, getopt, sys, random, time, re, pprint, gc, resource
+import pandas as pd
+import onlineldavb
+import scrapeWoS
+import gensim
+import nltk
+from nltk.stem import SnowballStemmer
+from nltk import word_tokenize
+import sys
+import time
+from multiprocess import Pool
+import django
+from functools import partial
+from sklearn.feature_extraction.text import TfidfVectorizer, CountVectorizer
+from sklearn.decomposition import NMF, LatentDirichletAllocation
+from time import time
+from django.utils import timezone
+from scipy.sparse import csr_matrix, find
+import numpy as np
+import psycopg2
+
+#conn = psycopg2.connect("dbname=tmv_app user=tmv password=topicmodels")
+
+sys.stdout.flush()
+
+# import file for easy access to browser database
+sys.path.append('/home/galm/software/tmv/BasicBrowser/')
+
+# sys.path.append('/home/max/Desktop/django/BasicBrowser/')
+import db as db
+from tmv_app.models import *
+from scoping.models import Doc
+from django.db import connection, transaction
+cursor = connection.cursor()
+
+def flatten(container):
+    for i in container:
+        if isinstance(i, (list,tuple)):
+            for j in flatten(i):
+                yield j
+        else:
+            yield i
+
+def f_gamma(docs,gamma,docsizes,docUTset,topic_ids):
+    dts = []
+    for d in docs:
+        if gamma[2][d] > 0.005:
+            dt = DocTopic(
[…]

### 2017-05-11 main.tex

@@
 \usepackage{booktabs}
+\usepackage{lineno}
+
+\linespread{2}
+
+% Title
 \title{A Topic Model of Climate Change Literature}
@@
 \author{Max Callaghan}
+
 \begin{document}
 \maketitle
+
+\linenumbers
+
 \textbf{
 To contribute to evidence-based policies on tackling climate change, the IPCC aims to comprehensively assess the relevant scientific literature \citep{IPCC2013}.
-With the size of this literature currently at least [x] times larger than at the time of the IPCC's first assessment report \citep{Houghton1990ClimateAssessment}, this task has become impossible without the aid of machine-reading.
-We collect over 300,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to give an overview of this unmanageably large corpus.
+With the size of this literature currently at least 100 times larger than at the time of the IPCC's first assessment report \citep{Houghton1990ClimateAssessment}, this task has become impossible without the aid of machine-reading.
+We collect over 600,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to give an overview of this unmanageably large corpus.
 We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of further IPCC reports.
@@
 While the first assessment report had around 7,000 articles to assess, 5,000 new articles are now published every month, bringing the total size of the literature to well over half a million papers, (Figure \ref{growth}).
-The increase in volume, velocity, and variety of content to be assessed has turned the task of the IPCC into a `Big Literature` challenge.
-To ask questions about the literature \textit{at scale}, we now need to employ computational techniques involving natural language processing.
+The increase in volume, velocity, and variety of content to be assessed has turned the task of the IPCC into a `Big Literature' challenge.
+To ask questions about the literature \textit{at scale}, we now need to apply computational techniques to the analysis of large document collections.
 
@@
 	\includegraphics[width=\linewidth]{plots/hot_topics}
-    \caption{Topic growth over time. The 3 topics in each assessment period that grew by the largest amount are labelled}
+    \caption{Topic growth over time. The 3 topics in each assessment period that grew by the largest amount are labelled [Example figure]}
 \end{figure}
@@
 
-\section{Introduction}
-\begin{itemize}
-	\item Literature exploding, IPCC not keeping up \citep{minx2016learning}
-    \item No systematic way of selecting references, no comprehensive assessment
-    \item First step towards this is a map provided by topic models. 
-    \item A map shows the places which the assessment makers need to navigate, leaving them to decide course. Computer assisted not computer decided.
-    \item What is the topic structure of climate change research? How has it changed over time?
-\end{itemize}
-
-\section{Methodology}
-
-\begin{itemize}
-\item Model selection: NMF \citep{Lee1999}
-\item How does it work?
-Advantages: Simple, scalable: better results than with other solutions, if only because it was possible to iterate with large document collections.
-LDA can be better but relies on tuning hyperparameters, hard to do with such big corpus
-\item Topic model browser \citet{Chaney2012}
-\item Human Validation: 
-\item Compare topic space to keyword space. Reduces dimensionality, overcomes non-standardisation
-\item Which topics get the most citations?
-
-\end{itemize}
-
-\section{Data}
-\begin{itemize}
-	\item Queries: use \citet{Grieneisen2011}, or take the best bits of \citet{Grieneisen2011} and \citet{Haunschild2016}?
-    \item Sources: WoS, Scopus or both?
-    \item Preprocessing: Remove punctuation, numbers, common, uncommon words, stemming
-\end{itemize}
-
-\section{Results}
+\section*{Results}
 \begin{itemize}
@@
 
-\section{Conclusion}
+\section{*Conclusion}
 \begin{itemize}
@@
 
+\section*{Methodology}
+
+\begin{itemize}
+\item Model selection: NMF \citep{Lee1999}
+\item How does it work?
+Advantages: Simple, scalable: better results than with other solutions, if only because it was possible to iterate with large document collections.
+LDA can be better but relies on tuning hyperparameters, hard to do with such big corpus
+\item Topic model browser \citet{Chaney2012}
+\item Human Validation: 
+\item Compare topic space to keyword space. Reduces dimensionality, overcomes non-standardisation
+\item Which topics get the most citations?
+
+\end{itemize}
+
+\section{Data}
+\begin{itemize}
+	\item Queries: use \citet{Grieneisen2011}, or take the best bits of \citet{Grieneisen2011} and \citet{Haunschild2016}?
+    \item Sources: WoS, Scopus or both?
+    \item Preprocessing: Remove punctuation, numbers, common, uncommon words, stemming
+\end{itemize}
+
 \listoffigures
-
+\linespread{1}
 \bibliography{Mendeley.bib}

### 2017-05-11 main.tex
Update on Overleaf.

@@
 To contribute to evidence-based policies on tackling climate change, the IPCC aims to comprehensively assess the relevant scientific literature \citep{IPCC2013}.
-With the size of this literature currently at least 100 times larger than at the time of the IPCC's first assessment report \citep{Houghton1990ClimateAssessment}, this task has become impossible without the aid of machine-reading.
-We collect over 600,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to give an overview of this unmanageably large corpus.
-We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of further IPCC reports.
+With the size of this literature currently almost two orders of magnitude larger than at the time of the IPCC's first assessment report \citep{Houghton1990ClimateAssessment}, this task has become impossible without the aid of machine-reading.
+We collect over 400,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to give an overview of this unmanageably large corpus.
+This overview shows us that the distribution and development of topics across the literature, and allows us to identify topics with greater and lesser representation in IPCC reports.
+We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of future IPCC assessments.
 }
@@
 The size of the scientific literature on climate change has expanded rapidly over the lifetime of the IPCC.
-While the first assessment report had around 7,000 articles to assess, 5,000 new articles are now published every month, bringing the total size of the literature to well over half a million papers, (Figure \ref{growth}).
+While the first assessment report had around 5,500 articles to assess, nearly 5,000 new articles are now published every month, bringing the total size of the literature to close to half a million papers, (Figure \ref{growth}).
 The increase in volume, velocity, and variety of content to be assessed has turned the task of the IPCC into a `Big Literature' challenge.
@@
 It shows a broad outline of the topics that make up this research and how they relate to each other, and demonstrates how this has changed over time.
-This relief map does not replace the maps drawn by assessment-makers-as-cartographers for policymakers described in \citet{Edenhofer2015}.
-Rather, it supplements it by reducing the exploration time necessary and acting as a reference, to compare how the assessment reflects the literature.
-[Rather, it provides a vital anchor.]
+This relief map should supplement the maps drawn by assessment-makers-as-cartographers for policymakers described in \citet{Edenhofer2015}, by allowing assessment makers to have an overview of unmanageably large and diverse landscape.
+Moreover, as demonstrated in this paper, such a map can be used as a reference to quantitatively measure whether the more detailed maps produced, for example, in IPCC reports, accurately reflect the underlying landscape.
+[map metaphor overworked?]
 

### 2017-05-15 code/do_runs.sh
add old topics

@@ -1,5 +1,5 @@
 
-features=(5000 10000 50000)
+features=(10000 50000 100000)
 ngrams=(1 2)
 
 

### 2017-05-24 code/nmf_multi.py
add new run stuff

@@ -78,7 +78,7 @@ def f_gamma(docs,gamma,docsizes,docUTset,topic_ids):
 def f_gamma2(docs,gamma,docsizes,docUTset,topic_ids):
     vl = []
     for d in docs:
-        if gamma[2][d] > 0.005:
+        if gamma[2][d] > 0.001:
             dt = (
                 docUTset[gamma[0][d]],
                 topic_ids[gamma[1][d]],
@@ -163,7 +163,7 @@ def main():
     stoplist.add('copyright')
 
     #docs = Doc.objects.filter(query=893,content__iregex='\w').values('UT','title','content')
-    docs = Doc.objects.filter(query=365,content__iregex='\w')
+    docs = Doc.objects.filter(query=894,content__iregex='\w')
     docs = docs#.values('UT','content')
     if limit is not False:
         docs = docs[:limit]

### 2017-05-24 main.tex
Update on Overleaf.

@@
 
+\begin{figure}
+	\includegraphics[width=\linewidth]{plots/ipcc_topics}
+    \caption{IPCC references by topic. The bars show the percentage of each topic that has been matched to an IPCC reference}
+\end{figure}
+
 \begin{table}
@@
 \caption{The top 5 topics in each assessment period by percentage growth since the last assessment period}
+\end{table}
+
+\begin{table}
+\small
+\setlength\tabcolsep{0.1cm}
+\begin{tabular}{cccccc}
+AR1 & AR2 & AR3 & AR4 & AR5 & AR6 \\
+\midrule \\
+\input{tables/bottomAR1} & \input{tables/bottomAR2}  & \input{tables/bottomAR3}
+ & \input{tables/bottomAR4}  & \input{tables/bottomAR5}  & \input{tables/bottomAR6}
+\end{tabular}
+\caption{The bottom 5 topics in each assessment period by percentage growth since the last assessment period}
 \end{table}

### 2017-05-24 main.tex
Update on Overleaf.

@@
 \title{A Topography of Climate Change Research}
-\author{Max Callaghan}
+%\author{Max Callaghan}
 
@@
 We collect over 400,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to give an overview of this unmanageably large corpus.
-This overview shows us that the distribution and development of topics across the literature, and allows us to identify topics with greater and lesser representation in IPCC reports.
-We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of future IPCC assessments.
+This overview shows us the distribution and development of topics across the literature, and allows us to identify topics with greater and lesser representation in IPCC reports.
+[We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of future IPCC assessments.]
 }
@@
 While the first assessment report had around 5,500 articles to assess, nearly 5,000 new articles are now published every month, bringing the total size of the literature to close to half a million papers, (Figure \ref{growth}).
-The increase in volume, velocity, and variety of content to be assessed has turned the task of the IPCC into a `Big Literature' challenge.
+The increase in volume, velocity, and variety of content to be assessed has turned the task of the IPCC into a `Big Literature' challenge \citep{Minx2017BigChange}.
 To ask questions about the literature \textit{at scale}, we now need to apply computational techniques to the analysis of large document collections.
@@
 While topic modelling has been employed to answer specific questions about small aspects of climate literature, e.g.
-\citep[e.g.][]{minx2016negative,Grubert2016}, this is the first application of topic models to gain an overview of the entire field.
+\citep[e.g.][]{Minx2017FastEmissions, Grubert2016}, this is the first application of topic models to gain an overview of the entire field.
 

### 2017-05-24 main.tex
shared

@@
 \documentclass{article}
-\usepackage[a4paper, total={7in, 8in}]{geometry}
+\usepackage[a4paper, total={6in, 8in}]{geometry}
 \usepackage{graphicx}
@@
 \begin{figure}
-	\includegraphics[width=\linewidth]{plots/hot_topics}
+	\includegraphics[width=\linewidth]{plots/hot_topics_65}
     \caption{Topic growth over time. The 3 topics in each assessment period that grew by the largest amount are labelled [Example figure]}
+    \label{topic_growth}
 \end{figure}
@@
     \caption{IPCC references by topic. The bars show the percentage of each topic that has been matched to an IPCC reference}
+    \label{IPCC}
 \end{figure}
@@
 \section*{Results}
+\subsection*{Literature Description}
 \begin{itemize}
-	\item The biggest topics are x and y
-	\item These topics have grown, these have decreased
-    \item X keywords fit into Y topics like so...
-    \item Finding similar documents works across topics, rather than just by keywords, so better.
-    \item Similar documents more or less likely to be across disciplinary boundaries ??
-    \item Model selection validated by these measurements.
+	\item Some big/interesting topics are x and y
+	\item These topics have grown at particularly interesting times (Figure \ref{topic_growth})
+    \item These topics are better covered in IPCC, these are less well covered \ref{IPCC}
+    \item Some interesting topic correlations are x and y; well fitting documents to both include x and y
+    \item
 \end{itemize}
 
-\section{*Conclusion}
+\subsection*{Information Retrieval Implications}
+\begin{itemize}
+    \item X keywords fit into Y topics like so...
+    \item Finding similar documents, how does this work with topics as opposed to keywords?
+    \item Similar documents more or less likely to be across disciplinary boundaries ??
+\end{itemize}
+
+\section*{Conclusion}
 \begin{itemize}
@@
     \item Topic models aid document discovery, have the potential to contribute to more comprehensive assessments.
-    \item Next steps for research: using topic models to assess the assessment process: find gaps etc.
+    \item Next steps for research: using topic models to assess the assessment process: more thorough gapfinding etc.
 \end{itemize}
@@
 \begin{figure}
-	%\includegraphics{}
+	\includegraphics[width=\linewidth]{plots/snip}
     \caption{Topic structure of climate change literature [network plot]}
+    \label{network}
 \end{figure}

### 2017-09-13 main.tex
Update on Overleaf.

@@
 This overview shows us the distribution and development of topics across the literature, and allows us to identify topics with greater and lesser representation in IPCC reports.
-[We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of future IPCC assessments.]
+%[We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of future IPCC assessments.]
 }
+
+\begin{figure}
+\begin{center}
+	\includegraphics[width=0.8\linewidth]{plots/wos_scopus_docs_time}
+    \caption{Growth in relevant literature in WoS and Scopus}
+    \label{growth}
+    \end{center}
+\end{figure}
 
@@
 
+Assessment-makers like the IPCC have been described as cartographers for policymakers \citep{Edenhofer2015}.
+As such their purpose is, summarising available scientific knowledge, to describe the problem and solution space of a policy issue.
 The topic model presented here is a rough map of climate change research since 1985.
 It shows a broad outline of the topics that make up this research and how they relate to each other, and demonstrates how this has changed over time.
-This relief map should supplement the maps drawn by assessment-makers-as-cartographers for policymakers described in \citet{Edenhofer2015}, by allowing assessment makers to have an overview of unmanageably large and diverse landscape.
-Moreover, as demonstrated in this paper, such a map can be used as a reference to quantitatively measure whether the more detailed maps produced, for example, in IPCC reports, accurately reflect the underlying landscape.
-[map metaphor overworked?]
+Such a map sheds light on the terrain of knowledge about a policy issue, making an overview of an unmanageably large and diverse landscape possible.
+This overview allows both for the production of policy pathways that are well informed by science, and, as demonstrated in this paper, the assessment of the comprehensiveness with which these pathways reflect the landscape.
 
@@
 \citep[e.g.][]{Minx2017FastEmissions, Grubert2016}, this is the first application of topic models to gain an overview of the entire field.
-
-\begin{figure}
-	\includegraphics[width=\linewidth]{plots/wos_scopus_docs_time}
-    \caption{Growth in relevant literature in WoS and Scopus}
-    \label{growth}
-\end{figure}
 

### 2017-09-15 main.tex
Update on Overleaf.

@@
 To contribute to evidence-based policies on tackling climate change, the IPCC aims to comprehensively assess the relevant scientific literature \citep{IPCC2013}.
-With the size of this literature currently almost two orders of magnitude larger than at the time of the IPCC's first assessment report \citep{Houghton1990ClimateAssessment}, this task has become impossible without the aid of machine-reading.
+With the size of this literature currently almost two orders of magnitude larger than at the time of the IPCC's first assessment report, this task has become impossible without the aid of machine-reading.
 We collect over 400,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to give an overview of this unmanageably large corpus.
@@
 
+\section*{Results}
+
+\todo{From here on in, the paper is more of an outline, with a mixture of bullet points about results that exist or I would still like to generate}
+
+\begin{figure}
+\begin{center}
+	\includegraphics[width=0.8\linewidth]{plots/network_wg_65}
+    \caption{Topic structure of climate change literature}
+    \label{network}
+    \end{center}
+\end{figure}
+
+\subsection*{Topic Model}
+\begin{itemize}
+	\item Figure \ref{network} shows the structure of the topic model with 100 topics, with each node coloured according to the IPCC working group in which the highest proportion of the topic's documents are cited.
+    \item Topics that systematically co-occur in documents are linked, and the resulting network is displayed with links weighted according to topic correlation score.
+The strength of links is greater where two topics are categorised as
+\end{itemize}
+
 \begin{figure}
@@
 \begin{figure}
-	\includegraphics[width=\linewidth]{plots/ipcc_topics}
+	\includegraphics[width=\linewidth]{plots/ipcc_topics_65}
     \caption{IPCC references by topic. The bars show the percentage of each topic that has been matched to an IPCC reference}
@@
 
-\section*{Results}
 \subsection*{Literature Description}
@@
 \end{itemize}
-
-\begin{figure}
-	\includegraphics[width=\linewidth]{plots/snip}
-    \caption{Topic structure of climate change literature [network plot]}
-    \label{network}
-\end{figure}
 

### 2017-09-22 pres/proposal.tex
start pres

\documentclass[9pt]{beamer}

\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{tikz}

\usetheme{Boadilla}

\usefonttheme{professionalfonts}

\title[Short Title]{Title}
\subtitle{}
\author{Max Callaghan}
\institute[MCC]{\includegraphics[height=1cm,width=2cm]{/home/max/Pictures/MCC_Logo_RZ_rgb.jpg}}

\newtheorem*{remark}{}

\bibliographystyle{apalike}

\begin{document}

\begin{frame}
	\titlepage
\end{frame}

\addtobeamertemplate{frametitle}{}{%
	\begin{tikzpicture}[remember picture,overlay]
	\node[anchor=north east,yshift=2pt] at (current page.north east) {\includegraphics[height=0.8cm]{/home/max/Pictures/MCC_Logo_RZ_rgb.jpg}};
	\end{tikzpicture}}

\begin{frame}{Frame Title}

\end{frame}

\begin{frame}{Frame Title}
	\small
	\bibliography{/home/max/Documents/library/bibliography}
\end{frame}

\end{document}

### 2017-09-28 main.tex

@@
     \item Topics that systematically co-occur in documents are linked, and the resulting network is displayed with links weighted according to topic correlation score.
-The strength of links is greater where two topics are categorised as
+The strength of links is greater where two topics are categorised as being in the same working group.
+This relationship is statistically significant (see SI)
 \end{itemize}
@@
 
-\subsection*{Literature Description}
 \begin{itemize}
@@
 
-\subsection*{Information Retrieval Implications}
-\begin{itemize}
-    \item X keywords fit into Y topics like so...
-    \item Finding similar documents, how does this work with topics as opposed to keywords?
-    \item Similar documents more or less likely to be across disciplinary boundaries ??
-\end{itemize}
+%\subsection*{Information Retrieval Implications}
+%\begin{itemize}
+%    \item X keywords fit into Y topics like so...
+%    \item Finding similar documents, how does this work with topics as opposed to keywords?
+%    \item Similar documents more or less likely to be across disciplinary boundaries ??
+%\end{itemize}
 
@@
     \item Topic models aid document discovery, have the potential to contribute to more comprehensive assessments.
-    \item Next steps for research: using topic models to assess the assessment process: more thorough gapfinding etc.
+	\item AR5 seemed to have less comprehensive coverage of x topics. This was a particular issue in WG y.
+	\item This may not be an issue, there could be good reasons for this, but these should be made transparent.
+	\item For the next assessment report, x topics may require particular attention.
+	\item The emerging topic on CCS resonates with a growing recognition of the importance of negative emissions and the lack of understanding about how they could fill their role.
+This will be of particular importance for the IPCC special report on 1.5 degrees.
+    %\item Next steps for research: using topic models to assess the assessment process: more thorough gapfinding etc.
 \end{itemize}
@@
 \begin{itemize}
+\item Topic modelling in general: reducing large matrix of documents to words to two smaller matrices of topics x words and topics x documents.
 \item Model selection: NMF \citep{Lee1999}
 \item How does it work?
-Advantages: Simple, scalable: better results than with other solutions, if only because it was possible to iterate with large document collections.
+Advantages: Simple, scalable: better results than with other solutions%, if only because it was possible to iterate with large document collections.
 LDA can be better but relies on tuning hyperparameters, hard to do with such big corpus
 \item Topic model browser \citet{Chaney2012}
-\item Human Validation: 
-\item Compare topic space to keyword space. Reduces dimensionality, overcomes non-standardisation
-\item Which topics get the most citations?
+\item Merging with IPCC citation dataset - caveats...
+\item Network explanation
+\item Regression of network score on dummy variable for same
+%\item Compare topic space to keyword space. Reduces dimensionality, overcomes non-standardisation
+%\item Which topics get the most citations?
 

### 2017-09-28 pres/proposal.tex

@@
 \usepackage{tikz}
+\usepackage{pgfgantt}
 
@@
 
+\definecolor{rd}{HTML}{2F2A40}
+\definecolor{methods}{HTML}{C6C6C6}
+\definecolor{research}{HTML}{8F84BE}
+\definecolor{skills}{HTML}{7A7A7A}
+\definecolor{rc}{HTML}{AC152A}
+
 \usefonttheme{professionalfonts}
 
-\title[Short Title]{Title}
+\title[Climate Topography]{A Topography of Climate Change Research}
 \subtitle{}
 \author{Max Callaghan}
-\institute[MCC]{\includegraphics[height=1cm,width=2cm]{/home/max/Pictures/MCC_Logo_RZ_rgb.jpg}}
+\institute[MCC]{
+	\includegraphics[height=1cm,width=2cm]{MCC_Logo_RZ_rgb.jpg}
+	\,
+	\includegraphics[height=1cm]{hertie_logo.png}
+}
 
@@
 	\begin{tikzpicture}[remember picture,overlay]
-	\node[anchor=north east,yshift=2pt] at (current page.north east) {\includegraphics[height=0.8cm]{/home/max/Pictures/MCC_Logo_RZ_rgb.jpg}};
+	\node[anchor=north east,yshift=2pt] at (current page.north east) {\includegraphics[height=0.8cm]{MCC_Logo_RZ_rgb.jpg}};
 	\end{tikzpicture}}
 
-\begin{frame}{Frame Title}
+\begin{frame}{Context}
+
+\begin{columns}
+	\begin{column}{0.5\linewidth}
+		\begin{center}
+		\includegraphics[width=0.6\linewidth]{syrcover.png}
+		\end{center}
+	\end{column}
+	\begin{column}{0.5\linewidth}
+	\begin{center}
+		\begin{itemize}
+			\item Climate Change is complicated
+			\item The IPCC \textit{assess} the science on climate change
+			\item These assessments should be comprehensive, credible and relevant
+		\end{itemize}
+	\end{center}
+	\end{column}
+	\end{columns}
+
+\end{frame}
+
+\begin{frame}{Motivation}
+
+\begin{columns}
+	\begin{column}{0.5\linewidth}
+		\begin{center}
+			\includegraphics[width=0.85\linewidth]{../plots/wos_scopus_docs_time.png}
+\begin{figure}
+	\includegraphics[width=0.85\linewidth]{merged_IPCC_spectral.png}
+	\caption{Source: \citet{Minx2017} }
+\end{figure}
+		\end{center}
+	\end{column}
+	\begin{column}{0.5\linewidth}
+		\begin{center}
+			\begin{itemize}
+				\item Comprehensive, credible and relevant assessments become
+				more challenging as the literature grows
+			\end{itemize}
+		\begin{remark}[]
+			To understand, and to aid, scientific assessments of climate change, we need to machine read the literature
+		\end{remark}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Approach - Words, words, words}
+
+\begin{columns}
+	\begin{column}{0.5\linewidth}
+		\begin{center}
+			\includegraphics[width=\linewidth]{volume_variety_bible.png}
+		\end{center}
+	\end{column}
+	\begin{column}{0.5\linewidth}
+		\begin{center}
+			\begin{itemize}
+				\item Topic modelling is a way of reducing the dimensionality of a corpus of documents
+				\item A large matrix of documents x words is factorised by
+				a matrix of topics x words and a matrix of topics x documents
+			\citep{Lee1999}
+				\item Topics describe the latent structure of the document corpus
+
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Preliminary results - explanation}
+
+\begin{columns}
+	\begin{column}{0.5\linewidth}
+		\begin{center}
+			\includegraphics[width=\linewidth]{../plots/biomass_eg.png}
+		\end{center}
+	\end{column}
+	\begin{column}{0.5\linewidth}
+		\begin{center}
+			\begin{itemize}
+				\item Documents are mixtures of topics, based on the words which occur in them
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Preliminary results - structure}
+
+\begin{columns}
+	\begin{column}{0.5\linewidth}
+		\begin{center}
+			\includegraphics[width=0.85\linewidth]{../plots/network_wg_65.png}
+		\end{center}
+	\end{column}
+	\begin{column}{0.5\linewidth}
+		\begin{center}
+			\begin{itemize}
+				\item A network of comprehensible topics is generated with 100 topics
+				\item Topics can be matched to the IPCC working group from which the majority of the topic documents are referenced in
+				\item Topics from the same working group are \textbf{significantly} more likely to be correlated with each other than those which are not
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Preliminary results - growth}
+
+\begin{columns}
+	\begin{column}{0.6\linewidth}
+		\begin{center}
+			\includegraphics[width=\linewidth]{../plots/hot_topics_65.png}
+		\end{center}
+	\end{column}
+	\begin{column}{0.4\linewidth}
+		\begin{center}
+			\begin{itemize}
+				\item Negative emissions related topics have shown strong growth in recent years
+				\item As have topics on food security and cities
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Preliminary results - gaps in coverage}
+
+\begin{columns}
+	\begin{column}{0.6\linewidth}
+		\begin{center}
+			\includegraphics[width=\linewidth]{../plots/ipcc_topics_65.png}
+		\end{center}
+	\end{column}
+	\begin{column}{0.4\linewidth}
+		\begin{center}
+			\begin{itemize}
+				\item The physical science aspects of climate change, as well topics on impacts, adaptation and scenarios are well covered by the IPCC
+				\item ``Niche'' topics on specific technological solutions, are less well covered
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Next steps}
+
+\begin{columns}
+%	\begin{column}{0.6\linewidth}
+%		\begin{center}
+%			\includegraphics[width=\linewidth]{../plots/ipcc_topics_65.png}
+%		\end{center}
+%	\end{column}
+	\begin{column}{0.7\linewidth}
+		\begin{center}
+			\begin{itemize}
+				\item Can I get a clearer research question, and make the analysis less descriptive?
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Outlook}
+
+\begin{figure}
+
+\tiny
+
+\begin{ganttchart}[
+	y unit title=0.3cm,
+	y unit chart=0.5cm,
+	x unit= 0.2cm,
+	vgrid,hgrid,
+	vgrid={{dotted,dotted,black}},
+	title height=1,
+	%     title/.style={fill=none},
+	title label font=\bfseries\scriptsize,
+	%bar/.style={fill=blue},
+	bar height=0.7,
+	bar label font=\tiny,
+	%   progress label text={},
+	group right shift=0,
+	group top shift=0.7,
+	group height=.3,
+	group peaks width={0.2},
+	inline]{1}{42}
+	\gantttitle{2017}{9}
+	\gantttitle{2018}{12}
+	\gantttitle{2019}{12}
+	\gantttitle{2020}{9} \\
+	\gantttitlelist{2,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,3}{3} \\
+	\gantttitlelist{4,...,12}{1} \gantttitlelist{1,...,12}{1}
+	%\gantttitlelist{J,F,M,A,M,J,J,A,S,O,N,D}{1}
+	\gantttitlelist{1,...,12}{1} \gantttitlelist{1,...,9}{1}\\
+
+	% HERTIE
+	\ganttgroup[inline=false]{Hertie Courses}{6}{42} \\
+
+	\ganttbar[inline=false, bar/.append style={fill=rd}]{Research Design}{6}{15} \\
+	\ganttbar[inline=false, bar/.append style={fill=methods}]{Methods}{6}{15} \\
+	\ganttbar[inline=false, bar/.append style={fill=skills}]{Skills}{6}{15} \\
+	\ganttbar[inline=false, bar/.append style={fill=rc}]{Research Colloquium}{19}{42} \\
+
+	% HERTIE
+	\ganttgroup[inline=false]{Thesis Research}{1}{42} \\
+	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Map}{1}{5} \\
+	\ganttbar[inline=false, bar/.append style={fill=research}]{Pyramid}{6}{15} \\
+
+	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Accumulation}{16}{27} \\
+
+	\ganttbar[inline=false, bar/.append style={fill=research}]{Evidence in Policy}{19}{27} \\
+
+	\ganttbar[inline=false, bar/.append style={fill=research}]{Envelope}{28}{33} \\
+
+	\ganttbar[inline=false, bar/.append style={fill=research}]{Revisions/Contingency}{34}{42} \\
+
+	%\ganttlinkedbar[inline=false]{Task 2}{3}{7} \ganttnewline
+	%\ganttmilestone[inline=false]{Milestone}{7} \ganttnewline
+
+\end{ganttchart}
+
+\end{figure}
 
@@
 	\small
-	\bibliography{/home/max/Documents/library/bibliography}
+	\bibliography{C:/Users/galm/Documents/library/library}
 \end{frame}

### 2017-09-28 main.tex
more writing

@@
 
-\todo{From here on in, the paper is more of an outline, with a mixture of bullet points about results that exist or I would still like to generate}
-
 \begin{figure}
 \begin{center}
-	\includegraphics[width=0.8\linewidth]{plots/network_wg_65}
+	\includegraphics[width=0.7\linewidth]{plots/network_wg_65}
     \caption{Topic structure of climate change literature}
@@
 \subsection*{Topic Model}
+
+\subsubsection*{Model Structure}
 \begin{itemize}
@@
 This relationship is statistically significant (see SI)
+    \item The largest topic is formed of the words \{research, sustain, issu, science, social, challeng\}.
+This is a broad topic that focuses on meta-issues of research priorities.
+The documents which score most highly on this topic discuss the role of research and science in tackling sustainability problems.
+[E.g.
+Miller2014].
+    \begin{itemize}
+    	\item sustainability as overarching thing
+    	\item connections of topic, wg mix of topic
+    	\item Number of documents it occurs in
     \end{itemize}
+	\item The smallest topic contains the words \{rice, paddi, field, straw, yield\}.
+It describes the relatively discrete topic of GHG emissions from rice fields.
+A closely related topic (Correlation=[x]) is \{methan, oxid, wetland\}, as the methane emissions from rice fields are of primary concern.
+This is not necessarily the smallest topic in an abstract sense in climate change research.
+Rather, it is an outcome of the decision to choose 100 topics, and represents the smallest topic visible at the scale implied by 100 clusters.
+	\begin{itemize}
+		\item number or documents it occurs in
+		\item WG balance
+	\end{itemize}
+\end{itemize}
+
+\subsubsection*{Model Dynamics}
 
@@
 \end{figure}
+
+As well as describing the structure of a research landscape, applying a topic model can indicate areas that have grown especially fast.
+This can give us an indicator of changing research priorities, and emerging areas of study.
+For each topic, we sum all topic document scores in each IPCC assessment period, and calculate the AR growth as the percentage increase from one period to the next.
+
+\begin{itemize}
+	\item Figure \ref{growth} plots the growth of topics across the 6 assessment periods of the IPCC. Table \ref{AR6} highlights the five topics that show the smallest and largest growth from AR5 to AR6
+	\begin{itemize}
+		\item \{Captur, adsopt, sorbent\} deals with the chemical process of capturing CO2, either from chimneys, or directly from the air.
+Though this topic has been discussed for some time, e.g.
+[Ward1983], the stringency of climate targets implied and lack of ambitious near term mitigation implied in the Paris Agreement [cite Dependency/betting] have made this topic, as a key component of many negative emissions, all the more relevant.
+Here we see evidence that the policy requirements is driving technical research.
+[What disciplines is this research in?]
+		\item \{urban, citi, plan\} Also reflects a growing interest in cities  - in relation to mitigation, decentralised, bla and impacts, urbanisation.
+		\item \{drought, stress, sever\} related to SDGs?
+	\end{itemize}
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% IPCC topics
+
+\begin{itemize}
+	\item For each topic, we sum the document-topic scores to calculate the size of the topic.
+The proportion of that sum which is accounted for by articles which we matched to the set of IPCC references can thus be seen as a measure of the coverage of each topic by IPCC reports.
+There is considerable variation in IPCC coverage between topics, with the extreme ends show in figure \ref{IPCC}.
+	\begin{itemize}
+		\item Is the propensity to be included in IPCC reports independent from topic scores?
+		\item This could be accounted for by bad matching, a larger pool to draw from (non explicitly climate papers).  [Do Matching by WG, AR]
+		\item This is an important area for future research.
+	\end{itemize}
+\end{itemize}
 
@@
 \begin{table}
-\small
-\setlength\tabcolsep{0.1cm}
-\begin{tabular}{cccccc}
-AR1 & AR2 & AR3 & AR4 & AR5 & AR6 \\
-\midrule \\
-\input{tables/topAR1} & \input{tables/topAR2}  & \input{tables/topAR3}
- & \input{tables/topAR4}  & \input{tables/topAR5}  & \input{tables/topAR6}
+	\begin{center}
+	\begin{tabular}{cc}
+	\input{tables/65_bottomAR6} & \input{tables/65_topAR6}
 	\end{tabular}
-\caption{The top 5 topics in each assessment period by percentage growth since the last assessment period}
+	\caption{Topics displaying the smallest (left) and largest (right) growth from AR5 to AR6}
+	\end{center}
+	\label{AR6}
 \end{table}
 
-\begin{table}
-\small
-\setlength\tabcolsep{0.1cm}
-\begin{tabular}{cccccc}
-AR1 & AR2 & AR3 & AR4 & AR5 & AR6 \\
-\midrule \\
-\input{tables/bottomAR1} & \input{tables/bottomAR2}  & \input{tables/bottomAR3}
- & \input{tables/bottomAR4}  & \input{tables/bottomAR5}  & \input{tables/bottomAR6}
-\end{tabular}
-\caption{The bottom 5 topics in each assessment period by percentage growth since the last assessment period}
-\end{table}
+%\begin{table}
+%\small
+%\setlength\tabcolsep{0.1cm}
+%\begin{tabular}{cccccc}
+%AR1 & AR2 & AR3 & AR4 & AR5 & AR6 \\
+%\midrule \\
+%\input{tables/topAR1} & \input{tables/topAR2}  & \input{tables/topAR3}
+% & \input{tables/topAR4}  & \input{tables/topAR5}  & \input{tables/topAR6}
+%\end{tabular}
+%\caption{The top 5 topics in each assessment period by percentage growth since the last assessment period}
+%\end{table}
+%
+%\begin{table}
+%\small
+%\setlength\tabcolsep{0.1cm}
+%\begin{tabular}{cccccc}
+%AR1 & AR2 & AR3 & AR4 & AR5 & AR6 \\
+%\midrule \\
+%\input{tables/bottomAR1} & \input{tables/bottomAR2}  & \input{tables/bottomAR3}
+% & \input{tables/bottomAR4}  & \input{tables/bottomAR5}  & \input{tables/bottomAR6}
+%\end{tabular}
+%\caption{The bottom 5 topics in each assessment period by percentage growth since the last assessment period}
+%\end{table}
 
 \begin{itemize}
-	\item Some big/interesting topics are x and y
-	\item These topics have grown at particularly interesting times (Figure \ref{topic_growth})
     \item These topics are better covered in IPCC, these are less well covered \ref{IPCC}

### 2017-11-08 pres/APSIS_17_11_09.tex
screenshots, pres

--- 2017-09-28 pres/proposal.tex
@@
 	\includegraphics[height=1cm,width=2cm]{MCC_Logo_RZ_rgb.jpg}
-	\,
-	\includegraphics[height=1cm]{hertie_logo.png}
+%	\,
+%	\includegraphics[height=1cm]{hertie_logo.png}
 }
@@
 		\begin{itemize}
-			\item Climate Change is complicated
-			\item The IPCC \textit{assess} the science on climate change
-			\item These assessments should be comprehensive, credible and relevant
+			\item To contribute evidence-based policy-making on climate change, the IPCC aims to \textit{comprehensively} assess  
+			\item These assessments should be aim to balance legitimacy, credibility and relevance \citep{Cash2001}
 		\end{itemize}
@@
 		\begin{center}
-			\includegraphics[width=0.85\linewidth]{../plots/wos_scopus_docs_time.png}
+%			\includegraphics[width=0.85\linewidth]{../plots/wos_scopus_docs_time.png}
 \begin{figure}
 	\includegraphics[width=0.85\linewidth]{merged_IPCC_spectral.png}
-	\caption{Source: \citet{Minx2017} }
+	\caption{Source: \citet{Minx2017l} }
 \end{figure}
@@
 \begin{columns}
-	\begin{column}{0.5\linewidth}
+	\begin{column}{0.6\linewidth}
 		\begin{center}
-			\includegraphics[width=0.85\linewidth]{../plots/network_wg_65.png}
+			\includegraphics[width=0.85\linewidth]{../plots/network_wg_372.PNG}
 		\end{center}
 	\end{column}
-	\begin{column}{0.5\linewidth}
+	\begin{column}{0.4\linewidth}
 		\begin{center}
@@
 
+\begin{frame}{Preliminary results - structure}
+
+\begin{columns}
+	\begin{column}{0.6\linewidth}
+		\begin{center}
+			\includegraphics[width=0.85\linewidth]{../plots/shares_10_372.PNG}
+
+			\medskip
+
+			\includegraphics[width=0.85\linewidth]{../plots/sustainability.PNG}
+		\end{center}
+	\end{column}
+	\begin{column}{0.4\linewidth}
+		\begin{center}
+			\begin{itemize}
+				\item In later assessment periods, the largest topic is on research priorities and sustainability
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
 \begin{frame}{Preliminary results - growth}
@@
 		\begin{center}
-			\includegraphics[width=\linewidth]{../plots/hot_topics_65.png}
+			\includegraphics[width=\linewidth]{../plots/top_20_372.png}
 		\end{center}
@@
 			\begin{itemize}
-				\item Negative emissions related topics have shown strong growth in recent years
-				\item As have topics on food security and cities
+				\item Negative emissions related topics have shown strong growth since the end of AR5
+				\item As have topics on cities and extreme weather events
 			\end{itemize}
@@
 
-\begin{frame}{Outlook}
-
-\begin{figure}
-
-\tiny
-
-\begin{ganttchart}[
-	y unit title=0.3cm,
-	y unit chart=0.5cm,
-	x unit= 0.2cm,
-	vgrid,hgrid,
-	vgrid={{dotted,dotted,black}},
-	title height=1,
-	%     title/.style={fill=none},
-	title label font=\bfseries\scriptsize,
-	%bar/.style={fill=blue},
-	bar height=0.7,
-	bar label font=\tiny,
-	%   progress label text={},
-	group right shift=0,
-	group top shift=0.7,
-	group height=.3,
-	group peaks width={0.2},
-	inline]{1}{42}
-	\gantttitle{2017}{9}
-	\gantttitle{2018}{12}
-	\gantttitle{2019}{12}
-	\gantttitle{2020}{9} \\
-	\gantttitlelist{2,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,3}{3} \\
-	\gantttitlelist{4,...,12}{1} \gantttitlelist{1,...,12}{1}
-	%\gantttitlelist{J,F,M,A,M,J,J,A,S,O,N,D}{1}
-	\gantttitlelist{1,...,12}{1} \gantttitlelist{1,...,9}{1}\\
-
-	% HERTIE
-	\ganttgroup[inline=false]{Hertie Courses}{6}{42} \\
-
-	\ganttbar[inline=false, bar/.append style={fill=rd}]{Research Design}{6}{15} \\
-	\ganttbar[inline=false, bar/.append style={fill=methods}]{Methods}{6}{15} \\
-	\ganttbar[inline=false, bar/.append style={fill=skills}]{Skills}{6}{15} \\
-	\ganttbar[inline=false, bar/.append style={fill=rc}]{Research Colloquium}{19}{42} \\
-
-	% HERTIE
-	\ganttgroup[inline=false]{Thesis Research}{1}{42} \\
-	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Map}{1}{5} \\
-	\ganttbar[inline=false, bar/.append style={fill=research}]{Pyramid}{6}{15} \\
-
-	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Accumulation}{16}{27} \\
-
-	\ganttbar[inline=false, bar/.append style={fill=research}]{Evidence in Policy}{19}{27} \\
-
-	\ganttbar[inline=false, bar/.append style={fill=research}]{Envelope}{28}{33} \\
-
-	\ganttbar[inline=false, bar/.append style={fill=research}]{Revisions/Contingency}{34}{42} \\
-
-	%\ganttlinkedbar[inline=false]{Task 2}{3}{7} \ganttnewline
-	%\ganttmilestone[inline=false]{Milestone}{7} \ganttnewline
-
-\end{ganttchart}
-
-\end{figure}
-
-\end{frame}
+%\begin{frame}{Outlook}
+%
+%\begin{figure}
+%
+%\tiny
+%
+%\begin{ganttchart}[
+%	y unit title=0.3cm,
+%	y unit chart=0.5cm,
+%	x unit= 0.2cm,
+%	vgrid,hgrid,
+%	vgrid={{dotted,dotted,black}},
+%	title height=1,
+%	%     title/.style={fill=none},
+%	title label font=\bfseries\scriptsize,
+%	%bar/.style={fill=blue},
+%	bar height=0.7,
+%	bar label font=\tiny,
+%	%   progress label text={},
+%	group right shift=0,
+%	group top shift=0.7,
+%	group height=.3,
+%	group peaks width={0.2},
+%	inline]{1}{42}
+%	\gantttitle{2017}{9}
+%	\gantttitle{2018}{12}
+%	\gantttitle{2019}{12}
+%	\gantttitle{2020}{9} \\
+%	\gantttitlelist{2,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,3}{3} \\
+%	\gantttitlelist{4,...,12}{1} \gantttitlelist{1,...,12}{1}
+%	%\gantttitlelist{J,F,M,A,M,J,J,A,S,O,N,D}{1}
+%	\gantttitlelist{1,...,12}{1} \gantttitlelist{1,...,9}{1}\\
+%	
+%	% HERTIE
+%	\ganttgroup[inline=false]{Hertie Courses}{6}{42} \\
+%	
+%	\ganttbar[inline=false, bar/.append style={fill=rd}]{Research Design}{6}{15} \\
+%	\ganttbar[inline=false, bar/.append style={fill=methods}]{Methods}{6}{15} \\
+%	\ganttbar[inline=false, bar/.append style={fill=skills}]{Skills}{6}{15} \\
+%	\ganttbar[inline=false, bar/.append style={fill=rc}]{Research Colloquium}{19}{42} \\
+%	
+%	% HERTIE
+%	\ganttgroup[inline=false]{Thesis Research}{1}{42} \\
+%	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Map}{1}{5} \\
+%	\ganttbar[inline=false, bar/.append style={fill=research}]{Pyramid}{6}{15} \\
+%	
+%	
+%	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Accumulation}{16}{27} \\
+%	
+%	\ganttbar[inline=false, bar/.append style={fill=research}]{Evidence in Policy}{19}{27} \\
+%	
+%	\ganttbar[inline=false, bar/.append style={fill=research}]{Envelope}{28}{33} \\
+%	
+%	\ganttbar[inline=false, bar/.append style={fill=research}]{Revisions/Contingency}{34}{42} \\
+%	
+%	%\ganttlinkedbar[inline=false]{Task 2}{3}{7} \ganttnewline
+%	%\ganttmilestone[inline=false]{Milestone}{7} \ganttnewline
+%	
+%	
+%	
+%\end{ganttchart} 
+%
+%\end{figure}
+%
+%\end{frame}
 

### 2017-11-08 code/do_runs.sh
more plots

@@ -2,13 +2,18 @@
 features=(10000 50000 100000)
 ngrams=(1 2)
 
+python3 /home/galm/software/django/tmv/BasicBrowser/manage.py nmf --alpha 0.1 365 100
 
-  for f in "${features[@]}"
-  do
-    :
-    for n in "${ngrams[@]}"
-    do
-      :
-      python3 /home/galm/projects/cc-topography/code/nmf_multi.py 20 $n $f
-    done
-  done
+#python3 /home/galm/software/django/tmv/BasicBrowser/manage.py nmf --alpha 0.05 365 120
+
+#python3 /home/galm/software/django/tmv/BasicBrowser/manage.py nmf --alpha 0.05 365 80
+
+  # for f in "${features[@]}"
+  # do
+  #   :
+  #   for n in "${ngrams[@]}"
+  #   do
+  #     :
+  #     python3 /home/galm/projects/cc-topography/code/nmf_multi.py 20 $n $f
+  #   done
+  # done

### 2017-11-08 code/nmf_copy.py

@@ -1,3 +1,23 @@
+#!/usr/bin/env python3
+
+# onlinewikipedia.py: Demonstrates the use of online VB for LDA to
+# analyze a bunch of random Wikipedia articles.
+#
+# Copyright (C) 2010  Matthew D. Hoffman
+#
+# This program is free software: you can redistribute it and/or modify
+# it under the terms of the GNU General Public License as published by
+# the Free Software Foundation, either version 3 of the License, or
+# (at your option) any later version.
+#
+# This program is distributed in the hope that it will be useful,
+# but WITHOUT ANY WARRANTY; without even the implied warranty of
+# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+# GNU General Public License for more details.
+#
+# You should have received a copy of the GNU General Public License
+# along with this program.  If not, see <http://www.gnu.org/licenses/>.
+
 import pickle, string, numpy, getopt, sys, random, time, re, pprint, gc, resource
 import pandas as pd
 import onlineldavb
@@ -24,7 +44,7 @@ import psycopg2
 sys.stdout.flush()
 
 # import file for easy access to browser database
-sys.path.append('/home/galm/software/django/tmv/BasicBrowser/')
+sys.path.append('/home/galm/software/tmv/BasicBrowser/')
 
 # sys.path.append('/home/max/Desktop/django/BasicBrowser/')
 import db as db
@@ -40,6 +60,28 @@ def flatten(container):
                 yield j
         else:
             yield i
+
+# def f_gamma(d,gamma,docsizes,docUTset,topic_ids):
+#     dts = []
+#     django.db.connections.close_all()
+#     doc_size = docsizes[d]
+#     doc_id = docUTset[d]
+#     row = gamma[d]
+#     nzs = find(row)
+#     for nz in range(len(nzs[1])):
+#         k = nzs[1][nz]
+#         score = nzs[2][nz]
+#         doc = Doc.objects.get(UT=doc_id)
+#         topic = Topic.objects.get(pk=topic_ids[k])
+#         dt = DocTopic(
+#             doc=doc, topic=topic, score=score,
+#             scaled_score=score,
+#             run_id=run_id
+#         )
+#         dts.append(dt)
+#         # db.add_doc_topic_sk(doc_id, topic_ids[k], gamma[d][k], gamma[d][k]/doc_size)
+#     return dts
+#     django.db.connections.close_all()
 
 def f_gamma(docs,gamma,docsizes,docUTset,topic_ids):
     dts = []

### 2017-11-09 code/run_id.py
topic model matrix plots

@@ -1,0 +1,1 @@
+run_id = 379

### 2017-11-10 main.tex
Update on Overleaf.

@@
 \textbf{
-To contribute to evidence-based policies on tackling climate change, the IPCC aims to comprehensively assess the relevant scientific literature \citep{IPCC2013}.
-With the size of this literature currently almost two orders of magnitude larger than at the time of the IPCC's first assessment report, this task has become impossible without the aid of machine-reading.
+%To contribute to evidence-based policies to tackle climate change, the IPCC aims to comprehensively assess the relevant scientific literature \citep{IPCC2013}.
+With the size of this literature currently almost two orders of magnitude larger than at the time of the IPCC's first assessment report, this task has become intractable without the aid of machine-reading.
 We collect over 400,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to give an overview of this unmanageably large corpus.
 This overview shows us the distribution and development of topics across the literature, and allows us to identify topics with greater and lesser representation in IPCC reports.
+Endogenously discovered topics on cities and carbon capture are shown to have experienced a period of high growth since the last assessment report.
+While topics on the basic science of climate change are well covered by IPCC reports, topics on specific solutions such as electric vehicles or building design are less well covered.
+%[We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of future IPCC assessments.]
+To contribute to evidence-based policies to tackle climate change, the IPCC aims to comprehensively assess the relevant scientific literature \citep{IPCC2013}.
+With the size of this literature currently almost two orders of magnitude larger than at the time of the IPCC's first assessment report, this task has become intractable without the aid of machine-reading.
+We collect over 250,000 abstracts from Web of Science (WoS), and develop a topic model in order to give an overview of this unmanageably large corpus.
+This overview shows us the distribution and development of topics across the literature, and allows us to identify topics with greater and lesser representation in IPCC reports.
+Endogenously discovered topics on cities and on negative emissions are shown to have experienced a period of high growth since the last assessment report.
+While topics on the basic science of climate change are well covered by IPCC reports, topics on specific solutions such as N or building design are less well covered.
 %[We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of future IPCC assessments.]
@@
 While the first assessment report had around 5,500 articles to assess, nearly 5,000 new articles are now published every month, bringing the total size of the literature to close to half a million papers, (Figure \ref{growth}).
-The increase in volume, velocity, and variety of content to be assessed has turned the task of the IPCC into a `Big Literature' challenge \citep{Minx2017BigChange}.
+The increase in volume, velocity, and variety of content to be assessed has turned the task of the IPCC into a `Big Literature' challenge \citep{Minx2017b}.
 To ask questions about the literature \textit{at scale}, we now need to apply computational techniques to the analysis of large document collections.
@@
 As such their purpose is, summarising available scientific knowledge, to describe the problem and solution space of a policy issue.
-The topic model presented here is a rough map of climate change research since 1985.
+The topic model presented here is a rough map of 440,000 papers making up climate change research.
 It shows a broad outline of the topics that make up this research and how they relate to each other, and demonstrates how this has changed over time.
@@
 
-While topic modelling has been employed to answer specific questions about small aspects of climate literature, e.g.
-\citep[e.g.][]{Minx2017FastEmissions, Grubert2016}, this is the first application of topic models to gain an overview of the entire field.
+An important feature of the topic-modelling approach is that topics emerge endogenously from the structure of the corpus.
+This means that they can be used to answer open-ended as well as specific questions about a corpus.
+
+This paper aims to address the following questions:
+
+\begin{itemize}
+	\item What topics are discovered endogenously from a corpus of > 200,000 abstracts on climate change?
+	\item How do these topics describe the structure of the literature?
+	\item Which topics have grown recently?
+	\item Which topics are better and worse represented in IPCC assessment reports?
+\end{itemize}
+
+While topic modelling has been employed to explore and characterise the development and structure of subfields of climate literature, e.g.
+\citep[e.g.][]{Minx2017c, Grubert2016}, this is the first application of topic models to gain an overview of the entire field.
 
@@
 \begin{itemize}
+
 	\item Figure \ref{network} shows the structure of the topic model with 100 topics, with each node coloured according to the IPCC working group in which the highest proportion of the topic's documents are cited.
+
     \item Topics that systematically co-occur in documents are linked, and the resulting network is displayed with links weighted according to topic correlation score.
@@
 This relationship is statistically significant (see SI)
+
     \item The largest topic is formed of the words \{research, sustain, issu, science, social, challeng\}.
@@
 The documents which score most highly on this topic discuss the role of research and science in tackling sustainability problems.
-[E.g.
-Miller2014].
+\citep[e.g.][]{Miller2014}.
+
     \begin{itemize}
-    	\item sustainability as overarching thing
+    	\item sustainability as overarching concept
     	\item connections of topic, wg mix of topic
@@
     \end{itemize}
+
 	\item The smallest topic contains the words \{rice, paddi, field, straw, yield\}.
@@
 Rather, it is an outcome of the decision to choose 100 topics, and represents the smallest topic visible at the scale implied by 100 clusters.
+
 	\begin{itemize}
@@
 	\end{itemize}
+
+    \item Some interesting topic correlations are x and y; well fitting documents to both include x and y
+
 \end{itemize}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Time stuff
 \subsubsection*{Model Dynamics}
@@
 
+\begin{table}
+	\begin{center}
+	\begin{tabular}{cc}
+	\input{tables/65_bottomAR6} & \input{tables/65_topAR6}
+	\end{tabular}
+	\caption{Topics displaying the smallest (left) and largest (right) growth from AR5 to AR6}
+    \label{AR6}
+	\end{center}
+
+\end{table}
+
 As well as describing the structure of a research landscape, applying a topic model can indicate areas that have grown especially fast.
@@
 	\begin{itemize}
-		\item \{Captur, adsopt, sorbent\} deals with the chemical process of capturing CO2, either from chimneys, or directly from the air.
-Though this topic has been discussed for some time, e.g.
-[Ward1983], the stringency of climate targets implied and lack of ambitious near term mitigation implied in the Paris Agreement [cite Dependency/betting] have made this topic, as a key component of many negative emissions, all the more relevant.
+		\item \{Captur, adsopt, sorbent\} deals with the chemical process of isolating CO2.
+The topic model points to articles which indicate that study of the chemical sorption of CO2 has existed for some time \citep[e.g][]{Ward1983}.
+However, the current policy landscape on climate change mitigation has given this topic a greatly increased relevance.
+The stringency of climate targets and lack of ambitious near term mitigation action implied in the Paris Agreement imply a much greater dependence on negative emissions [cite Dependency/betting].
+As the negative emissions technologies of Direct Air Capture [ref] and BECCS [ref] rely on the chemical isolation of CO2, either directly from the air, or from the chimney of power plants, this topic plays a much wider role in literature dealing with climate change.
 Here we see evidence that the policy requirements is driving technical research.
 [What disciplines is this research in?]
-		\item \{urban, citi, plan\} Also reflects a growing interest in cities  - in relation to mitigation, decentralised, bla and impacts, urbanisation.
+		\item \{urban, citi, plan\} Also reflects a growing interest in cities  - in relation to mitigation, decentralised - and impacts, urbanisation.
 		\item \{drought, stress, sever\} related to SDGs?
+        \item \{adapt, vulner, strategi\} shows increasing acceptance of and focus on adaptation as a response to climate change.
 	\end{itemize}
@@
 %% IPCC topics
-
-\begin{itemize}
-	\item For each topic, we sum the document-topic scores to calculate the size of the topic.
-The proportion of that sum which is accounted for by articles which we matched to the set of IPCC references can thus be seen as a measure of the coverage of each topic by IPCC reports.
-There is considerable variation in IPCC coverage between topics, with the extreme ends show in figure \ref{IPCC}.
-	\begin{itemize}
-		\item Is the propensity to be included in IPCC reports independent from topic scores?
-		\item This could be accounted for by bad matching, a larger pool to draw from (non explicitly climate papers).  [Do Matching by WG, AR]
-		\item This is an important area for future research.
-	\end{itemize}
-\end{itemize}
 
@@
 
-\begin{table}
-	\begin{center}
-	\begin{tabular}{cc}
-	\input{tables/65_bottomAR6} & \input{tables/65_topAR6}
-	\end{tabular}
-	\caption{Topics displaying the smallest (left) and largest (right) growth from AR5 to AR6}
-	\end{center}
-	\label{AR6}
-\end{table}
+\begin{itemize}
+	\item For each topic, we sum the document-topic scores to calculate the size of the topic.
+The proportion of that sum (only counting documents published before 2014) which is accounted for by articles which we matched to the set of IPCC references can thus be seen as a measure of the coverage of each topic by IPCC reports.
+There is considerable variation in IPCC coverage between topics, with the extreme ends show in figure \ref{IPCC}.
+	\begin{itemize}
+    	\item Topics that deal with the basic science of climate change, such as \{cloud, aerosol, radiat\}, or \{ozon, stratospher, topospher\}, as well as it's impacts (\{climat, chang, impact\}, \{precipit, extrem, annual\} are relatively well covered.
+        \item Topics that talk about specific sectors that could contribute to climate solutions (e.g.
+\{build, design, construct\}, \{oil, biodiesel, palm\}, \{vehicl, electr, hybrid\}) are much less well covered by IPCC reports.
+        \item Articles dealing with radiative forcing and climate change are more than [5] times more likely to be cited by the IPCC than articles dealing with electric vehicles and climate change.
+This observation highlights the challenges facing the IPCC in responding to the wishes of policy-makers to see more focus on solutions in environmental assessments documented in \citet{Kowarsch2017}
+		\item Is the propensity to be included in IPCC reports independent from topic scores?
+		\item This could be accounted for by bad matching, a larger pool to draw from (non explicitly climate papers).  [Do Matching by WG, AR]
+		\item This is an important area for future research.
+	\end{itemize}
+\end{itemize}
 
@@
 
-\begin{itemize}
-    \item These topics are better covered in IPCC, these are less well covered \ref{IPCC}
-    \item Some interesting topic correlations are x and y; well fitting documents to both include x and y
-    \item
-\end{itemize}
-
 %\subsection*{Information Retrieval Implications}
@@
 	\item A very simple topic model provides an overview of the whole landscape.
+    \item The endogenous nature of the approach reveals trends that were not explicitly looked for.
     \item This allows researchers / assessment makers to identify areas that have grown recently
     \item Topic models aid document discovery, have the potential to contribute to more comprehensive assessments.
-	\item AR5 seemed to have less comprehensive coverage of x topics. This was a particular issue in WG y.
+    \item The relative sparsity of references to solution-orientated topics points to challenge for future assessment reports.
+	%\item AR5 seemed to have less comprehensive coverage of x topics. This was a particular issue in WG y.
 	\item This may not be an issue, there could be good reasons for this, but these should be made transparent.
-	\item For the next assessment report, x topics may require particular attention.
-	\item The emerging topic on CCS resonates with a growing recognition of the importance of negative emissions and the lack of understanding about how they could fill their role.
+	\item Already, the analysis of quickly growing topics points to those areas where AR6 may want to focus its attentions. For example, CCS / cities.
+	%\item The emerging topic on CCS resonates with a growing recognition of the importance of negative emissions and the lack of understanding about how they could fill their role.
 This will be of particular importance for the IPCC special report on 1.5 degrees.
@@
 
-\begin{figure}
+%\begin{figure}
 	%\includegraphics{}
-    \caption{Focus on [biochar?] showing document with highlighted words}
-\end{figure}
+%    \caption{Focus on [biochar?] showing document with highlighted words}
+%\end{figure}
 
-\begin{figure}
+%\begin{figure}
 	%\includegraphics{}
-    \caption{Model validation graph, showing error for different topic numbers, feature numbers}
-\end{figure}
+%    \caption{Model validation graph, showing error for different topic numbers, feature numbers}
+%\end{figure}
 
-\begin{figure}
+%\begin{figure}
 	%\includegraphics{}
-    \caption{Some relation of topics to other features of dataset: e.g. most interdisciplinary journals and least, or so...}
-\end{figure}
+%    \caption{Some relation of topics to other features of dataset: e.g. most interdisciplinary journals and least, or so...}
+%\end{figure}
 
 \section*{Methodology}
+
+Topic modelling describes
 
@@
 \item Topic model browser \citet{Chaney2012}
+\item Time trends: post-hoc \citep{Hall2008}
 \item Merging with IPCC citation dataset - caveats...

### 2017-11-13 code/run_id.py
386

@@ -1,1 +1,1 @@
-run_id = 379
+run_id = 386

### 2017-11-14 pres/APSIS_17_11_09.tex
updated pres

@@
 
+\begin{frame}{Approach - Words, words, words}
+
+\begin{figure}
+
+	\[V_{i\mu} \]
+
+	\includegraphics[width=\linewidth]{../plots/VWH_blank.png}
+
+	\caption{A topic model of 3495 documents on climate change from the year 2000}
+
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Approach - Words, words, words}
+
+\begin{figure}
+
+	\[V_{i\mu} \approx (WH)_{i\mu} = \sum_{a=1}^{r}W_{ia}H_{a\mu} \]
+
+	\includegraphics[width=\linewidth]{../plots/VWH.png}
+
+	\caption{A topic model of 3495 documents on climate change from the year 2000}
+
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Research Questions}
+\begin{itemize}
+	\item What topics are discovered endogenously from a corpus of > 200,000 abstracts on climate change?
+	\item How do these topics describe the structure of the literature?
+	\item Which topics have grown recently?
+	\item Which topics are better and less well represented in IPCC assessment reports?
+\end{itemize}
+
+\end{frame}
+
 \begin{frame}{Preliminary results - explanation}
@@
 \begin{columns}
-	\begin{column}{0.6\linewidth}
+	\begin{column}{0.65\linewidth}
 		\begin{center}	
-			\includegraphics[width=0.85\linewidth]{../plots/network_wg_372.PNG}
+			\vspace*{-0.1\linewidth}
+			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372.PNG}
 		\end{center}
 	\end{column}
-	\begin{column}{0.4\linewidth}
+	\begin{column}{0.35\linewidth}
+		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key.PNG}
 		\begin{center}
@@
 
+\begin{frame}{Preliminary results - structure - WGI}
+
+\begin{columns}
+	\begin{column}{0.65\linewidth}
+		\begin{center}
+			\vspace*{-0.1\linewidth}
+			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_1.PNG}
+		\end{center}
+	\end{column}
+	\begin{column}{0.35\linewidth}
+		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key.PNG}
+		\begin{center}
+			\begin{itemize}
+				\item The largest topic in WGI is on models.
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Preliminary results - structure - WGII}
+
+\begin{columns}
+	\begin{column}{0.65\linewidth}
+		\begin{center}
+			\vspace*{-0.1\linewidth}
+			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_2.PNG}
+		\end{center}
+	\end{column}
+	\begin{column}{0.35\linewidth}
+		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key.PNG}
+		\begin{center}
+			\begin{itemize}
+				\item The largest primarily WGII topic is on climate change impacts
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Preliminary results - structure - WGIII}
+
+\begin{columns}
+	\begin{column}{0.65\linewidth}
+		\begin{center}
+			\vspace*{-0.1\linewidth}
+			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_3.PNG}
+		\end{center}
+	\end{column}
+	\begin{column}{0.35\linewidth}
+		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key.PNG}
+		\begin{center}
+			\begin{itemize}
+				\item The largest WGIII topic is on emissions reductions.
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Preliminary results - structure - other clusters}
+
+\begin{columns}
+	\begin{column}{0.65\linewidth}
+		\begin{center}
+			\vspace*{-0.1\linewidth}
+			\hspace*{-0.1\linewidth}
+			\includegraphics[width=1.25\linewidth]{../plots/network_wg_372_4.PNG}
+		\end{center}
+	\end{column}
+	\begin{column}{0.35\linewidth}
+		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key.PNG}
+		\begin{center}
+			\begin{itemize}
+				\item A fourth cluster of mostly WGII references contains topics on ecosystems, species and habitats
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
 \begin{frame}{Preliminary results - structure}
@@
 		\begin{center}			
-			\includegraphics[width=0.85\linewidth]{../plots/shares_10_372.PNG}
-
-			\medskip
-
-			\includegraphics[width=0.85\linewidth]{../plots/sustainability.PNG}
+			\includegraphics[width=\linewidth]{../plots/sustainability.PNG}
 		\end{center}
@@
 			\begin{itemize}
-				\item In later assessment periods, the largest topic is on research priorities and sustainability
+				\item In later assessment periods, a large meta-topic on research priorities and sustainability emerges
 			\end{itemize}
@@
 		\begin{center}
-			\includegraphics[width=\linewidth]{../plots/top_20_372.png}
+			\includegraphics[width=\linewidth]{../plots/top_20_386.png}
 		\end{center}
@@
 
+\begin{frame}{Preliminary results - growth - biochar}
+
+		\begin{center}
+			\includegraphics[width=\linewidth]{../plots/biochar_growth.png}
+
+		\medskip
+
+			\begin{itemize}
+				\item Biochar has emerged as an entirely new topic in the last 10 years
+			\end{itemize}
+		\end{center}
+
+\end{frame}
+
+\begin{frame}{Preliminary results - gaps in coverage}
+
+How can we get a sense of which topics are better covered in IPCC reports?
+
+\begin{itemize}
+	\item Each document \(d\) either matches or does not match an IPCC reference
+	\item For each topic \(h\), we can sum the scores for each category of document
+	\item The ``IPCC proportion'' of each topic is the proportion of the sum of the document score accounted for by documents which match IPCC references.
+\end{itemize}
+
+\end{frame}
+
 \begin{frame}{Preliminary results - gaps in coverage}
@@
 \begin{columns}
-	\begin{column}{0.6\linewidth}
+	\begin{column}{0.7\linewidth}
 		\begin{center}
-			\includegraphics[width=\linewidth]{../plots/ipcc_topics_65.png}
+			\includegraphics[width=\linewidth]{../plots/ipcc_topics_386.png}
 		\end{center}
 	\end{column}
-	\begin{column}{0.4\linewidth}
+	\begin{column}{0.3\linewidth}
 		\begin{center}
@@
 				\item The physical science aspects of climate change, as well topics on impacts, adaptation and scenarios are well covered by the IPCC
-				\item ``Niche'' topics on specific technological solutions, are less well covered
+				\item Topics on specific technological solutions (particularly NETs), as well as soils, are less well covered
 			\end{itemize}
@@
 
-\begin{frame}{Next steps}
+\begin{frame}{Conclusions}
+
+\begin{itemize}
+	\item Endogenously discovered topics make substantive sense of an unmanageable dataset of climate-relevant literature
+	\item Topic modelling discovers over-arching topics such as that on sustainability and research priorities, as well as individual, fast growing topics such as biochar or CCS
+	\item Topics from the same IPCC working group are more likely to be connected to each other.
+	\item Quantitative evidence is found to support policy makers' dissatisfaction with a lack of `solution orientation' in IPCC reports \citep{Kowarsch2017} 
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Extra results - Journals}
 
 \begin{columns}
-%	\begin{column}{0.6\linewidth}
-%		\begin{center}
-%			\includegraphics[width=\linewidth]{../plots/ipcc_topics_65.png}
-%		\end{center}
-%	\end{column}
-	\begin{column}{0.7\linewidth}
+	\begin{column}{0.55\linewidth}
+		\begin{center}
+			\includegraphics[width=\linewidth]{../plots/journals/journal_papers.png}
+		\end{center}
+	\end{column}
+	\begin{column}{0.45\linewidth}
 		\begin{center}
 			\begin{itemize}
-				\item Can I get a clearer research question, and make the analysis less descriptive?
+				\item Nature has been publishing about climate change for a long time
+				\item Plos One has very recently overtaken all other journals
+				\item The number of journals has risen very steeply
 			\end{itemize}
+		\includegraphics[width=0.9\linewidth]{../plots/journals/n_journals.png}
 		\end{center}
@@
 \end{columns}
+
+\end{frame}
+
+\begin{frame}{Extra results - Journals}
+
+\begin{columns}
+	\begin{column}{0.55\linewidth}
+		\begin{center}
+			\includegraphics[width=\linewidth]{../plots/journals/journal_entropy_386.png}
+		\end{center}
+	\end{column}
+	\begin{column}{0.45\linewidth}
+		\begin{center}
+			\begin{itemize}
+				\item Journal Entropy describes the distribution of topics in a journal \citep{Hall2008a}
+				\item High values mean the journal deals with a wider range of topics
+			\end{itemize}
+			\[  H(z\rvert c,y) = -\sum_{i=1}^{K} \hat{p}(z_i \rvert c,y) \; log \; \hat{p}(z_i \rvert c, y) \]
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Extra results - Journals}
+
+	\includegraphics[width=\linewidth]{../plots/journals/journal_topics_386.png}
 

### 2017-11-29 pres/Forster_29_11_09.tex
pres done

--- 2017-11-14 pres/APSIS_17_11_09.tex
@@
 \usepackage{pgfgantt}
+\usepackage{booktabs}
 
@@
 \end{itemize}
-
 \end{frame}
@@
 \end{columns}
+
+\end{frame}
+
+\begin{frame}{Preliminary results - Map}
+
+\begin{figure}
+			\includegraphics[width=\linewidth]{../plots/pca_map.png}
+			\caption{Topic Map, with topics placed according to Principal Component Analysis of topic-term matrix}
+\end{figure}
 
@@
 
-\begin{frame}{Preliminary results - structure}
+\begin{frame}{Preliminary results - structure - Sustainability}
 
@@
 \end{columns}
+
+\end{frame}
+
+\begin{frame}{Preliminary results - structure - Sustainability}
+
+\begin{columns}
+	\begin{column}{0.6\linewidth}
+		\begin{center}			
+			\includegraphics[width=\linewidth]{../plots/health_sustain_386.PNG}
+		\end{center}
+	\end{column}
+	\begin{column}{0.4\linewidth}
+		\begin{center}
+			\begin{itemize}
+				\item The flatness of its distribution across documents indicates a topic that occurs
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+%% Sus table
+
+\begin{frame}{Preliminary results - structure - Sustainability}
+\begin{table}
+	\footnotesize
+	\renewcommand{\arraystretch}{2}
+\begin{tabular}{p{0.3\linewidth}p{0.3\linewidth}p{0.3\linewidth}}
+	\toprule 
+	{polici, govern, tax} & {adapt, vulner, strategi}  & {urban, citi, area} \\ 
+	\midrule 
+	How Research-Prioritization Exercises Affect Conservation Policy & Methodological choices in solution-oriented adaptation research: a diagnostic framework & A review of urban ecosystem services: six key challenges for future research  \\
+	Role of hydrology and economics in water management policy under increasing uncertainty & When not every response to climate change is a good one: Identifying principles for sustainable adaptation & Lines of Tradition and Recent Approaches to Urban Ecology, Focussing on Germany and the USA \\
+	Informing food policy: balancing the evidence & Informed adaptation: Ethical considerations for adaptation researchers and decision-makers & Advancing understanding of the complex nature of urban systems \\
+	The identification of priority policy options for UK nature conservation & Future oriented conservation: knowledge governance, uncertainty and learning & Sustainable urban landscapes: South African perspectives on transdisciplinary possibilities \\
+	Environmental education policy research challenges and ways research might cope with them & Towards an integrated agenda for adaptation research: theory, practice and policy & A conceptual framework for addressing complexity and unfolding transition dynamics when developing sustainable adaptation strategies in urban water management \\
+	\bottomrule
+\end{tabular}
+
+\end{table}
 
@@
 
+\begin{frame}{Preliminary results - gaps in coverage}
+
+			\includegraphics[width=0.8\linewidth]{../plots/ipcc_topics_wg_386.png}
+
+\end{frame}
+
+\begin{frame}{Preliminary results - Inter-working Group topics - WG 1 and 3}
+
+\begin{table}
+
+	\input{../tables/386_wg_1_2}
+
+\end{table}
+
+\end{frame}
+
+%%%%%%%%
+
+\begin{frame}{Preliminary results - Inter-working Group topics - WG 1 and 3}
+
+\begin{table}
+
+\input{../tables/386_wg_1_3}
+
+\end{table}
+
+\end{frame}
+
+%%%%%%%
+
+\begin{frame}{Preliminary results - Inter-working Group topics - WG 2 and 3}
+
+\begin{table}
+
+\input{../tables/386_wg_2_3}
+
+\end{table}
+
+\end{frame}
+
 \begin{frame}{Conclusions}
@@
 	\item Topic modelling discovers over-arching topics such as that on sustainability and research priorities, as well as individual, fast growing topics such as biochar or CCS
-	\item Topics from the same IPCC working group are more likely to be connected to each other.
+	\item Matching documents to IPCC references, we can describe topics that belong to or bridge IPCC working groups
 	\item Quantitative evidence is found to support policy makers' dissatisfaction with a lack of `solution orientation' in IPCC reports \citep{Kowarsch2017} 

### 2018-01-29 code/dynamic_nmf0.py
validation graphs

@@ -149,7 +149,7 @@ def main():
     try:
         qid = int(sys.argv[1])
     except:
-        qid = 365
+        qid = 2355
     # The n in ngram
     try:
         K = int(sys.argv[2])
@@ -160,7 +160,7 @@ def main():
     n_features = 50000
     n_samples = 1000
     ng = 1
-    yrange=list(range(1990,2017))
+    yrange=list(range(1990,2018))
 
 
     global run_id
@@ -410,24 +410,16 @@ def main():
                 tdt.save()
 
     ## Calculate the primary dtopic for each topic
+
     for t in tops:
         try:
-            t.primary_dtopic = TopicDTopic.objects.filter(
+            t.primary_dtopic.add(TopicDTopic.objects.filter(
                 topic=t
-            ).order_by('-score').first().dynamictopic
+            ).order_by('-score').first().dynamictopic)
             t.save()
         except:
             pass
 
-    # dts = DynamicTopic.objects.filter(run_id=run_id)
-    # for dt in dts:
-    #     for y in yrange:
-    #         dtopic = TopicDTopic.objects.filter(
-    #             dynamictopic=dt,topic__year=y
-    #         ).order_by('-score').first()
-    #         topic = dtopic.topic
-    #         topic.primary_dtopic = dt
-    #         topic.save()
 
     stat.error = stat.error + nmf.reconstruction_err_
     stat.errortype = "Frobenius"

### 2018-02-05 pres/2018_02_pres.tex

\documentclass[9pt]{beamer}

\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{tikz}
\usepackage{pgfgantt}
\usepackage{booktabs}

\usetheme{Boadilla}

\definecolor{rd}{HTML}{2F2A40}
\definecolor{methods}{HTML}{C6C6C6}
\definecolor{research}{HTML}{8F84BE}
\definecolor{skills}{HTML}{7A7A7A}
\definecolor{rc}{HTML}{AC152A}

\usefonttheme{professionalfonts}

\title[Climate Topography]{A Topography of Climate Change Research}
\subtitle{}
\author{Max Callaghan}
\institute[MCC]{
	\includegraphics[height=1cm,width=2cm]{MCC_Logo_RZ_rgb.jpg}
%	\,
%	\includegraphics[height=1cm]{hertie_logo.png}
}

\newtheorem*{remark}{}

\bibliographystyle{apalike}

\begin{document}

\begin{frame}
	\titlepage
\end{frame}

\addtobeamertemplate{frametitle}{}{%
	\begin{tikzpicture}[remember picture,overlay]
	\node[anchor=north east,yshift=2pt] at (current page.north east) {\includegraphics[height=0.8cm]{MCC_Logo_RZ_rgb.jpg}};
	\end{tikzpicture}}

\begin{frame}{Context}

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
		\includegraphics[width=0.6\linewidth]{syrcover.png}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
	\begin{center}
		\begin{itemize}
			\item To contribute evidence-based policy-making on climate change, the IPCC aims to \textit{comprehensively} assess  
			\item These assessments should be aim to balance legitimacy, credibility and relevance \citep{Cash2001}
		\end{itemize}
	\end{center}
	\end{column}
	\end{columns}

\end{frame}

\begin{frame}{Motivation}

%\begin{columns}
%	\begin{column}{0.5\linewidth}
%		\begin{center}
%%			\includegraphics[width=0.85\linewidth]{../plots/wos_scopus_docs_time.png}
%\begin{figure}
%	\includegraphics[width=0.85\linewidth]{merged_IPCC_spectral.png}
%	\caption{Source: \citet{Minx2017l} }
%\end{figure}
%		\end{center}
%	\end{column}
%	\begin{column}{0.5\linewidth}
%		\begin{center}
%			\begin{itemize}
%				\item Comprehensive, credible and relevant assessments become
%				more challenging as the literature grows
%			\end{itemize}
%		\begin{remark}[]
%			To understand, and to aid, scientific assessments of climate change, we need to machine read the literature
%		\end{remark}
%		\end{center}
%	\end{column}
%\end{columns}

\begin{figure}
	\only<1>{
	\includegraphics[width=\linewidth]{../plots/volume_variety_AR1}	
}
\end{figure}

\end{frame}

\begin{frame}{Motivation - Update 2018}

Now that 2017 has ended, I have update the query to include papers from 2017 as well.

\medskip

\medskip

These extra 36,000 papers take the total number of documents to 309,697.

%% Add projections and real 2017

\end{frame}

\begin{frame}{Approach - Words, words, words}

\begin{columns}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{volume_variety_bible.png}
		\end{center}
	\end{column}
	\begin{column}{0.5\linewidth}
		\begin{center}
			\begin{itemize}
				\item Topic modelling is a way of reducing the dimensionality of a corpus of documents
				\item A large matrix of documents x words is factorised by
				a matrix of topics x words and a matrix of topics x documents
			\citep{Lee1999}
				\item Topics describe the latent structure of the document corpus

			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\end{frame}

\begin{frame}{Approach - Words, words, words}

\begin{figure}

	\[V_{i\mu} \]

	\includegraphics[width=\linewidth]{../plots/VWH_blank.png}

	\caption{A topic model of 3495 documents on climate change from the year 2000}

\end{figure}

\end{frame}

\begin{frame}{Approach - Words, words, words}

\begin{figure}

	\[V_{i\mu} \approx (WH)_{i\mu} = \sum_{a=1}^{r}W_{ia}H_{a\mu} \]

	\includegraphics[width=\linewidth]{../plots/VWH.png}

	\caption{A topic model of 3495 documents on climate change from the year 2000}

\end{figure}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Research Questions}
\begin{itemize}
	\item What is the thematic structure of the literature on climate change, and how has this changed over the five assessment periods of the IPCC
	\item What can this modelled thematic structure tell us about the past and future relationship between the IPCC and scientific literature on climate change? 
	%\item Which topics have had greater or less representation in the IPCC assessment reports?
	%	\item What topics are discovered endogenously from a corpus of > 200,000 abstracts on climate change?
	%	\item How do these topics describe the structure of the literature?
	%	\item Which topics have grown recently?
	%	\item Which topics are better and less well represented in IPCC assessment reports?
\end{itemize}
\end{frame}

%%

\begin{frame}{Methodology - Dynamic Topic Modelling}

The topic models above assume that the topics, and the words that make them up, are stable over time. Two approaches to better model dynamic topics:

\begin{itemize}
	\item<2->Dynamic Topic Modelling (DTM) \citep{Blei2006} assume that a constant number of topics exists over all topic models, but allows the words in the topics to evolve from one time period to another
	\item<3->Dynamic Non-negative Matrix Factorisation \citep{Greene2016} has varying numbers of topics in each window and allows for topics to emerge and/or disappear.
\end{itemize}

\onslide<4->{Where the size and variety of the literature we want to model has increased exponentially, we need an approach that allows for the emergence of new topics.}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%
%% D-NMF

\begin{frame}[t]{Dynamic NMF}

\only<1->{\includegraphics[]{C:/Users/galm/Documents/papers/sustainability/plots/VWH_1991}}
\only<2->{\includegraphics[]{C:/Users/galm/Documents/papers/sustainability/plots/VWH_1992}}

\only<3->{\includegraphics[]{C:/Users/galm/Documents/papers/sustainability/plots/VWH_1993}}

\end{frame}

\begin{frame}[t]{Dynamic NMF}

\includegraphics[width=\linewidth]{../plots/sustainability/conceptual_windows_only}

\end{frame}

\begin{frame}[t]{Dynamic NMF}

\includegraphics[width=\linewidth]{../plots/sustainability/conceptual_annotated_1}

\end{frame}

\begin{frame}[t]{Dynamic NMF}

\includegraphics[width=\linewidth]{../plots/sustainability/conceptual_annotated_2}

\end{frame}

\begin{frame}{Dynamic NMF - application to climate change}

\onslide<1->{
\begin{itemize}
	\item Choosing the number of window topics is non-trivial. Data-driven approaches are limited (see below), and human selection is time consuming.
	\item To facilitate the description of trends over the assessment periods of the IPCC, and to minimize the number of modelling decisions, I consider each IPCC assessment period as a time window.
\end{itemize}}

\begin{columns}
	\onslide<2->{
	\begin{column}{0.5\linewidth}

			\begin{itemize}
				\item Starting from a logarithmic relationship between the number of documents and the ideal topic number, I compare 5 runs with varying numbers of topics for each window
		\end{itemize}
	\end{column}
	\begin{column}{0.5\linewidth}
		\begin{figure}
			\includegraphics[width=\linewidth]{../plots/n_topics}	
		\end{figure}
	\end{column}
}
\end{columns}

\end{frame}

\begin{frame}[t]{Dynamic NMF - number of topics}

\begin{columns}
	\begin{column}{0.5\linewidth}
		\textbf{Human topic number criteria}
		\begin{itemize}
			\item Intelligibility
		\end{itemize}
		\textbf{Data-driven topic number criteria}
		\begin{itemize}
			\item Reconstruction accuracy
			\item Predictive capacity
		\end{itemize}
		\onslide<2->{\includegraphics[width=0.8\linewidth]{../plots/topic_validations_AR1}}
	\end{column}
	\begin{column}<2->{0.5\linewidth}

\begin{figure}
	\includegraphics[width=0.8\linewidth]{../plots/topic_validations_AR2}

	\includegraphics[width=0.8\linewidth]{../plots/topic_validations_AR3}
\end{figure}
	\end{column}
\end{columns}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% results

%\begin{frame}{Preliminary results - explanation}
%
%\begin{columns}
%	\begin{column}{0.5\linewidth}
%		\begin{center}
%			\includegraphics[width=\linewidth]{../plots/biomass_eg.png}
%		\end{center}
%	\end{column}
%	\begin{column}{0.5\linewidth}
%		\begin{center}
%			\begin{itemize}
%				\item Documents are mixtures of topics, based on the words which occur in them
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}

%\begin{frame}{Preliminary results - Map}
%
%\begin{figure}
%			\includegraphics[width=\linewidth]{../plots/pca_map.png}
%			\caption{Topic Map, with topics placed according to Principal Component Analysis of topic-term matrix}
%\end{figure}
%
%\end{frame}

\begin{frame}{Preliminary results - structure}

\begin{columns}
	\begin{column}{0.65\linewidth}
		\begin{center}	
			\vspace*{-0.1\linewidth}
			\includegraphics[width=\linewidth]{../plots/network_wg_654}
		\end{center}
	\end{column}
	\begin{column}{0.35\linewidth}
	%	\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
		\begin{center}
			\begin{itemize}
				\item A network of comprehensible topics is generated with 100 topics
				\item Topics can be matched to the IPCC working group from which the majority of the topic documents are referenced in
				\item Topics from the same working group are \textbf{significantly} more likely to be correlated with each other than those which are not
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\end{frame}

\begin{frame}{Preliminary results - Inter-working Group topics - WG 1 and 3}

	\begin{table}

		\input{../tables/654_wg_1_2}

	\end{table}

\end{frame}

%%%%%%%%

\begin{frame}{Preliminary results - Inter-working Group topics - WG 1 and 3}

	\begin{table}

		\input{../tables/654_wg_1_3}

	\end{table}

\end{frame}

%%%%%%%

\begin{frame}{Preliminary results - Inter-working Group topics - WG 2 and 3}

	\begin{table}

		\input{../tables/654_wg_2_3}

	\end{table}

\end{frame}

%\begin{frame}{Preliminary results - structure - WGI}
%
%\begin{columns}
%	\begin{column}{0.65\linewidth}
%		\begin{center}
%			\vspace*{-0.1\linewidth}
%%			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_1.PNG}
%		\end{center}
%	\end{column}
%	\begin{column}{0.35\linewidth}
%%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key.PNG}
%		\begin{center}
%			\begin{itemize}
%				\item The largest topic in WGI is on models.
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}
%
%\begin{frame}{Preliminary results - structure - WGII}
%
%\begin{columns}
%	\begin{column}{0.65\linewidth}
%		\begin{center}
%			\vspace*{-0.1\linewidth}
%			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_2}
%		\end{center}
%	\end{column}
%	\begin{column}{0.35\linewidth}
%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
%		\begin{center}
%			\begin{itemize}
%				\item The largest primarily WGII topic is on climate change impacts
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}
%
%\begin{frame}{Preliminary results - structure - WGIII}
%
%\begin{columns}
%	\begin{column}{0.65\linewidth}
%		\begin{center}
%			\vspace*{-0.1\linewidth}
%			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_3}
%		\end{center}
%	\end{column}
%	\begin{column}{0.35\linewidth}
%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
%		\begin{center}
%			\begin{itemize}
%				\item The largest WGIII topic is on emissions reductions.
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}
%
%\begin{frame}{Preliminary results - structure - other clusters}
%
%\begin{columns}
%	\begin{column}{0.65\linewidth}
%		\begin{center}
%			\vspace*{-0.1\linewidth}
%			\hspace*{-0.1\linewidth}
%			\includegraphics[width=1.25\linewidth]{../plots/network_wg_372_4}
%		\end{center}
%	\end{column}
%	\begin{column}{0.35\linewidth}
%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
%		\begin{center}
%			\begin{itemize}
%				\item A fourth cluster of mostly WGII references contains topics on ecosystems, species and habitats
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}

%\begin{frame}{Preliminary results - structure - Sustainability}
%
%
%
%\begin{columns}
%	\begin{column}{0.6\linewidth}
%		\begin{center}			
%			\includegraphics[width=\linewidth]{../plots/sustainability}
%		\end{center}
%	\end{column}
%	\begin{column}{0.4\linewidth}
%		\begin{center}
%			\begin{itemize}
%				\item In later assessment periods, a large meta-topic on research priorities and sustainability emerges
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}
%
%\begin{frame}{Preliminary results - structure - Sustainability}
%
%
%
%\begin{columns}
%	\begin{column}{0.6\linewidth}
%		\begin{center}			
%			\includegraphics[width=\linewidth]{../plots/health_sustain_386}
%		\end{center}
%	\end{column}
%	\begin{column}{0.4\linewidth}
%		\begin{center}
%			\begin{itemize}
%				\item The flatness of its distribution across documents indicates a topic that occurs
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}
%
%%% Sus table
%
%\begin{frame}{Preliminary results - structure - Sustainability}
%\begin{table}
%	\footnotesize
%	\renewcommand{\arraystretch}{2}
%\begin{tabular}{p{0.3\linewidth}p{0.3\linewidth}p{0.3\linewidth}}
%	\toprule 
%	{polici, govern, tax} & {adapt, vulner, strategi}  & {urban, citi, area} \\ 
%	\midrule 
%	How Research-Prioritization Exercises Affect Conservation Policy & Methodological choices in solution-oriented adaptation research: a diagnostic framework & A review of urban ecosystem services: six key challenges for future research  \\ 
%	Role of hydrology and economics in water management policy under increasing uncertainty & When not every response to climate change is a good one: Identifying principles for sustainable adaptation & Lines of Tradition and Recent Approaches to Urban Ecology, Focussing on Germany and the USA \\ 
%	Informing food policy: balancing the evidence & Informed adaptation: Ethical considerations for adaptation researchers and decision-makers & Advancing understanding of the complex nature of urban systems \\ 
%	The identification of priority policy options for UK nature conservation & Future oriented conservation: knowledge governance, uncertainty and learning & Sustainable urban landscapes: South African perspectives on transdisciplinary possibilities \\ 
%	Environmental education policy research challenges and ways research might cope with them & Towards an integrated agenda for adaptation research: theory, practice and policy & A conceptual framework for addressing complexity and unfolding transition dynamics when developing sustainable adaptation strategies in urban water management \\
%	\bottomrule
%\end{tabular} 
%
%\end{table}
%
%\end{frame}

%\begin{frame}{Preliminary results - growth}
%
%\begin{columns}
%	\begin{column}{0.6\linewidth}
%		\begin{center}
%			\includegraphics[width=\linewidth]{../plots/top_20_386}
%		\end{center}
%	\end{column}
%	\begin{column}{0.4\linewidth}
%		\begin{center}
%			\begin{itemize}
%				\item Negative emissions related topics have shown strong growth since the end of AR5
%				\item As have topics on cities and extreme weather events
%			\end{itemize}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}

%\begin{frame}{Preliminary results - growth - biochar}
%
%
%		\begin{center}
%			\includegraphics[width=\linewidth]{../plots/biochar_growth.png}
%
%		\medskip
%
%			\begin{itemize}
%				\item Biochar has emerged as an entirely new topic in the last 10 years
%			\end{itemize}
%		\end{center}
%
%\end{frame}

\begin{frame}{Preliminary results - gaps in coverage}

How can we get a sense of which topics are better covered in IPCC reports?

\begin{itemize}
	\item Each document \(d\) either matches or does not match an IPCC reference
	\item For each topic \(h\), we can sum the scores for each category of document
	\item The ``IPCC proportion'' of each topic is the proportion of the sum of the document score accounted for by documents which match IPCC references.
\end{itemize}

\end{frame}

\begin{frame}{Preliminary results - gaps in coverage}

\begin{columns}
	\begin{column}{0.7\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/ipcc_topics_654.png}
		\end{center}
	\end{column}
	\begin{column}{0.3\linewidth}
		\begin{center}
			\begin{itemize}
				\item The physical science aspects of climate change, as well topics on impacts, adaptation and scenarios are well covered by the IPCC
				\item Topics on specific technological solutions (particularly NETs), as well as soils, are less well covered
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\end{frame}

\begin{frame}{Preliminary results - gaps in coverage}

			\includegraphics[width=0.8\linewidth]{../plots/ipcc_topics_wg_654.png}

\end{frame}

\begin{frame}{Preliminary results - gaps in coverage}

	\includegraphics[width=0.8\linewidth]{../plots/ipcc_coverage_by_wg_654.png}

\end{frame}

\begin{frame}{Next steps}
	\begin{itemize}
		\item Adjusting second stage of model to give more weight to topics with many documents (to better capture emergence)
		\item Further analysis of new model
		\item (Manual) comparison of (AR6) topics with AR6 outline
	\end{itemize}
\end{frame}

%\begin{frame}{Conclusions}
%
%
%\begin{itemize}
%	\item Endogenously discovered topics make substantive sense of an unmanageable dataset of climate-relevant literature
%	\item Topic modelling discovers over-arching topics such as that on sustainability and research priorities, as well as individual, fast growing topics such as biochar or CCS
%	\item Matching documents to IPCC references, we can describe topics that belong to or bridge IPCC working groups
%	\item Quantitative evidence is found to support policy makers' dissatisfaction with a lack of `solution orientation' in IPCC reports \citep{Kowarsch2017} 
%	\item By uncovering the structure at scale of a large collection of documents, and by enabling the discovery of documents relevant to specific topics or combinations of topics, this approach can provide for more comprehensive and salient scientific assessments.
%\end{itemize}
%
%\end{frame}

%\begin{frame}{Extra results - Journals}
%
%\begin{columns}
%	\begin{column}{0.55\linewidth}
%		\begin{center}
%			\includegraphics[width=\linewidth]{../plots/journals/journal_papers.png}
%		\end{center}
%	\end{column}
%	\begin{column}{0.45\linewidth}
%		\begin{center}
%			\begin{itemize}
%				\item Nature has been publishing about climate change for a long time
%				\item Plos One has very recently overtaken all other journals
%				\item The number of journals has risen very steeply
%			\end{itemize}
%		\includegraphics[width=0.9\linewidth]{../plots/journals/n_journals.png}
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}

%\begin{frame}{Extra results - Journals}

%\begin{columns}
%	\begin{column}{0.55\linewidth}
%		\begin{center}
%			\includegraphics[width=\linewidth]{../plots/journals/journal_entropy_386.png}
%		\end{center}
%	\end{column}
%	\begin{column}{0.45\linewidth}
%		\begin{center}
%			\begin{itemize}
%				\item Journal Entropy describes the distribution of topics in a journal \citep{Hall2008a}
%				\item High values mean the journal deals with a wider range of topics
%			\end{itemize}
%			\[  H(z\rvert c,y) = -\sum_{i=1}^{K} \hat{p}(z_i \rvert c,y) \; log \; \hat{p}(z_i \rvert c, y) \]
%		\end{center}
%	\end{column}
%\end{columns}
%
%\end{frame}

%\begin{frame}{Extra results - Journals}
%
%	\includegraphics[width=\linewidth]{../plots/journals/journal_topics_386.png}
%
%\end{frame}

%\begin{frame}{Outlook}
%
%\begin{figure}
%
%\tiny
%
%\begin{ganttchart}[
%	y unit title=0.3cm,
%	y unit chart=0.5cm,
%	x unit= 0.2cm,
%	vgrid,hgrid,
%	vgrid={{dotted,dotted,black}},
%	title height=1,
%	%     title/.style={fill=none},
%	title label font=\bfseries\scriptsize,
%	%bar/.style={fill=blue},
%	bar height=0.7,
%	bar label font=\tiny,
%	%   progress label text={},
%	group right shift=0,
%	group top shift=0.7,
%	group height=.3,
%	group peaks width={0.2},
%	inline]{1}{42}
%	\gantttitle{2017}{9}
%	\gantttitle{2018}{12}
%	\gantttitle{2019}{12}
%	\gantttitle{2020}{9} \\
%	\gantttitlelist{2,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,3}{3} \\
%	\gantttitlelist{4,...,12}{1} \gantttitlelist{1,...,12}{1}
%	%\gantttitlelist{J,F,M,A,M,J,J,A,S,O,N,D}{1}
%	\gantttitlelist{1,...,12}{1} \gantttitlelist{1,...,9}{1}\\
%	
%	% HERTIE
%	\ganttgroup[inline=false]{Hertie Courses}{6}{42} \\
%	
%	\ganttbar[inline=false, bar/.append style={fill=rd}]{Research Design}{6}{15} \\
%	\ganttbar[inline=false, bar/.append style={fill=methods}]{Methods}{6}{15} \\
%	\ganttbar[inline=false, bar/.append style={fill=skills}]{Skills}{6}{15} \\
%	\ganttbar[inline=false, bar/.append style={fill=rc}]{Research Colloquium}{19}{42} \\
%	
%	% HERTIE
%	\ganttgroup[inline=false]{Thesis Research}{1}{42} \\
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Map}{1}{5} \\
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Pyramid}{6}{15} \\
%	
%	
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Accumulation}{16}{27} \\
%	
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Evidence in Policy}{19}{27} \\
%	
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Envelope}{28}{33} \\
%	
%	\ganttbar[inline=false, bar/.append style={fill=research}]{Revisions/Contingency}{34}{42} \\
%	
%	%\ganttlinkedbar[inline=false]{Task 2}{3}{7} \ganttnewline
%	%\ganttmilestone[inline=false]{Milestone}{7} \ganttnewline
%	
%	
%	
%\end{ganttchart} 
%
%\end{figure}
%
%\end{frame}

\begin{frame}{Frame Title}
	\small
	\bibliography{../Mendeley.bib}
\end{frame}

\end{document}

### 2018-02-06 pres/2018_02_pres.tex
feb pres

@@
 \usepackage{booktabs}
+\usepackage{framed}
 
@@
 
-%\begin{columns}
-%	\begin{column}{0.5\linewidth}
-%		\begin{center}
-%%			\includegraphics[width=0.85\linewidth]{../plots/wos_scopus_docs_time.png}
-%\begin{figure}
-%	\includegraphics[width=0.85\linewidth]{merged_IPCC_spectral.png}
-%	\caption{Source: \citet{Minx2017l} }
-%\end{figure}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.5\linewidth}
-%		\begin{center}
-%			\begin{itemize}
-%				\item Comprehensive, credible and relevant assessments become
-%				more challenging as the literature grows
-%			\end{itemize}
-%		\begin{remark}[]
-%			To understand, and to aid, scientific assessments of climate change, we need to machine read the literature
-%		\end{remark}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-
+\begin{columns}
+	\begin{column}{0.5\linewidth}
 		\begin{figure}
-	\only<1>{
-	\includegraphics[width=\linewidth]{../plots/volume_variety_AR1}	
+		\includegraphics<1>[width=1\linewidth]{../plots/volume_variety_AR0}
+		\includegraphics<2>[width=1\linewidth]{../plots/volume_variety_AR1}
+		\includegraphics<3>[width=1\linewidth]{../plots/volume_variety_bible_AR1}
+		\includegraphics<4>[width=1\linewidth]{../plots/volume_variety_bible_AR2}
+		\includegraphics<5>[width=1\linewidth]{../plots/volume_variety_bible_AR3}
+		\includegraphics<6>[width=1\linewidth]{../plots/volume_variety_bible_AR4}
+		\includegraphics<7>[width=1\linewidth]{../plots/volume_variety_bible_AR5}
+		\includegraphics<8->[width=1\linewidth]{../plots/volume_variety_bible_AR6}
+		\end{figure}
+	\end{column}
+	\begin{column}{0.5\linewidth}
+		\begin{center}
+		\only<1>{\framebox[1.1\width]{A matrix of documents x words } \par}
+		\only<2>{\framebox[1.1\width]{AR1: 1,848 documents x 3,528 words } \par}
+		\only<3>{\begin{framed}
+			The Luther Bible: 1,189 documents (chapters) x 11,973 words
+			\end{framed}}
+		%\only<3>{\framebox[1.1\width]{The Luther Bible: \par 1,189 documents (chapters) x 11,973 words } \par}
+		\only<4>{\framebox[1.1\width]{AR2: 6,941 documents x 15,781 words } \par}
+		\only<5>{\framebox[1.1\width]{AR3: 18,728 documents x 27,730 words } \par}
+		\only<6>{\framebox[1.1\width]{AR4: 44,000 documents x 45,388 words } \par}
+		\only<7>{\framebox[1.1\width]{AR5: 108,277 documents x 75,553 words } \par}
+		\only<8->{\framebox[1.1\width]{AR6: 128,357 documents x 86,149 words } \par}
+		\end{center}
+		\only<9->{		
+		\begin{center}
+			\begin{itemize}
+				\item Comprehensive, credible and relevant assessments become
+				more challenging as the literature grows
+			\end{itemize}
+		\begin{remark}[]
+			To understand, and to aid, scientific assessments of climate change, we need to machine read the literature
+		\end{remark}
+		\end{center}
 	}
-\end{figure}
-
-\end{frame}
-
-\begin{frame}{Motivation - Update 2018}
-
-Now that 2017 has ended, I have update the query to include papers from 2017 as well.
-
-\medskip
-
-\medskip
-
-These extra 36,000 papers take the total number of documents to 309,697.
-
-%% Add projections and real 2017
+	\end{column}
+\end{columns}
 
@@
 		\begin{center}
-			\includegraphics[width=\linewidth]{volume_variety_bible.png}
+			\includegraphics[width=\linewidth]{../plots/volume_variety_bible_AR6}
 		\end{center}
@@
 	\begin{column}{0.5\linewidth}
+		\textbf{Topic Modelling}
 		\begin{center}
@@
 
-	\[V_{i\mu} \]
+	\only<1>{\(V_{i\mu} \) is a term frequency-inverse document frequency matrix of \textit{stemmed} terms} 
+	\only<2>{\[V_{i\mu} \approx (WH)_{i\mu} = \sum_{a=1}^{r}W_{ia}H_{a\mu} \]} %\(V\) is approximated by the product of \(W\) and \(H\)}
 
-	\includegraphics[width=\linewidth]{../plots/VWH_blank.png}
+	\includegraphics<1>[width=\linewidth]{../plots/VWH_blank.png}
+	\includegraphics<2>[width=\linewidth]{../plots/VWH}
 
-	\caption{A topic model of 3495 documents on climate change from the year 2000}
+	\only<1>{\caption{A topic model of 3495 documents on climate change from the year 2000}}
 
-\end{figure}
-
-\end{frame}
-
-\begin{frame}{Approach - Words, words, words}
-
-\begin{figure}
-
-	\[V_{i\mu} \approx (WH)_{i\mu} = \sum_{a=1}^{r}W_{ia}H_{a\mu} \]
-
-	\includegraphics[width=\linewidth]{../plots/VWH.png}
-
-	\caption{A topic model of 3495 documents on climate change from the year 2000}
+	\only<2>{\caption{A topic model of 3495 documents on climate change from the year 2000}}
 
@@
 \begin{frame}{Research Questions}
-\begin{itemize}
-	\item What is the thematic structure of the literature on climate change, and how has this changed over the five assessment periods of the IPCC
-	\item What can this modelled thematic structure tell us about the past and future relationship between the IPCC and scientific literature on climate change? 
-	%\item Which topics have had greater or less representation in the IPCC assessment reports?
-	%	\item What topics are discovered endogenously from a corpus of > 200,000 abstracts on climate change?
-	%	\item How do these topics describe the structure of the literature?
-	%	\item Which topics have grown recently?
-	%	\item Which topics are better and less well represented in IPCC assessment reports?
-\end{itemize}
+\begin{columns}
+	\begin{column}<1->{0.5\linewidth}
+		\begin{framed}
+			What is the thematic structure of the literature on climate change, and how has this changed over the five assessment periods of the IPCC
+		\end{framed}
+	\end{column}
+	\begin{column}<2->{0.5\linewidth}
+		\begin{framed}
+			What can this modelled thematic structure tell us about the past and future relationship between the IPCC and scientific literature on climate change? 
+		\end{framed}
+	\end{column}
+\end{columns}
+
+\only<3->{
+\textbf{Steps}
+\begin{enumerate}
+	\item Download documents from Web of Science (WoS)
+	\item Match documents to reference lists from IPCC reports
+	\item Topic model stemmed document abstracts
+\end{enumerate}
+}
 \end{frame}
@@
 %%
+
+\begin{frame}{Data - Query}
+\begin{columns}
+	\begin{column}{0.65\linewidth}
+		\tiny
+		(SO=(Climate Alert OR Climate Dynamics OR Climate Policy OR Climatic Change OR Global and Planetary Change OR Global Change Biology OR International Journal of Greenhouse Gas Control OR Mitigation and Adaptation Strategies for Global Change) OR TS=(((CO2 OR "carbon dioxide" OR methane OR CH4 OR "carbon cycle" OR "carbon cycles" OR "carbon cycling" OR "carbon budget*" OR "carbon flux*" OR "carbon mitigation") AND (climat*)) OR (("carbon cycle" OR "carbon cycles" OR "carbon cycling" OR "carbon budget*" OR "carbon flux*" OR "carbon mitigation") AND (atmospher*))) OR TS=("carbon emission*" OR "sequestration of carbon" OR "sequester* carbon" OR "sequestration of CO2" OR "sequester* CO2" OR "carbon tax*" OR "CO2 abatement" OR "CO2 capture" OR "CO2 storage" OR "CO2 sequester*" OR "CO2 sequestration" OR "CO2 sink*" OR "anthropogenic carbon" OR "captur* of carbon dioxide" OR "captur* of CO2" OR "climat* variability" OR "climat* dynamic*" OR "chang* in climat*" OR "climat* proxies" OR "climat* proxy" OR "climat* sensitivity" OR "climat* shift*" OR "coupled ocean-climat*" OR "early climat*" OR "future climat*" OR "past climat*" OR "shift* climat*" OR "shift in climat*") OR TS=("atmospheric carbon dioxide" OR "atmospheric CH4" OR "atmospheric CO2" OR "atmospheric methane" OR "atmospheric N2O" OR "atmospheric nitrous oxide" OR "carbon dioxide emission*" OR "carbon sink*" OR "CH4 emission*" OR "climat* policies" OR "climat* policy" OR "CO2 emission*" OR dendroclimatolog* OR ("emission* of carbon dioxide" NOT nanotube*) OR "emission* of CH4" OR "emission* of CO2" OR "emission* of methane" OR "emission* of N2O" OR "emission* of nitrous oxide" OR "historical climat*" OR IPCC OR "methane emission*" OR "N2O emission*" OR "nitrous oxide emission*") OR TS=("climat* change*" OR "global warming" OR "greenhouse effect" OR "greenhouse gas*" OR "Kyoto Protocol" OR "warming climat*" OR "cap and trade" OR "carbon capture" OR "carbon footprint*" OR "carbon neutral" OR "carbon offset" OR "carbon sequestration" OR "carbon storage" OR "carbon trad*" OR "changing climat*" OR "climat* warming")) NOT PY=2018
+
+		\normalsize
+		\begin{itemize}
+			\item \citep{Haunschild2016}
+			\item 309,697 documents
+		\end{itemize}
+	\end{column}
+	\begin{column}{0.35\linewidth}
+		\textbf{Caveats}
+		\begin{itemize}
+			\item Not perfect query
+			\item WoS not all peer-reviewed literature
+			\item Missing grey literature
+			\item Missing relevant literature not directly about climate change
+		\end{itemize}
+	\end{column}
+\end{columns}
+\end{frame}
 

### 2018-02-12 pres/2018_02_pres.tex
literature volume bitbybit

@@
 
+\begin{frame}{Data - IPCC References}
+	\textbf{Matching process}
+
+	\medskip
+
+	For each Reference:
+	\begin{itemize}
+		\item Check for case-insensitive title matches
+		\item Calculate the Jaccard similarity score for two word every database document containing the first word and from the same year. Match if the Jaccard score is above 0.45
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Data - IPCC References}
+%\begin{columns}
+	%\begin{column}{0.5\linewidth}
+		\includegraphics[width=\linewidth]{../plots/ipcc_matches}
+	%\end{column}
+%\end{columns}
+\end{frame}
+
+\begin{frame}{Data - Unmatched IPCC References}
+	\tiny
+	\input{../tables/ipcc_matching_sample.tex}
+\end{frame}
+
+\begin{frame}{Data - Unmatched IPCC References}
+
+37\% of IPCC References could be matched to the database of climate-relevant documents
+
+\medskip
+
+\textbf{Reasons for not matching}
+\begin{enumerate}
+	\item<2->Reference is not in WoS (not peer-reviewed, in minor journal)
+	\item<3->Reference is not directly about climate change
+	\item<4->Reference has been incorrectly parsed
+\end{enumerate}
+
+\medskip
+
+\textbf{Observations}
+\begin{itemize}
+	\item<5-> The size of the literature appears to be \textit{much} bigger than our estimate
+	\item<6-> WG3 refers to more literature not directly about climate change, or not in peer-reviewed publications, than WG2, which refers to more than WG1
+\end{itemize}
+
+\end{frame}
+
 \begin{frame}{Methodology - Dynamic Topic Modelling}
@@
 
-\only<1->{\includegraphics[]{C:/Users/galm/Documents/papers/sustainability/plots/VWH_1991}}
-\only<2->{\includegraphics[]{C:/Users/galm/Documents/papers/sustainability/plots/VWH_1992}}
+\only<1->{\includegraphics[]{../plots/sustainability/VWH_1991}}
+\only<2->{\includegraphics[]{../plots/sustainability/VWH_1992}}
 
-\only<3->{\includegraphics[]{C:/Users/galm/Documents/papers/sustainability/plots/VWH_1993}}
+\only<3->{\includegraphics[]{../plots/sustainability/VWH_1993}}
 

### 2018-02-12 code/dynamic_nmf0.py

@@ -168,7 +168,7 @@ def main():
     stat = RunStats.objects.get(run_id=run_id)
     stat.query = Query.objects.get(pk=qid)
     stat.method = "DT"
-    stat.alpha = 0.05
+    stat.alpha = 0.01
     stat.save()
     i = 0
     #ndocs = Doc.objects.filter(query=qid,content__iregex='\w').count()
@@ -357,7 +357,7 @@ def main():
 
     nmf = NMF(
         n_components=K, random_state=1,
-        alpha=.1, l1_ratio=.5
+        alpha=stat.alpha, l1_ratio=.5
     ).fit(B)
 
 

### 2018-02-21 code/dynamic_nmf0.py
new maps

@@ -136,7 +136,7 @@ def predict(x):
 
 def predict(x):
     a = -75
-    b = 15
+    b = 14.5
     #b = 10
     x_hat = a+b*np.log(x)
     if x_hat > x:

### 2018-02-21 pres/2018_02_pres.tex
presentation updates

@@
 
-\usepackage[T1]{fontenc}
+\usepackage[LGR,T1]{fontenc}
+\usepackage[utf8]{inputenc} 
 \usepackage{color}
@@
 \definecolor{rc}{HTML}{AC152A}
+
+\newcommand{\textgreek}[1]{\begingroup\fontencoding{LGR}\selectfont#1\endgroup}
 
@@
 
+\begin{frame}{Introduction}
+\begin{columns}
+	\begin{column}{0.6\linewidth}
+		\begin{center}
+			\begin{figure}
+			\includegraphics[width=1\linewidth]{../plots/Hondius_Portrait_of_map-makers}
+			\caption{Portrait of map-makers, Gerard Mercator and Jodocus Hondius (Jodocus Hondius) source: \url{https://commons.wikimedia.org/wiki/File:Hondius_Portrait_of_map-makers.jpg}}
+			\end{figure}
+		\end{center}
+	\end{column}
+	\begin{column}{0.4\linewidth}
+		\begin{center}
+			\begin{itemize}
+				\item<2-> Topography is a description of a landscape
+				\item<3-> Topics (from the Greek \textgreek{τόπος}, place) can describe the features of body of text
+			\end{itemize}
+		\end{center}
+	\end{column}
+	\end{columns}
+\end{frame}
+
 \begin{frame}{Context}
@@
 		\begin{itemize}
-			\item To contribute evidence-based policy-making on climate change, the IPCC aims to \textit{comprehensively} assess  
+			\item To contribute evidence-based policy-making on climate change, the IPCC aims to \textit{comprehensively} assess scientific literature on climate change 
 			\item These assessments should be aim to balance legitimacy, credibility and relevance \citep{Cash2001}
@@
 			\citep{Lee1999}
-				\item Topics describe the latent structure of the document corpus
+				\item Topics describe the latent structure of the document corpus (What is the matter?)
 
@@
 
-\textbf{Observations}
+\only<5->{\textbf{Observations}}
 \begin{itemize}
@@
 
+\begin{frame}{Results}
+
+\begin{columns}
+	\begin{column}{0.5\linewidth}
+		\begin{center}	
+			\includegraphics[width=\linewidth]{../plots/pca_map_portrait}
+		\end{center}
+	\end{column}
+	\begin{column}{0.5\linewidth}
+		\textbf{Outline}	
+		\begin{center}
+			\begin{itemize}
+				\item<2-> Topography
+				\item<3-> Structure
+				\item<4-> Development
+				\item<5-> Representation in past IPCC reports
+				\item<6-> AR6 outlook
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
 %\begin{frame}{Preliminary results - explanation}
@@
 
-\begin{frame}{Preliminary results - structure}
+\begin{frame}{Results - structure}
 
@@
 			\begin{itemize}
-				\item A network of comprehensible topics is generated with 100 topics
-				\item Topics can be matched to the IPCC working group from which the majority of the topic documents are referenced in
-				\item Topics from the same working group are \textbf{significantly} more likely to be correlated with each other than those which are not
+				\item<1-> Topics describe comprehensible themes in climate change research
+				\item<2-> Matching topics to the IPCC working group from which the majority of the topics are referenced in, a structure is generated based on topic-document correlations
 			\end{itemize}
@@
 
-\begin{frame}{Preliminary results - Inter-working Group topics - WG 1 and 3}
+\begin{frame}{Results - Inter-working Group topics - WG 1 and 3}
 
@@
 
-%%%%%%%%
-
-\begin{frame}{Preliminary results - Inter-working Group topics - WG 1 and 3}
+\begin{frame}{Results - Inter-working Group topics - WG 1 and 3}
 
@@
 
-\begin{frame}{Preliminary results - Inter-working Group topics - WG 2 and 3}
+\begin{frame}{Results - Inter-working Group topics - WG 2 and 3}
 
@@
 \end{frame}
+
+%%%%%%%%
+%% RESULTS - DEVELOPMENT
+%\begin{frame}{Results - Development}
+%\only<1->{
+%\begin{figure}
+%	\includegraphics[width=0.8\linewidth]{../plots/development/662_sus}	
+%\end{figure}
+%}
+%\only<1->{
+%	\centering
+%	\textbf{Message}
+%}
+%\end{frame}
+
+\begin{frame}{Results - Development}
+\only<1->{
+	\begin{figure}
+		\includegraphics[width=0.8\linewidth]{../plots/development/662_holocene}	
+	\end{figure}
+}
+\only<1->{
+	\centering
+	\textbf{Basic climate science topics are not as prominent as they were previously}
+}
+\end{frame}
+
+\begin{frame}{Results - Development}
+\only<1->{
+	\begin{figure}
+		\includegraphics[width=0.8\linewidth]{../plots/development/662_sus}	
+	\end{figure}
+}
+\only<1->{
+	\centering
+	\textbf{Sustainable development, and research agendas are more prominent}
+}
+\end{frame}
+
+\begin{frame}
+	The documents that underpin this growth
+\end{frame}
+
+\begin{frame}{Results - Development}
+\only<1->{
+	\begin{figure}
+		\includegraphics[width=0.6\linewidth]{../plots/development/ar5_growth}	
+	\end{figure}
+}
+\only<1->{
+	\centering
+	\textbf{Fast growing topics in AR5 were on urban systems, negative emissions, buildings, consumption, biodiversity and risks}
+}
+\end{frame}
+
+\begin{frame}{Results - Development}
+\only<1->{
+\begin{figure}
+	\includegraphics[width=0.8\linewidth]{../plots/development/ar6_growth}	
+\end{figure}
+}
+\only<1->{
+	\centering
+	\textbf{Negative emissions topics continue to grow,}
+}
+\end{frame}
+
+%%%%%%%%%
 
@@
 
-\begin{frame}{Preliminary results - gaps in coverage}
+%\begin{frame}{Preliminary results - gaps in coverage}
+%
+%How can we get a sense of which topics are better covered in IPCC reports?
+%
+%\begin{itemize}
+%	\item Each document \(d\) either matches or does not match an IPCC reference
+%	\item For each topic \(h\), we can sum the scores for each category of document
+%	\item The ``IPCC proportion'' of each topic is the proportion of the sum of the document score accounted for by documents which match IPCC references.
+%\end{itemize}
+%
+%\end{frame}
+
+\begin{frame}{Results - topic representation in IPCC reports}
 
@@
 
-\begin{itemize}
-	\item Each document \(d\) either matches or does not match an IPCC reference
-	\item For each topic \(h\), we can sum the scores for each category of document
-	\item The ``IPCC proportion'' of each topic is the proportion of the sum of the document score accounted for by documents which match IPCC references.
-\end{itemize}
+\medskip
+
+We get a measure of proportionality between two distributions by dividing the each topics share in the IPCC sample by its share in the whole corpus
+
+%\begin{itemize}
+%	\item Each document \(d\) either matches or does not match an IPCC reference
+%	\item For each topic \(h\), we can sum the scores for each category of document
+%	\item The ``IPCC proportion'' of each topic is the proportion of the sum of the document score accounted for by documents which match IPCC references.
+%\end{itemize}
 
@@
 
-\begin{frame}{Preliminary results - gaps in coverage}
+\begin{frame}{Results - topic representation in IPCC reports}
 
@@
 		\begin{center}
-			\includegraphics[width=\linewidth]{../plots/ipcc_topics_654.png}
+			\includegraphics[width=\linewidth]{../plots/ipcc_representation/ipcc_rep_662_all.png}
 		\end{center}
@@
 				\item The physical science aspects of climate change, as well topics on impacts, adaptation and scenarios are well covered by the IPCC
-				\item Topics on specific technological solutions (particularly NETs), as well as soils, are less well covered
+				\item Topics on specific technological solutions (particularly NETs), as well as soils and plants are less well represented
 			\end{itemize}
@@
 
-\begin{frame}{Preliminary results - gaps in coverage}
+\begin{frame}{Results - topic representation in IPCC reports}
 
-			\includegraphics[width=0.8\linewidth]{../plots/ipcc_topics_wg_654.png}
+	\begin{figure}
+			\includegraphics[width=0.8\linewidth]{../plots/ipcc_representation/ipcc_rep_662_ARs}
+	\end{figure}
 
@@
 
-\begin{frame}{Next steps}
+\begin{frame}{Results - AR6 outlook}
+
+Outlines for the sixth assessment report have already been published.
+
+The words in each chapter were matched to the Topic-Term matrix generated by the model to calculate a [simplified] topic score for each chapter.
+
+These scores were summed and were compared to the corpus in general in the same way as with past reports
+
+\end{frame}
+
+\begin{frame}{Results - topic representation in IPCC reports}
+
+\begin{columns}
+	\begin{column}{0.7\linewidth}
+		\begin{center}
+			\includegraphics[width=\linewidth]{../plots/ipcc_representation/ipcc_rep_662_AR6.png}
+		\end{center}
+	\end{column}
+	\begin{column}{0.3\linewidth}
+		\begin{center}
 			\begin{itemize}
-		\item Adjusting second stage of model to give more weight to topics with many documents (to better capture emergence)
-		\item Further analysis of new model
-		\item (Manual) comparison of (AR6) topics with AR6 outline
+				\item The physical science aspects of climate change, as well topics on impacts, adaptation and scenarios are well covered by the IPCC
+				\item Topics on specific technological solutions (particularly NETs), as well as soils and plants are less well represented
 			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
 \end{frame}
+
+%\begin{frame}{Next steps}
+%	\begin{itemize}
+%		\item Adjusting second stage of model to give more weight to topics with many documents (to better capture emergence)
+%		\item Further analysis of new model
+%		\item (Manual) comparison of (AR6) topics with AR6 outline
+%	\end{itemize}
+%\end{frame}
 

### 2018-06-14 code/do_nmf.py
single doc page

@@ -1,0 +1,28 @@
+import sys
+import django
+import os
+# import file for easy access to browser database
+sys.path.append('/home/galm/software/django/tmv/BasicBrowser/')
+os.environ.setdefault("DJANGO_SETTINGS_MODULE", "BasicBrowser.settings")
+django.setup()
+
+from tmv_app.models import *
+from scoping.models import *
+from tmv_app.tasks import *
+
+K = int(sys.argv[1])
+
+q = Query.objects.get(pk=2355)
+
+stat = RunStats(
+    query=q,
+    K=K,
+    min_freq=5,
+    method='NM',
+    citations=True,
+    max_iterations=500
+)
+
+stat.save()
+
+do_nmf(stat.pk)

### 2018-06-14 code/nmf.py

@@ -1,6 +1,5 @@
 import pickle, string, numpy, getopt, sys, random, time, re, pprint, gc, resource
 import pandas as pd
-import onlineldavb
 import scrapeWoS
 import gensim
 import nltk
@@ -134,7 +133,7 @@ def main():
     stoplist.add('copyright')
 
     #docs = Doc.objects.filter(query=893,content__iregex='\w').values('UT','title','content')
-    docs = Doc.objects.filter(query=365,content__iregex='\w') | Doc.objects.filter(query=354,content__iregex='\w')
+    docs = Doc.objects.filter(query=2355,content__iregex='\w') | Doc.objects.filter(query=354,content__iregex='\w')
     docs = docs#.values('UT','content')
     if limit is not False:
         docs = docs[:limit]

### 2018-06-14 code/nmf_multi.py

@@ -45,6 +45,8 @@ sys.stdout.flush()
 
 # import file for easy access to browser database
 sys.path.append('/home/galm/software/tmv/BasicBrowser/')
+os.environ.setdefault("DJANGO_SETTINGS_MODULE", "BasicBrowser.settings")
+django.setup()
 
 # sys.path.append('/home/max/Desktop/django/BasicBrowser/')
 import db as db

### 2018-06-15 main.tex

--- 2017-09-28 main.tex
@@
 \textbf{
-To contribute to evidence-based policies on tackling climate change, the IPCC aims to comprehensively assess the relevant scientific literature \citep{IPCC2013}.
-With the size of this literature currently almost two orders of magnitude larger than at the time of the IPCC's first assessment report, this task has become impossible without the aid of machine-reading.
-We collect over 400,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to give an overview of this unmanageably large corpus.
-This overview shows us the distribution and development of topics across the literature, and allows us to identify topics with greater and lesser representation in IPCC reports.
-%[We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of future IPCC assessments.]
+The massive expansion of scientific literature on climate change challenges the Intergovenmental Panel on Climate Change (IPCC)'s ability to assess the science according to its objectives. 
+Moreover, the number and variety of papers hinders researchers of the science-policy interface from making objective judgements about those IPCC's assessments.
+In this paper, we present a novel application of a machine-reading approach to model the topical content of papers on climate change.
+This dynamic topic model provides the basis for a \textit{topography} of climate change literature.
+The thematic development of the field is outlined and used to inform an analysis of the topics which are better and less well covered by IPCC reports.
 }
+
+The IPCC sees its role as to ``assess on a comprehensive, objective, open and transparent basis the scientific, technical and socio-economic information relevant to [...] climate change'' \citep{IPCC2013}.
+This role is vital....
+
+Various researchers have attempted to analyse the IPCC's assessment reports, criticised the assessment processes of the IPCC.
+ref ref ref.
+Further, it has been pointed out that, in the age of ``big literature'', providing assessments that are comprehensivene, objective and transparent has become much more difficult \citep{Minx2017l}.
+
+The scale of the challenge is depicted in figure \ref{growth}.
+Less than two thousand documents relevant to climate change were published before the first assessment report (see Methods for data, exclusions and processing).
+These documents contained 3,528 unique terms, each of which was used on average in 0.49\% of documents.
+In the three complete years since the publication of AR5, 128,357 documents have been published, containing 86,419 unique terms.
+To put this into context, the 1,189 chapters of the Bible contain a vocabulary of 11,977 unique words.
+Put another way, the 236,634 publications published in AR5 and AR6 are significantly larger than the 178,118 publications recorded in the first volume of the `Catalogue of Scientific Papers', compiled by the Royal Society to record the entirety of scientific output from 1800 to 1863 \citep{Csiszar2017}
 
@@
 	\begin{center}
-	\includegraphics[width=0.8\linewidth]{plots/wos_scopus_docs_time}
-    \caption{Growth in relevant literature in WoS and Scopus}
+		\includegraphics[width=0.7\linewidth]{plots/volume_variety}
+		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions.
+Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period.
+The proportion of documents the average word occurs in is given in the key.
+		}
 		\label{growth}
@@
 
-The size of the scientific literature on climate change has expanded rapidly over the lifetime of the IPCC.
-While the first assessment report had around 5,500 articles to assess, nearly 5,000 new articles are now published every month, bringing the total size of the literature to close to half a million papers, (Figure \ref{growth}).
-The increase in volume, velocity, and variety of content to be assessed has turned the task of the IPCC into a `Big Literature' challenge \citep{Minx2017BigChange}.
-To ask questions about the literature \textit{at scale}, we now need to apply computational techniques to the analysis of large document collections.
+Clearly, if the IPCC is to continue producing comprehensive assessments, it has to engage in machine-reading in order to remain anchored to the wider literature.
+Without such an approach, it becomes harder to justify which ever-diminishing proportion of the wider literature is included in assessments.
+Indeed this same approach is required if researchers are to make convincing claims about what areas of the literature are well-covered, and what are overlooked.
 
-Topic models are one such technique.
-A topic model learns the latent topics that structure a large corpus of documents, by leveraging the systematic co-occurrence of words across documents.
-Topics are distributions of words, and the topic mixture of each document explains the words observed in that document.
-This means that topic models can aid the understanding of large corpuses, and of the place of individual documents within them, by showing a document or corpus as a combination of 100 or so intelligible topics, rather than combinations of thousands of words.
-
-Assessment-makers like the IPCC have been described as cartographers for policymakers \citep{Edenhofer2015}.
-As such their purpose is, summarising available scientific knowledge, to describe the problem and solution space of a policy issue.
-The topic model presented here is a rough map of climate change research since 1985.
-It shows a broad outline of the topics that make up this research and how they relate to each other, and demonstrates how this has changed over time.
-Such a map sheds light on the terrain of knowledge about a policy issue, making an overview of an unmanageably large and diverse landscape possible.
-This overview allows both for the production of policy pathways that are well informed by science, and, as demonstrated in this paper, the assessment of the comprehensiveness with which these pathways reflect the landscape.
-
-While topic modelling has been employed to answer specific questions about small aspects of climate literature, e.g.
-\citep[e.g.][]{Minx2017FastEmissions, Grubert2016}, this is the first application of topic models to gain an overview of the entire field.
+This paper uses
 
@@
 
-\todo{From here on in, the paper is more of an outline, with a mixture of bullet points about results that exist or I would still like to generate}
-
 \begin{figure}
 \begin{center}
-	\includegraphics[width=0.8\linewidth]{plots/network_wg_65}
-    \caption{Topic structure of climate change literature}
-    \label{network}
+	%\includegraphics[width=0.7\linewidth]{}
+    \caption{}
+    \label{}
     \end{center}
@@
 
-\subsection*{Topic Model}
-\begin{itemize}
-	\item Figure \ref{network} shows the structure of the topic model with 100 topics, with each node coloured according to the IPCC working group in which the highest proportion of the topic's documents are cited.
-    \item Topics that systematically co-occur in documents are linked, and the resulting network is displayed with links weighted according to topic correlation score.
-The strength of links is greater where two topics are categorised as being in the same working group.
-This relationship is statistically significant (see SI)
-\end{itemize}
-
-\begin{figure}
-	\includegraphics[width=\linewidth]{plots/hot_topics_65}
-    \caption{Topic growth over time. The 3 topics in each assessment period that grew by the largest amount are labelled [Example figure]}
-    \label{topic_growth}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[width=\linewidth]{plots/ipcc_topics_65}
-    \caption{IPCC references by topic. The bars show the percentage of each topic that has been matched to an IPCC reference}
-    \label{IPCC}
-\end{figure}
-
-\begin{table}
-\small
-\setlength\tabcolsep{0.1cm}
-\begin{tabular}{cccccc}
-AR1 & AR2 & AR3 & AR4 & AR5 & AR6 \\
-\midrule \\
-\input{tables/topAR1} & \input{tables/topAR2}  & \input{tables/topAR3}
- & \input{tables/topAR4}  & \input{tables/topAR5}  & \input{tables/topAR6}
-\end{tabular}
-\caption{The top 5 topics in each assessment period by percentage growth since the last assessment period}
-\end{table}
-
-\begin{table}
-\small
-\setlength\tabcolsep{0.1cm}
-\begin{tabular}{cccccc}
-AR1 & AR2 & AR3 & AR4 & AR5 & AR6 \\
-\midrule \\
-\input{tables/bottomAR1} & \input{tables/bottomAR2}  & \input{tables/bottomAR3}
- & \input{tables/bottomAR4}  & \input{tables/bottomAR5}  & \input{tables/bottomAR6}
-\end{tabular}
-\caption{The bottom 5 topics in each assessment period by percentage growth since the last assessment period}
-\end{table}
-
-\begin{itemize}
-	\item Some big/interesting topics are x and y
-	\item These topics have grown at particularly interesting times (Figure \ref{topic_growth})
-    \item These topics are better covered in IPCC, these are less well covered \ref{IPCC}
-    \item Some interesting topic correlations are x and y; well fitting documents to both include x and y
-    \item
-\end{itemize}
-
-%\subsection*{Information Retrieval Implications}
-%\begin{itemize}
-%    \item X keywords fit into Y topics like so...
-%    \item Finding similar documents, how does this work with topics as opposed to keywords?
-%    \item Similar documents more or less likely to be across disciplinary boundaries ??
-%\end{itemize}
-
-\section*{Conclusion}
-\begin{itemize}
-	\item A very simple topic model provides an overview of the whole landscape.
-    \item This allows researchers / assessment makers to identify areas that have grown recently
-    \item Topic models aid document discovery, have the potential to contribute to more comprehensive assessments.
-	\item AR5 seemed to have less comprehensive coverage of x topics. This was a particular issue in WG y.
-	\item This may not be an issue, there could be good reasons for this, but these should be made transparent.
-	\item For the next assessment report, x topics may require particular attention.
-	\item The emerging topic on CCS resonates with a growing recognition of the importance of negative emissions and the lack of understanding about how they could fill their role.
-This will be of particular importance for the IPCC special report on 1.5 degrees.
-    %\item Next steps for research: using topic models to assess the assessment process: more thorough gapfinding etc.
-\end{itemize}
-
-\begin{figure}
-	%\includegraphics{}
-    \caption{Focus on [biochar?] showing document with highlighted words}
-\end{figure}
-
-\begin{figure}
-	%\includegraphics{}
-    \caption{Model validation graph, showing error for different topic numbers, feature numbers}
-\end{figure}
-
-\begin{figure}
-	%\includegraphics{}
-    \caption{Some relation of topics to other features of dataset: e.g. most interdisciplinary journals and least, or so...}
-\end{figure}
-
-\section*{Methodology}
-
-\begin{itemize}
-\item Topic modelling in general: reducing large matrix of documents to words to two smaller matrices of topics x words and topics x documents.
-\item Model selection: NMF \citep{Lee1999}
-\item How does it work?
-Advantages: Simple, scalable: better results than with other solutions%, if only because it was possible to iterate with large document collections.
-LDA can be better but relies on tuning hyperparameters, hard to do with such big corpus
-\item Topic model browser \citet{Chaney2012}
-\item Merging with IPCC citation dataset - caveats...
-\item Network explanation
-\item Regression of network score on dummy variable for same
-%\item Compare topic space to keyword space. Reduces dimensionality, overcomes non-standardisation
-%\item Which topics get the most citations?
-
-\end{itemize}
-
-\section{Data}
-\begin{itemize}
-	\item Queries: use \citet{Grieneisen2011}, or take the best bits of \citet{Grieneisen2011} and \citet{Haunschild2016}?
-    \item Sources: WoS, Scopus or both?
-    \item Preprocessing: Remove punctuation, numbers, common, uncommon words, stemming
-\end{itemize}
+\section*{Methods}
+\label{methods}
 
@@
 \bibliography{Mendeley.bib}
-\bibliographystyle{apalike}
+\bibliographystyle{unsrt}
 

### 2018-07-06 main.tex

@@
 \usepackage{lineno}
+\usepackage{color}
+\usepackage{auto-pst-pdf}
+\usepackage[colaction]{multicol}
+\usepackage{caption}
 
-\linespread{2}
+\linespread{1.5}
+
+\makeatletter
+\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
+	\begin{flushleft}
+
+		{\huge\textbf{\@title}}
+
+		\bigskip
+
+ 		{\large\textbf{\@author}}
+	\end{flushleft}\egroup
+}
+\makeatother
+
+\newcommand{\multicollinenumbers}{
+	\linenumbers
+	\def\makeLineNumber{\docolaction
+		{\makeLineNumberLeft}
+		{}
+		{\makeLineNumberRight}
+		}
+}
+
+\newenvironment{figurehere}
+	{\def\@captype{figure}}
+	{}
 
@@
 \title{A Topography of Climate Change Research}
-%\author{Max Callaghan}
+\author{Max Callaghan}
 
@@
 
-\linenumbers
+\begin{linenumbers}
 
-\textbf{
+\noindent\textbf{	
 The massive expansion of scientific literature on climate change challenges the Intergovenmental Panel on Climate Change (IPCC)'s ability to assess the science according to its objectives. 
-Moreover, the number and variety of papers hinders researchers of the science-policy interface from making objective judgements about those IPCC's assessments.
+Moreover, the number and variety of papers hinders researchers of the science-policy interface from making objective judgements about those IPCC assessments.
 In this paper, we present a novel application of a machine-reading approach to model the topical content of papers on climate change.
@@
 
+\end{linenumbers}
+
+\bigskip
+
+%\begin{multicols}{2}
+
+%\multicollinenumbers
+
 The IPCC sees its role as to ``assess on a comprehensive, objective, open and transparent basis the scientific, technical and socio-economic information relevant to [...] climate change'' \citep{IPCC2013}.
@@
 
-Various researchers have attempted to analyse the IPCC's assessment reports, criticised the assessment processes of the IPCC.
-ref ref ref.
+Various researchers have attempted to analyse the IPCC's assessment reports \citep{jabbour2017}, criticised the assessment processes of the IPCC.
+\citep{Bjurström2011} ref ref.
 Further, it has been pointed out that, in the age of ``big literature'', providing assessments that are comprehensivene, objective and transparent has become much more difficult \citep{Minx2017l}.
@@
 These documents contained 3,528 unique terms, each of which was used on average in 0.49\% of documents.
-In the three complete years since the publication of AR5, 128,357 documents have been published, containing 86,419 unique terms.
+In the three complete years since the publication of AR5, 128,357 documents have been published, containing 86,419 unique terms, used on average in 0.12\% of documents.
 To put this into context, the 1,189 chapters of the Bible contain a vocabulary of 11,977 unique words.
@@
 	\begin{center}
-		\includegraphics[width=0.7\linewidth]{plots/volume_variety}
+		\includegraphics[width=0.5\linewidth]{plots/volume_variety.png}
+		%\captionof{figure}
 		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions.
 Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period.
-The proportion of documents the average word occurs in is given in the key.
+The percentage of documents the average word occurs in is given in the key.
 		}
@@
 Without such an approach, it becomes harder to justify which ever-diminishing proportion of the wider literature is included in assessments.
-Indeed this same approach is required if researchers are to make convincing claims about what areas of the literature are well-covered, and what are overlooked.
 
-This paper uses
+Machine reading approaches can of course not replace the task of human assessment-making.
+The contribution that could be made, though, is to pre-process the literature, producing a topographical map, used to navigate the literature while producing a more detailed assessment with human judgement.[[]] In fact this happens already - when IPCC authors search for literature on a topic, the results which appear on the search engine they use will be subject to algorithms based on the processing of millions of records of article text and metadata.
+This can be done in a much more systematic way when scientists perform directed analyses of the literature at scale.
+
+Indeed, this same problem of scale makes attempts to criticise the IPCC as assessment-makers more difficult. These too can be strengthened by big literature approaches. + examples.
+%Indeed this same approach is required if researchers are to make convincing claims about what areas of the literature are well-covered, and what are overlooked.
+
+This study demonstrates how dynamic topic modelling can be used to gain an overview of an otherwise unmanageably large set of literature.
+This overview, or topography, describes the thematic development of the climate change literature and, in a novelly systematic way, examines how  comprehensively the IPCC has been able to engage with it.
 
@@
 \begin{center}
-	%\includegraphics[width=0.7\linewidth]{}
+	\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
     \caption{}
@@
 
+Increase in the frequency of the use of the term ``solutions'' \citep{jabbour2017},
+
 \section*{Methods}
 \label{methods}
+
+\subsection*{Data}
+This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of
+
+%\end{multicols}
 

### 2018-07-13 main.tex

@@
 
-\end{linenumbers}
-
 \bigskip
@@
 %\multicollinenumbers
+\bigskip
+\noindent\textbf{To deal with the wicked problem of climate change, international policy-makers need the IPCC. The IPCC makes maps.}
 
 The IPCC sees its role as to ``assess on a comprehensive, objective, open and transparent basis the scientific, technical and socio-economic information relevant to [...] climate change'' \citep{IPCC2013}.
-This role is vital....
+This role is vital for....
+Making maps \citep{Edenhofer2015}
 
-Various researchers have attempted to analyse the IPCC's assessment reports \citep{jabbour2017}, criticised the assessment processes of the IPCC.
-\citep{Bjurström2011} ref ref.
+\bigskip
+\noindent\textbf{The task of the IPCC has beome much more difficult with big literature}
+
 Further, it has been pointed out that, in the age of ``big literature'', providing assessments that are comprehensivene, objective and transparent has become much more difficult \citep{Minx2017l}. 
+Is the map up to date, does it cover everything?
+
+%%%%%
+
+\bigskip
+\noindent\textbf{The IPCC, its reports and processes have been the object of study before. These are also hampered problems of scale though}
+
+Various researchers have attempted to do empirical research on the assessment reports, and processes of the inter.
+alia.
+the IPCC \citep{jabbour2017} \citep{Bjurström2011}.
+Policy makers, when asked about their interactions with the IPCC call for a greater focus on solutions \citep{Kowarsch2017}
+
+\bigskip
+\noindent\textbf{Some literature exists on bibliometrics and climate change, but tends not to deal with text}
+
+Bibliometrics e.g. \citep{Haunschild2016} \citep{Grieneisen2011}
+
+Text based approaches are usually of a smaller scope \citep{Grubert2016} or methodological contributions \citep{Blei2003}
+
+\bigskip
+\noindent\textbf{The scale of the problem in context}
 
@@
 	\begin{center}
-		\includegraphics[width=0.5\linewidth]{plots/volume_variety.png}
+		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
 		%\captionof{figure}
@@
 Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period.
-The percentage of documents the average word occurs in is given in the key.
+The percentage of documents in which the average word occurs in is given in the key.
 		}
@@
 
+\bigskip
+\noindent\textbf{Machine reading to deal with scale problems in the making and assessing of maps}
+
 Clearly, if the IPCC is to continue producing comprehensive assessments, it has to engage in machine-reading in order to remain anchored to the wider literature.
 Without such an approach, it becomes harder to justify which ever-diminishing proportion of the wider literature is included in assessments.
+Similarly, it becomes harder to criticise, with quantitavely evidenced claims, the outcomes of assessment processes.
+
+\bigskip
+\noindent\textbf{Dimension reduction makes possible the description in reduced form, and with less human bias, unmanageably large datasets}
+
+\citep{Greene2016} \citep{Lee1999}
+
+This reduced form description makes comparisons more useful, when cutting the dataset.
+
+\bigskip
+\noindent\textbf{Machine reading is a supplement to assessment-making and not free from bias; a topography is not a map}
 
@@
 
-Indeed, this same problem of scale makes attempts to criticise the IPCC as assessment-makers more difficult. These too can be strengthened by big literature approaches. + examples.
-%Indeed this same approach is required if researchers are to make convincing claims about what areas of the literature are well-covered, and what are overlooked.
+\bigskip
+\noindent\textbf{This study's contribution. Overarching themes, structure of the literature, development, relation to IPCC}
 
@@
 This overview, or topography, describes the thematic development of the climate change literature and, in a novelly systematic way, examines how  comprehensively the IPCC has been able to engage with it.
+In pulling together strands from text-mining, bibliometrics, and the study of science and policy, this study advances our understanding of the literature on climate change and the role of the IPCC in communicating this to policy makers.
 
@@
 	\begin{center}
-	\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
+		\includegraphics[width=1\linewidth]{plots/network_development_wgs_665.pdf}
+		\caption{The development of the topic-document correlation network over IPCC assessment periods.}
+		\label{}
+	\end{center}
+\end{figure}
+
+\bigskip
+\noindent\textbf{The topic-document correlation network is densest in AR2 and 3 but becomes more fragmented over time}
+
+(partly: Model less good at describing literature later on)
+
+\bigskip
+\noindent\textbf{Working groups are clustered together [dynamics], with topics like [x] containing documents across working groups and topics like [y] important network nodes}
+
+\bigskip
+\noindent\textbf{Sustainability has been an increasingly important theme in an overarching topic about environmental sciences}
+
+(compare to biochar, which is much more recent)
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=1\linewidth]{plots/single_topic_3_11046.pdf}
 		\caption{}
@@
 
-Increase in the frequency of the use of the term ``solutions'' \citep{jabbour2017},
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=1\linewidth]{plots/single_topic_3_11020.pdf}
+		\caption{SI}
+		\label{}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+	\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
+    \caption{SI}
+    \label{}
+    \end{center}
+\end{figure}
+
+\bigskip
+\noindent\textbf{Physical science topics tend to be the oldest, and the most well represented topics}
+
+\bigskip
+\noindent\textbf{Adaptation and impact studies have seen a lot of growth but are well represented in IPCC reports}
+
+\bigskip
+\noindent\textbf{New topics around negative emissions and urban form are very recent and not well represented in IPCC reports.}
+
+Negative emissions in special report on 1.5, demand side chapter in AR6
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=1\linewidth]{plots/ipcc_representation/ipcc_rep_new665_all.pdf}
+		\caption{}
+		\label{}
+	\end{center}
+\end{figure}
+
+\section*{Discussion}
+
+\bigskip
+\noindent\textbf{Solutions, policies and science}
+
+%Increase in the frequency of the use of the term ``solutions'' \citep{jabbour2017},
 
@@
 \subsection*{Data}
-This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of
+%This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of
+
+\end{linenumbers}
 

### 2018-07-16 main.tex
draft for EASST

@@
 \usepackage{caption}
+\usepackage{svg}
 
@@
 \bigskip
-\noindent\textbf{To deal with the wicked problem of climate change, international policy-makers need the IPCC. The IPCC makes maps.}
+\noindent\textbf{To deal with the wicked problem of climate change, international policy-makers need the IPCC. The IPCC as map-makers.}
 
 The IPCC sees its role as to ``assess on a comprehensive, objective, open and transparent basis the scientific, technical and socio-economic information relevant to [...] climate change'' \citep{IPCC2013}.
-This role is vital for....
+Climate science is so broad, multi-disciplinary, and laden with uncertainties and values, that the role of the IPCC as assessment maker is vitally important to developing evidence-based international climate policy.
 Making maps \citep{Edenhofer2015}
@@
 \bigskip
-\noindent\textbf{The task of the IPCC has beome much more difficult with big literature}
+\noindent\textbf{The task of the IPCC has become much more difficult with big literature}
 
-Further, it has been pointed out that, in the age of ``big literature'', providing assessments that are comprehensivene, objective and transparent has become much more difficult \citep{Minx2017l}. 
-Is the map up to date, does it cover everything?
+Further, it has been pointed out that, in the age of ``big literature'', providing assessments that are comprehensive, objective and transparent has become much more difficult \citep{Minx2017l}.
+
+When IPCC's citations constitute an ever-decreasing proportion of the totality of science on climate change, questions about the map that the IPCC reports produce become more pressing:
+
+- Is the map up to date? Is it complete? Is the perspective representative?
 
@@
 \bigskip
-\noindent\textbf{The IPCC, its reports and processes have been the object of study before. These are also hampered problems of scale though}
+\noindent\textbf{The IPCC, its reports and processes have been the object of study before. These are also hampered by problems of scale though}
 
-Various researchers have attempted to do empirical research on the assessment reports, and processes of the inter.
-alia.
-the IPCC \citep{jabbour2017} \citep{Bjurström2011}.
+Various researchers have attempted to do empirical research on the assessment reports, and processes of inter. alia. the IPCC \citep{jabbour2017} \citep{Bjurström2011} \citep{Hulme2016}.
+
 Policy makers, when asked about their interactions with the IPCC call for a greater focus on solutions \citep{Kowarsch2017}
+
+These studies are similarly challenged by the the size of the literature. Traditional bibliometric techniques are insufficient.
 
@@
 Without such an approach, it becomes harder to justify which ever-diminishing proportion of the wider literature is included in assessments.
-Similarly, it becomes harder to criticise, with quantitavely evidenced claims, the outcomes of assessment processes.
+Similarly, it becomes harder to criticise, with quantitatively evidenced claims, the outcomes of assessment processes.
 
 \bigskip
-\noindent\textbf{Dimension reduction makes possible the description in reduced form, and with less human bias, unmanageably large datasets}
+\noindent\textbf{Dimension reduction makes possible the description in reduced form, and with less human bias, of unmanageably large datasets}
 
@@
 
-This study demonstrates how dynamic topic modelling can be used to gain an overview of an otherwise unmanageably large set of literature.
+This study demonstrates how dynamic topic modelling can be used to gain an overview of an otherwise unmanageably large body of literature.
 This overview, or topography, describes the thematic development of the climate change literature and, in a novelly systematic way, examines how  comprehensively the IPCC has been able to engage with it.
@@
 \section*{Results}
+
+\bigskip
+\noindent\textbf{A topographical map of climate change documents shows the broad structure of climate change literature}
+
+Topics cut across both disciplinary, and working group lines - but disciplinary and working group structure remains visible in the map.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=1\linewidth]{plots/tsne.png}
+		\caption{A map of a sample of 10,000 documents about climate change. Document positions are obtained by reducing the topic scores to two dimensions via t-SNE}
+		\label{}
+	\end{center}
+\end{figure}
 
@@
 
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=1\linewidth]{plots/ipcc_representation/ipcc_rep_new665_all.pdf}
+		\caption{Representation and newness of dynamic topics}
+		\label{}
+	\end{center}
+\end{figure}
+
 \bigskip
@@
 		\includegraphics[width=1\linewidth]{plots/single_topic_3_11046.pdf}
-		\caption{}
+		\caption{Word and document development of the ``Research'' dynamic topic}
 		\label{}
@@
 		\includegraphics[width=1\linewidth]{plots/single_topic_3_11020.pdf}
-		\caption{SI}
+		\caption{SI Word and document development of the ``Biochar'' dynamic topic}
 		\label{}
@@
 	\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
-    \caption{SI}
+    \caption{SI Topic make up of a single document}
     \label{}
@@
 
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/ipcc_representation/ipcc_rep_new665_all.pdf}
-		\caption{}
-		\label{}
-	\end{center}
-\end{figure}
-
 \section*{Discussion}
@@
 \noindent\textbf{Solutions, policies and science}
+
+What do policy-makers mean when they ask for more solutions
+
+\bigskip
+\noindent\textbf{Perfect representation is not necessarily desirable, but the skewedness should be known}
+
+There may be good reasons for a topic to be less prominent in IPCC discussions than in the wider scientific literature, and these reasons can only be understood and acted upon by humans, not by machine-reading.
+Nevertheless, it is desirable that assessment makers are aware of the relationship
 

### 2018-07-23 code/tsne_runs.py
tsne runs and first big graphs

@@ -1,0 +1,142 @@
+import matplotlib
+matplotlib.use('agg')
+
+import django, sys, os, random
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+from pathlib import Path
+
+matplotlib.rcParams["figure.figsize"] = [7.2,4.5]
+matplotlib.rcParams['axes.labelsize'] = 7
+matplotlib.rcParams['xtick.labelsize'] = 5
+matplotlib.rcParams['ytick.labelsize'] = 5
+
+sys.path.append('/home/galm/software/django/tmv/BasicBrowser/')
+os.environ.setdefault("DJANGO_SETTINGS_MODULE", "BasicBrowser.settings")
+django.setup()
+from django.db.models import Q, F, Sum, Count, FloatField, Case, When, Value, Max
+from scipy.sparse import coo_matrix, find
+from sklearn.manifold import TSNE
+
+from scoping.models import *
+from tmv_app.models import *
+from scipy.sparse import csr_matrix
+from time import time
+from MulticoreTSNE import MulticoreTSNE as mTSNE
+
+
+
+run_id = 662
+
+def get_matrix(run_id,s_size):
+    stat = RunStats.objects.get(pk=run_id)
+    if stat.method=="DT":
+        dts = DocDynamicTopic.objects
+    else:
+        dts = DocTopic.objects
+
+    db_matrix = dts.filter(run_id=run_id,score__gt=0.01)
+    docs = set(db_matrix.values_list('doc__id',flat=True))
+    if s_size ==0:
+        s_docs = docs
+    else:
+        s_docs = random.sample(docs,s_size)
+
+    db_matrix = dts.filter(
+        run_id=run_id,
+        score__gt=0.01,
+        doc__id__in=s_docs
+    )
+
+    vs = list(db_matrix.values('score','doc_id','topic_id'))
+
+    c_ind = np.array(list(set(db_matrix.values_list('topic_id',flat=True).order_by('doc_id'))))
+    r_ind = np.array(list(set(db_matrix.values_list('doc_id',flat=True).order_by('doc_id'))))
+
+    d = [x['score'] for x in vs]
+    c = [int(np.where(c_ind==x['topic_id'])[0]) for x in vs]
+    r = [int(np.where(r_ind==x['doc_id'])[0]) for x in vs]
+
+    m = csr_matrix((d,(r,c)),shape=(len(r_ind),len(c_ind)))
+
[…]

### 2018-07-23 pres/CC_Topography_EASST_Callaghan.tex
EASST pres

--- 2018-02-12 pres/2018_02_pres.tex
@@
 
-\usepackage[T1]{fontenc}
+%\usepackage[LGR,T1]{fontenc}
+%\usepackage[Latin, Greek]{ucharclasses}
+\usepackage[utf8]{inputenc} 
 \usepackage{color}
@@
 \usepackage{framed}
+\usepackage{polyglossia}
+\usepackage{textgreek}
+\usepackage{appendixnumberbeamer}
 
@@
 
-\definecolor{rd}{HTML}{2F2A40}
-\definecolor{methods}{HTML}{C6C6C6}
-\definecolor{research}{HTML}{8F84BE}
-\definecolor{skills}{HTML}{7A7A7A}
-\definecolor{rc}{HTML}{AC152A}
+\newcommand{\backupbegin}{
+	\newcounter{finalframe}
+	\setcounter{finalframe}{\value{framenumber}}
+}
+\newcommand{\backupend}{
+	\setcounter{framenumber}{\value{finalframe}}
+}
+
+%\newcommand{\textgreek}[1]{\begingroup\fontencoding{LGR}\selectfont#1\endgroup}
 
@@
 
+\begin{frame}{Introduction}
+\begin{columns}
+	\begin{column}{0.6\linewidth}
+		\begin{center}
+			\begin{figure}
+				\includegraphics[width=1\linewidth]{../plots/Hondius_Portrait_of_map-makers}
+				\caption{Portrait of map-makers, Gerard Mercator and Jodocus Hondius (Jodocus Hondius) source: \url{https://commons.wikimedia.org/wiki/File:Hondius_Portrait_of_map-makers.jpg}}
+			\end{figure}
+		\end{center}
+	\end{column}
+	\begin{column}{0.4\linewidth}
+		\begin{center}
+			\begin{itemize}
+				\item<2-> Topography is a description of a landscape
+				\item<3-> Topics (from the Greek \texttau\textomikron\textpi\textomikron\textvarsigma, place) can describe the features of body of text
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+\end{frame}
+
 \begin{frame}{Context}
@@
 			\begin{itemize}
-			\item To contribute evidence-based policy-making on climate change, the IPCC aims to \textit{comprehensively} assess  
+				\item To contribute evidence-based policy-making on climate change, the IPCC aims to \textit{comprehensively} assess scientific literature on climate change 
 				\item These assessments should be aim to balance legitimacy, credibility and relevance \citep{Cash2001}
@@
 
-\begin{frame}{Motivation}
+\begin{frame}{Motivation - Big Literature}
 
@@
 					\item Comprehensive, credible and relevant assessments become
-				more challenging as the literature grows
+					more challenging as the literature grows \citep{Minx2017l}
 				\end{itemize}
@@
 			\citep{Lee1999}
-				\item Topics describe the latent structure of the document corpus
+			\item Topics describe the latent structure of the document corpus (What is the matter?)
 
@@
 \begin{enumerate}
-	\item Download documents from Web of Science (WoS)
-	\item Match documents to reference lists from IPCC reports
-	\item Topic model stemmed document abstracts
+\item<4-> Download documents from Web of Science (WoS)
+\item<5-> Match documents to reference lists from IPCC reports
+\item<6-> Topic model stemmed document abstracts
 \end{enumerate}
@@
 \begin{itemize}
-			\item Not perfect query
+\item Not perfect query (Expressio Unius Est Exclusio Alterius )
 \item WoS not all peer-reviewed literature
@@
 \item Check for case-insensitive title matches
-		\item Calculate the Jaccard similarity score for two word every database document containing the first word and from the same year. Match if the Jaccard score is above 0.45
+\item Calculate the Jaccard similarity score for two word shingles every database document containing the first word and from the same year. Match if the Jaccard score is above 0.45
 \end{itemize}
@@
 \end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% results
+
+\begin{frame}{Results}
+
+\begin{columns}
+	\begin{column}{0.5\linewidth}
+		\begin{center}	
+			\includegraphics[width=\linewidth]{../plots/pca_map_portrait}
+		\end{center}
+	\end{column}
+	\begin{column}{0.5\linewidth}
+		\textbf{Outline}	
+		\begin{center}
+			\begin{itemize}
+				\item<2-> Topography
+				\item<3-> Structure
+				\item<4-> Development
+				\item<5-> Representation in past IPCC reports
+				\item<6-> AR6 outlook
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Bib
+
+\begin{frame}{Bibliography}
+\small
+\bibliography{../Mendeley.bib}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Extra slides
+
+\appendix
+\backupbegin
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% results
-
-%\begin{frame}{Preliminary results - explanation}
-%
-%\begin{columns}
-%	\begin{column}{0.5\linewidth}
-%		\begin{center}
-%			\includegraphics[width=\linewidth]{../plots/biomass_eg.png}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.5\linewidth}
-%		\begin{center}
-%			\begin{itemize}
-%				\item Documents are mixtures of topics, based on the words which occur in them
-%			\end{itemize}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-
-%\begin{frame}{Preliminary results - Map}
-%
-%\begin{figure}
-%			\includegraphics[width=\linewidth]{../plots/pca_map.png}
-%			\caption{Topic Map, with topics placed according to Principal Component Analysis of topic-term matrix}
-%\end{figure}
-%
-%\end{frame}
-
-\begin{frame}{Preliminary results - structure}
-
-\begin{columns}
-	\begin{column}{0.65\linewidth}
-		\begin{center}	
-			\vspace*{-0.1\linewidth}
-			\includegraphics[width=\linewidth]{../plots/network_wg_654}
-		\end{center}
-	\end{column}
-	\begin{column}{0.35\linewidth}
-	%	\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
-		\begin{center}
-			\begin{itemize}
-				\item A network of comprehensible topics is generated with 100 topics
-				\item Topics can be matched to the IPCC working group from which the majority of the topic documents are referenced in
-				\item Topics from the same working group are \textbf{significantly} more likely to be correlated with each other than those which are not
-			\end{itemize}
-		\end{center}
-	\end{column}
-\end{columns}
-
-\end{frame}
-
-\begin{frame}{Preliminary results - Inter-working Group topics - WG 1 and 3}
-
-	\begin{table}
-
-		\input{../tables/654_wg_1_2}
-
-	\end{table}
-
-\end{frame}
-
-%%%%%%%%
-
-\begin{frame}{Preliminary results - Inter-working Group topics - WG 1 and 3}
-
-	\begin{table}
-
-		\input{../tables/654_wg_1_3}
-
-	\end{table}
-
-\end{frame}
-
-%%%%%%%
-
-\begin{frame}{Preliminary results - Inter-working Group topics - WG 2 and 3}
-
-	\begin{table}
-
-		\input{../tables/654_wg_2_3}
-
-	\end{table}
-
-\end{frame}
-
-%\begin{frame}{Preliminary results - structure - WGI}
-%
-%\begin{columns}
-%	\begin{column}{0.65\linewidth}
-%		\begin{center}
-%			\vspace*{-0.1\linewidth}
-%%			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_1.PNG}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.35\linewidth}
-%%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key.PNG}
-%		\begin{center}
-%			\begin{itemize}
-%				\item The largest topic in WGI is on models.
-%			\end{itemize}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-%
-%\begin{frame}{Preliminary results - structure - WGII}
-%
-%\begin{columns}
-%	\begin{column}{0.65\linewidth}
-%		\begin{center}
-%			\vspace*{-0.1\linewidth}
-%			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_2}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.35\linewidth}
-%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
-%		\begin{center}
-%			\begin{itemize}
-%				\item The largest primarily WGII topic is on climate change impacts
-%			\end{itemize}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-%
-%\begin{frame}{Preliminary results - structure - WGIII}
-%
-%\begin{columns}
-%	\begin{column}{0.65\linewidth}
-%		\begin{center}
-%			\vspace*{-0.1\linewidth}
-%			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_3}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.35\linewidth}
-%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
-%		\begin{center}
-%			\begin{itemize}
-%				\item The largest WGIII topic is on emissions reductions.
-%			\end{itemize}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-%
-%\begin{frame}{Preliminary results - structure - other clusters}
-%
-%\begin{columns}
-%	\begin{column}{0.65\linewidth}
-%		\begin{center}
-%			\vspace*{-0.1\linewidth}
-%			\hspace*{-0.1\linewidth}
-%			\includegraphics[width=1.25\linewidth]{../plots/network_wg_372_4}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.35\linewidth}
-%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
-%		\begin{center}
-%			\begin{itemize}
-%				\item A fourth cluster of mostly WGII references contains topics on ecosystems, species and habitats
-%			\end{itemize}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-
-%\begin{frame}{Preliminary results - structure - Sustainability}
-%
-%
-%
-%\begin{columns}
-%	\begin{column}{0.6\linewidth}
-%		\begin{center}			
-%			\includegraphics[width=\linewidth]{../plots/sustainability}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.4\linewidth}
-%		\begin{center}
-%			\begin{itemize}
-%				\item In later assessment periods, a large meta-topic on research priorities and sustainability emerges
-%			\end{itemize}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-%
-%\begin{frame}{Preliminary results - structure - Sustainability}
-%
-%
-%
-%\begin{columns}
-%	\begin{column}{0.6\linewidth}
-%		\begin{center}			
-%			\includegraphics[width=\linewidth]{../plots/health_sustain_386}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.4\linewidth}
-%		\begin{center}
-%			\begin{itemize}
-%				\item The flatness of its distribution across documents indicates a topic that occurs
-%			\end{itemize}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-%
-%%% Sus table
-%
-%\begin{frame}{Preliminary results - structure - Sustainability}
-%\begin{table}
-%	\footnotesize
-%	\renewcommand{\arraystretch}{2}
-%\begin{tabular}{p{0.3\linewidth}p{0.3\linewidth}p{0.3\linewidth}}
-%	\toprule 
-%	{polici, govern, tax} & {adapt, vulner, strategi}  & {urban, citi, area} \\ 
-%	\midrule 
-%	How Research-Prioritization Exercises Affect Conservation Policy & Methodological choices in solution-oriented adaptation research: a diagnostic framework & A review of urban ecosystem services: six key challenges for future research  \\
-%	Role of hydrology and economics in water management policy under increasing uncertainty & When not every response to climate change is a good one: Identifying principles for sustainable adaptation & Lines of Tradition and Recent Approaches to Urban Ecology, Focussing on Germany and the USA \\
-%	Informing food policy: balancing the evidence & Informed adaptation: Ethical considerations for adaptation researchers and decision-makers & Advancing understanding of the complex nature of urban systems \\
-%	The identification of priority policy options for UK nature conservation & Future oriented conservation: knowledge governance, uncertainty and learning & Sustainable urban landscapes: South African perspectives on transdisciplinary possibilities \\
-%	Environmental education policy research challenges and ways research might cope with them & Towards an integrated agenda for adaptation research: theory, practice and policy & A conceptual framework for addressing complexity and unfolding transition dynamics when developing sustainable adaptation strategies in urban water management \\
-%	\bottomrule
-%\end{tabular} 
-%
-%\end{table}
-%
-%\end{frame}
-
-%\begin{frame}{Preliminary results - growth}
-%
-%\begin{columns}
-%	\begin{column}{0.6\linewidth}
-%		\begin{center}
-%			\includegraphics[width=\linewidth]{../plots/top_20_386}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.4\linewidth}
-%		\begin{center}
-%			\begin{itemize}
-%				\item Negative emissions related topics have shown strong growth since the end of AR5
-%				\item As have topics on cities and extreme weather events
-%			\end{itemize}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-
-%\begin{frame}{Preliminary results - growth - biochar}
-%
-%
-%		\begin{center}
-%			\includegraphics[width=\linewidth]{../plots/biochar_growth.png}
-%
-%		\medskip
-%
-%			\begin{itemize}
-%				\item Biochar has emerged as an entirely new topic in the last 10 years
-%			\end{itemize}
-%		\end{center}
-%
-%\end{frame}
-
-\begin{frame}{Preliminary results - gaps in coverage}
-
-How can we get a sense of which topics are better covered in IPCC reports?
-
-\begin{itemize}
-	\item Each document \(d\) either matches or does not match an IPCC reference
-	\item For each topic \(h\), we can sum the scores for each category of document
-	\item The ``IPCC proportion'' of each topic is the proportion of the sum of the document score accounted for by documents which match IPCC references.
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Preliminary results - gaps in coverage}
-
-\begin{columns}
-	\begin{column}{0.7\linewidth}
-		\begin{center}
-			\includegraphics[width=\linewidth]{../plots/ipcc_topics_654.png}
-		\end{center}
-	\end{column}
-	\begin{column}{0.3\linewidth}
-		\begin{center}
-			\begin{itemize}
-				\item The physical science aspects of climate change, as well topics on impacts, adaptation and scenarios are well covered by the IPCC
-				\item Topics on specific technological solutions (particularly NETs), as well as soils, are less well covered
-			\end{itemize}
-		\end{center}
-	\end{column}
-\end{columns}
-
-\end{frame}
-
-\begin{frame}{Preliminary results - gaps in coverage}
-
-			\includegraphics[width=0.8\linewidth]{../plots/ipcc_topics_wg_654.png}
-
-\end{frame}
-
-\begin{frame}{Preliminary results - gaps in coverage}
-
-	\includegraphics[width=0.8\linewidth]{../plots/ipcc_coverage_by_wg_654.png}
-
-\end{frame}
-
-\begin{frame}{Next steps}
-	\begin{itemize}
-		\item Adjusting second stage of model to give more weight to topics with many documents (to better capture emergence)
-		\item Further analysis of new model
-		\item (Manual) comparison of (AR6) topics with AR6 outline
-	\end{itemize}
-\end{frame}
-
-%\begin{frame}{Conclusions}
-%
-%
-%\begin{itemize}
-%	\item Endogenously discovered topics make substantive sense of an unmanageable dataset of climate-relevant literature
-%	\item Topic modelling discovers over-arching topics such as that on sustainability and research priorities, as well as individual, fast growing topics such as biochar or CCS
-%	\item Matching documents to IPCC references, we can describe topics that belong to or bridge IPCC working groups
-%	\item Quantitative evidence is found to support policy makers' dissatisfaction with a lack of `solution orientation' in IPCC reports \citep{Kowarsch2017} 
-%	\item By uncovering the structure at scale of a large collection of documents, and by enabling the discovery of documents relevant to specific topics or combinations of topics, this approach can provide for more comprehensive and salient scientific assessments.
-%\end{itemize}
-%
-%\end{frame}
-
-%\begin{frame}{Extra results - Journals}
-%
-%\begin{columns}
-%	\begin{column}{0.55\linewidth}
-%		\begin{center}
-%			\includegraphics[width=\linewidth]{../plots/journals/journal_papers.png}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.45\linewidth}
-%		\begin{center}
-%			\begin{itemize}
-%				\item Nature has been publishing about climate change for a long time
-%				\item Plos One has very recently overtaken all other journals
-%				\item The number of journals has risen very steeply
-%			\end{itemize}
-%		\includegraphics[width=0.9\linewidth]{../plots/journals/n_journals.png}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-
-%\begin{frame}{Extra results - Journals}
-
-%\begin{columns}
-%	\begin{column}{0.55\linewidth}
-%		\begin{center}
-%			\includegraphics[width=\linewidth]{../plots/journals/journal_entropy_386.png}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.45\linewidth}
-%		\begin{center}
-%			\begin{itemize}
-%				\item Journal Entropy describes the distribution of topics in a journal \citep{Hall2008a}
-%				\item High values mean the journal deals with a wider range of topics
-%			\end{itemize}
-%			\[  H(z\rvert c,y) = -\sum_{i=1}^{K} \hat{p}(z_i \rvert c,y) \; log \; \hat{p}(z_i \rvert c, y) \]
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-
-%\begin{frame}{Extra results - Journals}
-%
-%	\includegraphics[width=\linewidth]{../plots/journals/journal_topics_386.png}
-%
-%\end{frame}
-
-%\begin{frame}{Outlook}
-%
-%\begin{figure}
-%
-%\tiny
-%
-%\begin{ganttchart}[
-%	y unit title=0.3cm,
-%	y unit chart=0.5cm,
-%	x unit= 0.2cm,
-%	vgrid,hgrid,
-%	vgrid={{dotted,dotted,black}},
-%	title height=1,
-%	%     title/.style={fill=none},
-%	title label font=\bfseries\scriptsize,
-%	%bar/.style={fill=blue},
-%	bar height=0.7,
-%	bar label font=\tiny,
-%	%   progress label text={},
-%	group right shift=0,
-%	group top shift=0.7,
-%	group height=.3,
-%	group peaks width={0.2},
-%	inline]{1}{42}
-%	\gantttitle{2017}{9}
-%	\gantttitle{2018}{12}
-%	\gantttitle{2019}{12}
-%	\gantttitle{2020}{9} \\
-%	\gantttitlelist{2,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,4}{3} \gantttitlelist{1,...,3}{3} \\
-%	\gantttitlelist{4,...,12}{1} \gantttitlelist{1,...,12}{1}
-%	%\gantttitlelist{J,F,M,A,M,J,J,A,S,O,N,D}{1}
-%	\gantttitlelist{1,...,12}{1} \gantttitlelist{1,...,9}{1}\\
-%	
-%	% HERTIE
-%	\ganttgroup[inline=false]{Hertie Courses}{6}{42} \\
-%	
-%	\ganttbar[inline=false, bar/.append style={fill=rd}]{Research Design}{6}{15} \\
-%	\ganttbar[inline=false, bar/.append style={fill=methods}]{Methods}{6}{15} \\
-%	\ganttbar[inline=false, bar/.append style={fill=skills}]{Skills}{6}{15} \\
-%	\ganttbar[inline=false, bar/.append style={fill=rc}]{Research Colloquium}{19}{42} \\
-%	
-%	% HERTIE
-%	\ganttgroup[inline=false]{Thesis Research}{1}{42} \\
-%	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Map}{1}{5} \\
-%	\ganttbar[inline=false, bar/.append style={fill=research}]{Pyramid}{6}{15} \\
-%	
-%	
-%	\ganttbar[inline=false, bar/.append style={fill=research}]{Knowledge Accumulation}{16}{27} \\
-%	
-%	\ganttbar[inline=false, bar/.append style={fill=research}]{Evidence in Policy}{19}{27} \\
-%	
-%	\ganttbar[inline=false, bar/.append style={fill=research}]{Envelope}{28}{33} \\
-%	
-%	\ganttbar[inline=false, bar/.append style={fill=research}]{Revisions/Contingency}{34}{42} \\
-%	
-%	%\ganttlinkedbar[inline=false]{Task 2}{3}{7} \ganttnewline
-%	%\ganttmilestone[inline=false]{Milestone}{7} \ganttnewline
-%	
-%	
-%	
-%\end{ganttchart} 
-%
-%\end{figure}
-%
-%\end{frame}
-
-\begin{frame}{Frame Title}
-	\small
-	\bibliography{../Mendeley.bib}
-\end{frame}
+\backupend
 

### 2018-07-25 pres/CC_Topography_EASST_Callaghan.tex
update pres

@@
 \begin{framed}
-What can this modelled thematic structure tell us about the past and future relationship between the IPCC and scientific literature on climate change? 
+What can this modelled thematic structure tell us about the relationship between the IPCC and scientific literature on climate change? How do the maps relate to the mapped?
 \end{framed}
@@
 \begin{columns}
-	\begin{column}{0.5\linewidth}
-		\begin{center}	
-			\includegraphics[width=\linewidth]{../plots/pca_map_portrait}
-		\end{center}
+	\begin{column}{0.75\linewidth}
+		\begin{figure}	
+			\includegraphics[width=\linewidth]{../tsne_results/plots/run_662_s_100000_p30_blank}
+			\caption{A topographical representation of 100,000 documents on climate change}
+		\end{figure}
 	\end{column}
-	\begin{column}{0.5\linewidth}
+	\begin{column}{0.25\linewidth}
 		\textbf{Outline}	
@@
 				\item<2-> Topography
-				\item<3-> Structure
 				\item<4-> Development
-				\item<5-> Representation in past IPCC reports
-				\item<6-> AR6 outlook
+				\item<5-> Representation in IPCC reports
+				%\item<6-> AR6 outlook
 			\end{itemize}
@@
 \end{columns}
+
+\end{frame}
+
+\begin{frame}{Results - Topography}
+
+\begin{columns}
+	\begin{column}{0.7\linewidth}
+		\begin{figure}	
+			\includegraphics[width=\linewidth]{../tsne_results/plots/run_662_s_100000_p30_oecds}
+			\caption{A topographical representation of 100,000 documents on climate change. Document positions are dictated by topic scores, reduced to two dimensions through t-SNE}
+		\end{figure}
+	\end{column}
+	\begin{column}{0.3\linewidth}	
+		\begin{center}
+			\begin{itemize}
+				\item<2-> t-distributed stochastic neighbour embedding (t-SNE) \citep{vandermaaten2008} places nodes with similar topic scores close together
+				\item<3-> This \textit{projects} the 100-dimensional topic scores onto a conventional 2-dimensional topographical map
+				\item<4-> Topics cut across journal disciplinary categories, but the disciplinary structure remains visible
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Results - Topography}
+
+\begin{columns}
+	\begin{column}{0.7\linewidth}
+		\begin{figure}	
+			\includegraphics[width=\linewidth]{../tsne_results/plots/run_662_s_100000_p30_wgs}
+			\caption{A topographical representation of 100,000 documents on climate change.
+Document positions are dictated by topic scores, reduced to two dimensions through t-SNE, nodes are coloured by references by IPCC reports}
+		\end{figure}
+	\end{column}
+	\begin{column}{0.3\linewidth}	
+		\begin{center}
+			\begin{itemize}
+				\item<1-> The disciplinary structure fits with the pattern of citations by IPCC reports
+				\item<2-> Citations by IPCC reports are densest in WGI/Natural science topical areas.
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Results - IPCC Representation}
+
+\begin{columns}
+	\begin{column}{0.65\linewidth}
+		\begin{figure}	
+			\includegraphics[width=\linewidth]{../tsne_results/plots/run_662_s_100000_p30_clusters_wgs.png}
+			\caption{Clusters of documents}
+		\end{figure}
+	\end{column}
+	\begin{column}{0.35\linewidth}	
+		\begin{center}
+			\begin{itemize}
+				\item<1-> We can identify clusters of documents, each of which are dominated by topics or clusters of topics
+				\item<2-> 58 is a mixture of economics, policies and taxes, and emissions reductions
+				\item<3-> 41 is on CO2 storage
+				\item<4-> 11 is on species and habitats
+				\item<5-> 33 is on forests
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Results - Topography}
+
+	\begin{figure}	
+		\includegraphics[width=\linewidth]{../plots/single_doc_3_536594.pdf}
+		\caption{How topics describe documents}
+	\end{figure}
+
+\end{frame}
+
+\begin{frame}{Results - Development}
+
+\begin{figure}	
+	\includegraphics[width=\linewidth]{../plots/single_topic_3_11046.pdf}
+	\caption{The evolution of topics}
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Results - Development}
+
+\begin{figure}	
+	\includegraphics[width=\linewidth]{../plots/single_topic_3_11020.pdf}
+	\caption{The emergence of new topics}
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Results - Development}
+
+\begin{figure}	
+	\includegraphics[width=\linewidth]{../plots/ar5_growth_665.png}
+	\caption{The emergence of new topics}
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Results - IPCC representation}
+
+\begin{itemize}
+	\item<1-> How can we get a sense of which topics are better covered in IPCC reports?
+	\item<2-> We get a measure of proportionality between two distributions by dividing each topic's share in the IPCC sample by its share in the whole corpus
+	\item<3-> This and other measures come from literature on the proportionality of electoral systems \citep[e.g][]{Karpov2008}
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Results - IPCC Representation}
+
+\begin{columns}
+	\begin{column}{0.65\linewidth}
+		\begin{figure}	
+			\includegraphics[width=\linewidth]{../plots/ipcc_representation/ipcc_rep_new665_all.pdf}
+			\caption{New and old, better and less well represented topics}
+		\end{figure}
+	\end{column}
+	\begin{column}{0.35\linewidth}	
+		\begin{center}
+			\begin{itemize}
+				\item<1-> Topics on the scientific basis of climate change are well represented in IPCC reports and have been around longer than average
+				\item<2->Topics on impacts have seen lots of recent growth, and are well represented in IPCC reports
+				\item<3->Topics on ``solutions'', or on new technologies or contexts for mitigation have seen lots of recent growth, but are under-represented in IPCC reports
+			\end{itemize}
+		\end{center}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Robustness}
+
+Most work focuses on the measuring the sensitivity of the reconstruction error to different framings and parameters of the model.
+What we are more interested in is checking if the key messages are sound.
+
+\begin{columns}<2->
+	\begin{column}<3->{0.33\linewidth}
+		\begin{figure}
+			\includegraphics[width=\linewidth]{../plots/aero_share}
+		\end{figure}
+	\end{column}
+
+	\begin{column}<4->{0.33\linewidth}
+		\begin{figure}
+			\includegraphics[width=\linewidth]{../plots/sus_share}
+		\end{figure}
+	\end{column}
+
+\end{columns}
+\begin{columns}
+
+	\begin{column}<5->{0.33\linewidth}
+		\begin{figure}
+			\includegraphics[width=\linewidth]{../plots/negative_emissions_share}
+		\end{figure}
+	\end{column}
+
+	\begin{column}<6->{0.33\linewidth}
+		\begin{figure}
+			\includegraphics[width=\linewidth]{../plots/ipcc_rep_simple}
+		\end{figure}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
+\begin{frame}{Conclusions}
+
+\begin{itemize}
+	\item<1-> Endogenously discovered topics map and make substantive sense of an unmanageable dataset of climate-relevant literature
+	\item<2-> Topic modelling discovers over-arching topics such as that on sustainability and research priorities, as well as specific, fast growing topics such those on negative emissions
+	\item<3-> Some quantitative evidence is found to support policy makers' dissatisfaction with a lack of `solution orientation' in IPCC reports \citep{Kowarsch2017} 
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Discussion}
+
+\begin{itemize}
+\item<1-> A perfectly representative relationship between the literature and IPCC reports is not necessarily desirable
+\item<2-> The IPCC are best placed to decide which aspects of the literature to emphasise
+\item<3-> A topography of the literature helps to address issues of emphasis from a point of understanding, and to make decisions clear and transparent
+\item<4-> More generally, maps like this present exciting opportunities to aid the process of literature selection, and to understand the science policy process
+\end{itemize}
 
@@
 \backupbegin
+
+\begin{frame}{Robustness}
+
+Most work focuses on the measuring the sensitivity of the reconstruction error to different framings and parameters of the model.
+What we are more interested in is checking if the key messages are sound.
+
+\begin{columns}<2->
+	\begin{column}<3->{0.33\linewidth}
+		\begin{figure}
+			\includegraphics[width=\linewidth]{../plots/aero_share}
+		\end{figure}
+	\end{column}
+
+	\begin{column}<4->{0.33\linewidth}
+		\begin{figure}
+			\includegraphics[width=\linewidth]{../plots/sus_share}
+		\end{figure}
+	\end{column}
+
+\end{columns}
+\begin{columns}
+
+	\begin{column}<5->{0.33\linewidth}
+		\begin{figure}
+			\includegraphics[width=\linewidth]{../plots/negative_emissions_share}
+		\end{figure}
+	\end{column}
+
+	\begin{column}<6->{0.33\linewidth}
+		\begin{figure}
+			\includegraphics[width=\linewidth]{../plots/ipcc_rep_simple}
+		\end{figure}
+	\end{column}
+\end{columns}
+
+\end{frame}
 

### 2018-07-26 pres/CC_Topography_EASST_Callaghan.tex
update presentation

@@
 				\item<2-> Topography is a description of a landscape
-				\item<3-> Topics (from the Greek \texttau\textomikron\textpi\textomikron\textvarsigma, place) can describe the features of body of text
+				\item<3-> Topics (from the Greek \texttau\textomikron\textpi\textomikron\textvarsigma, place) can describe the features of a body of text
 			\end{itemize}
@@
 \begin{enumerate}
-\item<4-> Download documents from Web of Science (WoS)
+\item<4-> Download document metadata from Web of Science (WoS)
 \item<5-> Match documents to reference lists from IPCC reports
@@
 \begin{frame}{Data - Unmatched IPCC References}
-\tiny
-\input{../tables/ipcc_matching_sample.tex}
-\end{frame}
-
-\begin{frame}{Data - Unmatched IPCC References}
 
@@
 
+\end{frame}
+
+\begin{frame}{Data - Unmatched IPCC References}
+\tiny
+\input{../tables/ipcc_matching_sample.tex}
 \end{frame}

### 2018-09-04 pres/2018_02_pres.tex

@@
 				\item Comprehensive, credible and relevant assessments become
-				more challenging as the literature grows
+				more challenging as the literature grows \citep{Minx2017l}
 			\end{itemize}
@@
 \begin{enumerate}
-	\item Download documents from Web of Science (WoS)
-	\item Match documents to reference lists from IPCC reports
-	\item Topic model stemmed document abstracts
+	\item<4-> Download documents from Web of Science (WoS)
+	\item<5-> Match documents to reference lists from IPCC reports
+	\item<6-> Topic model stemmed document abstracts
 \end{enumerate}
@@
 		\item Check for case-insensitive title matches
-		\item Calculate the Jaccard similarity score for two word every database document containing the first word and from the same year. Match if the Jaccard score is above 0.45
+		\item Calculate the Jaccard similarity score for two word shingles every database document containing the first word and from the same year. Match if the Jaccard score is above 0.45
 	\end{itemize}
@@
 
-\begin{frame}{Results - Inter-working Group topics - WG 1 and 3}
+\begin{frame}{Results - Inter-working Group topics - WG 1 and 2}
 
@@
 \begin{frame}
-	The documents that underpin this growth
+	\begin{figure}
+		\includegraphics[width=\linewidth]{../plots/sus_overview}
+	\end{figure}
 \end{frame}
@@
 	\begin{figure}
-		\includegraphics[width=0.6\linewidth]{../plots/development/ar5_growth}	
+		\includegraphics[width=0.8\linewidth]{../plots/ar5_growth_662}	
 	\end{figure}
@@
 \begin{figure}
-	\includegraphics[width=0.8\linewidth]{../plots/development/ar6_growth}	
+	\includegraphics[width=0.8\linewidth]{../plots/ar6_growth_662}	
 \end{figure}
@@
 
-%\begin{frame}{Preliminary results - structure - WGI}
-%
-%\begin{columns}
-%	\begin{column}{0.65\linewidth}
-%		\begin{center}
-%			\vspace*{-0.1\linewidth}
-%%			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_1.PNG}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.35\linewidth}
-%%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key.PNG}
-%		\begin{center}
-%			\begin{itemize}
-%				\item The largest topic in WGI is on models.
-%			\end{itemize}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-%
-%\begin{frame}{Preliminary results - structure - WGII}
-%
-%\begin{columns}
-%	\begin{column}{0.65\linewidth}
-%		\begin{center}
-%			\vspace*{-0.1\linewidth}
-%			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_2}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.35\linewidth}
-%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
-%		\begin{center}
-%			\begin{itemize}
-%				\item The largest primarily WGII topic is on climate change impacts
-%			\end{itemize}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-%
-%\begin{frame}{Preliminary results - structure - WGIII}
-%
-%\begin{columns}
-%	\begin{column}{0.65\linewidth}
-%		\begin{center}
-%			\vspace*{-0.1\linewidth}
-%			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_3}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.35\linewidth}
-%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
-%		\begin{center}
-%			\begin{itemize}
-%				\item The largest WGIII topic is on emissions reductions.
-%			\end{itemize}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-%
-%\begin{frame}{Preliminary results - structure - other clusters}
-%
-%\begin{columns}
-%	\begin{column}{0.65\linewidth}
-%		\begin{center}
-%			\vspace*{-0.1\linewidth}
-%			\hspace*{-0.1\linewidth}
-%			\includegraphics[width=1.25\linewidth]{../plots/network_wg_372_4}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.35\linewidth}
-%		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key}
-%		\begin{center}
-%			\begin{itemize}
-%				\item A fourth cluster of mostly WGII references contains topics on ecosystems, species and habitats
-%			\end{itemize}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-
-%\begin{frame}{Preliminary results - structure - Sustainability}
-%
-%
-%
-%\begin{columns}
-%	\begin{column}{0.6\linewidth}
-%		\begin{center}			
-%			\includegraphics[width=\linewidth]{../plots/sustainability}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.4\linewidth}
-%		\begin{center}
-%			\begin{itemize}
-%				\item In later assessment periods, a large meta-topic on research priorities and sustainability emerges
-%			\end{itemize}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-%
-%\begin{frame}{Preliminary results - structure - Sustainability}
-%
-%
-%
-%\begin{columns}
-%	\begin{column}{0.6\linewidth}
-%		\begin{center}			
-%			\includegraphics[width=\linewidth]{../plots/health_sustain_386}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.4\linewidth}
-%		\begin{center}
-%			\begin{itemize}
-%				\item The flatness of its distribution across documents indicates a topic that occurs
-%			\end{itemize}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-%
-%%% Sus table
-%
-%\begin{frame}{Preliminary results - structure - Sustainability}
-%\begin{table}
-%	\footnotesize
-%	\renewcommand{\arraystretch}{2}
-%\begin{tabular}{p{0.3\linewidth}p{0.3\linewidth}p{0.3\linewidth}}
-%	\toprule 
-%	{polici, govern, tax} & {adapt, vulner, strategi}  & {urban, citi, area} \\ 
-%	\midrule 
-%	How Research-Prioritization Exercises Affect Conservation Policy & Methodological choices in solution-oriented adaptation research: a diagnostic framework & A review of urban ecosystem services: six key challenges for future research  \\
-%	Role of hydrology and economics in water management policy under increasing uncertainty & When not every response to climate change is a good one: Identifying principles for sustainable adaptation & Lines of Tradition and Recent Approaches to Urban Ecology, Focussing on Germany and the USA \\
-%	Informing food policy: balancing the evidence & Informed adaptation: Ethical considerations for adaptation researchers and decision-makers & Advancing understanding of the complex nature of urban systems \\
-%	The identification of priority policy options for UK nature conservation & Future oriented conservation: knowledge governance, uncertainty and learning & Sustainable urban landscapes: South African perspectives on transdisciplinary possibilities \\
-%	Environmental education policy research challenges and ways research might cope with them & Towards an integrated agenda for adaptation research: theory, practice and policy & A conceptual framework for addressing complexity and unfolding transition dynamics when developing sustainable adaptation strategies in urban water management \\
-%	\bottomrule
-%\end{tabular} 
-%
-%\end{table}
-%
-%\end{frame}
-
-%\begin{frame}{Preliminary results - growth}
-%
-%\begin{columns}
-%	\begin{column}{0.6\linewidth}
-%		\begin{center}
-%			\includegraphics[width=\linewidth]{../plots/top_20_386}
-%		\end{center}
-%	\end{column}
-%	\begin{column}{0.4\linewidth}
-%		\begin{center}
-%			\begin{itemize}
-%				\item Negative emissions related topics have shown strong growth since the end of AR5
-%				\item As have topics on cities and extreme weather events
-%			\end{itemize}
-%		\end{center}
-%	\end{column}
-%\end{columns}
-%
-%\end{frame}
-
-%\begin{frame}{Preliminary results - growth - biochar}
-%
-%
-%		\begin{center}
-%			\includegraphics[width=\linewidth]{../plots/biochar_growth.png}
-%
-%		\medskip
-%
-%			\begin{itemize}
-%				\item Biochar has emerged as an entirely new topic in the last 10 years
-%			\end{itemize}
-%		\end{center}
-%
-%\end{frame}
-
-%\begin{frame}{Preliminary results - gaps in coverage}
-%
-%How can we get a sense of which topics are better covered in IPCC reports?
-%
-%\begin{itemize}
-%	\item Each document \(d\) either matches or does not match an IPCC reference
-%	\item For each topic \(h\), we can sum the scores for each category of document
-%	\item The ``IPCC proportion'' of each topic is the proportion of the sum of the document score accounted for by documents which match IPCC references.
-%\end{itemize}
-%
-%\end{frame}
-
 \begin{frame}{Results - topic representation in IPCC reports}
 
-How can we get a sense of which topics are better covered in IPCC reports?
+\begin{itemize}
+	\item<1-> How can we get a sense of which topics are better covered in IPCC reports?
+	\item<2-> We get a measure of proportionality between two distributions by dividing the each topics share in the IPCC sample by its share in the whole corpus
+	\item<3-> This and other measures come from literature on the proportionality of electoral systems \citep[e.g][]{Karpov2008}
+\end{itemize}
 
 \medskip
-
-We get a measure of proportionality between two distributions by dividing the each topics share in the IPCC sample by its share in the whole corpus
 
@@
 
-	\includegraphics[width=0.8\linewidth]{../plots/ipcc_coverage_by_wg_654.png}
+\begin{columns}
+	\begin{column}{0.7\linewidth}
+				\includegraphics[width=\linewidth]{../plots/ipcc_coverage_by_wg_654.png}
+	\end{column}
+	\begin{column}{0.3\linewidth}
+		\begin{itemize}
+			\item On average, topics that are primarily referenced by working group I report have a higher proportion of constituent documents matching IPCC references
+		\end{itemize}
+	\end{column}
+\end{columns}
 
@@
 
-Outlines for the sixth assessment report have already been published.
-
-The words in each chapter were matched to the Topic-Term matrix generated by the model to calculate a [simplified] topic score for each chapter.
-
-These scores were summed and were compared to the corpus in general in the same way as with past reports
+\begin{itemize}
+	\item<1-> Outlines for the sixth assessment report have already been published
+	\item<2-> The words in each chapter were matched to the Topic-Term matrix generated by the model to calculate a simplified topic score for each chapter
+	\item<3-> These scores were summed and were compared to the corpus in general in the same way as with past reports
+\end{itemize}
 
@@
 
+\begin{frame}{Robustness}
+
+Most work focuses on the measuring the sensitivity of the reconstruction error to different framings and parameters of the model.
+What we are more interested in is checking if the key messages are sound.
+
+\begin{columns}<2->
+	\begin{column}<3->{0.33\linewidth}
+		\begin{figure}
+			\includegraphics[width=\linewidth]{../plots/aero_share}
+		\end{figure}
+	\end{column}
+
+	\begin{column}<4->{0.33\linewidth}
+		\begin{figure}
+			\includegraphics[width=\linewidth]{../plots/sus_share}
+		\end{figure}
+	\end{column}
+
+\end{columns}
+\begin{columns}
+
+	\begin{column}<5->{0.33\linewidth}
+		\begin{figure}
+			\includegraphics[width=\linewidth]{../plots/negative_emissions_share}
+		\end{figure}
+	\end{column}
+
+	\begin{column}<6->{0.33\linewidth}
+	\begin{figure}
+		\includegraphics[width=\linewidth]{../plots/ipcc_rep_simple}
+	\end{figure}
+	\end{column}
+\end{columns}
+
+\end{frame}
+
 %\begin{frame}{Next steps}
@@
 
-%\begin{frame}{Conclusions}
-%
-%
-%\begin{itemize}
-%	\item Endogenously discovered topics make substantive sense of an unmanageable dataset of climate-relevant literature
-%	\item Topic modelling discovers over-arching topics such as that on sustainability and research priorities, as well as individual, fast growing topics such as biochar or CCS
-%	\item Matching documents to IPCC references, we can describe topics that belong to or bridge IPCC working groups
-%	\item Quantitative evidence is found to support policy makers' dissatisfaction with a lack of `solution orientation' in IPCC reports \citep{Kowarsch2017} 
-%	\item By uncovering the structure at scale of a large collection of documents, and by enabling the discovery of documents relevant to specific topics or combinations of topics, this approach can provide for more comprehensive and salient scientific assessments.
-%\end{itemize}
-%
-%\end{frame}
+\begin{frame}{Conclusions}
+
+\begin{itemize}
+	\item<1-> Endogenously discovered topics map and make substantive sense of an unmanageable dataset of climate-relevant literature
+	\item<2-> Topic modelling discovers over-arching topics such as that on sustainability and research priorities, as well as specific, fast growing topics such those on negative emissions
+	\item<3-> Some quantitative evidence is found to support policy makers' dissatisfaction with a lack of `solution orientation' in IPCC reports \citep{Kowarsch2017} 
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Discussion}
+
+\begin{itemize}
+	\item<1-> A perfectly representative relationship between the literature and IPCC reports is not necessarily desirable
+	\item<2-> The IPCC are best placed to decide which aspects of the literature to emphasise
+	\item<3-> A topography of the literature helps to address issues of emphasis from a point of understanding, and to make decisions clear and transparent
+	\item<4-> More generally, maps like this present exciting opportunities to aid the process of literature selection, and to understand the science policy process
+\end{itemize}
+
+\end{frame}
 
@@
 
-\begin{frame}{Frame Title}
+\begin{frame}{A Topography of Climate Change Research}
+\begin{columns}
+	\begin{column}{0.5\linewidth}
+		\begin{center}
+			\begin{figure}
+				\includegraphics[width=1\linewidth]{../plots/Hondius_Portrait_of_map-makers}
+				\caption{Portrait of map-makers, Gerard Mercator and Jodocus Hondius (Jodocus Hondius) source: \url{https://commons.wikimedia.org/wiki/File:Hondius_Portrait_of_map-makers.jpg}}
+			\end{figure}
+		\end{center}
+	\end{column}
+	\begin{column}{0.5\linewidth}
+		\begin{center}
+\includegraphics[width=\linewidth]{../plots/pca_map_portrait}
+		\end{center}
+	\end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{Bibliography}
 	\small

### 2018-09-04 tables/ipcc_matching_sample.tex

\begin{tabular}{l l p{4.5cm} p{2.5cm} r}
\toprule
 AR &  WG &                                                                                                                                                                                                                        text &                                                   authors &  year \\
\midrule
 2 &  2 &  Landfill gas: working with Gaia. Biodeterioration Extracts no. 4, Energy Technology Support Unit, Harwell Laboratory, Oxfordshire, UK.  &  Richards, K.M. &  1989 \\
 1 &  1 &  Longwave cloud radiative forcing as determined from Nimbus-7 observations J Cltm , 2, 766 799  &  Ardanuy, P E , L L Stowe, A Gruber, M Weiss and C S Long &  1989 \\
 3 &  2 &  Climate change: overview and implications   for wildlife. In: Wildlife Responses to Climate Change: North American Case   Studies [Schneider, S.H. and T.L. Root (eds.)]. Island Press, Washington, DC,   USA, (in press). &  Root, T.L. and S.H. Schneider &  2001 \\
 2 &  3 &  The impact ol' global wanning on the United States: A survey of recent literature, mimco. Institute lor Interna-tional Economics, Washington, DC (April).  &  Cline, W.R. &  1993 \\
 3 &  2 &  Population-environment   relations at the forested frontier of Nepal. Applied Geography, 20, 221-242. &  Conway, D., K. Bhattarai, and N.R. Shrestha &  2000 \\
 3 &  2 &  The Cities Project. Australian Geological Survey Organisation,   Australia. Available online at http://www.agso.gov.au/geohazards/grm/cities2.html. &  AGSO &  1999 \\
 4 &  1 &  CLIMBER-2: A climate system model of intermediate complexity. Part I: Model description and performance for present climate.  &  Petoukhov, V., et al. &  2000 \\
 5 &  1 &  A skill-score based evaluation of simulated Australian climate. Australian Meteorol. Oceanogr &  Watterson, I., A. C. Hirst, and L. D. Rotstayn &  2013 \\
 5 &  1 &  Enhanced aerosol backscatter adjacent to tropical trade wind clouds revealed by satellite-based lidar. Geophys. Res &  Tackett, J. L., and L. Di Girolamo &  2009 \\
 5 &  3 &  Promoting long-term invest-ments by institutional investors. OECD Journal: Financial Market Trends 1, 145 – 164 &  Della Croce R, F Stewart, and J Yermo &  2011 \\
\bottomrule
\end{tabular}

### 2018-11-02 code/dynamic_nmf0.py
tsne

@@ -13,6 +13,8 @@ from django.utils import timezone
 from scipy.sparse import csr_matrix, find
 import numpy as np
 from django.core import management
+import os
+from django.db.models import Count
 
 
 
@@ -20,9 +22,10 @@ sys.stdout.flush()
 
 # import file for easy access to browser database
 sys.path.append('/home/galm/software/django/tmv/BasicBrowser')
-
+os.environ.setdefault("DJANGO_SETTINGS_MODULE", "BasicBrowser.settings")
+django.setup()
 # sys.path.append('/home/max/Desktop/django/BasicBrowser/')
-import db as db
+import utils.db as db
 from tmv_app.models import *
 from scoping.models import *
 from django.db import connection, transaction
@@ -164,11 +167,12 @@ def main():
 
 
     global run_id
-    run_id = db.init(n_features,ng)
+    run_id = db.init(n_features)
     stat = RunStats.objects.get(run_id=run_id)
     stat.query = Query.objects.get(pk=qid)
     stat.method = "DT"
     stat.alpha = 0.01
+    stat.ng = ng
     stat.save()
     i = 0
     #ndocs = Doc.objects.filter(query=qid,content__iregex='\w').count()
@@ -203,8 +207,70 @@ def main():
         k = predict(ydocs)
         print("esimating {} topics...".format(k))
 
-        abstracts, docsizes, ids = proc_docs(docs, stoplist)
+        abstracts, docsizes, ids, citations = proc_docs(docs, stoplist, stat.fulltext, stat.citations)
         #abstracts, docsizes, ids, stoplist = proc_docs(docs,stoplist)
+
+        ######################################
+        ## A fancy tokenizer
+
+        from nltk import wordpunct_tokenize
+        from nltk import WordNetLemmatizer
+        from nltk import sent_tokenize
+        from nltk import pos_tag
+        from nltk.corpus import stopwords as sw
+        punct = set(string.punctuation)
+        from nltk.corpus import wordnet as wn
+        stopwords = set(sw.words('english'))
+
+        def lemmatize(token, tag):
+                tag = {
+                    'N': wn.NOUN,
+                    'V': wn.VERB,
+                    'R': wn.ADV,
+                    'J': wn.ADJ
+                }.get(tag[0], wn.NOUN)
+                return WordNetLemmatizer().lemmatize(token, tag)
+
+        kws = Doc.objects.filter(
+            query=stat.query,
[…]

### 2018-11-27 main.tex
formatting
dunno
no big files

@@
+<<<<<<< HEAD
 \documentclass{article}
@@
 \usepackage{color}
-\usepackage{auto-pst-pdf}
+%\usepackage{auto-pst-pdf}
 \usepackage[colaction]{multicol}
@@
 \usepackage{svg}
+\usepackage{authblk}
 
@@
  		{\large\textbf{\@author}}
+
+ 		\bigskip
+
+ 		{\large{Draft current \@date}}
+
 	\end{flushleft}\egroup
@@
 \title{A Topography of Climate Change Research}
-\author{Max Callaghan}
+\author[1,2]{Max Callaghan}
+
+\affil[1]{Mercator Research Institute on Global Commons and Climate Change, Torgauer Straße, 10829 Berlin, Germany}
+\affil[2]{School of Earth and Environment, University of Leeds, Leeds LS2 9JT, United Kingdom}
 
@@
 
-Various researchers have attempted to do empirical research on the assessment reports, and processes of inter. alia. the IPCC \citep{jabbour2017} \citep{Bjurström2011} \citep{Hulme2016}.
+Various researchers have attempted to do empirical research on the assessment reports, and processes of inter.
+alia.
+the IPCC \citep{jabbour2017} \citep{Bjurström2011} \citep{Corbera2016} \citep{Hulme2016}.
+
+Policy makers, when asked about their interactions with the IPCC call for a greater focus on solutions \citep{Kowarsch2017}
+
+These studies are similarly challenged by the the size of the literature. Traditional bibliometric techniques are insufficient.
+
+\bigskip
+\noindent\textbf{Some literature exists on bibliometrics and climate change, but tends not to deal with text}
+
+Bibliometrics e.g. \citep{Haunschild2016} \citep{Grieneisen2011}
+
+Text based approaches are usually of a smaller scope \citep{Grubert2016} or methodological contributions \citep{Blei2003}
+
+\bigskip
+\noindent\textbf{The scale of the problem in context}
+
+The scale of the challenge is depicted in figure \ref{growth}.
+Less than two thousand documents relevant to climate change were published before the first assessment report (see Methods for data, exclusions and processing).
+These documents contained 3,528 unique terms, each of which was used on average in 0.49\% of documents.
+In the three complete years since the publication of AR5, 128,357 documents have been published, containing 86,419 unique terms, used on average in 0.12\% of documents.
+To put this into context, the 1,189 chapters of the Bible contain a vocabulary of 11,977 unique words.
+Put another way, the 236,634 publications published in AR5 and AR6 are significantly larger than the 178,118 publications recorded in the first volume of the `Catalogue of Scientific Papers', compiled by the Royal Society to record the entirety of scientific output from 1800 to 1863 \citep{Csiszar2017}
+
+\begin{table}
+	\scriptsize	
+	\input{tables/growth_table.tex}
+	\caption{Growth in climate change literature}
+\end{table}
+
+%\begin{figure}
+%	\begin{center}
+%		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
+%		%\captionof{figure}
+%		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions.
+Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period.
+The percentage of documents in which the average word occurs in is given in the key.
+%		}
+%		\label{growth}
+%	\end{center}
+%\end{figure}
+
+\bigskip
+\noindent\textbf{Machine reading to deal with scale problems in the making and assessing of maps}
+
+Clearly, if the IPCC is to continue producing comprehensive assessments, it has to engage in machine-reading in order to remain anchored to the wider literature.
+Without such an approach, it becomes harder to justify which ever-diminishing proportion of the wider literature is included in assessments.
+Similarly, it becomes harder to criticise, with quantitatively evidenced claims, the outcomes of assessment processes.
+
+\bigskip
+\noindent\textbf{Dimension reduction makes possible the description in reduced form, and with less human bias, of unmanageably large datasets}
+
+\citep{Greene2016} \citep{Lee1999}
+
+This reduced form description makes comparisons more useful, when cutting the dataset.
+
+\bigskip
+\noindent\textbf{Machine reading is a supplement to assessment-making and not free from bias; a topography is not a map}
+
+Machine reading approaches can of course not replace the task of human assessment-making.
+The contribution that could be made, though, is to pre-process the literature, producing a topographical map, used to navigate the literature while producing a more detailed assessment with human judgement.[[]] In fact this happens already - when IPCC authors search for literature on a topic, the results which appear on the search engine they use will be subject to algorithms based on the processing of millions of records of article text and metadata.
+This can be done in a much more systematic way when scientists perform directed analyses of the literature at scale.
+
+\bigskip
+\noindent\textbf{This study's contribution. Overarching themes, structure of the literature, development, relation to IPCC}
+
+This study demonstrates how dynamic topic modelling can be used to gain an overview of an otherwise unmanageably large body of literature.
+This overview, or topography, describes the thematic development of the climate change literature and, in a novelly systematic way, examines how  comprehensively the IPCC has been able to engage with it.
+In pulling together strands from text-mining, bibliometrics, and the study of science and policy, this study advances our understanding of the literature on climate change and the role of the IPCC in communicating this to policy makers.
+
+\section*{Results}
+
+\begin{table}
+	\scriptsize	
+	\input{tables/top_topics.tex}
+	\caption{Top 10 topics in climate change literature}
+\end{table}
+
+\bigskip
+\noindent\textbf{A topographical map of climate change documents shows the broad structure of climate change literature}
+
+Topics cut across both disciplinary, and working group lines - but disciplinary and working group structure remains visible in the map.
+
+\begin{figure}
+	\begin{center}
+		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_double.pdf}
+		\caption{A map of the literature on climate change.
+Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom).
+See SI table for further description}
+		\label{}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_evolution.pdf}
+		\caption{The evolution of the landscape of climate change literature}
+		\label{}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		%\includegraphics[width=1\linewidth]{plots/network_development_wgs_665.pdf}
+		\caption{The development of the topic-document correlation network over IPCC assessment periods.}
+		\label{}
+	\end{center}
+\end{figure}
+
+\bigskip
+\noindent\textbf{The topic-document correlation network is densest in AR2 and 3 but becomes more fragmented over time}
+
+(partly: Model less good at describing literature later on)
+
+\bigskip
+\noindent\textbf{Working groups are clustered together [dynamics], with topics like [x] containing documents across working groups and topics like [y] important network nodes}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=1\linewidth]{plots/ipcc_representation/ipcc_rep_new665_all.pdf}
+		\caption{Representation and newness of dynamic topics}
+		\label{}
+	\end{center}
+\end{figure}
+
+\bigskip
+\noindent\textbf{Sustainability has been an increasingly important theme in an overarching topic about environmental sciences}
+
+(compare to biochar, which is much more recent)
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=1\linewidth]{plots/single_topic_3_11046.pdf}
+		\caption{Word and document development of the ``Research'' dynamic topic}
+		\label{}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=1\linewidth]{plots/single_topic_3_11020.pdf}
+		\caption{SI Word and document development of the ``Biochar'' dynamic topic}
+		\label{}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+	\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
+    \caption{SI Topic make up of a single document}
+    \label{}
+    \end{center}
+\end{figure}
+
+\bigskip
+\noindent\textbf{Physical science topics tend to be the oldest, and the most well represented topics}
+
+\bigskip
+\noindent\textbf{Adaptation and impact studies have seen a lot of growth but are well represented in IPCC reports}
+
+\bigskip
+\noindent\textbf{New topics around negative emissions and urban form are very recent and not well represented in IPCC reports.}
+
+Negative emissions in special report on 1.5, demand side chapter in AR6
+
+\section*{Discussion}
+
+\bigskip
+\noindent\textbf{Solutions, policies and science}
+
+What do policy-makers mean when they ask for more solutions
+
+\bigskip
+\noindent\textbf{Perfect representation is not necessarily desirable, but the skewedness should be known}
+
+There may be good reasons for a topic to be less prominent in IPCC discussions than in the wider scientific literature, and these reasons can only be understood and acted upon by humans, not by machine-reading.
+Nevertheless, it is desirable that assessment makers are aware of the relationship
+
+%Increase in the frequency of the use of the term ``solutions'' \citep{jabbour2017},
+
+\section*{Methods}
+\label{methods}
+
+\subsection*{Data}
+%This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of
+
+\end{linenumbers}
+
+%\end{multicols}
+
+\listoffigures
+\linespread{1}
+\bibliography{Mendeley.bib}
+\bibliographystyle{unsrt}
+
+\end{document}
+
+=======
+\documentclass{article}
+\usepackage[a4paper, total={6in, 8in}]{geometry}
+\usepackage{graphicx}
+\usepackage{url}
+\usepackage{natbib}
+\usepackage{todonotes}
+\usepackage{booktabs}
+\usepackage{lineno}
+\usepackage{color}
+\usepackage{auto-pst-pdf}
+\usepackage[colaction]{multicol}
+\usepackage{caption}
+\usepackage{svg}
+\usepackage{authblk}
+
+\linespread{1.5}
+
+\makeatletter
+\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
+	\begin{flushleft}
+
+		{\huge\textbf{\@title}}
+
+		\bigskip
+
+ 		{\large\textbf{\@author}}
+
+ 		\bigskip
+
+ 		{\large{Draft current \@date}}
+
+	\end{flushleft}\egroup
+}
+\makeatother
+
+\newcommand{\multicollinenumbers}{
+	\linenumbers
+	\def\makeLineNumber{\docolaction
+		{\makeLineNumberLeft}
+		{}
+		{\makeLineNumberRight}
+		}
+}
+
+\newenvironment{figurehere}
+	{\def\@captype{figure}}
+	{}
+
+% Title
+\title{A Topic Model of Climate Change Literature}
+\title{Words, words, words: Mapping the Matter of Climate Change Literature}
+\title{A Topography of Climate Change Research}
+\author[1,2]{Max Callaghan}
+
+\affil[1]{Mercator Research Institute on Global Commons and Climate Change, Torgauer Straße, 10829 Berlin, Germany}
+\affil[2]{School of Earth and Environment, University of Leeds, Leeds LS2 9JT, United Kingdom}
+
+\begin{document}
+\maketitle
+
+\begin{linenumbers}
+
+\noindent\textbf{	
+The massive expansion of scientific literature on climate change challenges the Intergovenmental Panel on Climate Change (IPCC)'s ability to assess the science according to its objectives. 
+Moreover, the number and variety of papers hinders researchers of the science-policy interface from making objective judgements about those IPCC assessments.
+In this paper, we present a novel application of a machine-reading approach to model the topical content of papers on climate change.
+This dynamic topic model provides the basis for a \textit{topography} of climate change literature.
+The thematic development of the field is outlined and used to inform an analysis of the topics which are better and less well covered by IPCC reports.
+}
+
+\bigskip
+
+%\begin{multicols}{2}
+
+%\multicollinenumbers
+\bigskip
+\noindent\textbf{To deal with the wicked problem of climate change, international policy-makers need the IPCC. The IPCC as map-makers.}
+
+The IPCC sees its role as to ``assess on a comprehensive, objective, open and transparent basis the scientific, technical and socio-economic information relevant to [...] climate change'' \citep{IPCC2013}.
+Climate science is so broad, multi-disciplinary, and laden with uncertainties and values, that the role of the IPCC as assessment maker is vitally important to developing evidence-based international climate policy.
+Making maps \citep{Edenhofer2015}
+
+\bigskip
+\noindent\textbf{The task of the IPCC has become much more difficult with big literature}
+
+Further, it has been pointed out that, in the age of ``big literature'', providing assessments that are comprehensive, objective and transparent has become much more difficult \citep{Minx2017l}.
+
+When IPCC's citations constitute an ever-decreasing proportion of the totality of science on climate change, questions about the map that the IPCC reports produce become more pressing:
+
+- Is the map up to date? Is it complete? Is the perspective representative?
+
+%%%%%
+
+\bigskip
+\noindent\textbf{The IPCC, its reports and processes have been the object of study before. These are also hampered by problems of scale though}
+
+Various researchers have attempted to do empirical research on the assessment reports, and processes of inter.
+alia.
+the IPCC \citep{jabbour2017} \citep{Bjurström2011} \citep{Corbera2016} \citep{Hulme2016}.
 
@@
 \end{document}
+
+>>>>>>> 0261e7b8054b72195fb991f1ca7947fd5b9a6b9d

### 2018-11-27 prog_report.tex
no big files

--- 2018-07-16 main.tex
@@
 \usepackage{color}
-\usepackage{auto-pst-pdf}
-\usepackage[colaction]{multicol}
 \usepackage{caption}
 \usepackage{svg}
+\usepackage{authblk}
+\usepackage{hyperref}
+\hypersetup{
+	pdfinfo={
+		Author={Max Callaghan},
+		Title={Progress Report},
+		CreationDate={D:20180601195600},
+		ModDate={...},
+		Keywords={PDF;LaTeX},
+	}
+}
 
@@
 		{\large\textbf{\@author}}
+
+		\bigskip
+
+		{\large\textbf{\@date}}
+
 	\end{flushleft}\egroup
@@
 
-\newcommand{\multicollinenumbers}{
-	\linenumbers
-	\def\makeLineNumber{\docolaction
-		{\makeLineNumberLeft}
-		{}
-		{\makeLineNumberRight}
-		}
-}
-
-\newenvironment{figurehere}
-	{\def\@captype{figure}}
-	{}
-
 % Title
-\title{A Topic Model of Climate Change Literature}
-\title{Words, words, words: Mapping the Matter of Climate Change Literature}
-\title{A Topography of Climate Change Research}
+\title{Progress Report}
 \author{Max Callaghan}
+\date{1 June 2016}
 
@@
 
-\begin{linenumbers}
+\section{Overview}
+
+The majority of my work in 2018 has been focussed on what will be my first first-authored publication, \textit{A Topography of Climate Change Literature}.
+A working draft of the introduction and some preliminary results are included in section 2, Paragraph headings are given in bold, with full paragraphs below sometimes to be flushed out.
+In parallel to this, and in support of the analysis, I have been further developing the tools documented in \url{https://github.com/mcallaghan/tmv} and described in section 3.1.
+These have further supported, and been improved by ideas generated from the collaborative work detailed in section 3.2.
+Section 3.3 elucidates other ideas for papers which will directly support my PhD.
+
+%\begin{figure}
+%	\begin{center}
+%		\includegraphics[width=0.9\linewidth]{/home/max/Documents/admin/leeds/candidature_report/max_18_pr.png}
+%		%\captionof{figure}
+%		\caption{
+%		}
+%		\label{activity}
+%	\end{center}
+%\end{figure}
+%
+%As a large part of my work is recorded in online repositories, figure \ref{activity} gives an overview to the time resources I have committed to each project recorded on Github.
+
+\section{A Topography of Climate Change Literature}
 
@@
 
-Various researchers have attempted to do empirical research on the assessment reports, and processes of inter. alia. the IPCC \citep{jabbour2017} \citep{Bjurström2011} \citep{Hulme2016}.
+Various researchers have attempted to do empirical research on the assessment reports, and processes of inter.
+alia.
+the IPCC \citep{jabbour2017} \citep{Bjurström2011} \citep{Corbera2016} \citep{Hulme2016}.
 
@@
 
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/tsne.png}
-		\caption{A map of a sample of 10,000 documents about climate change. Document positions are obtained by reducing the topic scores to two dimensions via t-SNE}
-		\label{}
-	\end{center}
-\end{figure}
+%\begin{figure}
+%	\begin{center}
+%		\includegraphics[width=1\linewidth]{plots/tsne.png}
+%		\caption{A map of a sample of 10,000 documents about climate change. Document positions are obtained by reducing the topic scores to two dimensions via t-SNE}
+%		\label{}
+%	\end{center}
+%\end{figure}
 
@@
 
-%Increase in the frequency of the use of the term ``solutions'' \citep{jabbour2017},
+\section{Other Projects}
 
-\section*{Methods}
-\label{methods}
+\subsection{Tools}
+The architecture of tools included in the TMV repository has expanded.
+The repository was built originally to view topic models interactively,  then extended to manage queries and systematic reviews.
+The query management part has facilitated the systematic reviews on negative emissions technologies (NETs) recently published.
+The joining together of the query management and topic model viewing parts of the tool through an interface to run topic models on queries has allowed for wider use.
+Planned additions include a system to record estimates for a meta-analysis, and the incorporation of machine-learning to speed up the screening process.
 
-\subsection*{Data}
-%This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of
+\subsection{Co-authored papers}
 
-\end{linenumbers}
+\subsubsection{Submitted}
 
-%\end{multicols}
+\citep{Lamb2018a} lays out a new role for machine-reading in evidence synthesis and as such is highly relevant to my PhD. 
+through the provision of the infrastructure to model topics, the iteration of models to choose the right topic size, the editing of the manuscript and the provision of data for the creation of figures.
 
-\listoffigures
+\citep{Hilaire2018} synthesises evidence from integrated assessment models on NETs by collecting and classifying statements about NETs.
+Together with first author Jérôme Hilaire, I added new functionality to the query management tool to provide for the classification of text excerpts from PDFs, and classified a portion of the statements.
+
+\subsubsection{Published}
+
+I contributed to \citep{Lamb2018} through the provision of the infrastructure to model topics, the iteration of models to choose the right topic size, the editing of the manuscript and the provision of data for the creation of figures.
+
+\citep{Minx2018}, \citep{Fuss2018} and \citep{Nemet2018}.
+Form a highly ambitious systematic review on negative emissions technologies.
+The query management tool contributed to the efficient and accurate screening of papers across a geographically dispersed team and the management of publication data.
+I further contributed to the review's analysis by creating the heat bars in \citep{Fuss2018}.
+
+\subsection{Paper ideas}
+
+\subsubsection{Rapid Systematic Maps}
+This paper should lay out, and validate the methods used in \citep{Lamb2018a}.
+The use of topic modelling to produce systematic maps is innovative: this paper should explain the methods and validate results against a human-coded dataset.
+
+\subsubsection{Quantifying the science-policy interface}
+In this paper, I aim, with scientometrics, to measure the properties of the knowledge pyramid, conceptualised by theorists of the science-policy interface.
+What kind of, and how many publications make up each layer of the pyramid, and how does information flow between layers?
+
 \linespread{1}

### 2018-11-27 tables/growth_table.tex
no big files

\begin{tabular}{l p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm}} 
&\textbf{AR1} & \textbf{AR2} & \textbf{AR3} & \textbf{AR4} & \textbf{AR5} & \textbf{AR6}\\ \hline\textbf{Documents} &625 & 7623 & 16395 & 34510 & 117758 & 128266\\ 
\textbf{Words} &1380 & 12409 & 20453 & 32644 & 67064 & 74196\\ 
\textbf{New words} & change (296) & loss (552) & downscaling (197) & sres (217) & biochar (1752) & mmms (192)\\ & climate (262) & efficiency (515) & degreesc (145) & petm (95) & redd (1058) & c3n4 (132)\\ & model (168) & mol (439) & ncep (130) & amf (87) & cmip5 (656) & cop21 (107)\\ & effect (160) & ambient (417) & otcs (87) & sf5cf3 (81) & cmip3 (569) & cmip6 (104)\\ & co2 (156) & coal (404) & nee (87) & cwd (74) & wrf (334) & zika (75)\\ & atmospheric (152) & photosynthetic (393) & fco (80) & embankment (72) & mofs (288) & brgdgts (71)\\ & climatic (133) & concern (381) & hadcm2 (78) & aod (69) & sdm (283) & twitter (68)\\ & global (131) & chamber (353) & dtr (75) & clc (69) & gosat (281) & jing (66)
\end{tabular}

### 2018-11-27 tables/top_topics.tex
no big files

\begin{tabular}{p{1.9cm} p{3cm} p{7.5cm} r}
\toprule
                      title &                                                                            top words &                                                                                                                                                                                                                                                                top docs &   share \\
\midrule
      climat, chang, impact &          [climat, chang, impact, respons, futur, effect, shift, sensit, affect, may] &                                                                                                                                                  \parbox[t]{7.5cm}{Climate oscillations and changes over Russia; \\World Regionalization of Climate Change (1961-2010)} &  2.73\% \\
     soil, moistur, microbi &       [soil, moistur, microbi, organ, respir, content, miner, depth, matter, efflux] &                                                                                    \parbox[t]{7.5cm}{PARTITIONING OF SOIL RESPIRATION IN A FIRST ROTATION BEECH PLANTATION; \\Responses of soil respiration to N fertilization in a loamy soil under maize cultivation} &  2.73\% \\
       emiss, reduct, reduc &      [emiss, reduct, reduc, greenhous, factor, total, estim, inventori, nox, measur] &                                                                                                             \parbox[t]{7.5cm}{China's CH4 and CO2 emissions: Bottom-up estimation and comparative analysis; \\Monitoring total emissions from industrial installations} &  2.21\% \\
   carbon, dioxid, sequestr &   [carbon, dioxid, sequestr, sink, organ, cycl, storag, stock, terrestri, atmospher] &                             \parbox[t]{7.5cm}{Interpreting carbon-isotope excursions: carbonates and organic matter; \\PARTICULATE FLUXES OF CARBONATE AND ORGANIC-CARBON IN THE OCEAN - IS THE MARINE BIOLOGICAL-ACTIVITY WORKING AS A SINK OF THE ATMOSPHERIC CARBON} &  1.74\% \\
      temperatur, air, mean &  [temperatur, air, mean, surfac, minimum, maximum, daili, increas, effect, degreesc] &                                                                                                     \parbox[t]{7.5cm}{Observed changes in shallow soil temperatures in Northeast China, 1960-2007; \\Beyond the Mean: Biological Impacts of Cryptic Temperature Change} &  1.71\% \\
      record, dure, glacial &       [record, dure, glacial, reconstruct, last, period, holocen, event, late, core] &                                                           \parbox[t]{7.5cm}{HIGH-RESOLUTION CLIMATE RECORDS FROM THE NORTH-ATLANTIC DURING THE LAST INTERGLACIAL; \\HIGH-RESOLUTION CLIMATIC INFORMATION FROM SHORT FIRN CORES, WESTERN DRONNING MAUD LAND, ANTARCTICA} &   1.7\% \\
     speci, distribut, rang &          [speci, distribut, rang, rich, invas, nich, predict, extinct, shift, abund] &                               \parbox[t]{7.5cm}{Northward range extensions of some mesopelagic fishes in the Northeastern Atlantic; \\Natural occurrence and backwater infection of C-4 plants in the vegetation of the Yangtze hydropower Three Gorges Project region} &   1.7\% \\
 increas, concentr, decreas &   [increas, concentr, decreas, effect, atmospher, doc, result, organ, nutrient, may] &                                                          \parbox[t]{7.5cm}{TERRESTRIAL HIGHER-PLANT RESPONSE TO INCREASING ATMOSPHERIC [CO2] IN RELATION TO THE GLOBAL CARBON-CYCLE; \\Hydrological response to climate change in the Black Hills of South Dakota, USA} &  1.61\% \\
      forest, tropic, stand &       [forest, tropic, stand, deforest, disturb, stock, boreal, redd, harvest, wood] &  \parbox[t]{7.5cm}{Spatially explicit estimates and temporal changes of forest tree biomass in a typical department of forest management, Turkey; \\Analysis of the changes in forest ecosystem functions, structure and composition in the Black Sea region of Turkey} &  1.56\% \\
    energi, renew, consumpt &        [energi, renew, consumpt, effici, demand, save, sector, sourc, industri, use] &                                                                                                                                       \parbox[t]{7.5cm}{Energy issues and energy priorities; \\Energy efficiency and CO2 emissions in Swedish manufacturing industries} &  1.56\% \\
\bottomrule
\end{tabular}

### 2018-11-27 code/tsne_runs.py

@@ -1,0 +1,142 @@
+import matplotlib
+matplotlib.use('agg')
+
+import django, sys, os, random
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+from pathlib import Path
+
+matplotlib.rcParams["figure.figsize"] = [7.2,4.5]
+matplotlib.rcParams['axes.labelsize'] = 7
+matplotlib.rcParams['xtick.labelsize'] = 5
+matplotlib.rcParams['ytick.labelsize'] = 5
+
+sys.path.append('/home/galm/software/django/tmv/BasicBrowser/')
+os.environ.setdefault("DJANGO_SETTINGS_MODULE", "BasicBrowser.settings")
+django.setup()
+from django.db.models import Q, F, Sum, Count, FloatField, Case, When, Value, Max
+from scipy.sparse import coo_matrix, find
+from sklearn.manifold import TSNE
+
+from scoping.models import *
+from tmv_app.models import *
+from scipy.sparse import csr_matrix
+from time import time
+from MulticoreTSNE import MulticoreTSNE as mTSNE
+
+
+
+run_id = 662
+
+def get_matrix(run_id,s_size):
+    stat = RunStats.objects.get(pk=run_id)
+    if stat.method=="DT":
+        dts = DocDynamicTopic.objects
+    else:
+        dts = DocTopic.objects
+
+    db_matrix = dts.filter(run_id=run_id,score__gt=0.01)
+    docs = set(db_matrix.values_list('doc__id',flat=True))
+    if s_size ==0:
+        s_docs = docs
+    else:
+        s_docs = random.sample(docs,s_size)
+
+    db_matrix = dts.filter(
+        run_id=run_id,
+        score__gt=0.01,
+        doc__id__in=s_docs
+    )
+
+    vs = list(db_matrix.values('score','doc_id','topic_id'))
+
+    c_ind = np.array(list(set(db_matrix.values_list('topic_id',flat=True).order_by('doc_id'))))
+    r_ind = np.array(list(set(db_matrix.values_list('doc_id',flat=True).order_by('doc_id'))))
+
+    d = [x['score'] for x in vs]
+    c = [int(np.where(c_ind==x['topic_id'])[0]) for x in vs]
+    r = [int(np.where(r_ind==x['doc_id'])[0]) for x in vs]
+
+    m = csr_matrix((d,(r,c)),shape=(len(r_ind),len(c_ind)))
+
[…]

### 2018-11-27 code/workout_AR_dtms.py

@@ -1,0 +1,157 @@
+import os, sys, time, resource, re, gc, shutil
+from multiprocess import Pool
+from functools import partial
+from urllib.parse import urlparse, parse_qsl
+import matplotlib
+matplotlib.use('pgf')
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import django
+import pickle
+from django.db.models import Count, Sum
+sys.path.append('/home/galm/software/django/tmv/BasicBrowser/')
+os.environ.setdefault("DJANGO_SETTINGS_MODULE", "BasicBrowser.settings")
+django.setup()
+
+import utils.text as tutils
+
+from scoping.models import *
+
+from sklearn.feature_extraction.text import CountVectorizer, TfidfVectorizer
+from sklearn.preprocessing import normalize
+import nltk
+from nltk.stem import SnowballStemmer
+import string
+
+stoplist = set(nltk.corpus.stopwords.words("english"))
+stoplist.add('elsevier')
+stoplist.add('rights')
+stoplist.add('reserved')
+stoplist.add('john')
+stoplist.add('wiley')
+stoplist.add('sons')
+stoplist.add('copyright')
+
+from nltk import wordpunct_tokenize
+from nltk import WordNetLemmatizer
+from nltk import sent_tokenize
+from nltk import pos_tag
+from nltk.corpus import stopwords as sw
+punct = set(string.punctuation)
+from nltk.corpus import wordnet as wn
+stopwords = stoplist
+
+q = Query.objects.get(pk=2355)
+
+def lemmatize(token, tag):
+        tag = {
+            'N': wn.NOUN,
+            'V': wn.VERB,
+            'R': wn.ADV,
+            'J': wn.ADJ
+        }.get(tag[0], wn.NOUN)
+        return WordNetLemmatizer().lemmatize(token, tag)
+
+kws = Doc.objects.filter(
+    query=q,
+    kw__text__iregex='\W'
+).values('kw__text').annotate(
+    n = Count('pk')
+).filter(n__gt=100).order_by('-n')
+
+kw_text = set([x['kw__text'].replace('-',' ') for x in kws])
+kw_ws = set([x['kw__text'].replace('-',' ').split()[0] for x in kws]) - stopwords
+
+def tokenize(X):
+    for sent in sent_tokenize(X):
+        for token, tag in pos_tag(wordpunct_tokenize(sent)):
+            token = token.lower().strip()
+            if token in stopwords:
+                continue
[…]

### 2018-11-27 main.tex

@@
-<<<<<<< HEAD
 \documentclass{article}
@@
 \end{document}
-
-=======
-\documentclass{article}
-\usepackage[a4paper, total={6in, 8in}]{geometry}
-\usepackage{graphicx}
-\usepackage{url}
-\usepackage{natbib}
-\usepackage{todonotes}
-\usepackage{booktabs}
-\usepackage{lineno}
-\usepackage{color}
-\usepackage{auto-pst-pdf}
-\usepackage[colaction]{multicol}
-\usepackage{caption}
-\usepackage{svg}
-\usepackage{authblk}
-
-\linespread{1.5}
-
-\makeatletter
-\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
-	\begin{flushleft}
-
-		{\huge\textbf{\@title}}
-
-		\bigskip
-
- 		{\large\textbf{\@author}}
-
- 		\bigskip
-
- 		{\large{Draft current \@date}}
-
-	\end{flushleft}\egroup
-}
-\makeatother
-
-\newcommand{\multicollinenumbers}{
-	\linenumbers
-	\def\makeLineNumber{\docolaction
-		{\makeLineNumberLeft}
-		{}
-		{\makeLineNumberRight}
-		}
-}
-
-\newenvironment{figurehere}
-	{\def\@captype{figure}}
-	{}
-
-% Title
-\title{A Topic Model of Climate Change Literature}
-\title{Words, words, words: Mapping the Matter of Climate Change Literature}
-\title{A Topography of Climate Change Research}
-\author[1,2]{Max Callaghan}
-
-\affil[1]{Mercator Research Institute on Global Commons and Climate Change, Torgauer Straße, 10829 Berlin, Germany}
-\affil[2]{School of Earth and Environment, University of Leeds, Leeds LS2 9JT, United Kingdom}
-
-\begin{document}
-\maketitle
-
-\begin{linenumbers}
-
-\noindent\textbf{	
-The massive expansion of scientific literature on climate change challenges the Intergovenmental Panel on Climate Change (IPCC)'s ability to assess the science according to its objectives. 
-Moreover, the number and variety of papers hinders researchers of the science-policy interface from making objective judgements about those IPCC assessments.
-In this paper, we present a novel application of a machine-reading approach to model the topical content of papers on climate change.
-This dynamic topic model provides the basis for a \textit{topography} of climate change literature.
-The thematic development of the field is outlined and used to inform an analysis of the topics which are better and less well covered by IPCC reports.
-}
-
-\bigskip
-
-%\begin{multicols}{2}
-
-%\multicollinenumbers
-\bigskip
-\noindent\textbf{To deal with the wicked problem of climate change, international policy-makers need the IPCC. The IPCC as map-makers.}
-
-The IPCC sees its role as to ``assess on a comprehensive, objective, open and transparent basis the scientific, technical and socio-economic information relevant to [...] climate change'' \citep{IPCC2013}.
-Climate science is so broad, multi-disciplinary, and laden with uncertainties and values, that the role of the IPCC as assessment maker is vitally important to developing evidence-based international climate policy.
-Making maps \citep{Edenhofer2015}
-
-\bigskip
-\noindent\textbf{The task of the IPCC has become much more difficult with big literature}
-
-Further, it has been pointed out that, in the age of ``big literature'', providing assessments that are comprehensive, objective and transparent has become much more difficult \citep{Minx2017l}.
-
-When IPCC's citations constitute an ever-decreasing proportion of the totality of science on climate change, questions about the map that the IPCC reports produce become more pressing:
-
-- Is the map up to date? Is it complete? Is the perspective representative?
-
-%%%%%
-
-\bigskip
-\noindent\textbf{The IPCC, its reports and processes have been the object of study before. These are also hampered by problems of scale though}
-
-Various researchers have attempted to do empirical research on the assessment reports, and processes of inter.
-alia.
-the IPCC \citep{jabbour2017} \citep{Bjurström2011} \citep{Corbera2016} \citep{Hulme2016}.
-
-Policy makers, when asked about their interactions with the IPCC call for a greater focus on solutions \citep{Kowarsch2017}
-
-These studies are similarly challenged by the the size of the literature. Traditional bibliometric techniques are insufficient.
-
-\bigskip
-\noindent\textbf{Some literature exists on bibliometrics and climate change, but tends not to deal with text}
-
-Bibliometrics e.g. \citep{Haunschild2016} \citep{Grieneisen2011}
-
-Text based approaches are usually of a smaller scope \citep{Grubert2016} or methodological contributions \citep{Blei2003}
-
-\bigskip
-\noindent\textbf{The scale of the problem in context}
-
-The scale of the challenge is depicted in figure \ref{growth}.
-Less than two thousand documents relevant to climate change were published before the first assessment report (see Methods for data, exclusions and processing).
-These documents contained 3,528 unique terms, each of which was used on average in 0.49\% of documents.
-In the three complete years since the publication of AR5, 128,357 documents have been published, containing 86,419 unique terms, used on average in 0.12\% of documents.
-To put this into context, the 1,189 chapters of the Bible contain a vocabulary of 11,977 unique words.
-Put another way, the 236,634 publications published in AR5 and AR6 are significantly larger than the 178,118 publications recorded in the first volume of the `Catalogue of Scientific Papers', compiled by the Royal Society to record the entirety of scientific output from 1800 to 1863 \citep{Csiszar2017}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
-		%\captionof{figure}
-		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions.
-Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period.
-The percentage of documents in which the average word occurs in is given in the key.
-		}
-		\label{growth}
-	\end{center}
-\end{figure}
-
-\bigskip
-\noindent\textbf{Machine reading to deal with scale problems in the making and assessing of maps}
-
-Clearly, if the IPCC is to continue producing comprehensive assessments, it has to engage in machine-reading in order to remain anchored to the wider literature.
-Without such an approach, it becomes harder to justify which ever-diminishing proportion of the wider literature is included in assessments.
-Similarly, it becomes harder to criticise, with quantitatively evidenced claims, the outcomes of assessment processes.
-
-\bigskip
-\noindent\textbf{Dimension reduction makes possible the description in reduced form, and with less human bias, of unmanageably large datasets}
-
-\citep{Greene2016} \citep{Lee1999}
-
-This reduced form description makes comparisons more useful, when cutting the dataset.
-
-\bigskip
-\noindent\textbf{Machine reading is a supplement to assessment-making and not free from bias; a topography is not a map}
-
-Machine reading approaches can of course not replace the task of human assessment-making.
-The contribution that could be made, though, is to pre-process the literature, producing a topographical map, used to navigate the literature while producing a more detailed assessment with human judgement.[[]] In fact this happens already - when IPCC authors search for literature on a topic, the results which appear on the search engine they use will be subject to algorithms based on the processing of millions of records of article text and metadata.
-This can be done in a much more systematic way when scientists perform directed analyses of the literature at scale.
-
-\bigskip
-\noindent\textbf{This study's contribution. Overarching themes, structure of the literature, development, relation to IPCC}
-
-This study demonstrates how dynamic topic modelling can be used to gain an overview of an otherwise unmanageably large body of literature.
-This overview, or topography, describes the thematic development of the climate change literature and, in a novelly systematic way, examines how  comprehensively the IPCC has been able to engage with it.
-In pulling together strands from text-mining, bibliometrics, and the study of science and policy, this study advances our understanding of the literature on climate change and the role of the IPCC in communicating this to policy makers.
-
-\section*{Results}
-
-\bigskip
-\noindent\textbf{A topographical map of climate change documents shows the broad structure of climate change literature}
-
-Topics cut across both disciplinary, and working group lines - but disciplinary and working group structure remains visible in the map.
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/tsne.png}
-		\caption{A map of a sample of 10,000 documents about climate change. Document positions are obtained by reducing the topic scores to two dimensions via t-SNE}
-		\label{}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/network_development_wgs_665.pdf}
-		\caption{The development of the topic-document correlation network over IPCC assessment periods.}
-		\label{}
-	\end{center}
-\end{figure}
-
-\bigskip
-\noindent\textbf{The topic-document correlation network is densest in AR2 and 3 but becomes more fragmented over time}
-
-(partly: Model less good at describing literature later on)
-
-\bigskip
-\noindent\textbf{Working groups are clustered together [dynamics], with topics like [x] containing documents across working groups and topics like [y] important network nodes}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/ipcc_representation/ipcc_rep_new665_all.pdf}
-		\caption{Representation and newness of dynamic topics}
-		\label{}
-	\end{center}
-\end{figure}
-
-\bigskip
-\noindent\textbf{Sustainability has been an increasingly important theme in an overarching topic about environmental sciences}
-
-(compare to biochar, which is much more recent)
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/single_topic_3_11046.pdf}
-		\caption{Word and document development of the ``Research'' dynamic topic}
-		\label{}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/single_topic_3_11020.pdf}
-		\caption{SI Word and document development of the ``Biochar'' dynamic topic}
-		\label{}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-	\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
-    \caption{SI Topic make up of a single document}
-    \label{}
-    \end{center}
-\end{figure}
-
-\bigskip
-\noindent\textbf{Physical science topics tend to be the oldest, and the most well represented topics}
-
-\bigskip
-\noindent\textbf{Adaptation and impact studies have seen a lot of growth but are well represented in IPCC reports}
-
-\bigskip
-\noindent\textbf{New topics around negative emissions and urban form are very recent and not well represented in IPCC reports.}
-
-Negative emissions in special report on 1.5, demand side chapter in AR6
-
-\section*{Discussion}
-
-\bigskip
-\noindent\textbf{Solutions, policies and science}
-
-What do policy-makers mean when they ask for more solutions
-
-\bigskip
-\noindent\textbf{Perfect representation is not necessarily desirable, but the skewedness should be known}
-
-There may be good reasons for a topic to be less prominent in IPCC discussions than in the wider scientific literature, and these reasons can only be understood and acted upon by humans, not by machine-reading.
-Nevertheless, it is desirable that assessment makers are aware of the relationship
-
-%Increase in the frequency of the use of the term ``solutions'' \citep{jabbour2017},
-
-\section*{Methods}
-\label{methods}
-
-\subsection*{Data}
-%This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of
-
-\end{linenumbers}
-
-%\end{multicols}
-
-\listoffigures
-\linespread{1}
-\bibliography{Mendeley.bib}
-\bibliographystyle{unsrt}
-
-\end{document}
-
->>>>>>> 0261e7b8054b72195fb991f1ca7947fd5b9a6b9d

### 2018-11-28 main.tex
pre-report

@@
 \usepackage{authblk}
+\usepackage{standalone}
 
@@
 
-\noindent\textbf{
-The massive expansion of scientific literature on climate change challenges the Intergovenmental Panel on Climate Change (IPCC)'s ability to assess the science according to its objectives.
-Moreover, the number and variety of papers hinders researchers of the science-policy interface from making objective judgements about those IPCC assessments.
-In this paper, we present a novel application of a machine-reading approach to model the topical content of papers on climate change.
-This dynamic topic model provides the basis for a \textit{topography} of climate change literature.
-The thematic development of the field is outlined and used to inform an analysis of the topics which are better and less well covered by IPCC reports.
-}
+\noindent\textbf{\input{abstract.tex}}
 
@@
 
-\listoffigures
-\linespread{1}
-\bibliography{Mendeley.bib}
-\bibliographystyle{unsrt}
+%\listoffigures
+%\linespread{1}
+%\bibliography{Mendeley}
+%\bibliographystyle{unsrt}
 

### 2018-11-28 code/tsne_runs.py
new graphs

@@ -39,6 +39,7 @@ def get_matrix(run_id,s_size):
 
     db_matrix = dts.filter(run_id=run_id,score__gt=0.01)
     docs = set(db_matrix.values_list('doc__id',flat=True))
+
     if s_size ==0:
         s_docs = docs
     else:
@@ -96,9 +97,13 @@ def draw_simple(results,r_ind,fname=None):
         plt.close()
 
 for run_id in [1013]:#,758]:
+    np.save("../tsne_results/data/test.npy",run_id)
+    print(run_id)
     #for s_size in [10000,20000,50000,100000,0]:
     for s_size in [100000,0]:
+        print(s_size)
         m, c_ind, r_ind = get_matrix(run_id,s_size)
+        print("got m")
         np.save(
             '../tsne_results/data/run_{}_s_{}_m.npy'.format(
                 run_id,

### 2018-11-28 abstract.tex

--- 2018-07-16 main.tex
@@
 \documentclass{article}
-\usepackage[a4paper, total={6in, 8in}]{geometry}
-\usepackage{graphicx}
-\usepackage{url}
-\usepackage{natbib}
-\usepackage{todonotes}
-\usepackage{booktabs}
-\usepackage{lineno}
-\usepackage{color}
-\usepackage{auto-pst-pdf}
-\usepackage[colaction]{multicol}
-\usepackage{caption}
-\usepackage{svg}
-
-\linespread{1.5}
-
-\makeatletter
-\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
-	\begin{flushleft}
-
-		{\huge\textbf{\@title}}
-
-		\bigskip
-
- 		{\large\textbf{\@author}}
-	\end{flushleft}\egroup
-}
-\makeatother
-
-\newcommand{\multicollinenumbers}{
-	\linenumbers
-	\def\makeLineNumber{\docolaction
-		{\makeLineNumberLeft}
-		{}
-		{\makeLineNumberRight}
-		}
-}
-
-\newenvironment{figurehere}
-	{\def\@captype{figure}}
-	{}
-
-% Title
-\title{A Topic Model of Climate Change Literature}
-\title{Words, words, words: Mapping the Matter of Climate Change Literature}
-\title{A Topography of Climate Change Research}
-\author{Max Callaghan}
 
 \begin{document}
-\maketitle
-
-\begin{linenumbers}
-
-\noindent\textbf{	
 	The massive expansion of scientific literature on climate change challenges the Intergovenmental Panel on Climate Change (IPCC)'s ability to assess the science according to its objectives.
@@
 The thematic development of the field is outlined and used to inform an analysis of the topics which are better and less well covered by IPCC reports.
-}
-
-\bigskip
-
-%\begin{multicols}{2}
-
-%\multicollinenumbers
-\bigskip
-\noindent\textbf{To deal with the wicked problem of climate change, international policy-makers need the IPCC. The IPCC as map-makers.}
-
-The IPCC sees its role as to ``assess on a comprehensive, objective, open and transparent basis the scientific, technical and socio-economic information relevant to [...] climate change'' \citep{IPCC2013}.
-Climate science is so broad, multi-disciplinary, and laden with uncertainties and values, that the role of the IPCC as assessment maker is vitally important to developing evidence-based international climate policy.
-Making maps \citep{Edenhofer2015}
-
-\bigskip
-\noindent\textbf{The task of the IPCC has become much more difficult with big literature}
-
-Further, it has been pointed out that, in the age of ``big literature'', providing assessments that are comprehensive, objective and transparent has become much more difficult \citep{Minx2017l}.
-
-When IPCC's citations constitute an ever-decreasing proportion of the totality of science on climate change, questions about the map that the IPCC reports produce become more pressing:
-
-- Is the map up to date? Is it complete? Is the perspective representative?
-
-%%%%%
-
-\bigskip
-\noindent\textbf{The IPCC, its reports and processes have been the object of study before. These are also hampered by problems of scale though}
-
-Various researchers have attempted to do empirical research on the assessment reports, and processes of inter. alia. the IPCC \citep{jabbour2017} \citep{Bjurström2011} \citep{Hulme2016}.
-
-Policy makers, when asked about their interactions with the IPCC call for a greater focus on solutions \citep{Kowarsch2017}
-
-These studies are similarly challenged by the the size of the literature. Traditional bibliometric techniques are insufficient.
-
-\bigskip
-\noindent\textbf{Some literature exists on bibliometrics and climate change, but tends not to deal with text}
-
-Bibliometrics e.g. \citep{Haunschild2016} \citep{Grieneisen2011}
-
-Text based approaches are usually of a smaller scope \citep{Grubert2016} or methodological contributions \citep{Blei2003}
-
-\bigskip
-\noindent\textbf{The scale of the problem in context}
-
-The scale of the challenge is depicted in figure \ref{growth}.
-Less than two thousand documents relevant to climate change were published before the first assessment report (see Methods for data, exclusions and processing).
-These documents contained 3,528 unique terms, each of which was used on average in 0.49\% of documents.
-In the three complete years since the publication of AR5, 128,357 documents have been published, containing 86,419 unique terms, used on average in 0.12\% of documents.
-To put this into context, the 1,189 chapters of the Bible contain a vocabulary of 11,977 unique words.
-Put another way, the 236,634 publications published in AR5 and AR6 are significantly larger than the 178,118 publications recorded in the first volume of the `Catalogue of Scientific Papers', compiled by the Royal Society to record the entirety of scientific output from 1800 to 1863 \citep{Csiszar2017}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
-		%\captionof{figure}
-		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions.
-Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period.
-The percentage of documents in which the average word occurs in is given in the key.
-		}
-		\label{growth}
-	\end{center}
-\end{figure}
-
-\bigskip
-\noindent\textbf{Machine reading to deal with scale problems in the making and assessing of maps}
-
-Clearly, if the IPCC is to continue producing comprehensive assessments, it has to engage in machine-reading in order to remain anchored to the wider literature.
-Without such an approach, it becomes harder to justify which ever-diminishing proportion of the wider literature is included in assessments.
-Similarly, it becomes harder to criticise, with quantitatively evidenced claims, the outcomes of assessment processes.
-
-\bigskip
-\noindent\textbf{Dimension reduction makes possible the description in reduced form, and with less human bias, of unmanageably large datasets}
-
-\citep{Greene2016} \citep{Lee1999}
-
-This reduced form description makes comparisons more useful, when cutting the dataset.
-
-\bigskip
-\noindent\textbf{Machine reading is a supplement to assessment-making and not free from bias; a topography is not a map}
-
-Machine reading approaches can of course not replace the task of human assessment-making.
-The contribution that could be made, though, is to pre-process the literature, producing a topographical map, used to navigate the literature while producing a more detailed assessment with human judgement.[[]] In fact this happens already - when IPCC authors search for literature on a topic, the results which appear on the search engine they use will be subject to algorithms based on the processing of millions of records of article text and metadata.
-This can be done in a much more systematic way when scientists perform directed analyses of the literature at scale.
-
-\bigskip
-\noindent\textbf{This study's contribution. Overarching themes, structure of the literature, development, relation to IPCC}
-
-This study demonstrates how dynamic topic modelling can be used to gain an overview of an otherwise unmanageably large body of literature.
-This overview, or topography, describes the thematic development of the climate change literature and, in a novelly systematic way, examines how  comprehensively the IPCC has been able to engage with it.
-In pulling together strands from text-mining, bibliometrics, and the study of science and policy, this study advances our understanding of the literature on climate change and the role of the IPCC in communicating this to policy makers.
-
-\section*{Results}
-
-\bigskip
-\noindent\textbf{A topographical map of climate change documents shows the broad structure of climate change literature}
-
-Topics cut across both disciplinary, and working group lines - but disciplinary and working group structure remains visible in the map.
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/tsne.png}
-		\caption{A map of a sample of 10,000 documents about climate change. Document positions are obtained by reducing the topic scores to two dimensions via t-SNE}
-		\label{}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/network_development_wgs_665.pdf}
-		\caption{The development of the topic-document correlation network over IPCC assessment periods.}
-		\label{}
-	\end{center}
-\end{figure}
-
-\bigskip
-\noindent\textbf{The topic-document correlation network is densest in AR2 and 3 but becomes more fragmented over time}
-
-(partly: Model less good at describing literature later on)
-
-\bigskip
-\noindent\textbf{Working groups are clustered together [dynamics], with topics like [x] containing documents across working groups and topics like [y] important network nodes}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/ipcc_representation/ipcc_rep_new665_all.pdf}
-		\caption{Representation and newness of dynamic topics}
-		\label{}
-	\end{center}
-\end{figure}
-
-\bigskip
-\noindent\textbf{Sustainability has been an increasingly important theme in an overarching topic about environmental sciences}
-
-(compare to biochar, which is much more recent)
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/single_topic_3_11046.pdf}
-		\caption{Word and document development of the ``Research'' dynamic topic}
-		\label{}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/single_topic_3_11020.pdf}
-		\caption{SI Word and document development of the ``Biochar'' dynamic topic}
-		\label{}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-	\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
-    \caption{SI Topic make up of a single document}
-    \label{}
-    \end{center}
-\end{figure}
-
-\bigskip
-\noindent\textbf{Physical science topics tend to be the oldest, and the most well represented topics}
-
-\bigskip
-\noindent\textbf{Adaptation and impact studies have seen a lot of growth but are well represented in IPCC reports}
-
-\bigskip
-\noindent\textbf{New topics around negative emissions and urban form are very recent and not well represented in IPCC reports.}
-
-Negative emissions in special report on 1.5, demand side chapter in AR6
-
-\section*{Discussion}
-
-\bigskip
-\noindent\textbf{Solutions, policies and science}
-
-What do policy-makers mean when they ask for more solutions
-
-\bigskip
-\noindent\textbf{Perfect representation is not necessarily desirable, but the skewedness should be known}
-
-There may be good reasons for a topic to be less prominent in IPCC discussions than in the wider scientific literature, and these reasons can only be understood and acted upon by humans, not by machine-reading.
-Nevertheless, it is desirable that assessment makers are aware of the relationship
-
-%Increase in the frequency of the use of the term ``solutions'' \citep{jabbour2017},
-
-\section*{Methods}
-\label{methods}
-
-\subsection*{Data}
-%This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of
-
-\end{linenumbers}
-
-%\end{multicols}
-
-\listoffigures
-\linespread{1}
-\bibliography{Mendeley.bib}
-\bibliographystyle{unsrt}
-
 \end{document}

### 2018-11-28 main.tex

@@
 %\multicollinenumbers
-\bigskip
-\noindent\textbf{To deal with the wicked problem of climate change, international policy-makers need the IPCC. The IPCC as map-makers.}
+%\bigskip
+%\noindent\textbf{To deal with the wicked problem of climate change, international policy-makers need the IPCC. The IPCC as map-makers.}
 
@@
 Climate science is so broad, multi-disciplinary, and laden with uncertainties and values, that the role of the IPCC as assessment maker is vitally important to developing evidence-based international climate policy.
-Making maps \citep{Edenhofer2015}
+In the Pragmatic Enlightened Model of the science-policy interface, the task of assessment making is a cartographic one \citep{Edenhofer2015}.
+Assessment makers map out the problem and the option space for policy-makers.
 
-\bigskip
-\noindent\textbf{The task of the IPCC has become much more difficult with big literature}
+%\bigskip
+%\noindent\textbf{The task of the IPCC has become much more difficult with big literature}
 
 Further, it has been pointed out that, in the age of ``big literature'', providing assessments that are comprehensive, objective and transparent has become much more difficult \citep{Minx2017l}.
+When the IPCC's citations constitute an ever-decreasing proportion of the totality of science on climate change, questions about the map that the IPCC reports produce become more pressing:
 
-When IPCC's citations constitute an ever-decreasing proportion of the totality of science on climate change, questions about the map that the IPCC reports produce become more pressing:
+\begin{itemize}
+	\item Is the map up to date?
+	\item Is the map complete?
+	\item Is the map's projection representative? Does it emphasise or obscure certain areas?
+\end{itemize}
 
-- Is the map up to date? Is it complete? Is the perspective representative?
+\section*{The IPCC as an object of scientific investigation}
 
@@
 
-\bigskip
-\noindent\textbf{The IPCC, its reports and processes have been the object of study before. These are also hampered by problems of scale though}
+%\bigskip
+%\noindent\textbf{The IPCC, its reports and processes have been the object of study before. These are also hampered by problems of scale though}
 
@@
 alia.
-the IPCC \citep{jabbour2017} \citep{Bjurström2011} \citep{Corbera2016} \citep{Hulme2016}.
+the IPCC \citep{jabbour2017, Bjurström2011, Corbera2016, Hulme2016}.
+Among the clear conclusions is that policy makers, when asked about their interactions with the IPCC call for a greater focus on solutions \citep{Kowarsch2017}.
+Studies that look directly at the content of IPCC reports, though, are similarly challenged by the the size of the literature that the reports assess.
+Without engaging with this literature, the conclusions drawn lack a reference point, and the phenomena identified (such as an over-representation of the natural sciences in IPCC citations \cite{Bjurström2011}) are hard to disentangle as specific to the way the IPCC assesses its literature, rather than a feature of the literature itself.
 
-Policy makers, when asked about their interactions with the IPCC call for a greater focus on solutions \citep{Kowarsch2017}
+%\bigskip
+%\noindent\textbf{Some literature exists on bibliometrics and climate change, but tends not to deal with text}
 
-These studies are similarly challenged by the the size of the literature. Traditional bibliometric techniques are insufficient.
+Some studies have attempted to identify and characterise the literature on climate change through bibliometric techniques \citep{Haunschild2016, Grieneisen2011}.
+Such studies are the jumping off point for this work, and form the basis of the identification strategy for the literature, but they do not engage with the \textit{texts} of the work identified, nor do they make the link to the IPCC.
+A growing body of scientific work deals with the unsupervised analysis of texts using topic modelling \cite{Lee1999,Blei2003, Greene2016, Roberts2013}.
+Applications to the field of climate change though are rare and often limited to closer analysis within sub-topics \cite{Grubert2017}, or calls for their greater use \cite{Grubert2016}.
 
-\bigskip
-\noindent\textbf{Some literature exists on bibliometrics and climate change, but tends not to deal with text}
+\section*{A problem of scale}
 
-Bibliometrics e.g. \citep{Haunschild2016} \citep{Grieneisen2011}
-
-Text based approaches are usually of a smaller scope \citep{Grubert2016} or methodological contributions \citep{Blei2003}
-
-\bigskip
-\noindent\textbf{The scale of the problem in context}
-
-The scale of the challenge is depicted in figure \ref{growth}.
-Less than two thousand documents relevant to climate change were published before the first assessment report (see Methods for data, exclusions and processing).
-These documents contained 3,528 unique terms, each of which was used on average in 0.49\% of documents.
-In the three complete years since the publication of AR5, 128,357 documents have been published, containing 86,419 unique terms, used on average in 0.12\% of documents.
-To put this into context, the 1,189 chapters of the Bible contain a vocabulary of 11,977 unique words.
-Put another way, the 236,634 publications published in AR5 and AR6 are significantly larger than the 178,118 publications recorded in the first volume of the `Catalogue of Scientific Papers', compiled by the Royal Society to record the entirety of scientific output from 1800 to 1863 \citep{Csiszar2017}
+%\bigskip
+%\noindent\textbf{The scale of the problem in context}
 
@@
 	\caption{Growth in climate change literature}
+	\label{growthtable}
 \end{table}
+
+The case for a greater application of text-mining approaches in understanding and assisting the IPCC is made by the scale of the challenge it faces, depicted in table \ref{growthtable}.
+Less than a thousand documents relevant to climate change were published before the first assessment report (see Methods for data, exclusions and processing).
+The abstracts of these documents contained 1,380 unique terms.
+In the three complete years since the publication of AR5, 128,266 documents have been published, containing 74,196 unique terms.
+The new words in each assessment period unearthed by a basic machine-reading of the literature already give an indication of the how the field has expanded.
+They chart the emergence of
+
+\linespread{1}
+\begin{itemize}
+	\item new compounds or materials, such as trifluoromethyl sulfur pentafluoride (SF5CF3) in AR4, or mixed matrix membranes (MMMs) in AR6
+	\item new models, or modelling approaches, such as HadCM2 in AR3, or CMIP in AR5 and AR6.
+	\item the involvement of new actors, such as NCEP (National Centers for Environmental Prediction) in AR3
+	\item new approaches, such as biochar and REDD in AR5
+	\item new applications of equipment, such as OTCs (Open-top Chambers) in AR3;
+	\item new phenomena in relation to climate change, such as zika and twitter;
+	\item and new concepts, such as CO2 fugacity (fco) in AR3
+\end{itemize}
+\linespread{1.5}
+
+%To put this into context, the 1,189 chapters of the Bible contain a vocabulary of 11,977 unique words. Put another way, 
+To put this growth into context, the 236,634 publications published in AR5 and AR6 are significantly larger than the 178,118 publications recorded in the first volume of the `Catalogue of Scientific Papers', compiled by the Royal Society to record the entirety of scientific output from 1800 to 1863 \citep{Csiszar2017}.
+In the last 10 years, climate science has produced significantly more papers than the were published across all scientific disciplines in the first half of the 19th Century.
 
@@
 
-\bigskip
-\noindent\textbf{Machine reading to deal with scale problems in the making and assessing of maps}
+%\bigskip
+%\noindent\textbf{Machine reading to deal with scale problems in the making and assessing of maps}
 
@@
 Without such an approach, it becomes harder to justify which ever-diminishing proportion of the wider literature is included in assessments.
-Similarly, it becomes harder to criticise, with quantitatively evidenced claims, the outcomes of assessment processes.
+The same arguement holds for scholars and critics of the IPCC.
+Without machine reading the literature at large, it becomes harder to analyse or criticise, with quantitatively evidenced claims, the outcomes of assessment processes.
 
-\bigskip
-\noindent\textbf{Dimension reduction makes possible the description in reduced form, and with less human bias, of unmanageably large datasets}
+%\bigskip
+%\noindent\textbf{Dimension reduction makes possible the description in reduced form, and with less human bias, of unmanageably large datasets}
 
-\citep{Greene2016} \citep{Lee1999}
+%\citep{Greene2016} \citep{Lee1999}
+In order to draw substantive messages from this high-dimensional document-word space, we apply a form of dimensionality reduction called topic-modelling \citep{Blei2010}.
+The non-negative matrix factorisation (NMF) approach to topic modelling is based on generating a ``perception of the whole based on perception of its parts'' \citep{Lee1999}.
+Here the corpus of documents (whole) is summarised by its parts (topics), which appear in varying proportions in each of the documents.
+Importantly, in such approaches, the parts are not pre-defined, but learned by the algorithm, leveraging systematic co-occurences of words within documents.
+This makes the discovery of unlooked-for features possible and can reduce the human bias risked by the pre-definition of categories.
 
-This reduced form description makes comparisons more useful, when cutting the dataset.
+%\bigskip
+%\noindent\textbf{Machine reading is a supplement to assessment-making and not free from bias; a topography is not a map}
 
-\bigskip
-\noindent\textbf{Machine reading is a supplement to assessment-making and not free from bias; a topography is not a map}
-
-Machine reading approaches can of course not replace the task of human assessment-making.
-The contribution that could be made, though, is to pre-process the literature, producing a topographical map, used to navigate the literature while producing a more detailed assessment with human judgement.[[]] In fact this happens already - when IPCC authors search for literature on a topic, the results which appear on the search engine they use will be subject to algorithms based on the processing of millions of records of article text and metadata.
+Despite these advantages, machine reading and machine learning approaches can of course not replace the task of human assessment-making.
+The contribution that could be made, though, is to pre-process the literature, producing a topographical map, used to navigate the literature while producing a more detailed assessment with human judgement.
+In fact this happens already - when IPCC authors search for literature on a topic, the results which appear on the search engine they use will be subject to algorithms based on the processing of millions of records of article text and metadata.
 This can be done in a much more systematic way when scientists perform directed analyses of the literature at scale.
 
-\bigskip
-\noindent\textbf{This study's contribution. Overarching themes, structure of the literature, development, relation to IPCC}
+%\bigskip
+%\noindent\textbf{This study's contribution. Overarching themes, structure of the literature, development, relation to IPCC}
 
-This study demonstrates how dynamic topic modelling can be used to gain an overview of an otherwise unmanageably large body of literature.
+In applying a dynamic version of NMF \cite{Greene2016}, this study demonstrates how topic modelling can be used to gain an overview of an otherwise unmanageably large body of literature.
 This overview, or topography, describes the thematic development of the climate change literature and, in a novelly systematic way, examines how comprehensively the IPCC has been able to engage with it.
@@
 
+Table \ref{top-topics} shows the 10 most prominent topics within the literature on climate change.
+The topics are characterised by the (stemmed) words that define them, and by the documents which are most well described by them.
+For example, the topic ``energi, renew, consumpt'' features the words energi, renew, consumpt,
+effici, demand,
+save, sector, sourc,
+industri, use, and best describes the documents ``Energy issues and energy priorities'' \cite{Demirbas2008} and ``Energy efficiency and CO2 emissions in Swedish manufacturing industries'' \cite{PardoMartinez2013}.
+The topics learned by dynamic NMF identify a set of interpretable topics and can identify which documents belong to these topics.
+
 \begin{table}
@@
 	\caption{Top 10 topics in climate change literature}
+	\label{top-topics}
 \end{table}
 
-\bigskip
-\noindent\textbf{A topographical map of climate change documents shows the broad structure of climate change literature}
-
-Topics cut across both disciplinary, and working group lines - but disciplinary and working group structure remains visible in the map.
+Such first results show the promise of topic modelling in the identification of studies in a thematic area, which is of high value to assessment exercises like the IPCC, but in themselves do not give a sense of the broad structure of the corpus.
+Figure \ref{map-double} projects the documents on to a two dimensional representation of the their topic composition derived through t-distributed Stochastic Network Embedding (t-SNE) \cite{vandermaaten2008}.
+In this approach, documents are positioned close to other documents with similar topic compositions.
+This projection enables us to show a topography of the whole literature on climate change.
 
@@
 		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_double.pdf}
+		\includegraphics[width=0.85\linewidth]{tsne_results/plots/run_665_s_0_p200_double.png}
 		\caption{A map of the literature on climate change.
 Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom).
-See SI table for further description}
-		\label{}
+See SI table for topic composition of each grid square}
+		\label{map-double}
 	\end{center}
 \end{figure}
+
+In the two panels of the figure, the documents are coloured by the IPCC working group which cites them (if any), and the disciplinary classification according to the Web of Science.
+The topic structure cuts across working group and disciplinary lines, but the disciplinary and working group structure is clearly visible in the topography.
+For example, in the south-eastern section of the map, we can see a concentration of documents in the social sciences that were cited by working group III (mitigation).
+
+The topography\_map\_reference.csv file in the supporting materials aids more detailed analysis of the map, describing the topic composition of each square.
+For example the square whose center is [12.5,-7.5] is made up of the topics \{energi, renew, consumpt\}, \{fuel, fossil, engin\}, \{emiss, reduct, reduc\}, \{countri, develop, trade\} and \{cost, optim, price\}, typical social science, working group III topics.
+The square whose center is [-17.5,-2.5], containing mostly working group I documents on the other hand, is made of largely by the topic {ozon, stratospher, tropospher} as well as by {increas, concentr, decreas}, and {climat, chang, impact}.
+
+%\bigskip
+%\noindent\textbf{A topographical map of climate change documents shows the broad structure of climate change literature}
 
@@
 		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_evolution.pdf}
+		\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_evolution.png}
 		\caption{The evolution of the landscape of climate change literature}
@@
 
-\begin{figure}
-	\begin{center}
-		%\includegraphics[width=1\linewidth]{plots/network_development_wgs_665.pdf}
-		\caption{The development of the topic-document correlation network over IPCC assessment periods.}
-		\label{}
-	\end{center}
-\end{figure}
+%\begin{figure}
+%	\begin{center}
+%		%\includegraphics[width=1\linewidth]{plots/network_development_wgs_665.pdf}
+%		\caption{The development of the topic-document correlation network over IPCC assessment periods.}
+%		\label{}
+%	\end{center}
+%\end{figure}
 
-\bigskip
-\noindent\textbf{The topic-document correlation network is densest in AR2 and 3 but becomes more fragmented over time}
+%\bigskip
+%\noindent\textbf{The topic-document correlation network is densest in AR2 and 3 but becomes more fragmented over time}
+%
+%(partly: Model less good at describing literature later on)
 
-(partly: Model less good at describing literature later on)
-
-\bigskip
-\noindent\textbf{Working groups are clustered together [dynamics], with topics like [x] containing documents across working groups and topics like [y] important network nodes}
+%\bigskip
+%\noindent\textbf{Working groups are clustered together [dynamics], with topics like [x] containing documents across working groups and topics like [y] important network nodes}
 

### 2019-01-22 main.tex
work on text

@@
 \usepackage{standalone}
+\usepackage[section]{placeins}
 
@@
 
-The topography\_map\_reference.csv file in the supporting materials aids more detailed analysis of the map, describing the topic composition of each square.
+The topography\_map\_reference.csv [ \url{https://github.com/mcallaghan/cc-topography/blob/master/tables/tsne_topic_index_665.csv}] file in the supporting materials aids more detailed analysis of the map, describing the topic composition of each square.
 For example the square whose center is [12.5,-7.5] is made up of the topics \{energi, renew, consumpt\}, \{fuel, fossil, engin\}, \{emiss, reduct, reduc\}, \{countri, develop, trade\} and \{cost, optim, price\}, typical social science, working group III topics.
-The square whose center is [-17.5,-2.5], containing mostly working group I documents on the other hand, is made of largely by the topic {ozon, stratospher, tropospher} as well as by {increas, concentr, decreas}, and {climat, chang, impact}.
+The square whose center is [-17.5,-2.5], containing mostly working group I (the physical science basis) documents on the other hand, is made of largely by the topic {ozon, stratospher, tropospher} as well as by {increas, concentr, decreas}, and {climat, chang, impact}.
 
@@
 %\noindent\textbf{A topographical map of climate change documents shows the broad structure of climate change literature}
+Figure \ref{map-growth} shows the evolution of the landscape of climate change literature over the 6 (including the in progress AR6) assessment periods of the IPCC.
+In each assessment period, the grid squares which contain a higher (lower) proportion of documents than in the previous assessment period are coloured green (red).
+This mapping allows us to identify topic areas as they appear in the literature.
+For example, the square with the center [-12.5,12.5] is composed largely of the topic \{coral, reef, bleach\}, and contained no documents before a sudden growth in AR3.
+Indeed, the topic of coral bleaching  was little discussed in the context of climate change before AR3, with just two out of 693 results from Web of Science for the terms  "Coral bleaching" AND "climate change" published before 1996.
+More recently, the square [12.5,12.5] identifies the topic \{biochar, amend, applic\} as a quickly emerging field within climate change in present times.
 
@@
 		\caption{The evolution of the landscape of climate change literature}
-		\label{}
+		\label{map-growth}
 	\end{center}
@@
 
+The dynamic nature of the topic model also allows us to identify changes within topics.
+SI figure \ref{sus} shows the evolution of the topic \{research, social, issu\}.
+In this overarching topic on research priorities we can detect an increasing prominence of the word ``sustainability''.
+
+Finally, by comparing the topic distribution across all documents (published before the end of AR5) with the topic distribution across documents that were cited by the IPCC, we can identify those topics which were over- or under- represented, with respect to the underlying literature, in IPCC reports.
+Figure \ref{representation} plots the representation and novelty of all topics in the model, labelling those topics most under- or over-represented.
+The topics are coloured according to the working group from which most IPCC citations to its documents came.
+
+The negative slope of the plot shows that the IPCC better represents those topics which have a longer history in the literature.
+The majority of well represented older topics come from working group I, such as \{aerosol, cloud, radiat\}.
+New topics in working group II on adaptation and vulnerability are well represented in IPCC reports.
+However, a cluster of new topics on mitigation issues appear to be under-represented by the IPCC.
+Moreover, these topics, such as those on buildings, waste, biochar, carbon capture and carbon storage are those that deal with climate solutions.
+
 \begin{figure}
@@
 		\caption{Representation and newness of dynamic topics}
-		\label{}
+		\label{representation}
 	\end{center}
@@
 
-\bigskip
-\noindent\textbf{Sustainability has been an increasingly important theme in an overarching topic about environmental sciences}
-
-(compare to biochar, which is much more recent)
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/single_topic_3_11046.pdf}
-		\caption{Word and document development of the ``Research'' dynamic topic}
-		\label{}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/single_topic_3_11020.pdf}
-		\caption{SI Word and document development of the ``Biochar'' dynamic topic}
-		\label{}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-	\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
-    \caption{SI Topic make up of a single document}
-    \label{}
-    \end{center}
-\end{figure}
-
-\bigskip
-\noindent\textbf{Physical science topics tend to be the oldest, and the most well represented topics}
-
-\bigskip
-\noindent\textbf{Adaptation and impact studies have seen a lot of growth but are well represented in IPCC reports}
-
-\bigskip
-\noindent\textbf{New topics around negative emissions and urban form are very recent and not well represented in IPCC reports.}
-
-Negative emissions in special report on 1.5, demand side chapter in AR6
+%\bigskip
+%\noindent\textbf{Sustainability has been an increasingly important theme in an overarching topic about environmental sciences}
+%
+%(compare to biochar, which is much more recent)
 
@@
 
-\bigskip
-\noindent\textbf{Solutions, policies and science}
+%\bigskip
+%\noindent\textbf{Solutions, policies and science}
+%
+%What do policy-makers mean when they ask for more solutions
 
-What do policy-makers mean when they ask for more solutions
+The results from a dynamic topic model of climate change literature delineate the structure and evolution of the field, telling its history and identifying areas of rapid growth that are of high relevance for future assessments.
+Further, they suggest that the demand by policy-makers from the IPCC for a greater focus on solutions is well-founded.
+Topics related to climate solutions are the least well represented in the IPCC's assessments.
 
-\bigskip
-\noindent\textbf{Perfect representation is not necessarily desirable, but the skewedness should be known}
-
-There may be good reasons for a topic to be less prominent in IPCC discussions than in the wider scientific literature, and these reasons can only be understood and acted upon by humans, not by machine-reading.
-Nevertheless, it is desirable that assessment makers are aware of the relationship
+%\bigskip
+%\noindent\textbf{Perfect representation is not necessarily desirable, but the skewedness should be known}
+There may well be excellent reasons for over- or under-representation of topics in IPCC reports, and indeed it is the institution of the IPCC, not machines, who can best make judgements about what to include and what not to include.
+However, it is unclear whether the decisions which resulted in such unequal distributions were made consciously, on the basis of an understanding of the breadth of the extant literature.
+For future assessments to be relevant, transparent and comprehensive in the age of big literature, these decisions should be supported by machine-supported engagement with the literature as a whole.
 
@@
 
-\section*{Methods}
-\label{methods}
+%\section*{Methods}
+%\label{methods}
+%
+%
+%
+%\subsection*{Data}
+%This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of
 
-\subsection*{Data}
-%This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of
+\pagebreak
+
+\input{methods.tex}
 

### 2019-02-28 code/tsne_runs.py
before new docs

@@ -96,9 +96,9 @@ def draw_simple(results,r_ind,fname=None):
         plt.savefig(fname)
         plt.close()
 
-for run_id in [1103,1104]:#,758]:
+for run_id in [1275]:#,758]:
     #for s_size in [10000,20000,50000,100000,0]:
-    for s_size in [0]:
+    for s_size in [50000,0]:
         print(s_size)
         m, c_ind, r_ind = get_matrix(run_id,s_size)
         print("got m")

### 2019-03-04 results.tex

--- 2018-11-28 main.tex
@@
 \documentclass{article}
-\usepackage[a4paper, total={6in, 8in}]{geometry}
+\usepackage[a4paper, total={7.5in, 10in}]{geometry}
+\geometry{paperwidth=8in, paperheight=16383pt, left=1in, top=40pt, textwidth=6in, marginparsep=20pt, marginparwidth=100pt, textheight=16263pt, footskip=40pt}
 \usepackage{graphicx}
@@
 \title{Words, words, words: Mapping the Matter of Climate Change Literature}
-\title{A Topography of Climate Change Research}
+\title{A Topography of Climate Change Research - Results}
 \author[1,2]{Max Callaghan}
@@
 
-\begin{linenumbers}
+\section{Results}
 
-\noindent\textbf{\input{abstract.tex}}
+\setcounter{totalnumber}{200}
 
-\bigskip
-
-%\begin{multicols}{2}
-
-%\multicollinenumbers
-\bigskip
-\noindent\textbf{To deal with the wicked problem of climate change, international policy-makers need the IPCC. The IPCC as map-makers.}
-
-The IPCC sees its role as to ``assess on a comprehensive, objective, open and transparent basis the scientific, technical and socio-economic information relevant to [...] climate change'' \citep{IPCC2013}.
-Climate science is so broad, multi-disciplinary, and laden with uncertainties and values, that the role of the IPCC as assessment maker is vitally important to developing evidence-based international climate policy.
-Making maps \citep{Edenhofer2015}
-
-\bigskip
-\noindent\textbf{The task of the IPCC has become much more difficult with big literature}
-
-Further, it has been pointed out that, in the age of ``big literature'', providing assessments that are comprehensive, objective and transparent has become much more difficult \citep{Minx2017l}.
-
-When IPCC's citations constitute an ever-decreasing proportion of the totality of science on climate change, questions about the map that the IPCC reports produce become more pressing:
-
-- Is the map up to date? Is it complete? Is the perspective representative?
-
-%%%%%
-
-\bigskip
-\noindent\textbf{The IPCC, its reports and processes have been the object of study before. These are also hampered by problems of scale though}
-
-Various researchers have attempted to do empirical research on the assessment reports, and processes of inter.
-alia.
-the IPCC \citep{jabbour2017} \citep{Bjurström2011} \citep{Corbera2016} \citep{Hulme2016}.
-
-Policy makers, when asked about their interactions with the IPCC call for a greater focus on solutions \citep{Kowarsch2017}
-
-These studies are similarly challenged by the the size of the literature. Traditional bibliometric techniques are insufficient.
-
-\bigskip
-\noindent\textbf{Some literature exists on bibliometrics and climate change, but tends not to deal with text}
-
-Bibliometrics e.g. \citep{Haunschild2016} \citep{Grieneisen2011}
-
-Text based approaches are usually of a smaller scope \citep{Grubert2016} or methodological contributions \citep{Blei2003}
-
-\bigskip
-\noindent\textbf{The scale of the problem in context}
-
-The scale of the challenge is depicted in figure \ref{growth}.
-Less than two thousand documents relevant to climate change were published before the first assessment report (see Methods for data, exclusions and processing).
-These documents contained 3,528 unique terms, each of which was used on average in 0.49\% of documents.
-In the three complete years since the publication of AR5, 128,357 documents have been published, containing 86,419 unique terms, used on average in 0.12\% of documents.
-To put this into context, the 1,189 chapters of the Bible contain a vocabulary of 11,977 unique words.
-Put another way, the 236,634 publications published in AR5 and AR6 are significantly larger than the 178,118 publications recorded in the first volume of the `Catalogue of Scientific Papers', compiled by the Royal Society to record the entirety of scientific output from 1800 to 1863 \citep{Csiszar2017}
-
-\begin{table}
+\begin{table}[h]
 	\scriptsize
@@
 	\caption{Growth in climate change literature}
+	\label{growthtable}
 \end{table}
 
-%\begin{figure}
-%	\begin{center}
-%		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
-%		%\captionof{figure}
-%		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions.
+\begin{figure}[h]
+	\begin{center}
+		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
+		%\captionof{figure}
+		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions.
 Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period.
 The percentage of documents in which the average word occurs in is given in the key.
-%		}
-%		\label{growth}
-%	\end{center}
-%\end{figure}
+		}
 
-\bigskip
-\noindent\textbf{Machine reading to deal with scale problems in the making and assessing of maps}
+		\label{growth}
+	\end{center}
+\end{figure}
 
-Clearly, if the IPCC is to continue producing comprehensive assessments, it has to engage in machine-reading in order to remain anchored to the wider literature.
-Without such an approach, it becomes harder to justify which ever-diminishing proportion of the wider literature is included in assessments.
-Similarly, it becomes harder to criticise, with quantitatively evidenced claims, the outcomes of assessment processes.
+\begin{figure}[h]
+	\begin{center}
+		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_double.pdf}
+		\includegraphics[width=0.85\linewidth]{tsne_results/plots/run_1275_s_0_p100_double.png}
+		\caption{A map of the literature on climate change.
+Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom).
+See SI table for topic composition of each grid square}
+		\label{map-double}
+	\end{center}
+\end{figure}
 
-\bigskip
-\noindent\textbf{Dimension reduction makes possible the description in reduced form, and with less human bias, of unmanageably large datasets}
+\begin{figure}[h!]
+	\begin{center}
+		\includegraphics[width=0.85\linewidth]{plots/ipcc_representation/ipcc_rep_oecds_time.pdf}
+		\caption{A map of the literature on climate change.
+Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom).
+See SI table for topic composition of each grid square}
+		\label{oecd_rep}
+	\end{center}
+\end{figure}
 
-\citep{Greene2016} \citep{Lee1999}
+\begin{figure}[h!]
+	\begin{center}
+		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_double.pdf}
+		\includegraphics[width=1\linewidth]{tsne_results/plots/run_1275_s_0_p100_evolution.png}
+		\caption{A map of the literature on climate change.
+Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom).
+See SI table for topic composition of each grid square}
+		\label{map-double}
+	\end{center}
+\end{figure}
 
-This reduced form description makes comparisons more useful, when cutting the dataset.
+\begin{figure}[h!]
+	\begin{center}
+		\includegraphics[width=0.85\linewidth]{plots/ipcc_representation/ipcc_rep_new1275_all.pdf}
+		\caption{A map of the literature on climate change.
+Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom).
+See SI table for topic composition of each grid square}
+		\label{ipcc_rep}
+	\end{center}
+\end{figure}
 
-\bigskip
-\noindent\textbf{Machine reading is a supplement to assessment-making and not free from bias; a topography is not a map}
-
-Machine reading approaches can of course not replace the task of human assessment-making.
-The contribution that could be made, though, is to pre-process the literature, producing a topographical map, used to navigate the literature while producing a more detailed assessment with human judgement.[[]] In fact this happens already - when IPCC authors search for literature on a topic, the results which appear on the search engine they use will be subject to algorithms based on the processing of millions of records of article text and metadata.
-This can be done in a much more systematic way when scientists perform directed analyses of the literature at scale.
-
-\bigskip
-\noindent\textbf{This study's contribution. Overarching themes, structure of the literature, development, relation to IPCC}
-
-This study demonstrates how dynamic topic modelling can be used to gain an overview of an otherwise unmanageably large body of literature.
-This overview, or topography, describes the thematic development of the climate change literature and, in a novelly systematic way, examines how  comprehensively the IPCC has been able to engage with it.
-In pulling together strands from text-mining, bibliometrics, and the study of science and policy, this study advances our understanding of the literature on climate change and the role of the IPCC in communicating this to policy makers.
-
-\section*{Results}
-
-\begin{table}
+\begin{table}[h!]
 	\scriptsize
@@
 	\caption{Top 10 topics in climate change literature}
+	\label{top-topics}
 \end{table}
 
-\bigskip
-\noindent\textbf{A topographical map of climate change documents shows the broad structure of climate change literature}
-
-Topics cut across both disciplinary, and working group lines - but disciplinary and working group structure remains visible in the map.
-
-\begin{figure}
-	\begin{center}
-		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_double.pdf}
-		\caption{A map of the literature on climate change.
-Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom).
-See SI table for further description}
-		\label{}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_evolution.pdf}
-		\caption{The evolution of the landscape of climate change literature}
-		\label{}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		%\includegraphics[width=1\linewidth]{plots/network_development_wgs_665.pdf}
-		\caption{The development of the topic-document correlation network over IPCC assessment periods.}
-		\label{}
-	\end{center}
-\end{figure}
-
-\bigskip
-\noindent\textbf{The topic-document correlation network is densest in AR2 and 3 but becomes more fragmented over time}
-
-(partly: Model less good at describing literature later on)
-
-\bigskip
-\noindent\textbf{Working groups are clustered together [dynamics], with topics like [x] containing documents across working groups and topics like [y] important network nodes}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/ipcc_representation/ipcc_rep_new665_all.pdf}
-		\caption{Representation and newness of dynamic topics}
-		\label{}
-	\end{center}
-\end{figure}
-
-\bigskip
-\noindent\textbf{Sustainability has been an increasingly important theme in an overarching topic about environmental sciences}
-
-(compare to biochar, which is much more recent)
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/single_topic_3_11046.pdf}
-		\caption{Word and document development of the ``Research'' dynamic topic}
-		\label{}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/single_topic_3_11020.pdf}
-		\caption{SI Word and document development of the ``Biochar'' dynamic topic}
-		\label{}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-	\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
-    \caption{SI Topic make up of a single document}
-    \label{}
-    \end{center}
-\end{figure}
-
-\bigskip
-\noindent\textbf{Physical science topics tend to be the oldest, and the most well represented topics}
-
-\bigskip
-\noindent\textbf{Adaptation and impact studies have seen a lot of growth but are well represented in IPCC reports}
-
-\bigskip
-\noindent\textbf{New topics around negative emissions and urban form are very recent and not well represented in IPCC reports.}
-
-Negative emissions in special report on 1.5, demand side chapter in AR6
-
-\section*{Discussion}
-
-\bigskip
-\noindent\textbf{Solutions, policies and science}
-
-What do policy-makers mean when they ask for more solutions
-
-\bigskip
-\noindent\textbf{Perfect representation is not necessarily desirable, but the skewedness should be known}
-
-There may be good reasons for a topic to be less prominent in IPCC discussions than in the wider scientific literature, and these reasons can only be understood and acted upon by humans, not by machine-reading.
-Nevertheless, it is desirable that assessment makers are aware of the relationship
-
-%Increase in the frequency of the use of the term ``solutions'' \citep{jabbour2017},
-
-\section*{Methods}
-\label{methods}
-
-\subsection*{Data}
-%This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of
-
-\end{linenumbers}
-
-%\end{multicols}
-
-%\listoffigures
-%\linespread{1}
-%\bibliography{Mendeley}
-%\bibliographystyle{unsrt}
-
 \end{document}

### 2019-03-25 code/dtm.py
new runs

@@ -1,0 +1,392 @@
+import pickle, string, numpy, getopt, sys, random, time, re, pprint, gc, resource
+import pandas as pd
+import nltk, subprocess, psycopg2, math
+from nltk.stem import SnowballStemmer
+from nltk import word_tokenize
+from multiprocess import Pool
+import django
+from functools import partial
+from sklearn.feature_extraction.text import TfidfVectorizer, CountVectorizer
+from sklearn.decomposition import NMF, LatentDirichletAllocation
+from time import time
+from django.utils import timezone
+from scipy.sparse import csr_matrix, find
+import numpy as np
+from django.core import management
+import os
+
+sys.stdout.flush()
+
+# import file for easy access to browser database
+sys.path.append('/home/galm/software/django/tmv/BasicBrowser')
+os.environ.setdefault("DJANGO_SETTINGS_MODULE", "BasicBrowser.settings")
+django.setup()
+
+
+# sys.path.append('/home/max/Desktop/django/BasicBrowser/')
+import utils.db as db
+from tmv_app.models import *
+from scoping.models import *
+from django.db import connection, transaction
+from django.db.models import Count, Sum
+from utils.text import *
+from tmv_app.utils.blei import readInfo, dtm_topic
+cursor = connection.cursor()
+
+
+def main():
+    try:
+        qid = int(sys.argv[1])
+    except:
+        qid = 6099
+    # The n in ngram
+    try:
+        K = int(sys.argv[2])
+        print(K)
+    except:
+        K = 100
+    try:
+        sample = int(sys.argv[3])
+        print(sample)
+    except:
+        sample = False
+
+    try:
+        alpha = int(sys.argv[4])
+        print(alpha)
+    except:
+        alpha = 0.2
+
+    try:
+        top_chain_var = int(sys.argv[5])
+        print(sample)
+    except:
+        top_chain_var = 0.05
+
+    try:
+        no_model = sys.argv[6]
+        no_model = True
+    except:
+        no_model = False
+
+    print("DTM")
+    dtm_path = "/home/galm/software/dtm/dtm/main"
+    call_to_blei_algorithm=True
+
+    n_features = 50000
+    n_samples = 1000
+    ng = 1
+
+    q = Query.objects.get(pk=qid)
+
+    stat = RunStats(
+        query=q,
+        method="BD",
+        alpha=alpha,
+        K=K,
+        max_features=50000,
+        top_chain_var=top_chain_var
+    )
+    stat.save()
+
+    run_id = stat.pk
+
[…]

### 2019-03-26 code/workout_AR_dtms.py
new plots

@@ -42,7 +42,7 @@ punct = set(string.punctuation)
 from nltk.corpus import wordnet as wn
 stopwords = stoplist
 
-q = Query.objects.get(pk=2355)
+q = Query.objects.get(pk=6187)
 
 def lemmatize(token, tag):
         tag = {

### 2019-04-08 results.tex
EGU presentation

@@
 \usepackage[a4paper, total={7.5in, 10in}]{geometry}
-\geometry{paperwidth=8in, paperheight=16383pt, left=1in, top=40pt, textwidth=6in, marginparsep=20pt, marginparwidth=100pt, textheight=16263pt, footskip=40pt}
+\geometry{paperwidth=10in, 
+	%paperheight=16383pt, 
+	paperheight=8100pt,
+	left=2in, top=40pt, textwidth=6in, marginparsep=20pt, marginparwidth=1.5in, %textheight=16263pt, 
+	textheight=8000pt,
+	footskip=40pt
+}
 \usepackage{graphicx}
@@
 
+\subsection{Literature growth}
+
 \begin{table}[h]
@@
 
-\begin{figure}[h]
+%\begin{figure}[h]
+%	\begin{center}
+%		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_double.pdf}
+%		\includegraphics[width=0.85\linewidth]{tsne_results/plots/run_1275_s_0_p100_double.png}
+%		\caption{A map of the literature on climate change.
+Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom).
+See SI table for topic composition of each grid square}
+%		\label{map-double}
+%	\end{center}
+%\end{figure}
+
+\subsection{Disciplinary structure}
+
+\todo{Label some topics particularly representative of certain disciplines, and their growth with reference to below}
+
+\begin{figure}[h!]
 	\begin{center}
 		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_double.pdf}
-		\includegraphics[width=0.85\linewidth]{tsne_results/plots/run_1275_s_0_p100_double.png}
+		\includegraphics[width=1\linewidth]{tsne_results/plots/run_1275_s_0_p100_oecds.png}
 		\caption{A map of the literature on climate change.
-Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom).
+Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by web of science discipline category.
 See SI table for topic composition of each grid square}
-		\label{map-double}
+		\label{map-oecd}
 	\end{center}
 \end{figure}
+
+\begin{itemize}
+	\item The thematic structure of the topics reflects journal disciplinary categories. 
+	\item Different disciplines clearly deal with different themes, although some topics are more interdisciplinary \todo{Show disciplinary entropy of topics in SI, give examples}
+	\item Medicine has the most specialized topic distribution  
+	\item (Some examples of individual topics using the labels to be added)
+\end{itemize}
+
+\bigskip
 
@@
 		\includegraphics[width=0.85\linewidth]{plots/ipcc_representation/ipcc_rep_oecds_time.pdf}
-		\caption{A map of the literature on climate change.
-Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom).
-See SI table for topic composition of each grid square}
+		\caption{The representation within the IPCC of each discipline over time}
 		\label{oecd_rep}
@@
 
+\begin{itemize}
+	\item The natural sciences have always made up the greatest share of IPCC citations and documents about climate change
+	\item The natural sciences were particularly over-represented in earlier assessment periods
+	\item contrary to what is claimed, the natural sciences are not over-represented as compared to social sciences, these are now the most over-represented
+	\item the disciplines that are under-represented are the agricultural sciences and engineering (also humanities to a small extent although they make up an extremely small share of all documents about climate change)
+	\item (some examples of topics which portray this story - the ones which will be labelled above)
+\end{itemize}
+
+\bigskip
+
+\subsection{IPCC working group structure}
+\todo{Just 4 subplots, mashing together ar1-2, and 3-4}
 \begin{figure}[h!]
@@
 		\caption{A map of the literature on climate change.
-Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom).
-See SI table for topic composition of each grid square}
-		\label{map-double}
+Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations.
+In each assessment period, the largest cluster of documents relating to each of the 10 fastest growing topics is outlined.}
+		\label{map-evolution}
+
+	\end{center}
+\end{figure}
+
+\begin{itemize}
+	\item The thematic structure is also reflected in the division of labour between IPCC working groups.
+Documents cited by each working group appear in discrete parts of the map (which correspond also to the disciplinary structure)
+	\item Some topics cut across working groups [e.g. Urban, say more about]
+	\item Some fast growing topics [e.g. health] are well represented in IPCC [WGII], whereas others (particularly on negative emissions) are not so well represented.
+
+\end{itemize}
+
+\begin{figure}[h!]
+	\begin{center}
+		\includegraphics[width=0.85\linewidth]{example-image}
+		\caption{Optional figure, instead of above, one large wg map, with the topics below labelled}
+		\label{ipcc_rep}
 	\end{center}
@@
 		\includegraphics[width=0.85\linewidth]{plots/ipcc_representation/ipcc_rep_new1275_all.pdf}
-		\caption{A map of the literature on climate change.
-Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom).
-See SI table for topic composition of each grid square}
+		\caption{The IPCC representation and age of the topics.
+Representation shows the log of the share of topic documents in IPCC citations divided by the share of topic documents among all documents.
+Assessment period occurence shows the assessment period in which the mean topic document was published}
 		\label{ipcc_rep}
@@
 \end{figure}
+
+\begin{itemize}
+	\item Those topics that deal with working group III issues (materials and recycling, negative emissions, buildings) are in general fast growing and under-represented in IPCC reports
+	\item Some working group III topics (on scenarios, on policies, and on international trade and cross country comparisons) are however over-represented in IPCC reports [see SI]
+	\item Working group I topics are in general older and better represented. Could also be same topics but new knowledge
+	\item Of the newer topics that are well represented, many are on WG III issues [detail required]
+	\item Are WGII better at reflecting changes in the literature?
+	\item Another plot showing lines for each topic showing growth in literature and growth in ipcc?
+\end{itemize}
+
+\section{SI}
+
+\begin{table}[h!]
+	\scriptsize
+	\input{tables/ipcc_shares_time.tex}
+	\caption{Top 10 topics in climate change literature}
+	\label{top-topics}
+\end{table}
 

### 2019-04-24 tables/growth_table.tex
nmf

@@
 \begin{tabular}{l p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm}} 
-&\textbf{AR1} & \textbf{AR2} & \textbf{AR3} & \textbf{AR4} & \textbf{AR5} & \textbf{AR6}\\ \hline\textbf{Documents} &625 & 7623 & 16395 & 34510 & 117758 & 128266\\ 
-\textbf{Words} &1380 & 12409 & 20453 & 32644 & 67064 & 74196\\ 
-\textbf{New words} & change (296) & loss (552) & downscaling (197) & sres (217) & biochar (1752) & mmms (192)\\ & climate (262) & efficiency (515) & degreesc (145) & petm (95) & redd (1058) & c3n4 (132)\\ & model (168) & mol (439) & ncep (130) & amf (87) & cmip5 (656) & cop21 (107)\\ & effect (160) & ambient (417) & otcs (87) & sf5cf3 (81) & cmip3 (569) & cmip6 (104)\\ & co2 (156) & coal (404) & nee (87) & cwd (74) & wrf (334) & zika (75)\\ & atmospheric (152) & photosynthetic (393) & fco (80) & embankment (72) & mofs (288) & brgdgts (71)\\ & climatic (133) & concern (381) & hadcm2 (78) & aod (69) & sdm (283) & twitter (68)\\ & global (131) & chamber (353) & dtr (75) & clc (69) & gosat (281) & jing (66)
+&\textbf{AR1} & \textbf{AR2} & \textbf{AR3} & \textbf{AR4} & \textbf{AR5} & \textbf{AR6}\\ \hline\textbf{Documents} &1167 & 8539 & 21716 & 38750 & 134413 & 201606\\ 
+\textbf{Words} &2000 & 12480 & 23346 & 34637 & 71867 & 94746\\ 
+\textbf{New words} & change (560) & oil (287) & downscaling (217) & sres (234) & biochar (1791) & mmms (313)\\ & climate (428) & deltac (283) & degreesc (187) & petm (95) & redd (1113) & cop21 (234)\\ & co2 (318) & whole (256) & ncep (130) & amf (88) & cmip5 (679) & c3n4 (214)\\ & climatic (289) & tax (254) & fco (107) & sf5cf3 (86) & cmip3 (587) & sdg (187)\\ & model (288) & landscape (249) & pfc (98) & clc (81) & mofs (299) & zika (182)\\ & atmospheric (281) & alternative (243) & otcs (98) & embankment (81) & sdm (297) & ndcs (168)\\ & effect (280) & availability (242) & dtr (95) & cwd (79) & mof (275) & indc (164)\\ & global (224) & life (239) & nee (89) & etm (75) & biochars (252) & indcs (134)
 \end{tabular}

### 2019-04-24 code/nmf.py

@@ -133,8 +133,7 @@ def main():
     stoplist.add('copyright')
 
     #docs = Doc.objects.filter(query=893,content__iregex='\w').values('UT','title','content')
-    docs = Doc.objects.filter(query=2355,content__iregex='\w') | Doc.objects.filter(query=354,content__iregex='\w')
-    docs = docs#.values('UT','content')
+    docs = Doc.objects.filter(query=6187,content__iregex='\w')
     if limit is not False:
         docs = docs[:limit]
 

### 2019-04-24 code/run_models.py

@@ -1,0 +1,42 @@
+import sys, os, django
+
+sys.path.append('/home/galm/software/django/tmv/BasicBrowser/')
+os.environ.setdefault("DJANGO_SETTINGS_MODULE", "BasicBrowser.settings")
+django.setup()
+
+from scoping.models import *
+from tmv_app.models import *
+from tmv_app.tasks import *
+
+sw = set([])
+
+sw.add('elsevier')
+sw.add('rights')
+sw.add('reserved')
+sw.add('john')
+sw.add('wiley')
+sw.add('sons')
+sw.add('copyright')
+
+q = Query.objects.get(pk=6187)
+
+for k in [100]:
+    for a in [0.01,0.05,0.1]:
+        for m in ["NM","LD"]:
+            if m=="LD":
+                alpha=a*10
+            else:
+                alpha=a
+            stat, created = RunStats.objects.get_or_create(
+                K=k,
+                alpha=alpha,
+                fancy_tokenization=True,
+                extra_stopwords=list(sw),
+                max_df=0.9,
+                max_iter=200,
+                method=m,
+                min_freq=50,
+                ngram=1,
+                query=q
+            )
+            do_nmf(stat.pk)

### 2019-04-24 code/tsne_runs.py

@@ -96,7 +96,7 @@ def draw_simple(results,r_ind,fname=None):
         plt.savefig(fname)
         plt.close()
 
-for run_id in [1429,1434]:#,758]:
+for run_id in [1771]:#,758]:
     #for s_size in [10000,20000,50000,100000,0]:
     for s_size in [0]:
         print(s_size)

### 2019-04-24 code/workout_AR_dtms.py

@@ -107,7 +107,7 @@ def fancy_tokenize(X):
 
 all_ys = range(0,100000)
 
-if "A" == "B":
+if "A" == "A":
     X = []
     vecs = []
     ars = AR.objects.filter(ar__gt=0).order_by('ar')
@@ -151,7 +151,7 @@ for ar in ars:
     print(X_y.shape)
 
 with open("tables/sizes_f_X.pickle", "wb") as f:
-    pickle.dump(X,f)
+    pickle.dump(f_X,f)
 
 with open("tables/f_vecs.pickle", "wb") as f:
-    pickle.dump(vecs,f)
+    pickle.dump(f_vecs,f)

### 2019-04-24 egu-abstract.tex

--- 2018-11-28 abstract.tex
@@
 	Moreover, the number and variety of papers hinders researchers of the science-policy interface from making objective judgements about those IPCC assessments.
+This Big Literature problem requires innovative solutions to understanding and assessing the science of climate change.
 	In this paper, we present a novel application of a machine-reading approach to model the topical content of papers on climate change.
-This dynamic topic model provides the basis for a \textit{topography} of climate change literature.
-The thematic development of the field is outlined and used to inform an analysis of the topics which are better and less well covered by IPCC reports.
+This dynamic topic model provides the basis for a \textit{topography} of the literature.
+We outline the thematic development of the field, identifying emerging topics in climate change literature, such as coral bleaching in the mid-90s or biochar more recently.
+Topics are used to analyse which areas of research are better covered by IPCC reports, uncovering an under-representation of solution-focused topics such as those on negative emissions, buildings and urban mitigation.
+
 \end{document}

### 2019-04-24 methods.tex

\documentclass{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{lineno}
\usepackage{color}
%\usepackage{auto-pst-pdf}
\usepackage[colaction]{multicol}
\usepackage{caption}
\usepackage{svg}
\usepackage{authblk}
\usepackage{standalone}
\usepackage[section]{placeins}

\makeatletter
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
	\begin{flushleft}

		{\huge\textbf{\@title}}

		\bigskip

		{\large\textbf{\@author}}

		\bigskip

		{\large{Draft current \@date}}

	\end{flushleft}\egroup
}
\makeatother

\begin{document}
	% Title
	\title{A Topic Model of Climate Change Literature}
	\title{Words, words, words: Mapping the Matter of Climate Change Literature}
	\title{A Topography of Climate Change Research - Methods}
	\author[1,2]{Max Callaghan}

	\affil[1]{Mercator Research Institute on Global Commons and Climate Change, Torgauer Straße, 10829 Berlin, Germany}
	\affil[2]{School of Earth and Environment, University of Leeds, Leeds LS2 9JT, United Kingdom}
	\maketitle
	\begin{linenumbers}

	\subsection*{Data}

	This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on the Web of Science core collection. Though not exhaustive, it gives a good coverage of the literature in major peer-reviewed journals.	Each document is assigned to an assessment period according to the timeline shown in table \ref{aryears}.

	We use the references scraped from IPCC assessment reports from \citep{Minx2017l}, and attempt to match these with the results from the web of science. Table [x] shows the percentage of IPCC citations matched in each working group for each assessment report.

	\begin{table}[htp]
		\begin{tabular}{ll}
			\toprule
			name &      years \\
			\midrule
			AR1 &  1988-1989 \\
			AR2 &  1990-1994 \\
			AR3 &  1996-2000 \\
			AR4 &  2001-2006 \\
			AR5 &  2007-2013 \\
			AR6 &      2014- \\
			\bottomrule
		\end{tabular}
		\caption{Assessment period time windows}
		\label{aryears}
	\end{table}

	\subsection*{Pre-processing}

	Data quality in earlier Web of Science results is poorer, and some documents have missing abstracts. In the quantification of the size of the literature and its vocabulary in table [], titles are substituted for abstracts where they are not available.  The words of the documents are lemmatized/stemmed, replacing different forms of the same word (i.e. word/words) with a single instance. Commonly occuring words, or ``stopwords'' are removed, as are all words shorter than 3 characters, and all words containing only punctuation or numbers.

	For each period, the documents are transformed into a document-term matrix, each row represents a document, and each column represents a unique word.  Each cell contains the number of that column's terms in that document. Only terms which occur more than once are considered.

	For the calculation of the topic model, documents with missing abstracts are ignored, and the document term matrix is transformed into a document
	frequency-inverse document frequency (tf-idf) matrix, where scores are scaled according to the frequency of their occurence in the corpus. This gives more weight to terms which appear in few documents, and less weight to those which appear in many.

	\begin{equation}
	tf(t,d) = f_{t,d} \mathrm{,}\quad idf(t,D) = \log\frac{N}{|\{d \in D:t \in d|\}}
	\end{equation}

	\subsection*{Dynamic Non-negative Matrix Factorisation}

	Non-negative Matrix Factorisation (NMF) is an approach to topic modelling which factorises the term-frequency-inverse document frequency matrix \( V \) into the matrices \(W\), the topic-term matrix, and \( H \) the document-topic matrix, whose product approximates \(V\):

	\begin{equation}
		V_{i\mu} \approx (WH)_{i\mu} = \sum_{a=1}^{r}W_{ia}H_{a\mu}
	\end{equation}

	As demonstrated in Figure \ref{doc-topic}, each topic is represented as a set of word scores, and each document a set of topic scores. The combination of the two give the word scores in the document. For clarity in the figure, these are shown as simple counts, but in the model these are scaled according to each term's frequency within the corpus.

	In Dynamic Non-negative Matrix Factorisation, proposed by Greene \cite{Greene2016}, a separate topic model is run for each period. These are then joined through another topic model, which takes the topic-term matrices of the all periods as \( V \), and produces dynamic topics, which describe the window topics according to the words which occur in them. Similar topics across and within time periods are thereby grouped together.

	While Greene uses an automatic approach to deciding on topic numbers within time periods, we found the number of topics derived from topic coherence scores (as used by Greene) to be noisy, and instead opt for  identifying (subjectively) an optimal number of topics for each window. We do this by comparing topic lists with increasing numbers of topics, where similar topics are automatically placed next to each other. We similarly compare different numbers of Dynamic topics.

	We settle on [x,x,x,x,x] topics for ARs 1 to 6, and [x] dynamic topics.

	Topics are calculated using the scikitlearn library \cite{Pedregosa2011}

	\subsubsection*{Topic Representation and Newness}

	To calculate topic representation in IPCC reports we divide each topic's share in the subsample of documents cited by IPCC reports by its share in the whole corpus.

	We calculate a dynamic topic's total score as the sum of document-dynamic topic scores (which in turn are made of the product of all document-window topic and window topic-dynamic topic scores). A dynamic topic's window score is the sum of document-dynamic scores considering only documents in the given time window. To represent a dynamic topic's newness, we multiply each assessment period number by the share of it's total score occurring in that window, and take the mean of these scores. A topic in which 100\% of documents which make it up occurred in assessment period 1 (6) would thereby receive a score of 1 (6), while a topic evenly distributed across all assessment periods would receive a score of 3.5.

	\begin{figure}
		\begin{center}
			\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
			\caption{SI Topic make up of a single document}
			\label{doc-topic}
		\end{center}
	\end{figure}

	\begin{figure}
		\begin{center}
			\includegraphics[width=1\linewidth]{plots/single_topic_3_11046.pdf}
			\caption{Word and document development of the ``Research'' dynamic topic}
			\label{sus}
		\end{center}
	\end{figure}

	\end{linenumbers}

\linespread{1}
\bibliography{Mendeley}
\bibliographystyle{unsrt}

\end{document}

### 2019-04-24 pres/2019_03_results.tex

\documentclass[9pt]{beamer}
\mode<presentation>
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric}
\usepackage{xmpmulti}
\usepackage{animate}
\usepackage{tcolorbox}
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{adjustbox}
\usepackage{todonotes}
%\usepackage{polyglossia}
\usepackage{textgreek}

\usetheme{Boadilla}
%\usecolortheme{seahorse}

\usefonttheme{professionalfonts}

\title[A Topography of Climate Research]{A Topography of Climate Change Research}
\author{Max Callaghan }
\institute[MCC]{
	\url{callaghan[at]mcc-berlin.net} \\
	\includegraphics[height=1cm,width=2cm]{MCC_Logo_RZ_rgb.jpg} \\ \medskip Mercator Research on Global Commons and Climate Change \\ School of Earth and Environment, University of Leeds
}

\newtheorem*{remark}{}

\bibliographystyle{apalike}

\begin{document}

\begin{frame}
	\titlepage
\end{frame}

\begin{frame}{Introduction}
	\begin{columns}
		\begin{column}{0.6\linewidth}
			\begin{center}
				\begin{figure}
					\includegraphics[width=1\linewidth]{../plots/Hondius_Portrait_of_map-makers}
					\caption{Portrait of map-makers, Gerard Mercator and Jodocus Hondius (Jodocus Hondius) source: Wikipedia Commons}
				\end{figure}
			\end{center}
		\end{column}
		\begin{column}{0.4\linewidth}
			\begin{center}
				\begin{itemize}
					\item<2-> Topography is a description of a landscape
					\item<3-> Topics (from the Greek \texttau\textomikron\textpi\textomikron\textvarsigma, place) can describe the features of a body of text
				\end{itemize}
			\end{center}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Outline}

\tableofcontents

\end{frame}

\section{Motivation}

\begin{frame}{Literature growth}

\begin{columns}
	\begin{column}{0.618\linewidth}
		\begin{figure}
			\includegraphics[width=\linewidth]{../plots/literature_size/pubs_time.pdf}
			\caption{Updated from \citet{Minx2017l}}
		\end{figure}
	\end{column}
	\begin{column}{0.382\linewidth}
		\begin{itemize}
			\item<2->  The Literature on climate change has grown, and continues to grow
			\item<3-> A general understanding of the literature becomes ever more difficult

		\end{itemize}
	\end{column}
\end{columns}

\end{frame}

\begin{frame}{Literature growth}

\begin{columns}
	\begin{column}{0.382\linewidth}
	\begin{itemize}
		\item<1->We entrust the IPCC with providing a \textit{comprehensive} and \textit{transparent} assessment of the literature 
		\item<2->Although IPCC reports cite ever greater numbers of papers, this number decreases in proportion to the number of papers in literature

	\end{itemize}
\end{column}
	\begin{column}{0.618\linewidth}<2->
		\begin{figure}
			\includegraphics[width=\linewidth]{../plots/wos_IPCC_shares.png}
			\caption{\citep{Minx2017l}}
		\end{figure}
	\end{column}
\end{columns}

\end{frame}

\begin{frame}{Research Questions}
\begin{itemize}
	\item<1-> What is the literature about?
	\item<2-> Does the IPCC cite some areas of the literature more than others?
\end{itemize}
\end{frame}

\section{Approach}

\begin{frame}{Data - Words, words, words}

	\begin{table}[h]
		\begin{adjustbox}{width=\linewidth}
			\input{../tables/growth_table.tex}
		\end{adjustbox}			
		\caption{Growth in climate change literature}
		\label{growthtable}
	\end{table}

%		\begin{itemize}
%			\item bla
%			
%		\end{itemize}

Data from WoS Core Collection, query following \citet{Grieneisen2011}

\end{frame}

\begin{frame}{Approach - What is the matter?}

\begin{columns}
	\begin{column}{0.382\linewidth}
		\begin{itemize}
			\item<1-> Topic modelling \citep{Blei2012} describes a suite of algorithms to discover the latent semantic content of documents
			\item<2-> NMF \citep{Lee1999} is a dimensionality reduction technique that can be used for topic modelling
			\item<3-> I follow \citet{Greene2016} in using NMF to generate static models of time windows (ARs 1-6) and a topic model of these topic models to generate dynamic topics, which describe topics across time

		\end{itemize}
	\end{column}
	\begin{column}{0.618\linewidth}<2->
		\only<2->{\(V_{i\mu} \) is a term frequency-inverse document frequency matrix of \textit{stemmed} terms} 
		\only<2->{\[V_{i\mu} \approx (WH)_{i\mu} = \sum_{a=1}^{r}W_{ia}H_{a\mu} \] \(V\) is approximated by the product of \(W\) and \(H\)}

		\begin{figure}
			\includegraphics[width=\linewidth]{../plots/VWH.png}
		\end{figure}
	\end{column}

\end{columns}

\end{frame}

\section{Results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Topics and Disciplines}
\begin{columns}
	\begin{column}{0.618\linewidth}
		\begin{figure}
			\begin{center}
				%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_double.pdf}
				\includegraphics[width=0.8\linewidth]{../tsne_results/plots/run_1429_s_0_p50_oecds.png}
				\caption{A map of the literature on climate change. Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by web of science discipline category. See SI table for topic composition of each grid square}
				\label{map-oecd}
			\end{center}
		\end{figure}
	\end{column}
	\begin{column}{0.382\linewidth}
		\begin{itemize}
			\item<2-> Corpus mainly natural sciences
			\item<3-> Topic space maps to disciplinary structure, with cross-cutting topic areas, e.g. social science and engineering

		\end{itemize}
	\end{column}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{frame}{Topics and Disciplines}
%\begin{columns}
%	\begin{column}{0.618\linewidth}
%		\begin{figure}
%			\includegraphics[width=\linewidth]{example-image}
%		\end{figure}
%	\end{column}
%	\begin{column}{0.382\linewidth}
%		\begin{itemize}
%			\item TODO: map topics to categories		
%		\end{itemize}
%	\end{column}
%\end{columns}
%\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Disciplinary representation}
\begin{columns}
	\begin{column}{0.382\linewidth}
	\begin{itemize}
		\item<1-> The social sciences are seen as under-represented in IPCC reports
		\item<3-> \citet{Bjurström2011} even name biases in IPCC citation patterns
		\item<4-> These statements are based on observed disciplinary makeup of IPCC citations

	\end{itemize}
\end{column}
	\begin{column}{0.618\linewidth}<2->
		\begin{figure}[h!]
			\begin{center}
				\includegraphics[width=0.85\linewidth]{../plots/victor.png}
				\caption{\citep{Victor2015}}
			\end{center}
		\end{figure}
	\end{column}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Disciplinary representation}
\begin{columns}
	\begin{column}{0.618\linewidth}
\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.85\linewidth]{../plots/ipcc_representation/ipcc_rep_oecds_time.pdf}
		\caption{The representation within the IPCC of each discipline over time}
		\label{oecd_rep}
	\end{center}
\end{figure}
	\end{column}
	\begin{column}{0.382\linewidth}
		\begin{itemize}
			\item<1-> Natural sciences have remained a large part of the literature and well-represented in IPCC reports. 
			\item<2-> The social sciences have long been over-represented
			\item<3-> Agricultural sciences and engineering are the most clearly under-represented (humanities make up a very small portion of the literature)

		\end{itemize}
	\end{column}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{The Social Sciences}
\begin{columns}
	\begin{column}{0.618\linewidth}
		\begin{figure}
			\includegraphics[width=\linewidth]{../plots/ipcc_representation/ipcc_rep_cats_time_Social_Sciences.pdf}
		\end{figure}
	\end{column}
	\begin{column}{0.382\linewidth}
		\begin{itemize}
			\item<1->  Economics has remained over-represented
			\item<2-> Political science and social and economic geography large under-represented literatures that have now become over-represented
			\item<3-> Sociology and Psychology remain small parts of the literature that are also under-represented

		\end{itemize}
	\end{column}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{IPCC Working Groups}
\begin{columns}
	\begin{column}{0.618\linewidth}
		\begin{figure}
		\only{
	\includegraphics[width=0.8\linewidth]{../tsne_results/plots/run_1429_s_0_p50_wgs.png}
}<1>
		\only{
		\includegraphics[width=0.8\linewidth]{../tsne_results/plots/run_1429_s_0_p50_interesting_topics_wgs.png}
		}<2->
		\label{map-wgs}
\end{figure}
	\end{column}
	\begin{column}{0.382\linewidth}
		\begin{itemize}
	\item The thematic structure is also reflected in the division of labour between IPCC working groups. Documents cited by each working group appear in discrete parts of the map (which correspond also to the disciplinary structure)

		\end{itemize}
	\end{column}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Newness and representation}
\begin{columns}
	\begin{column}{0.618\linewidth}
\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=0.85\linewidth]{../plots/ipcc_representation/ipcc_rep_new1429_all.pdf}
		\caption{The IPCC representation and age of the topics. Representation shows the log of the share of topic documents in IPCC citations divided by the share of topic documents among all documents. Assessment period occurence shows the assessment period in which the mean topic document was published}
		\label{ipcc_rep}
	\end{center}
\end{figure}
	\end{column}
	\begin{column}{0.382\linewidth}
		\begin{itemize}
			\item<2-> Those topics that deal with working group III \textit{solutions} issues (materials and recycling, negative emissions, buildings) are in general fast growing and under-represented in IPCC reports
			\item<3-> Some working group III topics (on scenarios, on policies, and on international trade and cross country comparisons) are however over-represented in IPCC reports [see SI]
			\item<4-> Working group I topics are in general older and better represented
			\item<5-> Of the newer topics that are well represented, many are on WG II issues

		\end{itemize}
	\end{column}
\end{columns}
\end{frame}

\section{Conclusions}

\begin{frame}{Conclusions}

\begin{itemize}
	\item<1-> Comparing IPCC citations to wider set of documents sheds new light on imbalances/biases within the IPCC
	\begin{itemize}
		\item Perception of lack of social science knowledge on climate change may be justified, but implications for wider research community, not just IPCC
	\end{itemize}
	\item<2-> Topic modelling enriches our understanding of the content of literature that is emerging, and that is over- or under-represented by the IPCC
	\begin{itemize}
		\item Topics suggest that policymakers' demand for ``solution'' orientated scientific assessments \citep{Kowarsch2017}, may be justified, and possible to achieve with an adjustment of IPCC focus
	\end{itemize}
	\item<3-> The IPCC, not a topic model, is in the best position to decide on what literature to cite
		\begin{itemize}
			\item But, the IPCC can best make these decisions when supported by machines to find out what is out there.
		\end{itemize}
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Bib

\begin{frame}{Bibliography}
\small
\bibliography{../Mendeley}
\end{frame}

\begin{frame}{Thanks for your attention}
\begin{columns}
	\begin{column}{0.5\linewidth}
						\begin{figure}
			\includegraphics[width=1\linewidth]{../plots/Hondius_Portrait_of_map-makers}
		\end{figure}
	\end{column}
	\begin{column}{0.5\linewidth}
			\begin{figure}
		\begin{center}
			%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_double.pdf}
			\includegraphics[width=1\linewidth]{../tsne_results/plots/run_1429_s_0_p50_oecds.png}
		\end{center}
	\end{figure}
	\end{column}
\end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Doc Topic Example}
\includegraphics[width=\linewidth]{../plots/single_doc_3_ex.pdf}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2019-04-24 code/assemble_pubs.sh
new plots

@@ -1,0 +1,17 @@
+#!/bin/bash
+
+# Args: run_id, perplexity
+
+echo "assembling plots for run $1"
+
+cp tsne_results/plots/run_$1_s_0_p$2_all_topic_words_wgs.png plots_pub/all_topic_words_wgs.png
+
+cp tsne_results/plots/run_$1_s_0_p$2_all_topic_words_wgs.png plots_pub/all_topic_words_ars.png
+
+cp tsne_results/plots/run_$1_s_0_p$2_all_topic_words_wgs.png plots_pub/all_topic_words_oecds.png
+
+cp plots/ipcc_representation/ipcc_rep_new$1_all.pdf plots_pub/ipcc_represntation.pdf
+
+cp plots/ipcc_representation/ipcc_rep_oecds_time.pdf plots_pub/ipcc_rep_oecds_time.pdf
+
+cp plots/ipcc_representation/ipcc_rep_oecds_simplified.pdf plots_pub/ipcc_rep_oecds_simplified.pdf

### 2019-04-24 code/run_models.py

@@ -19,10 +19,9 @@ sw.add('sons')
 sw.add('copyright')
 
 q = Query.objects.get(pk=6187)
-
-for k in [100]:
+for m in ["NM","LD"]:
     for a in [0.01,0.05,0.1]:
-        for m in ["NM","LD"]:
+        for k in [80,90,100,110,120,130]:
             if m=="LD":
                 alpha=a*10
             else:
@@ -39,4 +38,5 @@ for k in [100]:
                 ngram=1,
                 query=q
             )
-            do_nmf(stat.pk)
+            if created or stat.status==0:
+                do_nmf(stat.pk)

### 2019-05-06 results.tex
update writing

@@
 
-\begin{figure}[h]
-	\begin{center}
-		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
-		%\captionof{figure}
-		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions.
+%\begin{figure}[h]
+%	\begin{center}
+%		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
+%		%\captionof{figure}
+%		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions.
 Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period.
 The percentage of documents in which the average word occurs in is given in the key.
-		}
-
-		\label{growth}
-	\end{center}
-\end{figure}
+%		}
+%	
+%		\label{growth}
+%	\end{center}
+%\end{figure}
 
@@
 
+\subsection{Glossary}
+
+ncep
+fco
+pfc
+otcs
+dtr
+sres
+petm
+amf
+sf5cf3
+clc
+cwd
+etm
+cmip5
+cmip3
+mofs
+sdm
+mmms
+cop21
+c3n4
+sdg
+indc
+
 \begin{table}[h!]

### 2019-05-08 tables/growth_table_large.tex
large table

--- 2019-04-24 tables/growth_table.tex
@@
-\begin{tabular}{l p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm}} 
+\begin{tabular}{l p{2.8cm} p{2.8cm} p{2.8cm} p{2.8cm} p{2.8cm} p{2.8cm}} 
 &\textbf{AR1} & \textbf{AR2} & \textbf{AR3} & \textbf{AR4} & \textbf{AR5} & \textbf{AR6}\\ \hline\textbf{Documents} &1167 & 8539 & 21716 & 38750 & 134413 & 201606\\ 

### 2019-05-13 code/tsne_runs.py
new graphs

@@ -96,7 +96,7 @@ def draw_simple(results,r_ind,fname=None):
         plt.savefig(fname)
         plt.close()
 
-for run_id in [1810,1811,1809,1818,1817,1814]:#,758]:
+for run_id in [1861]:#,758]:
     #for s_size in [10000,20000,50000,100000,0]:
     for s_size in [0]:
         print(s_size)

### 2019-05-13 tables/growth_table.tex
adjust growth table

@@
 \begin{tabular}{l p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm}} 
-&\textbf{AR1} & \textbf{AR2} & \textbf{AR3} & \textbf{AR4} & \textbf{AR5} & \textbf{AR6}\\ \hline\textbf{Documents} &1167 & 8539 & 21716 & 38750 & 134413 & 201606\\ 
+&\textbf{AR1} & \textbf{AR2} & \textbf{AR3} & \textbf{AR4} & \textbf{AR5} & \textbf{AR6}\\ \hline\textbf{Years} &1986-1989 & 1990-1994 & 1995-2000 & 2001-2006 & 2007-2013 & 2014-\\ 
+\textbf{Documents} &1167 & 8539 & 21716 & 38750 & 134413 & 201606\\ 
 \textbf{Words} &2000 & 12480 & 23346 & 34637 & 71867 & 94746\\ 

### 2019-05-22 main.tex
before new docs
poster and writing

--- 2018-11-28 main.tex
@@
 
+\noindent We know that the scientific literature on climate change is growing rapidly \cite{Grieneisen2011}, and that this growth poses problems for the IPCC, whose task it is to provide a comprehensive and transparent summary of it \cite{Minx2017l}.
+Despite this, we know little about thematic trends within the literature, or how the IPCC performs in reflecting this growing body of knowledge on climate change.
+Understanding these trends is a crucial task if we are to assess and improve comprehensiveness in global environmental assessments.
+
+\begin{table}
+	{\scriptsize
+		\input{tables/growth_table.tex}}
+	\caption{Growth of Literature on Climate Change. A glossary of acronyms is provided in SI}
+	\label{tab}
+\end{table}
+
+Table \ref{tab} depicts the scale of the challenge to the IPCC.
+In the years since the publication of AR5, as much literature has been published as in the 30 years previously.
+Moreover, not only are more articles being published, but the vocabulary of climate knowledge has expanded.
+While the 8,539 documents published in AR2 contained 12,480 unique words, the 201,606 documents published in AR6 contain a vocabulary of 94,746 unique words.
+
+Such analysis provides a limited insight into the evolution of the literature since 1980s. We use topic modelling to produce a topographic map.  \todo{expand}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=1\linewidth]{tsne_results/plots/run_1861_s_0_p100_all_topic_words_oecds_big.png}
+		\caption{A map of the literature on climate change.
+Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by web of science discipline category.
+Topic labels are placed in the center of each of the large clusters of documents associated with each topic.
+}
+		\label{oecd_topic_map}
+	\end{center}
+\end{figure}
+
+\subsection*{Social Sciences in IPCC citations}
+
+It was argued after the fifth assessment report that the IPCC needs to do more to incorporate knowledge from the social sciences \cite{Victor2015}, and a scientometric study of the  the third assessment report claimed the IPCC gave a greater \textit{emphasis} to natural sciences and, within the social sciences, to economics.
+The study, however, operationalised disciplinary emphasis as simply the number of citations from each field.
+Here we look at \textit{representativeness}, that is, the share of IPCC citations in each field divided by the share of all climate related documents in that field.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.85\linewidth]{plots/ipcc_representation/ipcc_rep_oecds_simplified_short.pdf}
+		\caption{The representation within the IPCC of each discipline over time}
+		\label{oecd_rep}
+	\end{center}
+\end{figure}
+
+Looked at this way, we see that the social sciences were indeed under-represented in earlier assessment reports, but by the fifth assessment report were over-represented.
+Although economics was previously over-represented among social sciences, while others were under-represented, more subdisciplines of the social sciences are now over-represented.
+
 %\begin{multicols}{2}
@@
 %\multicollinenumbers
-\bigskip
-\noindent\textbf{To deal with the wicked problem of climate change, international policy-makers need the IPCC. The IPCC as map-makers.}
-
-The IPCC sees its role as to ``assess on a comprehensive, objective, open and transparent basis the scientific, technical and socio-economic information relevant to [...] climate change'' \citep{IPCC2013}.
+%\bigskip
+%\noindent\textbf{To deal with the wicked problem of climate change, international policy-makers need the IPCC. The IPCC as map-makers.}
+%
+%The IPCC sees its role as to ``assess on a comprehensive, objective, open and transparent basis the scientific, technical and socio-economic information relevant to [...] climate change'' \citep{IPCC2013}.
 Climate science is so broad, multi-disciplinary, and laden with uncertainties and values, that the role of the IPCC as assessment maker is vitally important to developing evidence-based international climate policy.
-Making maps \citep{Edenhofer2015}
-
-\bigskip
-\noindent\textbf{The task of the IPCC has become much more difficult with big literature}
-
-Further, it has been pointed out that, in the age of ``big literature'', providing assessments that are comprehensive, objective and transparent has become much more difficult \citep{Minx2017l}.
-
-When IPCC's citations constitute an ever-decreasing proportion of the totality of science on climate change, questions about the map that the IPCC reports produce become more pressing:
-
-- Is the map up to date? Is it complete? Is the perspective representative?
-
-%%%%%
-
-\bigskip
-\noindent\textbf{The IPCC, its reports and processes have been the object of study before. These are also hampered by problems of scale though}
-
-Various researchers have attempted to do empirical research on the assessment reports, and processes of inter.
+In the Pragmatic Enlightened Model of the science-policy interface, the task of assessment making is a cartographic one \citep{Edenhofer2015}.
+Assessment makers map out the problem and the option space for policy-makers.
+%
+%
+%
+%%\bigskip
+%%\noindent\textbf{The task of the IPCC has become much more difficult with big literature}
+%
+%Further, it has been pointed out that, in the age of ``big literature'', providing assessments that are comprehensive, objective and transparent has become much more difficult \citep{Minx2017l}.
+When the IPCC's citations constitute an ever-decreasing proportion of the totality of science on climate change, questions about the map that the IPCC reports produce become more pressing:
+%
+%\begin{itemize}
+%	\item Is the map up to date?
+%	\item Is the map complete?
+%	\item Is the map's projection representative? Does it emphasise or obscure certain areas?
+%\end{itemize}
+%
+%
+%\section*{The IPCC as an object of scientific investigation}
+%
+%%%%%%
+%
+%%\bigskip
+%%\noindent\textbf{The IPCC, its reports and processes have been the object of study before. These are also hampered by problems of scale though}
+%
+%Various researchers have attempted to do empirical research on the assessment reports, and processes of inter.
 alia.
-the IPCC \citep{jabbour2017} \citep{Bjurström2011} \citep{Corbera2016} \citep{Hulme2016}.
-
-Policy makers, when asked about their interactions with the IPCC call for a greater focus on solutions \citep{Kowarsch2017}
-
-These studies are similarly challenged by the the size of the literature. Traditional bibliometric techniques are insufficient.
-
-\bigskip
-\noindent\textbf{Some literature exists on bibliometrics and climate change, but tends not to deal with text}
-
-Bibliometrics e.g. \citep{Haunschild2016} \citep{Grieneisen2011}
-
-Text based approaches are usually of a smaller scope \citep{Grubert2016} or methodological contributions \citep{Blei2003}
-
-\bigskip
-\noindent\textbf{The scale of the problem in context}
-
-The scale of the challenge is depicted in figure \ref{growth}.
-Less than two thousand documents relevant to climate change were published before the first assessment report (see Methods for data, exclusions and processing).
-These documents contained 3,528 unique terms, each of which was used on average in 0.49\% of documents.
-In the three complete years since the publication of AR5, 128,357 documents have been published, containing 86,419 unique terms, used on average in 0.12\% of documents.
-To put this into context, the 1,189 chapters of the Bible contain a vocabulary of 11,977 unique words.
-Put another way, the 236,634 publications published in AR5 and AR6 are significantly larger than the 178,118 publications recorded in the first volume of the `Catalogue of Scientific Papers', compiled by the Royal Society to record the entirety of scientific output from 1800 to 1863 \citep{Csiszar2017}
-
-\begin{table}
-	\scriptsize
-	\input{tables/growth_table.tex}
-	\caption{Growth in climate change literature}
-\end{table}
-
+the IPCC \citep{jabbour2017, Bjurström2011, Corbera2016, Hulme2016}.
+Among the clear conclusions is that policy makers, when asked about their interactions with the IPCC call for a greater focus on solutions \citep{Kowarsch2017}.
+Studies that look directly at the content of IPCC reports, though, are similarly challenged by the the size of the literature that the reports assess.
+Without engaging with this literature, the conclusions drawn lack a reference point, and the phenomena identified (such as an over-representation of the natural sciences in IPCC citations \cite{Bjurström2011}) are hard to disentangle as specific to the way the IPCC assesses its literature, rather than a feature of the literature itself.
+%
+%%\bigskip
+%%\noindent\textbf{Some literature exists on bibliometrics and climate change, but tends not to deal with text}
+%
+%Some studies have attempted to identify and characterise the literature on climate change through bibliometric techniques \citep{Haunschild2016, Grieneisen2011}.
+Such studies are the jumping off point for this work, and form the basis of the identification strategy for the literature, but they do not engage with the \textit{texts} of the work identified, nor do they make the link to the IPCC.
+A growing body of scientific work deals with the unsupervised analysis of texts using topic modelling \cite{Lee1999,Blei2003, Greene2016, Roberts2013}.
+Applications to the field of climate change though are rare and often limited to closer analysis within sub-topics \cite{Grubert2017}, or calls for their greater use \cite{Grubert2016}.
+%
+%\section*{A problem of scale}
+%
+%
+%%\bigskip
+%%\noindent\textbf{The scale of the problem in context}
+%
+%\begin{table}
+%	\scriptsize
+%	\input{tables/growth_table.tex}
+%	\caption{Growth in climate change literature}
+%	\label{growthtable}
+%\end{table}
+%
+%The case for a greater application of text-mining approaches in understanding and assisting the IPCC is made by the scale of the challenge it faces, depicted in table \ref{growthtable}.
+Less than a thousand documents relevant to climate change were published before the first assessment report (see Methods for data, exclusions and processing).
+The abstracts of these documents contained 1,380 unique terms.
+In the three complete years since the publication of AR5, 128,266 documents have been published, containing 74,196 unique terms.
+The new words in each assessment period unearthed by a basic machine-reading of the literature already give an indication of the how the field has expanded.
+They chart the emergence of
+%
+%\linespread{1}
+%\begin{itemize}
+%	\item new compounds or materials, such as trifluoromethyl sulfur pentafluoride (SF5CF3) in AR4, or mixed matrix membranes (MMMs) in AR6
+%	\item new models, or modelling approaches, such as HadCM2 in AR3, or CMIP in AR5 and AR6.
+%	\item the involvement of new actors, such as NCEP (National Centers for Environmental Prediction) in AR3
+%	\item new approaches, such as biochar and REDD in AR5
+%	\item new applications of equipment, such as OTCs (Open-top Chambers) in AR3;
+%	\item new phenomena in relation to climate change, such as zika and twitter;
+%	\item and new concepts, such as CO2 fugacity (fco) in AR3
+%\end{itemize}
+%\linespread{1.5}
+%
+%
+%
+%
+%%To put this into context, the 1,189 chapters of the Bible contain a vocabulary of 11,977 unique words. Put another way, 
+%To put this growth into context, the 236,634 publications published in AR5 and AR6 are significantly larger than the 178,118 publications recorded in the first volume of the `Catalogue of Scientific Papers', compiled by the Royal Society to record the entirety of scientific output from 1800 to 1863 \citep{Csiszar2017}.
+In the last 10 years, climate science has produced significantly more papers than the were published across all scientific disciplines in the first half of the 19th Century.
+%
+%
+%
+%
+%%\begin{figure}
+%%	\begin{center}
+%%		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
+%%		%\captionof{figure}
+%%		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions.
+Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period.
+The percentage of documents in which the average word occurs in is given in the key.
+%%		}
+%%		\label{growth}
+%%	\end{center}
+%%\end{figure}
+%
+%
+%%\bigskip
+%%\noindent\textbf{Machine reading to deal with scale problems in the making and assessing of maps}
+%
+%
+%Clearly, if the IPCC is to continue producing comprehensive assessments, it has to engage in machine-reading in order to remain anchored to the wider literature.
+Without such an approach, it becomes harder to justify which ever-diminishing proportion of the wider literature is included in assessments.
+The same arguement holds for scholars and critics of the IPCC.
+Without machine reading the literature at large, it becomes harder to analyse or criticise, with quantitatively evidenced claims, the outcomes of assessment processes.
+%
+%
+%%\bigskip
+%%\noindent\textbf{Dimension reduction makes possible the description in reduced form, and with less human bias, of unmanageably large datasets}
+%
+%%\citep{Greene2016} \citep{Lee1999}
+%In order to draw substantive messages from this high-dimensional document-word space, we apply a form of dimensionality reduction called topic-modelling \citep{Blei2010}.
+The non-negative matrix factorisation (NMF) approach to topic modelling is based on generating a ``perception of the whole based on perception of its parts'' \citep{Lee1999}.
+Here the corpus of documents (whole) is summarised by its parts (topics), which appear in varying proportions in each of the documents.
+Importantly, in such approaches, the parts are not pre-defined, but learned by the algorithm, leveraging systematic co-occurences of words within documents.
+This makes the discovery of unlooked-for features possible and can reduce the human bias risked by the pre-definition of categories.
+%
+%%\bigskip
+%%\noindent\textbf{Machine reading is a supplement to assessment-making and not free from bias; a topography is not a map}
+%
+%Despite these advantages, machine reading and machine learning approaches can of course not replace the task of human assessment-making.
+The contribution that could be made, though, is to pre-process the literature, producing a topographical map, used to navigate the literature while producing a more detailed assessment with human judgement.
+In fact this happens already - when IPCC authors search for literature on a topic, the results which appear on the search engine they use will be subject to algorithms based on the processing of millions of records of article text and metadata.
+This can be done in a much more systematic way when scientists perform directed analyses of the literature at scale.
+%
+%
+%%\bigskip
+%%\noindent\textbf{This study's contribution. Overarching themes, structure of the literature, development, relation to IPCC}
+%
+%In applying a dynamic version of NMF \cite{Greene2016}, this study demonstrates how topic modelling can be used to gain an overview of an otherwise unmanageably large body of literature.
+This overview, or topography, describes the thematic development of the climate change literature and, in a novelly systematic way, examines how comprehensively the IPCC has been able to engage with it.
+In pulling together strands from text-mining, bibliometrics, and the study of science and policy, this study advances our understanding of the literature on climate change and the role of the IPCC in communicating this to policy makers.
+%
+%
+%\section*{Results}
+%
+%Table \ref{top-topics} shows the 10 most prominent topics within the literature on climate change.
+The topics are characterised by the (stemmed) words that define them, and by the documents which are most well described by them.
+For example, the topic ``energi, renew, consumpt'' features the words energi, renew, consumpt,
+%effici, demand,
+%save, sector, sourc,
+%industri, use, and best describes the documents ``Energy issues and energy priorities'' \cite{Demirbas2008} and ``Energy efficiency and CO2 emissions in Swedish manufacturing industries'' \cite{PardoMartinez2013}.
+The topics learned by dynamic NMF identify a set of interpretable topics and can identify which documents belong to these topics.
+%
+%\begin{table}
+%	\scriptsize
+%	\input{tables/top_topics.tex}
+%	\caption{Top 10 topics in climate change literature}
+%	\label{top-topics}
+%\end{table}
+%
+%Such first results show the promise of topic modelling in the identification of studies in a thematic area, which is of high value to assessment exercises like the IPCC, but in themselves do not give a sense of the broad structure of the corpus.
+Figure \ref{map-double} projects the documents on to a two dimensional representation of the their topic composition derived through t-distributed Stochastic Network Embedding (t-SNE) \cite{vandermaaten2008}.
+In this approach, documents are positioned close to other documents with similar topic compositions.
+This projection enables us to show a topography of the whole literature on climate change.
+%
 %\begin{figure}
 %	\begin{center}
-%		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
-%		%\captionof{figure}
-%		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions.
-Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period.
-The percentage of documents in which the average word occurs in is given in the key.
-%		}
-%		\label{growth}
+%		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_double.pdf}
+%		\includegraphics[width=0.85\linewidth]{tsne_results/plots/run_665_s_0_p200_double.png}
+%		\caption{A map of the literature on climate change.
+Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom).
+See SI table for topic composition of each grid square}
+%		\label{map-double}
 %	\end{center}
 %\end{figure}
-
-\bigskip
-\noindent\textbf{Machine reading to deal with scale problems in the making and assessing of maps}
-
-Clearly, if the IPCC is to continue producing comprehensive assessments, it has to engage in machine-reading in order to remain anchored to the wider literature.
-Without such an approach, it becomes harder to justify which ever-diminishing proportion of the wider literature is included in assessments.
-Similarly, it becomes harder to criticise, with quantitatively evidenced claims, the outcomes of assessment processes.
-
-\bigskip
-\noindent\textbf{Dimension reduction makes possible the description in reduced form, and with less human bias, of unmanageably large datasets}
-
-\citep{Greene2016} \citep{Lee1999}
-
-This reduced form description makes comparisons more useful, when cutting the dataset.
-
-\bigskip
-\noindent\textbf{Machine reading is a supplement to assessment-making and not free from bias; a topography is not a map}
-
-Machine reading approaches can of course not replace the task of human assessment-making.
-The contribution that could be made, though, is to pre-process the literature, producing a topographical map, used to navigate the literature while producing a more detailed assessment with human judgement.[[]] In fact this happens already - when IPCC authors search for literature on a topic, the results which appear on the search engine they use will be subject to algorithms based on the processing of millions of records of article text and metadata.
-This can be done in a much more systematic way when scientists perform directed analyses of the literature at scale.
-
-\bigskip
-\noindent\textbf{This study's contribution. Overarching themes, structure of the literature, development, relation to IPCC}
-
-This study demonstrates how dynamic topic modelling can be used to gain an overview of an otherwise unmanageably large body of literature.
-This overview, or topography, describes the thematic development of the climate change literature and, in a novelly systematic way, examines how  comprehensively the IPCC has been able to engage with it.
-In pulling together strands from text-mining, bibliometrics, and the study of science and policy, this study advances our understanding of the literature on climate change and the role of the IPCC in communicating this to policy makers.
-
-\section*{Results}
-
-\begin{table}
-	\scriptsize
-	\input{tables/top_topics.tex}
-	\caption{Top 10 topics in climate change literature}
-\end{table}
-
-\bigskip
-\noindent\textbf{A topographical map of climate change documents shows the broad structure of climate change literature}
-
-Topics cut across both disciplinary, and working group lines - but disciplinary and working group structure remains visible in the map.
-
-\begin{figure}
-	\begin{center}
-		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_double.pdf}
-		\caption{A map of the literature on climate change.
-Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom).
-See SI table for further description}
-		\label{}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_evolution.pdf}
-		\caption{The evolution of the landscape of climate change literature}
-		\label{}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		%\includegraphics[width=1\linewidth]{plots/network_development_wgs_665.pdf}
-		\caption{The development of the topic-document correlation network over IPCC assessment periods.}
-		\label{}
-	\end{center}
-\end{figure}
-
-\bigskip
-\noindent\textbf{The topic-document correlation network is densest in AR2 and 3 but becomes more fragmented over time}
-
-(partly: Model less good at describing literature later on)
-
-\bigskip
-\noindent\textbf{Working groups are clustered together [dynamics], with topics like [x] containing documents across working groups and topics like [y] important network nodes}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/ipcc_representation/ipcc_rep_new665_all.pdf}
-		\caption{Representation and newness of dynamic topics}
-		\label{}
-	\end{center}
-\end{figure}
-
-\bigskip
-\noindent\textbf{Sustainability has been an increasingly important theme in an overarching topic about environmental sciences}
-
-(compare to biochar, which is much more recent)
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/single_topic_3_11046.pdf}
-		\caption{Word and document development of the ``Research'' dynamic topic}
-		\label{}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots/single_topic_3_11020.pdf}
-		\caption{SI Word and document development of the ``Biochar'' dynamic topic}
-		\label{}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-	\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
-    \caption{SI Topic make up of a single document}
-    \label{}
-    \end{center}
-\end{figure}
-
-\bigskip
-\noindent\textbf{Physical science topics tend to be the oldest, and the most well represented topics}
-
-\bigskip
-\noindent\textbf{Adaptation and impact studies have seen a lot of growth but are well represented in IPCC reports}
-
-\bigskip
-\noindent\textbf{New topics around negative emissions and urban form are very recent and not well represented in IPCC reports.}
-
-Negative emissions in special report on 1.5, demand side chapter in AR6
-
-\section*{Discussion}
-
-\bigskip
-\noindent\textbf{Solutions, policies and science}
-
-What do policy-makers mean when they ask for more solutions
-
-\bigskip
-\noindent\textbf{Perfect representation is not necessarily desirable, but the skewedness should be known}
-
-There may be good reasons for a topic to be less prominent in IPCC discussions than in the wider scientific literature, and these reasons can only be understood and acted upon by humans, not by machine-reading.
-Nevertheless, it is desirable that assessment makers are aware of the relationship
-
-%Increase in the frequency of the use of the term ``solutions'' \citep{jabbour2017},
-
-\section*{Methods}
-\label{methods}
-
-\subsection*{Data}
-%This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of
-
+%
+%
+%In the two panels of the figure, the documents are coloured by the IPCC working group which cites them (if any), and the disciplinary classification according to the Web of Science.
+The topic structure cuts across working group and disciplinary lines, but the disciplinary and working group structure is clearly visible in the topography.
+For example, in the south-eastern section of the map, we can see a concentration of documents in the social sciences that were cited by working group III (mitigation).
+%
+%The topography\_map\_reference.csv [ \url{https://github.com/mcallaghan/cc-topography/blob/master/tables/tsne_topic_index_665.csv}] file in the supporting materials aids more detailed analysis of the map, describing the topic composition of each square.
+For example the square whose center is [12.5,-7.5] is made up of the topics \{energi, renew, consumpt\}, \{fuel, fossil, engin\}, \{emiss, reduct, reduc\}, \{countri, develop, trade\} and \{cost, optim, price\}, typical social science, working group III topics.
+The square whose center is [-17.5,-2.5], containing mostly working group I (the physical science basis) documents on the other hand, is made of largely by the topic {ozon, stratospher, tropospher} as well as by {increas, concentr, decreas}, and {climat, chang, impact}.
+%
+%%\bigskip
+%%\noindent\textbf{A topographical map of climate change documents shows the broad structure of climate change literature}
+%Figure \ref{map-growth} shows the evolution of the landscape of climate change literature over the 6 (including the in progress AR6) assessment periods of the IPCC.
+In each assessment period, the grid squares which contain a higher (lower) proportion of documents than in the previous assessment period are coloured green (red).
+This mapping allows us to identify topic areas as they appear in the literature.
+For example, the square with the center [-12.5,12.5] is composed largely of the topic \{coral, reef, bleach\}, and contained no documents before a sudden growth in AR3.
+Indeed, the topic of coral bleaching  was little discussed in the context of climate change before AR3, with just two out of 693 results from Web of Science for the terms  "Coral bleaching" AND "climate change" published before 1996.
+More recently, the square [12.5,12.5] identifies the topic \{biochar, amend, applic\} as a quickly emerging field within climate change in present times.
+%
+%\begin{figure}
+%	\begin{center}
+%		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_evolution.pdf}
+%		\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_evolution.png}
+%		\caption{The evolution of the landscape of climate change literature}
+%		\label{map-growth}
+%	\end{center}
+%\end{figure}
+%
+%
+%%\begin{figure}
+%%	\begin{center}
+%%		%\includegraphics[width=1\linewidth]{plots/network_development_wgs_665.pdf}
+%%		\caption{The development of the topic-document correlation network over IPCC assessment periods.}
+%%		\label{}
+%%	\end{center}
+%%\end{figure}
+%
+%%\bigskip
+%%\noindent\textbf{The topic-document correlation network is densest in AR2 and 3 but becomes more fragmented over time}
+%%
+%%(partly: Model less good at describing literature later on)
+%
+%%\bigskip
+%%\noindent\textbf{Working groups are clustered together [dynamics], with topics like [x] containing documents across working groups and topics like [y] important network nodes}
+%
+%The dynamic nature of the topic model also allows us to identify changes within topics.
+SI figure \ref{sus} shows the evolution of the topic \{research, social, issu\}.
+In this overarching topic on research priorities we can detect an increasing prominence of the word ``sustainability''.
+%
+%Finally, by comparing the topic distribution across all documents (published before the end of AR5) with the topic distribution across documents that were cited by the IPCC, we can identify those topics which were over- or under- represented, with respect to the underlying literature, in IPCC reports.
+Figure \ref{representation} plots the representation and novelty of all topics in the model, labelling those topics most under- or over-represented.
+The topics are coloured according to the working group from which most IPCC citations to its documents came.
+%
+%The negative slope of the plot shows that the IPCC better represents those topics which have a longer history in the literature.
+The majority of well represented older topics come from working group I, such as \{aerosol, cloud, radiat\}.
+New topics in working group II on adaptation and vulnerability are well represented in IPCC reports.
+However, a cluster of new topics on mitigation issues appear to be under-represented by the IPCC.
+Moreover, these topics, such as those on buildings, waste, biochar, carbon capture and carbon storage are those that deal with climate solutions.
+%
+%
+%\begin{figure}
+%	\begin{center}
+%		\includegraphics[width=1\linewidth]{plots/ipcc_representation/ipcc_rep_new665_all.pdf}
+%		\caption{Representation and newness of dynamic topics}
+%		\label{representation}
+%	\end{center}
+%\end{figure}
+%
+%
+%%\bigskip
+%%\noindent\textbf{Sustainability has been an increasingly important theme in an overarching topic about environmental sciences}
+%%
+%%(compare to biochar, which is much more recent)
+%
+%
+%
+%
+%\section*{Discussion}
+%
+%%\bigskip
+%%\noindent\textbf{Solutions, policies and science}
+%%
+%%What do policy-makers mean when they ask for more solutions
+%
+%The results from a dynamic topic model of climate change literature delineate the structure and evolution of the field, telling its history and identifying areas of rapid growth that are of high relevance for future assessments.
+Further, they suggest that the demand by policy-makers from the IPCC for a greater focus on solutions is well-founded.
+Topics related to climate solutions are the least well represented in the IPCC's assessments.
+%
+%%\bigskip
+%%\noindent\textbf{Perfect representation is not necessarily desirable, but the skewedness should be known}
+%There may well be excellent reasons for over- or under-representation of topics in IPCC reports, and indeed it is the institution of the IPCC, not machines, who can best make judgements about what to include and what not to include.
+However, it is unclear whether the decisions which resulted in such unequal distributions were made consciously, on the basis of an understanding of the breadth of the extant literature.
+For future assessments to be relevant, transparent and comprehensive in the age of big literature, these decisions should be supported by machine-supported engagement with the literature as a whole.
+%
+%
+%%Increase in the frequency of the use of the term ``solutions'' \citep{jabbour2017},
+%
+%%\section*{Methods}
+%%\label{methods}
+%%
+%%
+%%
+%%\subsection*{Data}
+%%This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of
+%
+%\pagebreak
+%
+%
+%\input{methods.tex}
+%
+%
 \end{linenumbers}
@@
 %\listoffigures
-%\linespread{1}
-%\bibliography{Mendeley}
-%\bibliographystyle{unsrt}
+\linespread{1}
+\bibliography{Mendeley}
+\bibliographystyle{unsrt}
 

### 2019-05-22 methods.tex
poster and writing

@@
 	This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on the Web of Science core collection.
-Though not exhaustive, it gives a good coverage of the literature in major peer-reviewed journals.	Each document is assigned to an assessment period according to the timeline shown in table \ref{aryears}.
+Though not exhaustive, it gives a good coverage of the literature in major peer-reviewed journals.	Each document is assigned to an assessment period according to the timeline shown in table 1.
 
@@
 Table [x] shows the percentage of IPCC citations matched in each working group for each assessment report.
-
-	\begin{table}[htp]
-		\begin{tabular}{ll}
-			\toprule
-			name &      years \\
-			\midrule
-			AR1 &  1988-1989 \\
-			AR2 &  1990-1994 \\
-			AR3 &  1996-2000 \\
-			AR4 &  2001-2006 \\
-			AR5 &  2007-2013 \\
-			AR6 &      2014- \\
-			\bottomrule
-		\end{tabular}
-		\caption{Assessment period time windows}
-		\label{aryears}
-	\end{table}
 
@@
 
-	\subsection*{Dynamic Non-negative Matrix Factorisation}
+	\subsection*{Non-negative Matrix Factorisation}
 
@@
 
-	In Dynamic Non-negative Matrix Factorisation, proposed by Greene \cite{Greene2016}, a separate topic model is run for each period.
+%	In Dynamic Non-negative Matrix Factorisation, proposed by Greene \cite{Greene2016}, a separate topic model is run for each period.
 These are then joined through another topic model, which takes the topic-term matrices of the all periods as \( V \), and produces dynamic topics, which describe the window topics according to the words which occur in them.
 Similar topics across and within time periods are thereby grouped together.
-
-	While Greene uses an automatic approach to deciding on topic numbers within time periods, we found the number of topics derived from topic coherence scores (as used by Greene) to be noisy, and instead opt for  identifying (subjectively) an optimal number of topics for each window.
+%	
+%	While Greene uses an automatic approach to deciding on topic numbers within time periods, we found the number of topics derived from topic coherence scores (as used by Greene) to be noisy, and instead opt for  identifying (subjectively) an optimal number of topics for each window.
 We do this by comparing topic lists with increasing numbers of topics, where similar topics are automatically placed next to each other.
 We similarly compare different numbers of Dynamic topics.
-
-	We settle on [x,x,x,x,x] topics for ARs 1 to 6, and [x] dynamic topics.
+%	
+%	We settle on [x,x,x,x,x] topics for ARs 1 to 6, and [x] dynamic topics.
 
@@
 
-	We calculate a dynamic topic's total score as the sum of document-dynamic topic scores (which in turn are made of the product of all document-window topic and window topic-dynamic topic scores).
-A dynamic topic's window score is the sum of document-dynamic scores considering only documents in the given time window.
+	We calculate a topic's total score as the sum of document-topic scores.
+A topic's window score is the sum of document-topic scores considering only documents in the given time window.
 To represent a dynamic topic's newness, we multiply each assessment period number by the share of it's total score occurring in that window, and take the mean of these scores.
@@
 
-	\begin{figure}
-		\begin{center}
-			\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
-			\caption{SI Topic make up of a single document}
-			\label{doc-topic}
-		\end{center}
-	\end{figure}
+%	\begin{figure}
+%		\begin{center}
+%			\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
+%			\caption{SI Topic make up of a single document}
+%			\label{doc-topic}
+%		\end{center}
+%	\end{figure}
 
-	\begin{figure}
-		\begin{center}
-			\includegraphics[width=1\linewidth]{plots/single_topic_3_11046.pdf}
-			\caption{Word and document development of the ``Research'' dynamic topic}
-			\label{sus}
-		\end{center}
-	\end{figure}
+%	\begin{figure}
+%		\begin{center}
+%			\includegraphics[width=1\linewidth]{plots/single_topic_3_11046.pdf}
+%			\caption{Word and document development of the ``Research'' dynamic topic}
+%			\label{sus}
+%		\end{center}
+%	\end{figure}
 

### 2019-05-22 poster/baposter.tex
poster and writing

% --------------------------------------------------------------------------- %
% Poster for the ECCS 2011 Conference about Elementary Dynamic Networks.      %
% --------------------------------------------------------------------------- %
% Created with Brian Amberg's LaTeX Poster Template. Please refer for the     %
% attached README.md file for the details how to compile with `pdflatex`.     %
% --------------------------------------------------------------------------- %
% $LastChangedDate:: 2011-09-11 10:57:12 +0200 (V, 11 szept. 2011)          $ %
% $LastChangedRevision:: 128                                                $ %
% $LastChangedBy:: rlegendi                                                 $ %
% $Id:: poster.tex 128 2011-09-11 08:57:12Z rlegendi                        $ %
% --------------------------------------------------------------------------- %
\documentclass[a0paper,portrait]{baposter}

\usepackage{relsize}		% For \smaller
\usepackage{url}			% For \url
\usepackage{epstopdf}	% Included EPS files automatically converted to PDF to include with pdflatex

\usepackage{multicol}

%%% Global Settings %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\graphicspath{{pix/}}	% Root directory of the pictures 
\tracingstats=2			% Enabled LaTeX logging with conditionals

%%% Color Definitions %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\definecolor{bordercol}{RGB}{40,40,40}
\definecolor{headercol1}{HTML}{DEEEB2}
\definecolor{headercol2}{RGB}{80,80,80}
\definecolor{headerfontcol}{RGB}{0,0,0}
\definecolor{boxcolor}{HTML}{f0f0f0}

%\definecolor{orange}{HTML}{FF7F00}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Utility functions %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Save space in lists. Use this after the opening of the list %%%%%%%%%%%%%%%%
\newcommand{\compresslist}{
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Document Start %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\typeout{Poster rendering started}

%%% Setting Background Image %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\background{
%	\begin{tikzpicture}[remember picture,overlay]%
%	\draw (current page.north west)+(-2em,2em) node[anchor=north west]
%	{\includegraphics[height=1.1\textheight]{background}};
%	\end{tikzpicture}
}

%%% General Poster Settings %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%% Eye Catcher, Title, Authors and University Images %%%%%%%%%%%%%%%%%%%%%%
\begin{poster}{
	grid=false,
	% Option is left on true though the eyecatcher is not used. The reason is
	% that we have a bit nicer looking title and author formatting in the headercol
	% this way
	%eyecatcher=false, 
	borderColor=bordercol,
	headerColorOne=headercol1,
	headerColorTwo=headercol2,
	headerFontColor=headerfontcol,
	% Only simple background color used, no shading, so boxColorTwo isn't necessary
	boxColorOne=boxcolor,
	headershade=plain,
	boxColorTwo=green,
	headershape=roundedright,
	headerfont=\Large\sf\bf,
	textborder=rectangle,
	background=user,
%  	boxshade=shade-lr,
  	headerborder=closed
}
%%% Eye Cacther %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
	Eye Catcher, empty if option eyecatcher=false - unused
}
%%% Title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\sf\bf
	A Topography of Climate Change Literature
}
%%% Authors %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
	\vspace{0.8em} Max Callaghan\\
	{\smaller callaghan@mcc-berlin.net}
}
%%% Logo %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
% The logos are compressed a bit into a simple box to make them smaller on the result
\setlength\fboxsep{0pt}
\setlength\fboxrule{0.5pt}
	\fbox{
		\begin{minipage}{14em}
			\begin{minipage}{7em}
				\centering
			\vspace*{0.005\textheight}
			\includegraphics[width=6.5em]{../pres/MCC_Logo_RZ_rgb.jpg}
			\\
			\vspace*{0.005\textheight}
			\includegraphics[width=6.5em]{../pres/University_of_Leeds_Logo.png}
			\vspace*{0.005\textheight}
			\end{minipage}
			\begin{minipage}{7em}
				\centering
			\includegraphics[width=6.5em]{../pres/logo_hbs.jpg}
			\end{minipage}
		\end{minipage}
	}
}

\headerbox{Problem}{name=problem,column=0,row=0}{

\includegraphics[width=\linewidth]{../plots/literature_size/pubs_time}

Massive growth of literature on climate change challenges IPCC \cite{Minx2017l}

}

\headerbox{Proportionality}{name=definitions,column=0,below=problem}{
\begin{center}
	\includegraphics[width=0.98\linewidth]{../plots/ipcc_representation/ipcc_rep_oecds_simplified_short.pdf}
\end{center}
\vspace{-1.4em} 
Contrary to suggestions/previously \cite{Victor2015, Bjurström2011}, the social sciences are over-represented in IPCC reports, engineering/agricultural sciences are under-represented
}

\headerbox{Supply/Demand of Solutions}{name=models,column=0,below=definitions}{

\begin{center}
	\includegraphics[width=0.98\linewidth]{../plots/ipcc_representation/ipcc_rep_new1771_all.pdf}
\end{center}

Physical science topics are well represented and have been around longer. Solution-oriented topics, particularly in WGIII are newer and under-represented.

}

\headerbox{References}{name=references,column=0,below=models}{
\tiny												% Make the whole text smaller
\vspace{-0.4em} 										% Save some space at the beginning
\bibliographystyle{plain}							% Use plain style
\renewcommand{\section}[2]{\vskip 0.05em}		% Omit "References" title
\smaller
\bibliography{../Mendeley}
}

\headerbox{Acknowledgements}{name=acknowledgements,column=0,below=references, above=bottom}{
\smaller						% Make the whole text smaller
%\vspace{-0.4em}			% Save some space at the beginning
This research is funded by a PhD scholarship from the Heinrich Böll Stiftung
}

\headerbox{New Concepts}{name=concepts,span=2,column=1,row=0}{
	{\scriptsize
	\input{../tables/growth_table.tex}}

	A simple analysis of the words in the documents about climate change shows us that not only are there more articles, they discuss \textbf{new concepts}. The \textbf{topic model} below \cite{Lee1999} mobilises large patterns of words in documents to make broad conceptual developments and differences comprehensible.
}

\headerbox{A Topographic Map of 400,000 Climate Change Articles}{name=density,span=2,column=1,below=concepts}{

\begin{minipage}{0.74\linewidth}
	\begin{center}
	\includegraphics[width=1\linewidth]{../tsne_results/plots/run_1771_s_0_p200_all_topic_words_oecds_big.png}
	\end{center}
\end{minipage}
\begin{minipage}{0.24\linewidth}
	Using T-SNE \cite{vandermaaten2008}, we can project each document into a 2D space such that documents with similar 100-dimensional topic vectors are close together.

	\medskip

	 Documents similar in topic tend to be from similar disciplines, with some cross-disciplinary work around the energy system, or on soils.

	 \medskip

	 The majority of topics are from the natural sciences
\end{minipage}
%\begin{minipage}{0.3\linewidth}
%\end{minpage}

}

\headerbox{Evolution }%Interdisciplinarity}
{name=degreeDistribution,span=1,column=1,below=density,above=bottom}{

\begin{center}
	\includegraphics[width=0.98\linewidth]{../tsne_results/plots/run_1771_s_0_p200_evolution_4.png}
\end{center}

Solutions topics have grown fast in recent assessment reports, as have topics on impacts and vulnerability. New WGII topics are better covered by IPCC reports. We can also witness the emergence of new topics such as coral bleaching.

}

\headerbox{Social Science \& Solutions}
{name=socSciSol,span=1,column=2,below=density}{
	\begin{center}
		\includegraphics[width=0.98\linewidth]{../plots/run_1771_wg3_socsci.pdf}
	\end{center}
	\vspace{-1.4em}
Those WGIII topics with a higher share of social science documents are better-represented in IPCC. Either the IPCC must engage with the social science literature, or the social sciences must cover solutions-topics.
}

\headerbox{Further work}
{name=further,span=1,column=2,below=socSciSol,above=bottom}{

Computer-assisted systematic map of climate impacts.

Quantification of knowledge transfer pyramid.

Tools/methodologies for computer assisted evidence synthesis.

}

\end{poster}
\end{document}

### 2019-05-22 poster/literatur.tex
poster and writing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Literaturverzeichnis

%\begin{übler Trick um die Orinalüberschrift zu unterdrücken}
\vspace*{1cm}
      \begin{center} \textbf{\Large Literatur} \end{center}
\vspace*{-4.5cm}
%\end{übler Trick}

\renewcommand{\baselinestretch}{1.05}\small\normalsize
\begin{thebibliography}{9}
\bibitem{drp} \textsc{C. Tam \& J. Webb,} ``Dispersion-Relation-Preserving Finite Difference Schemes for Computational Acoustics'', \textsl{J. Comput. Phys.} 107, 1993.

\bibitem{lddrk} \textsc{F. Q. Hu, M. Y. Hussani \& J. L. Manthey,}  ``Low-Dissipation and -Dispersion Runge-Kutta Schemes for Computational Acoustics'',  \textsl{J. Comput. Phys.} 124(1), 1996.

\bibitem{shortwave} \textsc{C.K.W. Tam, J.C. Webb \& Z. Dong,} ``A study of the short wave components in computational acoustics'', \textsl{J. Comput. Acoust.} 1, 1993.

\bibitem{hamilton} \textsc{Hamilton \& Blackstock}, \textit{Nonlinear Acoustics}, Academic Press, 1997.

\bibitem{blackstock} \textsc{Blackstock \& Hamilton}, \textit{Nonlinear Acoustics}, Academic Press, 1997.
\end{thebibliography}

### 2019-05-22 poster/texta.tex
poster and writing

      \begin{center} \textbf{\Large Abschnitt A} \end{center}
Zkjkl \cite{blackstock} kljlödksjf iouepoitueoiut ölakösdlkfj  uopweuroiwe eri iweuro wiueoweor 
ioruwerilkvklvmkl meio difji ifjeoij  ijfiowej. Zkjkl kljlödksjf iouepoitueoiut 
ölakösdlkfj  uopweuroiwe eri iweuro wiueoweor ioruwerilkvklvmkl meio difji ifjeoij
  ijfiowej. Zkjkl kljlödksjf iouepoitueoiut ölakösdlkfj  uopweuroiwe eri iweuro
 wiueoweor ioruwerilkvklvmkl meio difji ifjeoij  ijfiowej. Zkjkl kljlödksjf 
iouepoitueoiut ölakösdlkfj

Zlakösdlkfj \cite{drp} uopweuroiwe eri iweuro wiueoweor ioruwerilkvklvmkl meio difji ifjeoij  
kwjheorw jsku3w48oi9 jhk9 r98 jkhkf fdgre.
A lkdso dlksloiio  lsdo lwflkweklf offeowlkd io kdjfljweoie sdkfowpe
kwjheorw jsku3w48oi9 jhk9 r98 jkhkf \cite{drp} fdgre.

### 2019-05-22 poster/textb.tex
poster and writing

      \begin{center} \textbf{\Large Abschnitt B} \end{center}
Zkjkl \cite{blackstock} kljlödksjf iouepoitueoiut ölakösdlkfj  uopweuroiwe eri iweuro wiueoweor 
ioruwerilkvklvmkl meio difji ifjeoij  ijfiowej. Zkjkl kljlödksjf iouepoitueoiut 
ölakösdlkfj  uopweuroiwe eri iweuro wiueoweor ioruwerilkvklvmkl meio difji ifjeoij
  ijfiowej. Zkjkl kljlödksjf iouepoitueoiut ölakösdlkfj  uopweuroiwe eri iweuro
 wiueoweor ioruwerilkvklvmkl meio difji ifjeoij  ijfiowej. Zkjkl kljlödksjf 
iouepoitueoiut ölakösdlkfj

uopweuroiwe eri iweuro wiueoweor ioruwerilkvklvmkl meio difji ifjeoij  ijfiowej. 
Zkjkl kljlödksjf iouepoitueoiut ölakösdlkfj  uopweuroiwe eri iweuro wiueoweor 
ioruwerilkvklvmkl meio difji ifjeoij  ijfiowej. Zkjkl kljlödksjf iouepoitueoiut 
ölakösdlkfj  uopweuroiwe eri iweuro wiueoweor ioruwerilkvklvmkl meio difji ifjeoij

ijfiowej. Zkjkl kljlödksjf iouepoitueoiut ölakösdlkfj  uopweuroiwe eri iweuro 
wiueoweor ioruwerilkvklvmkl meio difji ifjeoij  ijfiowej. Zkjkl kljlödksjf 
iouepoitueoiut ölakösdlkfj  kl kljlödksjf iouepoit.
A lkdso dlksloiio  lsdo lwflkweklf offeowlkd io iojoiojoi kdjfljweoie sdkfowpe
kslduoiwue9874 930875  hjfojd 3489 ölkj ölkj0ppooi4 44 kldjfljowi lskdjfoi 
kwjheorw jsku3w48oi9 jhk9 r98 jkhkf fdgre.
A lkdso dlksloiio  lsdo lwflkweklf offeowlkd io kdjfljweoie sdkfowpe
kwjheorw jsku3w48oi9 jhk9 r98 jkhkf \cite{drp} fdgre.
\begin{center}
\begin{picture}(\spaltenbreite, 12.3)
  \put(4.8,1.6){\includegraphics[width=0.2\textwidth,height=0.13\textwidth]{dummy}}
  \put(0.2,0.3){\parbox{720pt}{{\bf \small Abb. 1:} \small Vergleich der physikalischen und numerischen Wellenzahl}}
%\input{ruler}
\end{picture}
\end{center}

### 2019-05-22 results.tex
poster and writing

@@
 \linespread{1.5}
+
+\bibliographystyle{apalike}
 
@@
 
+The literature on climate change has grown rapidly \citep{Grieneisen2011}.
+The implications for the IPCC are discussed in \citep{Minx2017l}.
+Since that study's publication, growth has continued (see SI figure x.)
+
+Not only are more articles being published, the range of themes being discussed in the context of climate change (see for example recently zika and biochar, which were not to be found at all before ARs 6 and 5 respectively) has expanded.
+
 \begin{table}[h]
@@
 \end{table}
+
+Topic modelling helps us to map out the literature, and make sense of broad patterns in the distribution of documents and their words.
+In this way, we can answer questions about the growth of the climate change literature, and its representation in IPCC assessment reports.
+The answers to these questions can help inform IPCC processes, and understand how the IPCC functions.
 
@@
 
-\subsection{Disciplinary structure}
+\subsection{Topic structure of literature maps to broad disciplinary categories}
 
-\todo{Label some topics particularly representative of certain disciplines, and their growth with reference to below}
+%\todo{Label some topics particularly representative of certain disciplines, and their growth with reference to below}
 
@@
 		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_double.pdf}
-		\includegraphics[width=1\linewidth]{tsne_results/plots/run_1275_s_0_p100_oecds.png}
+		\includegraphics[width=1\linewidth]{tsne_results/plots/run_1771_s_0_p200_all_topic_words_oecds.png}
 		\caption{A map of the literature on climate change.
@@
 	\item Different disciplines clearly deal with different themes, although some topics are more interdisciplinary \todo{Show disciplinary entropy of topics in SI, give examples}
-	\item Medicine has the most specialized topic distribution  
-	\item (Some examples of individual topics using the labels to be added)
+	%\item Medicine has the most specialized topic distribution  
+	\item Topics in the south of the map (coal, oil, gas, cement, power) show a strong mix of social sciences and engineering
 \end{itemize}
@@
 
+\subsection{Contrary to suggestions, the social sciences are over-represented in IPCC reports, while agricultural sciences and engineering are under-represented}
+
+\citep{Bjurström2011} and \citep{Victor2015} point to an under-representation of social science literature within the IPCC, and a dominance of the natural sciences
+
 \begin{figure}[h!]
 	\begin{center}
-		\includegraphics[width=0.85\linewidth]{plots/ipcc_representation/ipcc_rep_oecds_time.pdf}
+		\includegraphics[width=0.85\linewidth]{plots/ipcc_representation/ipcc_rep_oecds_simplified.pdf}
 		\caption{The representation within the IPCC of each discipline over time}
@@
 	\item The natural sciences have always made up the greatest share of IPCC citations and documents about climate change
-	\item The natural sciences were particularly over-represented in earlier assessment periods
-	\item contrary to what is claimed, the natural sciences are not over-represented as compared to social sciences, these are now the most over-represented
-	\item the disciplines that are under-represented are the agricultural sciences and engineering (also humanities to a small extent although they make up an extremely small share of all documents about climate change)
-	\item (some examples of topics which portray this story - the ones which will be labelled above)
+	\item The ratio of these two proportions tells us whether a certain discipline is over-represented or under-represented
+	\item The natural are indeed slightly over-represented
+	\item Although the Social sciences were under-represented in the past, by AR5, they were the most over-represented discipline
+
 \end{itemize}
@@
 
-\subsection{IPCC working group structure}
-\todo{Just 4 subplots, mashing together ar1-2, and 3-4}
+\subsection{Solution oriented topics have seen rapid growth, which has not been matched by coverage in the IPCC}
+
+The topic model allows us to dig deeper into the content of the types of documents which are under-represented in the IPCC, as well as helping us understand how the thematic structure of the literature has developed.
+
+%\todo{Just 4 subplots, mashing together ar1-2, and 3-4}
 \begin{figure}[h!]
@@
 		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_double.pdf}
-		\includegraphics[width=1\linewidth]{tsne_results/plots/run_1275_s_0_p100_evolution.png}
+		\includegraphics[width=1\linewidth]{tsne_results/plots/run_1771_s_0_p200_evolution_4.png}
 		\caption{A map of the literature on climate change.
@@
 Documents cited by each working group appear in discrete parts of the map (which correspond also to the disciplinary structure)
-	\item Some topics cut across working groups [e.g. Urban, say more about]
-	\item Some fast growing topics [e.g. health] are well represented in IPCC [WGII], whereas others (particularly on negative emissions) are not so well represented.
+	\item A number of different patterns of growth are visible.
+Adsorption was a fast growing topic in AR5, but had few IPCC citations, while risk and adaptation were fast growing, with many WGII citations
+
+	%\item Some fast growing topics [e.g. health] are well represented in IPCC [WGII], whereas others (particularly on negative emissions) are not so well represented.
 
@@
 
-\begin{figure}[h!]
-	\begin{center}
-		\includegraphics[width=0.85\linewidth]{example-image}
-		\caption{Optional figure, instead of above, one large wg map, with the topics below labelled}
-		\label{ipcc_rep}
-	\end{center}
-\end{figure}
+%\begin{figure}[h!]
+%	\begin{center}
+%		\includegraphics[width=0.85\linewidth]{example-image}
+%		\caption{Optional figure, instead of above, one large wg map, with the topics below labelled}
+%		\label{ipcc_rep}
+%	\end{center}
+%\end{figure}
+
+\bigskip
+
+\noindent By plotting each topic's newness and IPCC representation, we can dig down into the types of topics which are over or under represented
 
@@
 	\begin{center}
-		\includegraphics[width=0.85\linewidth]{plots/ipcc_representation/ipcc_rep_new1275_all.pdf}
+		\includegraphics[width=0.85\linewidth]{plots/ipcc_representation/ipcc_rep_new1771_all.pdf}
 		\caption{The IPCC representation and age of the topics.
@@
 \begin{itemize}
-	\item Those topics that deal with working group III issues (materials and recycling, negative emissions, buildings) are in general fast growing and under-represented in IPCC reports
-	\item Some working group III topics (on scenarios, on policies, and on international trade and cross country comparisons) are however over-represented in IPCC reports [see SI]
-	\item Working group I topics are in general older and better represented. Could also be same topics but new knowledge
-	\item Of the newer topics that are well represented, many are on WG III issues [detail required]
-	\item Are WGII better at reflecting changes in the literature?
-	\item Another plot showing lines for each topic showing growth in literature and growth in ipcc?
+	\item Those topics that deal with working group III issues (negative emissions, buildings) are in general fast growing and under-represented in IPCC reports
+	%\item Some working group III topics (on scenarios, on policies, and on international trade and cross country comparisons) are however over-represented in IPCC reports [see SI]
+	\item Working group I topics are in general older and better represented. 
+	\item Of the newer topics that are well represented, many are on WG II issues 
+	%\item Are WGII better at reflecting changes in the literature?
+	%\item Another plot showing lines for each topic showing growth in literature and growth in ipcc?
 \end{itemize}
 
+Within working group III, those topics which have more citations from the social sciences are better represented (SI figure x.) These are general topics about policy options, and international politics.
+Those topics which are not well represented are on specific solutions, such as vehicles, buildings, and negative emissions.
+
+While there may be a need for more social science knowledge in IPCC assessments, this analysis makes it clear that this is rather a task for social scientists to produce more knowledge, than for the IPCC to reflect it better.
+
+Further, given Policymakers' demands for more solution-oriented knowledge, the IPCC may do well to make efforts to cover more of the literature on individual solutions.
+
+It may be argued that the technical solution-oriented knowledge is not yet in a proper form for synthesis by the IPCC.
+Although this is not an argument made for WGII (where the relationship between social science percentage and IPCC coverage for topics is not found), it would then be a task for the social sciences to produce research on solution oriented topics: increasing, for example, the less than 5\% of the research on biochar that is published by social scientists.
+
 \section{SI}
+\begin{figure}[h!]
+	\begin{center}
+		\includegraphics[width=0.85\linewidth]{plots/run_1771_wgs_socsci.pdf}
+		\caption{}
+		\label{ipcc_rep}
+	\end{center}
+\end{figure}
 
@@
 
-ncep
-fco
-pfc
-otcs
-dtr
-sres
-petm
-amf
-sf5cf3
-clc
-cwd
-etm
-cmip5
-cmip3
-mofs
-sdm
-mmms
-cop21
-c3n4
-sdg
-indc
+\noindent\textbf{ncep:} National Centers for Environmental Protection
+
+\noindent\textbf{fco:} Fugacity of Carbon Dioxide
+
+\noindent\textbf{pfc:} Perflourocompound
+
+\noindent\textbf{otcs:} Open Top Chambers
+
+\noindent\textbf{dtr:} Diurnal Temperature Range
+
+\noindent\textbf{sres:} Special Report on Emissions Scenarios
+
+\noindent\textbf{petm:} Paleocene Eocene Thermal Maximum
+
+\noindent\textbf{amf:}  Arbuscular Mycorrhizal Fungal
+
+\noindent\textbf{sf5cf3:} trifluoromethyl sulfur pentafluoride (A Potent Greenhouse Gas Identified in the Atmosphere, 2000)
+
+\noindent\textbf{clc:} Chemical Looping Combustion
+
+\noindent\textbf{cwd:} Coarse woody debris
+
+\noindent\textbf{etm:} Enhanced Thematic Mapper (NASA satellite sensor)
+
+\noindent\textbf{cmip5:} Coupled Model Intercomparison Project 5 (Starting 2008)
+
+\noindent\textbf{cmip3:} Coupled Model Intercomparison Project phase 3 (2005-2006)
+
+\noindent\textbf{mofs:} metal-organic frameworks (for CO2 storage)
+
+\noindent\textbf{sdm:} statistical-dynamical model
+
+\noindent\textbf{mmms:} Mixed Matrix Membranes (for CO2 capture)
+
+\noindent\textbf{cop21:} 21 Conference of Parties (Paris 2015)
+
+\noindent\textbf{c3n4:} Carbon nitride (a synthetic nanomaterial used for hydrogen production)
+
+\noindent\textbf{sdg:} Sustainable Development Goals
+
+\noindent\textbf{indc:} Intended Nationally Determined Contributions
 
@@
 	\input{tables/ipcc_shares_time.tex}
-	\caption{Top 10 topics in climate change literature}
+	\caption{Topics and their representation}
 	\label{top-topics}
@@
 
-\begin{table}[h!]
-	\scriptsize
-	\input{tables/top_topics.tex}
-	\caption{Top 10 topics in climate change literature}
-	\label{top-topics}
-\end{table}
+%\begin{table}[h!]
+%	\scriptsize
+%	\input{tables/top_topics.tex}
+%	\caption{Top 10 topics in climate change literature}
+%	\label{top-topics}
+%\end{table}
+
+\bibliography{Mendeley}
 

### 2019-05-27 main.tex

@@
 \documentclass{article}
-\usepackage[a4paper, total={6in, 8in}]{geometry}
+\usepackage[a4paper, total={180mm, 260mm}]{geometry}
 \usepackage{graphicx}
@@
 \usepackage{standalone}
+
 \usepackage[section]{placeins}
@@
 
-\noindent We know that the scientific literature on climate change is growing rapidly \cite{Grieneisen2011}, and that this growth poses problems for the IPCC, whose task it is to provide a comprehensive and transparent summary of it \cite{Minx2017l}.
+\noindent We know that the scientific literature on climate change is growing rapidly \cite{Grieneisen2011}, and that this growth poses problems for the IPCC.
+Their task of providing a comprehensive and transparent summary of the literature on climate change is severely challenged by the growth of the literature \cite{Minx2017l}.
 Despite this, we know little about thematic trends within the literature, or how the IPCC performs in reflecting this growing body of knowledge on climate change.
@@
 
-Such analysis provides a limited insight into the evolution of the literature since 1980s. We use topic modelling to produce a topographic map.  \todo{expand}
+The zika virus, the sustainable development goals, intended nationally determined contributions and mixed matrix membranes are all significant parts of the literature since 2014 which were simply not discussed in the context of climate change before the last IPCC report.
+In the context of this expanding vocabulary, this study employs topic modelling to draw out patterns in the content of scientific literature.
+Topic modelling is an unsupervised machine-learning technique, where patterns of word co-occurrences in documents are used to learn a set of topics which can be used to describe the corpus \cite{Blei2012}, and it is applied here for the first time to the whole scientific literature on climate change.
+
+\subsection*{A Topography of Climate Change}
+
+Topics, from the greek word ``topos" (meaning place), refer here to concepts or themes within the literature.
+In this sense, the topographic map shown in figure 1 \textit{situates} the 400,000 documents about climate change in a topical landscape derived from the 140 topics discovered through topic modelling.
+Using t-distributed stochastic network embedding (t-SNE)\cite{vandermaaten2008} as a dimensionality reduction technique, the 140 dimensional topic space is \textit{projected} onto two dimensions, such that documents with similar topical content are placed next to each other.
 
@@
 	\begin{center}
-		\includegraphics[width=1\linewidth]{tsne_results/plots/run_1861_s_0_p100_all_topic_words_oecds_big.png}
+		\includegraphics[width=180mm]{tsne_results/plots/run_1861_s_0_p100_all_topic_words_oecds.png}
 		\caption{A map of the literature on climate change.
@@
 	\begin{center}
-		\includegraphics[width=0.85\linewidth]{plots/ipcc_representation/ipcc_rep_oecds_simplified_short.pdf}
-		\caption{The representation within the IPCC of each discipline over time}
+		\includegraphics[width=180mm]{plots_pub/big_panel_representation.pdf}
+		\caption{\textbf{a)} the representation of each discipline in IPCC reports, \textbf{b)} the representation and social science proportion of WG 3 topics, \textbf{c)} The representation and novelty of all topics }
 		\label{oecd_rep}
@@
 Although economics was previously over-represented among social sciences, while others were under-represented, more subdisciplines of the social sciences are now over-represented.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=180mm]{tsne_results/plots/run_1861_s_0_p100_evolution_4.png}
+		\caption{Evolution of the landscape of climate change literature}
+		\label{oecd_topic_map}
+	\end{center}
+\end{figure}
 

### 2019-05-28 main.tex
publication plots + writing

@@
 Their task of providing a comprehensive and transparent summary of the literature on climate change is severely challenged by the growth of the literature \cite{Minx2017l}.
-Despite this, we know little about thematic trends within the literature, or how the IPCC performs in reflecting this growing body of knowledge on climate change.
-Understanding these trends is a crucial task if we are to assess and improve comprehensiveness in global environmental assessments.
+In the light of policymakers' demand for more solutions-oriented knowledge from assessments \cite{Kowarsch2017}; calls for more representation of certain disciplines in IPCC reports \cite{Victor2015, Barnes2013}; and criticism of bias in the knowledge reflected by the IPCC \cite{Bjurström2011, Hulme2010}, \textit{what}, in the (dwindling) proportion of the literature that gets cited by IPCC reports,  is more salient than ever.
 
-\begin{table}
+Despite this, we know little about thematic trends within the literature, or how the IPCC performs in reflecting different parts of this growing body of knowledge on climate change.
+Understanding these trends, and their reflection in IPCC reports is a crucial task if we are to assess and improve comprehensiveness in global environmental assessments.
+
+\begin{table}[htp]
 	{\scriptsize
@@
 Table \ref{tab} depicts the scale of the challenge to the IPCC.
-In the years since the publication of AR5, as much literature has been published as in the 30 years previously.
+In the years since the publication of AR5, almost as much literature has been published as in the 30 years previously.
 Moreover, not only are more articles being published, but the vocabulary of climate knowledge has expanded.
@@
 
-\subsection*{A Topography of Climate Change}
+\subsection*{A Topography of Climate Change Research}
 
@@
 In this sense, the topographic map shown in figure 1 \textit{situates} the 400,000 documents about climate change in a topical landscape derived from the 140 topics discovered through topic modelling.
-Using t-distributed stochastic network embedding (t-SNE)\cite{vandermaaten2008} as a dimensionality reduction technique, the 140 dimensional topic space is \textit{projected} onto two dimensions, such that documents with similar topical content are placed next to each other.
+Using t-distributed stochastic network embedding \cite{vandermaaten2008} (t-SNE) as a dimensionality reduction technique, the 140 dimensional topic space is \textit{projected} onto two dimensions, such that documents with similar topical content are placed next to each other.
 
-\begin{figure}
+To understand the map we find clusters of documents relating to each topic, and superimpose the topic label in the center of each cluster (see methods for a more detailed description).
+Documents are coloured by their categorisation in the Web of Science into broad disciplinary categories, showing us how the topical content of the documents fits into disciplinary structures.
+Across the map, it is clear that different disciplines focus on different groups of topics, with more natural science research on the left hand side of the map, more engineering in the upper right and right, more agricultural sciences at the bottom of the map, and more social sciences on the inner right.
+
+Further, the map allows us to examine topics consisting of research from across disciplines.
+With reference to SI figure [x] which shows the disciplinary diversity of each topic, we can see that research on coral comes almost exclusively from the natural sciences, while papers discussing socioeconomic issues come from a variety of disciplines.
+\todo{more here}
+
+\todo{Mapping, systematic maps, knowledge gaps, what we know about the ipcc and the literature}
+
+\begin{figure}[htp]
 	\begin{center}
@@
 
-\subsection*{Social Sciences in IPCC citations}
+\subsection*{Disciplinary bias in IPCC citations?}
 
-It was argued after the fifth assessment report that the IPCC needs to do more to incorporate knowledge from the social sciences \cite{Victor2015}, and a scientometric study of the  the third assessment report claimed the IPCC gave a greater \textit{emphasis} to natural sciences and, within the social sciences, to economics.
-The study, however, operationalised disciplinary emphasis as simply the number of citations from each field.
-Here we look at \textit{representativeness}, that is, the share of IPCC citations in each field divided by the share of all climate related documents in that field.
+It was argued after the fifth assessment report that the IPCC needs to do more to incorporate knowledge from the social sciences \cite{Victor2015}.
+Further, a scientometric study from 2011 claimed that the IPCC gave a greater \textit{emphasis} to natural sciences and, within the social sciences, to economics \cite{Bjurström2011}.
+This claim has been interpreted as a disciplinary bias by the IPCC \cite{Hulme2010, Corbera2016}, but the study operationalised disciplinary emphasis as simply the share of citations from each field, and was based on analysis of the Third Assessment report, published in 2001.
+The share of citations in each discipline does not take into account the distribution of climate change research across disciplines in the wider literature.
+Here we look at \textit{representativeness}, that is, the share of IPCC citations in each field divided by the share of all climate related documents in that field, and carry out this analysis across assessment periods.
 
-\begin{figure}
+\begin{figure}[htp]
 	\begin{center}
 		\includegraphics[width=180mm]{plots_pub/big_panel_representation.pdf}
-		\caption{\textbf{a)} the representation of each discipline in IPCC reports, \textbf{b)} the representation and social science proportion of WG 3 topics, \textbf{c)} The representation and novelty of all topics }
+		\caption{Representation in IPCC reports: \textbf{a)} by discipline, \textbf{b)} by social science proportion of WG 3 topics, \textbf{c)} and novelty of all topics, where topics in the highest and lowest 10\% of either axis are labelled.
+Topics are coloured according to the working group from which they receive the most citations.
+Representation is the share of the subset of documents being cited by the IPCC divided by the share of the subset in the whole literature.
+The log is taken so that 0 is equal to perfectly proportional representation, and -1 and 1 are equally under and over represented.}
 		\label{oecd_rep}
@@
 
-Looked at this way, we see that the social sciences were indeed under-represented in earlier assessment reports, but by the fifth assessment report were over-represented.
-Although economics was previously over-represented among social sciences, while others were under-represented, more subdisciplines of the social sciences are now over-represented.
+Looked at this way (Figure 2.a), we see that the social sciences were indeed under-represented in the third assessment report, but by the fifth assessment report were over-represented.
+The disciplines under-represented in IPCC reports (with respect to the distribution of studies in the wider literature) are in fact Agricultural Sciences, Engineering \& Technology and Humanities.
+In each field, the under-representation has been present across assessment reports.
+
+A similar story is visible within the social sciences (see figure \ref{subfield}f). 
+Economics was previously over-represented among social sciences, while other subfields were under-represented.
+In AR5, though, the share of economics citations in the IPCC was close to that in the wider literature, while social \& economic geography (4.3\% of the literature), political science (1.0\%), and sociology (0.8\%) were better represented than in AR3 and above or close to a proportional representation.
+
+With more up to date data and a more comprehensive method, both results contradict previous evidence on disciplinary representation in the IPCC.
+This new evidence is a compelling reason to rethink our view of the relationship between disciplinary knowledge and the IPCC.
+%, and to further investigate the content of the documents that are more less proportionately represented in the IPCC.
 
@@
 		\caption{Evolution of the landscape of climate change literature}
-		\label{oecd_topic_map}
+		\label{evolution-map}
 	\end{center}
 \end{figure}
+
+\subsection*{Supply and demand for solutions-oriented knowledge}
+
+Beyond the disciplinary categories analysed so far, the topographical map helps us to dig down further into the themes that are more or less proportionately represented.
+Figures \ref{oecd_rep}b and \ref{oecd_rep}c plot the representation of the topics which locate the documents on the map, showing us, in figure \ref{oecd_rep}c that topics more commonly cited by IPCC working group I, are older, and are largely better represented in IPCC reports.
+That these topics, on ozone, oceans, clouds, aerosols and sea levels, for example, are older, cited by WG I and well cited by IPCC reports makes intuitive sense, as these are some of the core topics of the physical science of climate change.
+
+The topics in the lower right hand part of the graph are the most pertinent to the question of whether the IPCC is well representing the existing knowledge on climate change.
+These topics are relatively newer and until now under-represented in IPCC reports.
+They are the topics that could be seen as potential gaps in the IPCC's coverage of the science.
+These topics are primarily in working group III, on the mitigation of climate change, with the exception of adsorption, CLC and hydrogen which are primarily of relevance to WG III but are miscategorised due to the low number of citations of relevant documents and citations of tangentially relevant documents by other working groups \footnote{For example, the word ``capacity" is relevant to the adsorption topic, so documents talking about adaptive capacity receive a low score for the topic.
+Because only very few documents highly relevant to the topic (in that they talk about adsorption or adsorptive capacity) are cited by the IPCC, and many of the weakly relevant documents are cited by the IPCC, the sum of the topic scores of the weakly relevant documents outweighs the sum of the topic scores of the strongly relevant documents}.
+
+\todo{WG + map}
+Although it is not surprising that these newer topics are less well represented than the older topics that make up the core of the physical science research on climate change, the difference between these new topics and other new topics that are better represented is intriguing.
+This difference is visible in figure \ref{evolution-map}, where the fastest growing topics in each period are labelled, and the documents are coloured according to the working group, if any, which cites them.
+In AR5, the clusters of documents around the \textbf{adsorption}, \textbf{buildings}, and \textbf{biochar} topics contain few IPCC citations, whereas the clusters around \textbf{food}, \textbf{health}, \textbf{adaptation}, and \textbf{GHGs} contain relatively more.
+This is is
+
+One reason seems to be
+\todo{WG + social sciences}
+Not only about social sciences, or disciplines, but what topic+social science
+
+Given policymakers' demands for more solution-oriented assessments, we could also interpret these topics as solutions relevant.
+Many deal with negative emissions, or with mitigation options in the transport, buildings and power sectors.
+However, while policymakers' demands for solutions-oriented knowledge was rather about policy options, these under-represented new topics deal rather with technical solutions.
+
+\subsection*{The IPCC as an informed decision-maker on topical representation}
+
+IPCC best to decide but informed
+technical vs general knowledge.
+Technical questions about the effectiveness of specific technologies are perhaps just as disputed as the workings of climate change
+
+information helps to set priorities
+
+if we feel we need more social science knowledge, the information here tells us that we may need to change the social sciences
+
+once again, this is to be answered best by the IPCC,
+
+limitation, not all literature, doesn't fundamentally change conclusions, means the challenges are even larger than portrayed here.
+More potentially relevant literature, other potentially important and under-cited topics.
+Other types of knowledge.
 
@@
 
+\appendix
+
 %\listoffigures
@@
 
+\include{methods}
+
 \end{document}

### 2019-06-12 abstract.tex
0 draft

@@
 	Moreover, the number and variety of papers hinders researchers of the science-policy interface from making objective judgements about those IPCC assessments.
-In this paper, we present a novel application of a machine-reading approach to model the topical content of papers on climate change.
-This dynamic topic model provides the basis for a \textit{topography} of climate change literature.
-The thematic development of the field is outlined and used to inform an analysis of the topics which are better and less well covered by IPCC reports.
+In this paper, we present a novel application of a machine-reading approach to model the topical content of 400,000 papers on climate change.
+This topic model provides the basis for a \textit{topography} of climate change literature.
+By comparing the climate change literature as a whole to that which is cited by IPCC reports, we show that, contrary to previous estimations \cite{Bjurström2011}, social science research on climate change is relatively well represented by IPCC reports.
+Conversely, topics on technical solutions to climate change, and knowledge from Engineering and the Agricultural Sciences in general, are under-represented.
 \end{document}

### 2019-06-12 main.tex
0 draft

--- 2019-05-22 main.tex
@@
 
-\noindent We know that the scientific literature on climate change is growing rapidly \cite{Grieneisen2011}, and that this growth poses problems for the IPCC, whose task it is to provide a comprehensive and transparent summary of it \cite{Minx2017l}.
-Despite this, we know little about thematic trends within the literature, or how the IPCC performs in reflecting this growing body of knowledge on climate change.
-Understanding these trends is a crucial task if we are to assess and improve comprehensiveness in global environmental assessments.
+\noindent We know that the scientific literature on climate change is growing rapidly \cite{Grieneisen2011, Haunschild2016}, and that this growth poses problems for the IPCC.
+Their task of providing a comprehensive and transparent summary of the literature on climate change is severely challenged by the growth of the literature: the proportion of the literature that gets cited by the IPCC is dwindling \cite{Minx2017l}.
+In the light of policymakers' demand for more solutions-oriented knowledge from assessments \cite{Kowarsch2017}; calls for more representation of certain disciplines in IPCC reports \cite{Victor2015, Barnes2013}; and criticism of bias in the knowledge reflected by the IPCC \cite{Bjurström2011, Hulme2010}, what gets cited and what doesn't is more salient than ever.
 
-\begin{table}
+However, we know little about thematic trends within the literature, or how the IPCC performs in reflecting different parts of this growing body of knowledge on climate change.
+We lack an overview of the literature itself, and without this, our understanding of the IPCC \cite{} lacks the context of the literature which it is supposed to assess.
+Mapping out this literature, and its reflection in IPCC reports is a crucial task if we are to assess and improve the IPCC's comprehensiveness.
+
+\begin{table}[htp]
 	{\scriptsize
@@
 
-Table \ref{tab} depicts the scale of the challenge to the IPCC.
-In the years since the publication of AR5, as much literature has been published as in the 30 years previously.
+Table \ref{tab} depicts the scale of the challenge faced by the IPCC.
+Since the publication of the fifth assessment report (AR5), almost as much literature has been published as in the 30 years previously.
 Moreover, not only are more articles being published, but the vocabulary of climate knowledge has expanded.
@@
 
-Such analysis provides a limited insight into the evolution of the literature since 1980s. We use topic modelling to produce a topographic map.  \todo{expand}
+The zika virus, the Sustainable Development Goals (SDGs), Intended Nationally Determined Contributions (INDCs), and mixed matrix membranes (MMMs) are all significant parts of the literature since 2014 which were simply not discussed in the context of climate change before the last IPCC report.
+In view of this expanding vocabulary, this study employs topic modelling to draw out patterns in the content of scientific literature.
+Topic modelling is an unsupervised machine-learning technique, where patterns of word co-occurrences in documents are used to learn a set of topics which can be used to describe the corpus \cite{Blei2012}.
+It is applied here for the first time to the whole scientific literature on climate change.
 
-\begin{figure}
+\subsection*{A Topography of Climate Change Research}
+
+Topics, from the greek word ``topos" (meaning place), refer here to concepts or themes within the literature.
+Using the same geographic-thematic metaphor, the topographic map shown in figure 1 \textit{situates} the 400,000 documents about climate change in a topical landscape derived from the 140 topics discovered through topic modelling.
+Using t-distributed stochastic network embedding \cite{vandermaaten2008} (t-SNE) as a dimensionality reduction technique, the 140 dimensional topic space is \textit{projected} onto two dimensions, such that documents with similar topical content are placed next to each other.
+If scientists, in global environmental assessments, act as mapmakers \cite{Edenhofer2015}, this topography, as a broad outline of the features of the research landscape, help understand the relationship of the map to the mapped.
+
+To make the map readable, we find clusters of documents relating to each topic, and superimpose the topic label in the center of each cluster (see methods for a more detailed description).
+Documents are coloured by their categorisation in the Web of Science into broad disciplinary categories, showing us how the topical content of the documents fits into disciplinary structures.
+Across the map, it is clear that different disciplines focus on different groups of topics, with more natural science research on the left hand side of the map, more engineering in the upper right and right, more agricultural sciences at the bottom of the map, and more social sciences on the inner right.
+
+\todo{Get rid of numbers, replace with letters ?}
+
+The map also allows us to examine topics consisting of research from across disciplines.
+With reference to figure \ref{dis-entropy} which shows the disciplinary diversity of each topic, we can see that research on coral comes almost exclusively from the natural sciences, while papers discussing socioeconomic issues come from a variety of disciplines.
+
+The map plays an important role in generating knowledge about what we do and do not know about climate change.
+Though not strictly systematic, in that all studies have been checked for relevance and categorised by hand, it moves in the direction of evidence maps, or systematic maps \cite{McKinnon2015, James2016}, by categorising and quantifying the literature and its uptake by the IPCC.
+The approach is weakly systematic in the sense that the studies are selected according transparent criteria (see methods), and are categorised consistently by the topic model.
+Further, that the categories are learnt from the data without human input, means that we can find patterns we didn't know we were looking for.
+
+\begin{figure}[htp]
 	\begin{center}
-		\includegraphics[width=1\linewidth]{tsne_results/plots/run_1861_s_0_p100_all_topic_words_oecds_big.png}
+		\includegraphics[width=180mm]{plots_pub/all_topic_words_oecds.pdf}
 		\caption{A map of the literature on climate change.
@@
 
-\subsection*{Social Sciences in IPCC citations}
+\subsection*{Disciplinary bias in IPCC citations?}
 
-It was argued after the fifth assessment report that the IPCC needs to do more to incorporate knowledge from the social sciences \cite{Victor2015}, and a scientometric study of the  the third assessment report claimed the IPCC gave a greater \textit{emphasis} to natural sciences and, within the social sciences, to economics.
-The study, however, operationalised disciplinary emphasis as simply the number of citations from each field.
-Here we look at \textit{representativeness}, that is, the share of IPCC citations in each field divided by the share of all climate related documents in that field.
+It was argued after the fifth assessment report that the IPCC needed to do more to incorporate knowledge from the social sciences \cite{Victor2015}.
+Further, a scientometric study from 2011 claimed that the IPCC gave a greater \textit{emphasis} to natural sciences and, within the social sciences, to economics \cite{Bjurström2011}.
+This claim has been interpreted as a disciplinary bias by the IPCC \cite{Hulme2010, Corbera2016}, but the study operationalised disciplinary emphasis as simply the share of citations from each field, and was based on analysis of the Third Assessment report, published in 2001.
+The share of citations in each discipline does not take into account the distribution of climate change research across disciplines in the wider literature.
+Here we look at \textit{representativeness}, that is, the share of IPCC citations in each field divided by the share of all climate related documents in that field, and carry out this analysis across assessment periods.
 
-\begin{figure}
+\begin{figure}[htp]
 	\begin{center}
-		\includegraphics[width=0.85\linewidth]{plots/ipcc_representation/ipcc_rep_oecds_simplified_short.pdf}
-		\caption{The representation within the IPCC of each discipline over time}
+		\includegraphics[width=180mm]{plots_pub/big_panel_representation.pdf}
+		\caption{Representation in IPCC reports: \textbf{a)} by discipline, \textbf{b)} by social science proportion of WG 3 topics, \textbf{c)} and novelty of all topics, where topics in the highest and lowest 10\% of either axis are labelled.
+Topics are coloured according to the working group from which they receive the most citations.
+Representation is the share of the subset of documents being cited by the IPCC divided by the share of the subset in the whole literature.
+The log is taken so that 0 is equal to perfectly proportional representation, and -1 and 1 are equally under and over represented.}
 		\label{oecd_rep}
@@
 
-Looked at this way, we see that the social sciences were indeed under-represented in earlier assessment reports, but by the fifth assessment report were over-represented.
-Although economics was previously over-represented among social sciences, while others were under-represented, more subdisciplines of the social sciences are now over-represented.
+Looked at this way (Figure 2.a), we see that the social sciences were indeed under-represented in the third assessment report, but by the fifth assessment report were over-represented.
+The disciplines under-represented in IPCC reports (with respect to the distribution of studies in the wider literature) are in fact Agricultural Sciences, Engineering \& Technology and Humanities (although the humanities make up a very small proportion of the literature).
+In each field, the under-representation has been present across assessment reports.
 
-%\begin{multicols}{2}
+A similar story is visible within the social sciences (see figure \ref{subfield}f). 
+Economics was previously over-represented among social sciences, while other subfields were under-represented.
+In AR5, though, the share of economics citations in the IPCC was close to that in the wider literature, while social \& economic geography (4.3\% of the literature), political science (1.0\%), and sociology (0.8\%) were better represented than in AR3 and above or close to a proportional representation.
 
-%\multicollinenumbers
-%\bigskip
-%\noindent\textbf{To deal with the wicked problem of climate change, international policy-makers need the IPCC. The IPCC as map-makers.}
-%
-%The IPCC sees its role as to ``assess on a comprehensive, objective, open and transparent basis the scientific, technical and socio-economic information relevant to [...] climate change'' \citep{IPCC2013}.
-Climate science is so broad, multi-disciplinary, and laden with uncertainties and values, that the role of the IPCC as assessment maker is vitally important to developing evidence-based international climate policy.
-In the Pragmatic Enlightened Model of the science-policy interface, the task of assessment making is a cartographic one \citep{Edenhofer2015}.
-Assessment makers map out the problem and the option space for policy-makers.
-%
-%
-%
-%%\bigskip
-%%\noindent\textbf{The task of the IPCC has become much more difficult with big literature}
-%
-%Further, it has been pointed out that, in the age of ``big literature'', providing assessments that are comprehensive, objective and transparent has become much more difficult \citep{Minx2017l}.
-When the IPCC's citations constitute an ever-decreasing proportion of the totality of science on climate change, questions about the map that the IPCC reports produce become more pressing:
-%
-%\begin{itemize}
-%	\item Is the map up to date?
-%	\item Is the map complete?
-%	\item Is the map's projection representative? Does it emphasise or obscure certain areas?
-%\end{itemize}
-%
-%
-%\section*{The IPCC as an object of scientific investigation}
-%
-%%%%%%
-%
-%%\bigskip
-%%\noindent\textbf{The IPCC, its reports and processes have been the object of study before. These are also hampered by problems of scale though}
-%
-%Various researchers have attempted to do empirical research on the assessment reports, and processes of inter.
-alia.
-the IPCC \citep{jabbour2017, Bjurström2011, Corbera2016, Hulme2016}.
-Among the clear conclusions is that policy makers, when asked about their interactions with the IPCC call for a greater focus on solutions \citep{Kowarsch2017}.
-Studies that look directly at the content of IPCC reports, though, are similarly challenged by the the size of the literature that the reports assess.
-Without engaging with this literature, the conclusions drawn lack a reference point, and the phenomena identified (such as an over-representation of the natural sciences in IPCC citations \cite{Bjurström2011}) are hard to disentangle as specific to the way the IPCC assesses its literature, rather than a feature of the literature itself.
-%
-%%\bigskip
-%%\noindent\textbf{Some literature exists on bibliometrics and climate change, but tends not to deal with text}
-%
-%Some studies have attempted to identify and characterise the literature on climate change through bibliometric techniques \citep{Haunschild2016, Grieneisen2011}.
-Such studies are the jumping off point for this work, and form the basis of the identification strategy for the literature, but they do not engage with the \textit{texts} of the work identified, nor do they make the link to the IPCC.
-A growing body of scientific work deals with the unsupervised analysis of texts using topic modelling \cite{Lee1999,Blei2003, Greene2016, Roberts2013}.
-Applications to the field of climate change though are rare and often limited to closer analysis within sub-topics \cite{Grubert2017}, or calls for their greater use \cite{Grubert2016}.
-%
-%\section*{A problem of scale}
-%
-%
-%%\bigskip
-%%\noindent\textbf{The scale of the problem in context}
-%
-%\begin{table}
-%	\scriptsize
-%	\input{tables/growth_table.tex}
-%	\caption{Growth in climate change literature}
-%	\label{growthtable}
-%\end{table}
-%
-%The case for a greater application of text-mining approaches in understanding and assisting the IPCC is made by the scale of the challenge it faces, depicted in table \ref{growthtable}.
-Less than a thousand documents relevant to climate change were published before the first assessment report (see Methods for data, exclusions and processing).
-The abstracts of these documents contained 1,380 unique terms.
-In the three complete years since the publication of AR5, 128,266 documents have been published, containing 74,196 unique terms.
-The new words in each assessment period unearthed by a basic machine-reading of the literature already give an indication of the how the field has expanded.
-They chart the emergence of
-%
-%\linespread{1}
-%\begin{itemize}
-%	\item new compounds or materials, such as trifluoromethyl sulfur pentafluoride (SF5CF3) in AR4, or mixed matrix membranes (MMMs) in AR6
-%	\item new models, or modelling approaches, such as HadCM2 in AR3, or CMIP in AR5 and AR6.
-%	\item the involvement of new actors, such as NCEP (National Centers for Environmental Prediction) in AR3
-%	\item new approaches, such as biochar and REDD in AR5
-%	\item new applications of equipment, such as OTCs (Open-top Chambers) in AR3;
-%	\item new phenomena in relation to climate change, such as zika and twitter;
-%	\item and new concepts, such as CO2 fugacity (fco) in AR3
-%\end{itemize}
-%\linespread{1.5}
-%
-%
-%
-%
-%%To put this into context, the 1,189 chapters of the Bible contain a vocabulary of 11,977 unique words. Put another way, 
-%To put this growth into context, the 236,634 publications published in AR5 and AR6 are significantly larger than the 178,118 publications recorded in the first volume of the `Catalogue of Scientific Papers', compiled by the Royal Society to record the entirety of scientific output from 1800 to 1863 \citep{Csiszar2017}.
-In the last 10 years, climate science has produced significantly more papers than the were published across all scientific disciplines in the first half of the 19th Century.
-%
-%
-%
-%
-%%\begin{figure}
-%%	\begin{center}
-%%		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
-%%		%\captionof{figure}
-%%		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions.
-Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period.
-The percentage of documents in which the average word occurs in is given in the key.
-%%		}
-%%		\label{growth}
-%%	\end{center}
-%%\end{figure}
-%
-%
-%%\bigskip
-%%\noindent\textbf{Machine reading to deal with scale problems in the making and assessing of maps}
-%
-%
-%Clearly, if the IPCC is to continue producing comprehensive assessments, it has to engage in machine-reading in order to remain anchored to the wider literature.
-Without such an approach, it becomes harder to justify which ever-diminishing proportion of the wider literature is included in assessments.
-The same arguement holds for scholars and critics of the IPCC.
-Without machine reading the literature at large, it becomes harder to analyse or criticise, with quantitatively evidenced claims, the outcomes of assessment processes.
-%
-%
-%%\bigskip
-%%\noindent\textbf{Dimension reduction makes possible the description in reduced form, and with less human bias, of unmanageably large datasets}
-%
-%%\citep{Greene2016} \citep{Lee1999}
-%In order to draw substantive messages from this high-dimensional document-word space, we apply a form of dimensionality reduction called topic-modelling \citep{Blei2010}.
-The non-negative matrix factorisation (NMF) approach to topic modelling is based on generating a ``perception of the whole based on perception of its parts'' \citep{Lee1999}.
-Here the corpus of documents (whole) is summarised by its parts (topics), which appear in varying proportions in each of the documents.
-Importantly, in such approaches, the parts are not pre-defined, but learned by the algorithm, leveraging systematic co-occurences of words within documents.
-This makes the discovery of unlooked-for features possible and can reduce the human bias risked by the pre-definition of categories.
-%
-%%\bigskip
-%%\noindent\textbf{Machine reading is a supplement to assessment-making and not free from bias; a topography is not a map}
-%
-%Despite these advantages, machine reading and machine learning approaches can of course not replace the task of human assessment-making.
-The contribution that could be made, though, is to pre-process the literature, producing a topographical map, used to navigate the literature while producing a more detailed assessment with human judgement.
-In fact this happens already - when IPCC authors search for literature on a topic, the results which appear on the search engine they use will be subject to algorithms based on the processing of millions of records of article text and metadata.
-This can be done in a much more systematic way when scientists perform directed analyses of the literature at scale.
-%
-%
-%%\bigskip
-%%\noindent\textbf{This study's contribution. Overarching themes, structure of the literature, development, relation to IPCC}
-%
-%In applying a dynamic version of NMF \cite{Greene2016}, this study demonstrates how topic modelling can be used to gain an overview of an otherwise unmanageably large body of literature.
-This overview, or topography, describes the thematic development of the climate change literature and, in a novelly systematic way, examines how comprehensively the IPCC has been able to engage with it.
-In pulling together strands from text-mining, bibliometrics, and the study of science and policy, this study advances our understanding of the literature on climate change and the role of the IPCC in communicating this to policy makers.
-%
-%
-%\section*{Results}
-%
-%Table \ref{top-topics} shows the 10 most prominent topics within the literature on climate change.
-The topics are characterised by the (stemmed) words that define them, and by the documents which are most well described by them.
-For example, the topic ``energi, renew, consumpt'' features the words energi, renew, consumpt,
-%effici, demand,
-%save, sector, sourc,
-%industri, use, and best describes the documents ``Energy issues and energy priorities'' \cite{Demirbas2008} and ``Energy efficiency and CO2 emissions in Swedish manufacturing industries'' \cite{PardoMartinez2013}.
-The topics learned by dynamic NMF identify a set of interpretable topics and can identify which documents belong to these topics.
-%
-%\begin{table}
-%	\scriptsize
-%	\input{tables/top_topics.tex}
-%	\caption{Top 10 topics in climate change literature}
-%	\label{top-topics}
-%\end{table}
-%
-%Such first results show the promise of topic modelling in the identification of studies in a thematic area, which is of high value to assessment exercises like the IPCC, but in themselves do not give a sense of the broad structure of the corpus.
-Figure \ref{map-double} projects the documents on to a two dimensional representation of the their topic composition derived through t-distributed Stochastic Network Embedding (t-SNE) \cite{vandermaaten2008}.
-In this approach, documents are positioned close to other documents with similar topic compositions.
-This projection enables us to show a topography of the whole literature on climate change.
-%
-%\begin{figure}
-%	\begin{center}
-%		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_double.pdf}
-%		\includegraphics[width=0.85\linewidth]{tsne_results/plots/run_665_s_0_p200_double.png}
-%		\caption{A map of the literature on climate change.
-Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom).
-See SI table for topic composition of each grid square}
-%		\label{map-double}
-%	\end{center}
-%\end{figure}
-%
-%
-%In the two panels of the figure, the documents are coloured by the IPCC working group which cites them (if any), and the disciplinary classification according to the Web of Science.
-The topic structure cuts across working group and disciplinary lines, but the disciplinary and working group structure is clearly visible in the topography.
-For example, in the south-eastern section of the map, we can see a concentration of documents in the social sciences that were cited by working group III (mitigation).
-%
-%The topography\_map\_reference.csv [ \url{https://github.com/mcallaghan/cc-topography/blob/master/tables/tsne_topic_index_665.csv}] file in the supporting materials aids more detailed analysis of the map, describing the topic composition of each square.
-For example the square whose center is [12.5,-7.5] is made up of the topics \{energi, renew, consumpt\}, \{fuel, fossil, engin\}, \{emiss, reduct, reduc\}, \{countri, develop, trade\} and \{cost, optim, price\}, typical social science, working group III topics.
-The square whose center is [-17.5,-2.5], containing mostly working group I (the physical science basis) documents on the other hand, is made of largely by the topic {ozon, stratospher, tropospher} as well as by {increas, concentr, decreas}, and {climat, chang, impact}.
-%
-%%\bigskip
-%%\noindent\textbf{A topographical map of climate change documents shows the broad structure of climate change literature}
-%Figure \ref{map-growth} shows the evolution of the landscape of climate change literature over the 6 (including the in progress AR6) assessment periods of the IPCC.
-In each assessment period, the grid squares which contain a higher (lower) proportion of documents than in the previous assessment period are coloured green (red).
-This mapping allows us to identify topic areas as they appear in the literature.
-For example, the square with the center [-12.5,12.5] is composed largely of the topic \{coral, reef, bleach\}, and contained no documents before a sudden growth in AR3.
-Indeed, the topic of coral bleaching  was little discussed in the context of climate change before AR3, with just two out of 693 results from Web of Science for the terms  "Coral bleaching" AND "climate change" published before 1996.
-More recently, the square [12.5,12.5] identifies the topic \{biochar, amend, applic\} as a quickly emerging field within climate change in present times.
-%
-%\begin{figure}
-%	\begin{center}
-%		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_evolution.pdf}
-%		\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_evolution.png}
-%		\caption{The evolution of the landscape of climate change literature}
-%		\label{map-growth}
-%	\end{center}
-%\end{figure}
-%
-%
-%%\begin{figure}
-%%	\begin{center}
-%%		%\includegraphics[width=1\linewidth]{plots/network_development_wgs_665.pdf}
-%%		\caption{The development of the topic-document correlation network over IPCC assessment periods.}
-%%		\label{}
-%%	\end{center}
-%%\end{figure}
-%
-%%\bigskip
-%%\noindent\textbf{The topic-document correlation network is densest in AR2 and 3 but becomes more fragmented over time}
-%%
-%%(partly: Model less good at describing literature later on)
-%
-%%\bigskip
-%%\noindent\textbf{Working groups are clustered together [dynamics], with topics like [x] containing documents across working groups and topics like [y] important network nodes}
-%
-%The dynamic nature of the topic model also allows us to identify changes within topics.
-SI figure \ref{sus} shows the evolution of the topic \{research, social, issu\}.
-In this overarching topic on research priorities we can detect an increasing prominence of the word ``sustainability''.
-%
-%Finally, by comparing the topic distribution across all documents (published before the end of AR5) with the topic distribution across documents that were cited by the IPCC, we can identify those topics which were over- or under- represented, with respect to the underlying literature, in IPCC reports.
-Figure \ref{representation} plots the representation and novelty of all topics in the model, labelling those topics most under- or over-represented.
-The topics are coloured according to the working group from which most IPCC citations to its documents came.
-%
-%The negative slope of the plot shows that the IPCC better represents those topics which have a longer history in the literature.
-The majority of well represented older topics come from working group I, such as \{aerosol, cloud, radiat\}.
-New topics in working group II on adaptation and vulnerability are well represented in IPCC reports.
-However, a cluster of new topics on mitigation issues appear to be under-represented by the IPCC.
-Moreover, these topics, such as those on buildings, waste, biochar, carbon capture and carbon storage are those that deal with climate solutions.
-%
-%
-%\begin{figure}
-%	\begin{center}
-%		\includegraphics[width=1\linewidth]{plots/ipcc_representation/ipcc_rep_new665_all.pdf}
-%		\caption{Representation and newness of dynamic topics}
-%		\label{representation}
-%	\end{center}
-%\end{figure}
-%
-%
-%%\bigskip
-%%\noindent\textbf{Sustainability has been an increasingly important theme in an overarching topic about environmental sciences}
-%%
-%%(compare to biochar, which is much more recent)
-%
-%
-%
-%
-%\section*{Discussion}
-%
-%%\bigskip
-%%\noindent\textbf{Solutions, policies and science}
-%%
-%%What do policy-makers mean when they ask for more solutions
-%
-%The results from a dynamic topic model of climate change literature delineate the structure and evolution of the field, telling its history and identifying areas of rapid growth that are of high relevance for future assessments.
-Further, they suggest that the demand by policy-makers from the IPCC for a greater focus on solutions is well-founded.
-Topics related to climate solutions are the least well represented in the IPCC's assessments.
-%
-%%\bigskip
-%%\noindent\textbf{Perfect representation is not necessarily desirable, but the skewedness should be known}
-%There may well be excellent reasons for over- or under-representation of topics in IPCC reports, and indeed it is the institution of the IPCC, not machines, who can best make judgements about what to include and what not to include.
-However, it is unclear whether the decisions which resulted in such unequal distributions were made consciously, on the basis of an understanding of the breadth of the extant literature.
-For future assessments to be relevant, transparent and comprehensive in the age of big literature, these decisions should be supported by machine-supported engagement with the literature as a whole.
-%
-%
-%%Increase in the frequency of the use of the term ``solutions'' \citep{jabbour2017},
-%
-%%\section*{Methods}
-%%\label{methods}
-%%
-%%
-%%
-%%\subsection*{Data}
-%%This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of
-%
-%\pagebreak
-%
-%
-%\input{methods.tex}
-%
-%
+With more up to date data and a more comprehensive method, both results contradict previous evidence on disciplinary representation in the IPCC.
+This new evidence is a compelling reason to rethink our view of the relationship between disciplinary knowledge and the IPCC.
+%, and to further investigate the content of the documents that are more less proportionately represented in the IPCC.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=180mm]{plots_pub/topic_evolution_4.pdf}
+		\caption{Evolution of the landscape of climate change literature}
+		\label{evolution-map}
+	\end{center}
+\end{figure}
+
+\subsection*{Supply and demand for solutions-oriented knowledge}
+
+Beyond the disciplinary categories analysed so far, the topographical map helps us to dig down further into the themes that are more or less proportionately represented.
+Figures \ref{oecd_rep}b and \ref{oecd_rep}c plot the representation of the topics.
+Figure \ref{oecd_rep}c shows that topics more commonly cited by IPCC working group I are older and largely better represented in IPCC reports.
+It makes intuitive sense that these topics, for example on ozone, oceans, clouds, aerosols and sea levels, are older, predominantly cited by WG I, and well cited by IPCC reports, as these are some of the core topics of the physical science of climate change.
+
+The topics in the lower right of the graph are the most pertinent to the question of whether the IPCC is well representing knowledge on climate change.
+These topics are newer and until now have been under-represented in IPCC reports.
+They are the topics that could be seen as potential gaps in the IPCC's coverage of the science.
+These topics are primarily in working group III, on the mitigation of climate change, with the exception of adsorption, CLC and hydrogen which are primarily of relevance to WG III but are miscategorised due to the low number of citations of relevant documents \footnote{For example, the word ``capacity" is relevant to the adsorption topic, so documents talking about adaptive capacity receive a low relevance score for that topic.
+Because only very few documents highly relevant to the adsorption topic (in that they talk about adsorption or adsorptive capacity) are cited by the IPCC, and many of the weakly relevant documents are cited by the IPCC, the sum of the topic scores of the weakly relevant WG II documents outweighs the sum of the topic scores of the strongly relevant WG III documents}.
+and citations of tangentially relevant documents by other working groups
+
+Although it is not surprising that these newer topics are less well represented than the older topics that make up the core of the physical science research on climate change, the difference between these new topics and other new topics that are better represented is intriguing.
+This difference is visible in figure \ref{evolution-map}, where the fastest growing topics in each period are labelled, and the documents are coloured according to the working group, if any, which cites them.
+In AR5, the clusters of documents around the \textbf{adsorption}, \textbf{buildings}, and \textbf{biochar} topics contain few IPCC citations, whereas the clusters around \textbf{food}, \textbf{health}, \textbf{adaptation}, and \textbf{GHGs} contain more.
+This is also evident in figure \ref{oecd_rep}c, where these topics display corresponding representation values.
+The IPCC, then, has been better at integrating new knowledge from these topics, and in general better at integrating new knowledge from WG II  than WG III topics.
+
+Within WG III topics, those that are well represented contain a greater proportion of social science research (figure \ref{oecd_rep}b).
+Topics on countries, policy, and prices are close to a proportional representation and are made up of around 30\% social science research.
+Waste, biochar, cement and coal, are more than 3 times more prevalent in the wider literature than in the literature cited by the IPCC, and are made up of around 5\% social science research.
+This pattern is not visible in other working groups (see Figure \ref{socsci-wgs}), and complicates the perception of the under-representation of the social sciences.
+
+Recalling policymakers' demands for more solution-oriented assessments \cite{Kowarsch2017}, we could also interpret the topics that are newer and under-represented as ``solutions-relevant''.
+Many deal with negative emissions, or with mitigation (or to a lesser extent adaptation) options in the transport, buildings and power sectors.
+All are arguably related to climate solutions.
+However, while policymakers' demands for solutions-oriented knowledge were rather about policy options, these under-represented new topics deal with more technical solutions.
+
+\subsection*{The IPCC as an informed decision-maker on topical representation}
+
+Deciding on the optimal proportion of each topic's literature to be cited by the IPCC is not a trivial task.
+A perfectly proportional representation of each topic is almost certainly not optimal, and as such, decisions about which topics to over-, or under- represent are best made by experts, not by a computer.
+Indeed, the IPCC itself is the best-placed institution to make these decisions.
+But in the age of ``Big Literature'' \cite{Nunez-Mir2016}, these decision should at best be underpinned by systematic knowledge of the landscape of the literature, and made in discussion with the wider research community, funders, policymakers and other stakeholders.
+
+The analysis in this study provide a useful input to this discussion.
+It could be argued that the under-represented technical literature on specific technological or sectoral solutions is not relevant to policymakers, and that working group III should give more weight to evidence about general policy instruments such as carbon taxes.
+Conversely, one could argue that establishing a technical understanding of specific climate solutions is as important a task as establishing a technical understanding of the physical science of climate change.
+The desire for more social science research in IPCC reports may imply, given the evidence here, that more social science research on climate change needs to be produced and funded, rather than that the IPCC should cite more of what already exists.
+Or, one could argue that, in light of the evidence that there is little social science research on solutions-relevant, under-represented topics, that the social sciences could do more to address more technical or specific solutions topics such as negative emissions, green concrete, or waste and recycling.
+
+An understanding of the topography of the literature helps bring these arguments to the foreground, and allows them to be made in an informed way.
+Machine reading the literature in this way is not without its limitations though, and indeed many are apparent in this analysis.
+The corpus of potentially relevant literature is of course much wider than what is included in this study.
+The analysis excludes studies about climate change that do not match our query, studies relevant to tackling climate change that do not mention it specifically, studies written in languages other than English (unless the abstract has been translated), studies not indexed in the Web of Science, and reports published outside peer reviewed journals, not to mention Indigenous knowledge \cite{Ford2016b}.
+Despite this, unless the social science literature in the above categories is systematically less often cited by the IPCC than the social science literature that was analysed in this study, or the solutions-relevant literature in the above categories is systematically more cited by the IPCC, then the two main conclusions of this study hold.
+
+Ultimately, computers can only \textit{assist} humans in understanding a climate change literature which is produced by human individuals and institutions.
+As in other areas of machine learning \cite{Barocas2016}, computational assessments of the literature run the risk of reproducing biases or gaps in the training data.
+However, just as with other applications of machine learning, machine-reading the science of climate change can provide information that helps us to understand gaps in what we have knowledge about, and potential biases, or options for emphasis, in how we represent that knowledge in the IPCC.
+%Machine learning approaches to understanding scientific literature are already latently present in our engagement with  when we use academic search engines or are recommended articles
+
 \end{linenumbers}
 
-%\end{multicols}
+\appendix
 
@@
 \linespread{1}
-\bibliography{Mendeley}
+%\bibliography{Mendeley}
+\begin{thebibliography}{10}
+
+	\bibitem{Bjurström2011}
+	Andreas Bjurstr{\"{o}}m and Merritt Polk.
+	\newblock {Physical and economic bias in climate change research: A
+		scientometric study of IPCC Third Assessment Report}.
+	\newblock {\em Climatic Change}, 108(1):1--22, 2011.
+
+	\bibitem{Grieneisen2011}
+	Michael Grieneisen and Minghua Zhang.
+	\newblock {The Current Status of Climate Change Research}.
+	\newblock {\em Nature Climate Change}, 1:72--73, 2011.
+
+	\bibitem{Haunschild2016}
+	Robin Haunschild, Lutz Bornmann, and Werner Marx.
+	\newblock {Climate Change Research in View of Bibliometrics}.
+	\newblock {\em PLoS ONE}, 11(7):1--19, 2016.
+
+	\bibitem{Minx2017l}
+	Jan~C. Minx, Max Callaghan, William~F. Lamb, Jennifer Garard, and Ottmar
+	Edenhofer.
+	\newblock {Learning about climate change solutions in the IPCC and beyond}.
+	\newblock {\em Environmental Science {\&} Policy}, 2017.
+
+	\bibitem{Kowarsch2017}
+	Martin Kowarsch, Jason Jabbour, Christian Flachsland, Marcel T.~J. Kok, Robert
+	Watson, Peter~M. Haas, Jan~C. Minx, Joseph Alcamo, Jennifer Garard, Pauline
+	Riousset, L{\'{a}}szl{\'{o}} Pint{\'{e}}r, Cameron Langford, Yulia Yamineva,
+	Christoph von Stechow, Jessica O'Reilly, and Ottmar Edenhofer.
+	\newblock {A road map for global environmental assessments}.
+	\newblock {\em Nature Climate Change}, 7(6):379--382, 2017.
+
+	\bibitem{Victor2015}
+	{David G. Victor}.
+	\newblock {Embed the social sciences in climate policy - David Victor}.
+	\newblock {\em Nature}, 520:7--9, 2015.
+
+	\bibitem{Barnes2013}
+	Jessica Barnes, Michael Dove, Myanna Lahsen, Andrew Mathews, Pamela McElwee,
+	Roderick McIntosh, Frances Moore, Jessica O'Reilly, Ben Orlove, Rajindra
+	Puri, Harvey Weiss, and Karina Yager.
+	\newblock {Contribution of anthropology to the study of climate change}.
+	\newblock {\em Nature Climate Change}, 3(6):541--544, 2013.
+
+	\bibitem{Hulme2010}
+	Mike Hulme and Martin Mahony.
+	\newblock {Climate change: What do we know about the IPCC?}
+	\newblock {\em Progress in Physical Geography}, 34(5):705--718, 2010.
+
+	\bibitem{Blei2012}
+	David Blei, Lawrence Carin, and David Dunson.
+	\newblock {Probabilistic topic models}.
+	\newblock {\em Communications of the ACM}, 55(4):77--84, 2012.
+
+	\bibitem{vandermaaten2008}
+	Laurens van~der Maaten and Geoffrey Hinton.
+	\newblock {Visualizing Data using t-SNE}.
+	\newblock {\em Journal of Machine Learning Research}, 9:2579--2605, 2008.
+
+	\bibitem{Edenhofer2015}
+	Ottmar Edenhofer and Martin Kowarsch.
+	\newblock {Cartography of pathways: A new model for environmental policy
+		assessments}.
+	\newblock {\em Environmental Science and Policy}, 51:56--64, 2015.
+
+	\bibitem{McKinnon2015}
+	Madeleine~C McKinnon, Samantha~H Cheng, Ruth Garside, Yuta~J Masuda, and
+	Daniel~C Miller.
+	\newblock {Sustainability: Map the evidence}.
+	\newblock {\em Nature}, 528(7581):185--187, 2015.
+
+	\bibitem{James2016}
+	Katy~L. James, Nicola~P. Randall, and Neal~R. Haddaway.
+	\newblock {A methodology for systematic mapping in environmental sciences}.
+	\newblock {\em Environmental Evidence}, 5(1):1--13, 2016.
+
+	\bibitem{Corbera2016}
+	Esteve Corbera, Laura Calvet-Mir, Hannah Hughes, and Matthew Paterson.
+	\newblock {Patterns of authorship in the IPCC Working Group III report}.
+	\newblock {\em Nature Climate Change}, 6(1):94--99, 2016.
+
+	\bibitem{Nunez-Mir2016}
+	Gabriela~C. Nunez-Mir, Basil~V. Iannone, Bryan~C. Pijanowski, Ningning Kong,
+	Songlin Fei, and Richard Fitzjohn.
+	\newblock {Automated content analysis: addressing the big literature challenge
+		in ecology and evolution}.
+	\newblock {\em Methods in Ecology and Evolution}, 7(11):1262--1272, 2016.
+
+	\bibitem{Ford2016b}
+	James~D. Ford, Laura Cameron, Jennifer Rubis, Michelle Maillet, Douglas
+	Nakashima, Ashlee~Cunsolo Willox, and Tristan Pearce.
+	\newblock {Including indigenous knowledge and experience in IPCC assessment
+		reports}.
+	\newblock {\em Nature Climate Change}, 6(4):349--353, 2016.
+
+	\bibitem{Barocas2016}
+	Solon Barocas and Andrew~D Selbst.
+	\newblock {Big Data's Disparate Impact}.
+	\newblock {\em California Law Review}, 104:671--732, 2016.
+
+\end{thebibliography}
 \bibliographystyle{unsrt}
 
+%\include{methods}
+
 \end{document}

### 2019-06-12 methods.tex
0 draft

@@
 
+	\setcounter{figure}{0}
+	\renewcommand\thefigure{SI.\arabic{figure}}
+
 	\subsection*{Data}
@@
 	This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on the Web of Science core collection.
-Though not exhaustive, it gives a good coverage of the literature in major peer-reviewed journals.	Each document is assigned to an assessment period according to the timeline shown in table 1.
+Though not exhaustive, the Web of Science gives a good coverage of the literature in major peer-reviewed journals.	Each document is assigned to an assessment period according to the timeline shown in table 1.
 
 	We use the references scraped from IPCC assessment reports from \citep{Minx2017l}, and attempt to match these with the results from the web of science.
-Table [x] shows the percentage of IPCC citations matched in each working group for each assessment report.
+Table \todo{}[x] shows the percentage of IPCC citations matched in each working group for each assessment report.
 
@@
 
-	For each period, the documents are transformed into a document-term matrix, each row represents a document, and each column represents a unique word.
+	The documents are transformed into a document-term matrix, where each row represents a document, and each column represents a unique word.
 Each cell contains the number of that column's terms in that document.
@@
 	\begin{equation}
-	tf(t,d) = f_{t,d} \mathrm{,}\quad idf(t,D) = \log\frac{N}{|\{d \in D:t \in d|\}}
+	tf(t,d) = f_{t,d} \mathrm{,}\quad idf(t,D) = \log\frac{N}{|\{d \in D:t \in d\}|}
 	\end{equation}
 
-	\subsection*{Non-negative Matrix Factorisation}
+	\subsection*{Topic Model}
 
-	Non-negative Matrix Factorisation (NMF) is an approach to topic modelling which factorises the term-frequency-inverse document frequency matrix \( V \) into the matrices \(W\), the topic-term matrix, and \( H \) the document-topic matrix, whose product approximates \(V\):
+	We use non-negative Matrix Factorisation (NMF) \cite{Lee1999}, an approach to topic modelling which factorises the term-frequency-inverse document frequency matrix \( V \) into the matrices \(W\), the topic-term matrix, and \( H \) the document-topic matrix, whose product approximates \(V\):
 
@@
 The combination of the two give the word scores in the document.
-For clarity in the figure, these are shown as simple counts, but in the model these are scaled according to each term's frequency within the corpus.
+For clarity in the figure, these are shown as simple counts, but in the model these are scaled according to each term's frequency within the corpus as explained above.
 
-%	In Dynamic Non-negative Matrix Factorisation, proposed by Greene \cite{Greene2016}, a separate topic model is run for each period.
-These are then joined through another topic model, which takes the topic-term matrices of the all periods as \( V \), and produces dynamic topics, which describe the window topics according to the words which occur in them.
-Similar topics across and within time periods are thereby grouped together.
-%	
-%	While Greene uses an automatic approach to deciding on topic numbers within time periods, we found the number of topics derived from topic coherence scores (as used by Greene) to be noisy, and instead opt for  identifying (subjectively) an optimal number of topics for each window.
-We do this by comparing topic lists with increasing numbers of topics, where similar topics are automatically placed next to each other.
-We similarly compare different numbers of Dynamic topics.
-%	
-%	We settle on [x,x,x,x,x] topics for ARs 1 to 6, and [x] dynamic topics.
+	Topics are calculated using the scikitlearn library \cite{Pedregosa2011}, and are saved in a database and topic visualisation system based on \cite{Chaney2012} \footnote{The system adds new functionality to \cite{Chaney2012} and combines it with a system for managing sets of documents and queries.
+The code and additional information is published online at \url{https://github.com/mcallaghan/tmv}}.
 
-	Topics are calculated using the scikitlearn library \cite{Pedregosa2011}
+	\subsubsection*{Model selection}
+
+	Topic models are calculated for 70, 80, 90, 100, 110, 120, 130 and 140 topics.
+The relative usefulness of each model was assessed subjectively by the authors, based on inspection of the online visualisation tool, and the spreadsheet \textbf{topic\_comparison.xlsx} accompanying the supporting information.
+The spreadsheet shows each set of topics in adjacent columns.
+Topics from each model are placed next to the topics with the largest number of each topic's 10 highest scoring words in common.
+This helps authors to find an appropriate level of granularity for the analysis.
 
@@
 A topic's window score is the sum of document-topic scores considering only documents in the given time window.
-To represent a dynamic topic's newness, we multiply each assessment period number by the share of it's total score occurring in that window, and take the mean of these scores.
+To represent a topic's newness, we multiply each assessment period number by the share of it's total score occurring in that window, and take the mean of these scores.
 A topic in which 100\% of documents which make it up occurred in assessment period 1 (6) would thereby receive a score of 1 (6), while a topic evenly distributed across all assessment periods would receive a score of 3.5.
 
-%	\begin{figure}
-%		\begin{center}
-%			\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
-%			\caption{SI Topic make up of a single document}
-%			\label{doc-topic}
-%		\end{center}
-%	\end{figure}
+	\subsubsection*{Disciplinary Entropy}
 
-%	\begin{figure}
-%		\begin{center}
-%			\includegraphics[width=1\linewidth]{plots/single_topic_3_11046.pdf}
-%			\caption{Word and document development of the ``Research'' dynamic topic}
-%			\label{sus}
-%		\end{center}
-%	\end{figure}
+	Disciplinary Entropy inverts the measurement of a conference's topical diversity suggested in \cite{Hall2008}, by measuring a topic \(z\)'s entropy \(H\), where
+
+	\begin{equation}
+		H(f|z) = -\sum_{i=1}^K \hat{p}(f|z) \log \hat{p}(f|z) 
+	\end{equation}
+
+	based on the empirical distribution of a field \(f\) in the documents \(d\) in each topic:
+
+	\begin{equation}
+		\hat{p}(f|z) = \sum_{d:z_d=z} \hat{p} (f|d) \hat{p} (d|z)
+	\end{equation}
+
+	\begin{figure}
+		\begin{center}
+			\includegraphics[width=1\linewidth]{plots_pub/topic_oecd_entropy.pdf}
+			\caption{SI Disciplinary Entropy}
+			\label{dis-entropy}
+		\end{center}
+	\end{figure}
+
+	\begin{figure}
+		\begin{center}
+			\includegraphics[width=1\linewidth]{plots_pub/single_doc_3_536594_1861.pdf}
+			\caption{SI Topic make up of a single document}
+			\label{doc-topic}
+		\end{center}
+	\end{figure}
+
+	\begin{figure}
+	\begin{center}
+		\includegraphics[width=1\linewidth]{plots_pub/ipcc_rep_wcs_simplified.pdf}
+		\caption{SI Representation by subfield}
+		\label{subfield}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=1\linewidth]{plots_pub/wgs_socsci.pdf}
+		\caption{SI Social science \& representation in topics across working groups}
+		\label{socsci-wgs}
+	\end{center}
+\end{figure}
+
+\subsection*{Glossary}
+
+\noindent\textbf{ncep:} National Centers for Environmental Protection
+
+\noindent\textbf{fco:} Fugacity of Carbon Dioxide
+
+\noindent\textbf{pfc:} Perflourocompound
+
+\noindent\textbf{otcs:} Open Top Chambers
+
+\noindent\textbf{dtr:} Diurnal Temperature Range
+
+\noindent\textbf{sres:} Special Report on Emissions Scenarios (200)
+
+\noindent\textbf{petm:} Paleocene Eocene Thermal Maximum
+
+\noindent\textbf{amf:}  Arbuscular Mycorrhizal Fungal
+
+\noindent\textbf{sf5cf3:} trifluoromethyl sulfur pentafluoride (A Potent Greenhouse Gas Identified in the Atmosphere, 2000)
+
+\noindent\textbf{clc:} Chemical Looping Combustion
+
+\noindent\textbf{cwd:} Coarse woody debris
+
+\noindent\textbf{etm:} Enhanced Thematic Mapper (NASA satellite sensor)
+
+\noindent\textbf{cmip5:} Coupled Model Intercomparison Project 5 (Starting 2008)
+
+\noindent\textbf{cmip3:} Coupled Model Intercomparison Project phase 3 (first published 2007 \cite{Meehl2007})
+
+\noindent\textbf{mofs:} metal-organic frameworks (for CO2 storage)
+
+\noindent\textbf{sdm:} statistical-dynamical model
+
+\noindent\textbf{mmms:} Mixed Matrix Membranes (for CO2 capture)
+
+\noindent\textbf{cop21:} 21st Conference of Parties (Paris 2015)
+
+\noindent\textbf{c3n4:} Carbon nitride (a synthetic nanomaterial used for hydrogen production)
+
+\noindent\textbf{sdg:} Sustainable Development Goals
+
+\noindent\textbf{indc:} Intended Nationally Determined Contributions
 
@@
 \linespread{1}
-\bibliography{Mendeley}
+%\bibliography{Mendeley}
+
+\begin{thebibliography}{1}
+
+	\bibitem{Grieneisen2011}
+	Michael Grieneisen and Minghua Zhang.
+	\newblock {The Current Status of Climate Change Research}.
+	\newblock {\em Nature Climate Change}, 1:72--73, 2011.
+
+	\bibitem{Minx2017l}
+	Jan~C. Minx, Max Callaghan, William~F. Lamb, Jennifer Garard, and Ottmar
+	Edenhofer.
+	\newblock {Learning about climate change solutions in the IPCC and beyond}.
+	\newblock {\em Environmental Science {\&} Policy}, 2017.
+
+	\bibitem{Lee1999}
+	D~D Lee and H~S Seung.
+	\newblock {Learning the parts of objects by non-negative matrix factorization.}
+	\newblock {\em Nature}, 401(6755):788--91, 1999.
+
+	\bibitem{Pedregosa2011}
+	Fabian Pedregosa, Ga{\"{e}}l Varoquaux, Alexandre Gramfort, Vincent Michel,
+	Bertrand Thirion, Olivier Grisel, Mathieu Blondel, Peter Prettenhofer, Ron
+	Weiss, Vincent Dubourg, Jake Vanderplas, Alexandre Passos, David Cournapeau,
+	Matthieu Brucher, Mattheiu Perrot, and {\'{E}}douard Duchesnay.
+	\newblock {Scikit-learn: Machine Learning in Python Fabian}.
+	\newblock {\em Journal of Machine Learning Research}, 12:2825--2830, 2011.
+
+	\bibitem{Chaney2012}
+	Allison J~B Chaney and David~M. Blei.
+	\newblock {Visualizing Topic Models}.
+	\newblock {\em Icwsm}, pages 419--422, 2012.
+
+	\bibitem{Hall2008}
+	David Hall, Daniel Jurafsky, and Christopher~D. Manning.
+	\newblock {Studying the history of ideas using topic models}.
+	\newblock {\em Proceedings of the Conference on Empirical Methods in Natural
+		Language Processing - EMNLP '08}, pages 363--371, 2008.
+
+	\bibitem{Meehl2007}
+	Gerald~A. Meehl, Curt Covey, Thomas Delworth, Mojib Latif, Bryant McAvaney,
+	John~F.B. Mitchell, Ronald~J. Stouffer, and Karl~E. Taylor.
+	\newblock {The WCRP CMIP3 multimodel dataset: A new era in climatic change
+		research}.
+	\newblock {\em Bulletin of the American Meteorological Society},
+	88(9):1383--1394, 2007.
+
+\end{thebibliography}
+
 \bibliographystyle{unsrt}

### 2019-06-12 code/assemble_pubs.sh

@@ -4,14 +4,8 @@
 
 echo "assembling plots for run $1"
 
-cp tsne_results/plots/run_$1_s_0_p$2_all_topic_words_wgs.png plots_pub/all_topic_words_wgs.png
+cp tsne_results/plots/run_$1_s_0_p$2_all_topic_words_oecds.png plots_pub/all_topic_words_oecds.png
+cp tsne_results/plots/run_$1_s_0_p$2_all_topic_words_oecds.pdf plots_pub/all_topic_words_oecds.pdf
 
-cp tsne_results/plots/run_$1_s_0_p$2_all_topic_words_wgs.png plots_pub/all_topic_words_ars.png
-
-cp tsne_results/plots/run_$1_s_0_p$2_all_topic_words_wgs.png plots_pub/all_topic_words_oecds.png
-
-cp plots/ipcc_representation/ipcc_rep_new$1_all.pdf plots_pub/ipcc_represntation.pdf
-
-cp plots/ipcc_representation/ipcc_rep_oecds_time.pdf plots_pub/ipcc_rep_oecds_time.pdf
-
-cp plots/ipcc_representation/ipcc_rep_oecds_simplified.pdf plots_pub/ipcc_rep_oecds_simplified.pdf
+cp tsne_results/plots/run_$1_s_0_p$2_evolution_4.png plots_pub/topic_evolution_4.png
+cp tsne_results/plots/run_$1_s_0_p$2_evolution_4.pdf plots_pub/topic_evolution_4.pdf

### 2019-06-13 methods.tex

--- 2019-05-22 methods.tex
@@
 	We use the references scraped from IPCC assessment reports from \citep{Minx2017l}, and attempt to match these with the results from the web of science.
-Table [x] shows the percentage of IPCC citations matched in each working group for each assessment report.
+Table \todo{}[x] shows the percentage of IPCC citations matched in each working group for each assessment report.
 
@@
 
-	\subsection*{Non-negative Matrix Factorisation}
+	\subsection*{Topic Model}
 
-	Non-negative Matrix Factorisation (NMF) is an approach to topic modelling which factorises the term-frequency-inverse document frequency matrix \( V \) into the matrices \(W\), the topic-term matrix, and \( H \) the document-topic matrix, whose product approximates \(V\):
+	We use non-negative Matrix Factorisation (NMF), an approach to topic modelling which factorises the term-frequency-inverse document frequency matrix \( V \) into the matrices \(W\), the topic-term matrix, and \( H \) the document-topic matrix, whose product approximates \(V\):
 
@@
 The combination of the two give the word scores in the document.
-For clarity in the figure, these are shown as simple counts, but in the model these are scaled according to each term's frequency within the corpus.
+For clarity in the figure, these are shown as simple counts, but in the model these are scaled according to each term's frequency within the corpus as explained above.
+
+	Topics are calculated using the scikitlearn library \cite{Pedregosa2011}
+
+	\subsubsection*{Model selection}
 
@@
 
-	Topics are calculated using the scikitlearn library \cite{Pedregosa2011}
-
 	\subsubsection*{Topic Representation and Newness}
@@
 A topic's window score is the sum of document-topic scores considering only documents in the given time window.
-To represent a dynamic topic's newness, we multiply each assessment period number by the share of it's total score occurring in that window, and take the mean of these scores.
+To represent a topic's newness, we multiply each assessment period number by the share of it's total score occurring in that window, and take the mean of these scores.
 A topic in which 100\% of documents which make it up occurred in assessment period 1 (6) would thereby receive a score of 1 (6), while a topic evenly distributed across all assessment periods would receive a score of 3.5.
 
-%	\begin{figure}
-%		\begin{center}
-%			\includegraphics[width=1\linewidth]{plots/single_doc_3_536594.pdf}
-%			\caption{SI Topic make up of a single document}
-%			\label{doc-topic}
-%		\end{center}
-%	\end{figure}
+	\subsubsection*{Disciplinary Entropy}
+
+	\begin{figure}
+		\begin{center}
+			\includegraphics[width=1\linewidth]{plots_pub/topic_oecd_entropy.pdf}
+			\caption{SI Disciplinary Entropy}
+			\label{dis-entropy}
+		\end{center}
+	\end{figure}
+
+	\begin{figure}
+		\begin{center}
+			\includegraphics[width=1\linewidth]{plots/single_doc_3_536594_1861.pdf}
+			\caption{SI Topic make up of a single document}
+			\label{doc-topic}
+		\end{center}
+	\end{figure}
+
+	\begin{figure}
+	\begin{center}
+		\includegraphics[width=1\linewidth]{plots_pub/ipcc_rep_wcs_simplified.pdf}
+		\caption{SI Representation by subfield}
+		\label{subfield}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=1\linewidth]{plots_pub/wgs_socsci.pdf}
+		\caption{SI Social science \& representation in topics across working groups}
+		\label{socsci-wgs}
+	\end{center}
+\end{figure}
 

### 2019-06-13 main.tex
draft 1

@@
 
-\noindent We know that the scientific literature on climate change is growing rapidly \cite{Grieneisen2011, Haunschild2016}, and that this growth poses problems for the IPCC.
-Their task of providing a comprehensive and transparent summary of the literature on climate change is severely challenged by the growth of the literature: the proportion of the literature that gets cited by the IPCC is dwindling \cite{Minx2017l}.
-In the light of policymakers' demand for more solutions-oriented knowledge from assessments \cite{Kowarsch2017}; calls for more representation of certain disciplines in IPCC reports \cite{Victor2015, Barnes2013}; and criticism of bias in the knowledge reflected by the IPCC \cite{Bjurström2011, Hulme2010}, what gets cited and what doesn't is more salient than ever.
-
-However, we know little about thematic trends within the literature, or how the IPCC performs in reflecting different parts of this growing body of knowledge on climate change.
-We lack an overview of the literature itself, and without this, our understanding of the IPCC \cite{} lacks the context of the literature which it is supposed to assess.
-Mapping out this literature, and its reflection in IPCC reports is a crucial task if we are to assess and improve the IPCC's comprehensiveness.
+\noindent We live in an age of ``Big Literature'' 
+\cite{Nunez-Mir2016}, where the science of climate change is expanding rapidly \cite{Grieneisen2011, Haunschild2016}.
+In the five years since the publication of the last IPCC assessment report \cite{IPCC2014c}, 201,606 papers were published (see Table \ref{tab}).
+This is almost as much as the 204,585 papers published during the first five assessment periods, a period of nearly 30 years.
+The vocabulary of the literature has also expanded - from 2,000 unique words in AR1 to 94,746 words so far in AR6 - indicating that the field has incorporated new content.
+For example, the zika virus, which was mentioned in 182 articles from 2014-2018, had never before been discussed in the titles or abstracts of articles relating to climate change.
+Yet it has emerged as a topic of high relevance: the incidence of the virus, the outbreak of which in Brazil in 2016 was declared a public health emergency by the WHO, is set to increase under rising global temperatures \cite{Rao2019}.
+Similar rapid emergences can be seen for [Intended] Nationally Determined Contributions ([I]NDCs) and Sustainable Development Goals (SDGs) in AR6, and Biochar and REDD (The United Nations Collaborative Programme on Reducing Emissions from Deforestation and Forest Degradation in Developing Countries) in AR5, among others.
+This large and rapidly evolving literature demands innovative machine-reading methods to enable understanding of the field at scale.
 
@@
 
-Table \ref{tab} depicts the scale of the challenge faced by the IPCC.
-Since the publication of the fifth assessment report (AR5), almost as much literature has been published as in the 30 years previously.
-Moreover, not only are more articles being published, but the vocabulary of climate knowledge has expanded.
-While the 8,539 documents published in AR2 contained 12,480 unique words, the 201,606 documents published in AR6 contain a vocabulary of 94,746 unique words.
+Research synthesis offers structured methodologies for integrating knowledge from bodies of evidence \cite{Chalmers2002}.
+Systematic reviews, which are common in the health sciences, collect all literature relevant to a specific question, in order to establish whether findings are consistent and generalisable \cite{Mulrow597}.
+Already in 1994, systematic review was being proposed as an answer to the ``small mountain of information'' presented by two million annual publications in biomedical literature \cite{Mulrow597}.
+Although climate change faces a similar scale problem, systematic review is little used in the field \cite{Berrang-Ford2015}.
+Systematic maps are a more recent methodological development, which show the state of the evidence in a broad subject area \cite{James2016}.
+There have been high profile calls to broaden the applications of evidence mapping in sustainable development \cite{McKinnon2015}, and they are similar underused in climate change, with only 25 of the more than 400,000 relevant papers containing the phrase "systematic map" in the abstract or title.
 
-The zika virus, the Sustainable Development Goals (SDGs), Intended Nationally Determined Contributions (INDCs), and mixed matrix membranes (MMMs) are all significant parts of the literature since 2014 which were simply not discussed in the context of climate change before the last IPCC report.
-In view of this expanding vocabulary, this study employs topic modelling to draw out patterns in the content of scientific literature.
-Topic modelling is an unsupervised machine-learning technique, where patterns of word co-occurrences in documents are used to learn a set of topics which can be used to describe the corpus \cite{Blei2012}.
-It is applied here for the first time to the whole scientific literature on climate change.
+In the research synthesis field, researchers are introducing new methods from natural language processing and machine-learning to scale up synthesis work \cite{OMara-Eves2015, Westgate2018a}.
+In the same way, this study uses topic modelling \cite{Blei2010} to map out the vast body of evidence on climate change.
+Topic modelling is an unsupervised machine-learning technique, where patterns of word co-occurrences in documents are used to learn a set of topics which can be used to describe the corpus.
+The word topic derives from the Greek word for place (topos), and by \textit{situating} the documents in a reduced-form projection of their thematic content (see Figure \ref{oecd_topic_map}), we create a \textit{topographic map} of the literature on climate change.
+Such a systematic engagement with the thematic content of the climate science is missing from the literature so far.%To our knowledge, this is the first
 
-\subsection*{A Topography of Climate Change Research}
+Systematic maps can have several uses: from the identification of knowledge gaps and gluts to the can identification of authors or institutions with expertise on a subject.
+The map in this paper also has several potential uses, but we focus here on using the map to understand the evolution of relationship between the five IPCC assessment reports and the wider literature on climate change.
+Big Literature in climate change poses a great challenge to the IPCC, who's mandate is to comprehensively assess the science of climate change \cite{IPCC2013}.
+The ratio of studies cited in IPCC reports to the number or relevant studies has declined from 60\% to 20\%  \cite{Minx2017l}, thus increasing the risk of a lack of comprehensiveness, or even bias.
 
-Topics, from the greek word ``topos" (meaning place), refer here to concepts or themes within the literature.
-Using the same geographic-thematic metaphor, the topographic map shown in figure 1 \textit{situates} the 400,000 documents about climate change in a topical landscape derived from the 140 topics discovered through topic modelling.
-Using t-distributed stochastic network embedding \cite{vandermaaten2008} (t-SNE) as a dimensionality reduction technique, the 140 dimensional topic space is \textit{projected} onto two dimensions, such that documents with similar topical content are placed next to each other.
-If scientists, in global environmental assessments, act as mapmakers \cite{Edenhofer2015}, this topography, as a broad outline of the features of the research landscape, help understand the relationship of the map to the mapped.
+What gets included in IPCC reports is also much discussed.
+Policymakers demand more solution-oriented knowledge \cite{Kowarsch2017}, and there have been calls for the inclusion of more knowledge from the social sciences \cite{Victor2015}.
+But what we say about the literature cited in the IPCC has often been limited by a failure to consider the context of the wider literature.
+A scientometric study from 2011 claimed that the IPCC gave a greater \textit{emphasis} to natural sciences and, within the social sciences, to economics \cite{Bjurström2011}.
+This claim has subsequently been interpreted as a disciplinary bias by the IPCC \cite{Hulme2010, Corbera2016} towards the natural sciences, but the study operationalised disciplinary emphasis as simply the share of citations from each field, and was based on analysis of the Third Assessment report, published in 2001.
+In the following sections, we compare distributions of literature in the subset that is cited by the IPCC and the wider corpora, to analyse the \textit{representation}, proportional or otherwise, of scientific fields, as well as of topics.
 
-To make the map readable, we find clusters of documents relating to each topic, and superimpose the topic label in the center of each cluster (see methods for a more detailed description).
-Documents are coloured by their categorisation in the Web of Science into broad disciplinary categories, showing us how the topical content of the documents fits into disciplinary structures.
-Across the map, it is clear that different disciplines focus on different groups of topics, with more natural science research on the left hand side of the map, more engineering in the upper right and right, more agricultural sciences at the bottom of the map, and more social sciences on the inner right.
+\subsection*{Proportionality in IPCC citations}
 
-\todo{Get rid of numbers, replace with letters ?}
+Figure \ref{oecd_rep}.a shows that the social sciences were indeed under-represented in the third assessment report, but by the fifth assessment report were over-represented.
+Likewise, other social sciences than economics have become better represented since AR3  (see figure \ref{subfield}f) with social \& economic geography (4.3\% of the literature), political science (1.0\%), and sociology (0.8\%) showing improved representation in AR5 compared to AR3, and Social and economic geography, political science, and other social sciences better represented than economics when taking into account the distribution of studies in the literature.
 
-The map also allows us to examine topics consisting of research from across disciplines.
-With reference to figure \ref{dis-entropy} which shows the disciplinary diversity of each topic, we can see that research on coral comes almost exclusively from the natural sciences, while papers discussing socioeconomic issues come from a variety of disciplines.
-
-The map plays an important role in generating knowledge about what we do and do not know about climate change.
-Though not strictly systematic, in that all studies have been checked for relevance and categorised by hand, it moves in the direction of evidence maps, or systematic maps \cite{McKinnon2015, James2016}, by categorising and quantifying the literature and its uptake by the IPCC.
-The approach is weakly systematic in the sense that the studies are selected according transparent criteria (see methods), and are categorised consistently by the topic model.
-Further, that the categories are learnt from the data without human input, means that we can find patterns we didn't know we were looking for.
+This challenges what we think we know about the IPCC.
+The social sciences, by now, are actually the best represented field, with a share in the literature cited by IPCC reports [1.5] times as high as in the literature at large.
+On the other hand the Agricultural Sciences and Engineering \& Technology have been consistently under-represented, with [2.5] and [3.5] times the share of studies in the wider literature than in the literature cited by the IPCC in AR5 respectively.
+% (Humanities are also underrepresented, but making up only 0.9\% of the wider literature, the proportionality is particularly sensitive).
 
@@
 	\begin{center}
-		\includegraphics[width=180mm]{plots_pub/all_topic_words_oecds.pdf}
+		\includegraphics[width=180mm]{plots_pub/all_topic_words_oecds.png}
 		\caption{A map of the literature on climate change.
@@
 
-\subsection*{Disciplinary bias in IPCC citations?}
+%\subsection*{A Topography of Climate Change Research}
 
-It was argued after the fifth assessment report that the IPCC needed to do more to incorporate knowledge from the social sciences \cite{Victor2015}.
-Further, a scientometric study from 2011 claimed that the IPCC gave a greater \textit{emphasis} to natural sciences and, within the social sciences, to economics \cite{Bjurström2011}.
-This claim has been interpreted as a disciplinary bias by the IPCC \cite{Hulme2010, Corbera2016}, but the study operationalised disciplinary emphasis as simply the share of citations from each field, and was based on analysis of the Third Assessment report, published in 2001.
-The share of citations in each discipline does not take into account the distribution of climate change research across disciplines in the wider literature.
-Here we look at \textit{representativeness}, that is, the share of IPCC citations in each field divided by the share of all climate related documents in that field, and carry out this analysis across assessment periods.
+Figure \ref{oecd_topic_map} shows the 400,000 documents on climate change in our dataset in a dimensionality reduction enabled representation of their topic structure, with topic labels placed near clusters of documents highly relevant to each topic.
+The map shows the high proportion of the natural sciences in climate change research, and the large proportion of the topic space dominated by natural science publications.
+These two features of the landscape account for the proportionally high share of natural science publications in IPCC citations.
+
+The thematic structure of the literature also maps well to the disciplinary structure, with clusters of social science topics, such as \textbf{policy}, \textbf{research}, \textbf{sector} and \textbf{growth} in the centre right of the graph, and natural sciences on the left.
+With reference to figure \ref{dis-entropy}, we can identify the topics which are more or less distributed across disciplines.
+\textbf{Coral}, for example, is almost exclusively discussed in the natural sciences, while papers on socio-economic issues are discussed in a variety of disciplines.
+Further, by using the topographical map, we can dig down further into the subject matter that is more or less proportionately represented, within and across disciplines.
 
@@
 
-Looked at this way (Figure 2.a), we see that the social sciences were indeed under-represented in the third assessment report, but by the fifth assessment report were over-represented.
-The disciplines under-represented in IPCC reports (with respect to the distribution of studies in the wider literature) are in fact Agricultural Sciences, Engineering \& Technology and Humanities (although the humanities make up a very small proportion of the literature).
-In each field, the under-representation has been present across assessment reports.
-
-A similar story is visible within the social sciences (see figure \ref{subfield}f). 
-Economics was previously over-represented among social sciences, while other subfields were under-represented.
-In AR5, though, the share of economics citations in the IPCC was close to that in the wider literature, while social \& economic geography (4.3\% of the literature), political science (1.0\%), and sociology (0.8\%) were better represented than in AR3 and above or close to a proportional representation.
-
-With more up to date data and a more comprehensive method, both results contradict previous evidence on disciplinary representation in the IPCC.
-This new evidence is a compelling reason to rethink our view of the relationship between disciplinary knowledge and the IPCC.
  %, and to further investigate the content of the documents that are more less proportionately represented in the IPCC.
@@
 	\begin{center}
-		\includegraphics[width=180mm]{plots_pub/topic_evolution_4.pdf}
+		\includegraphics[width=180mm]{plots_pub/topic_evolution_4.png}
 		\caption{Evolution of the landscape of climate change literature}
@@
 
-Beyond the disciplinary categories analysed so far, the topographical map helps us to dig down further into the themes that are more or less proportionately represented.
-Figures \ref{oecd_rep}b and \ref{oecd_rep}c plot the representation of the topics.
+Figures \ref{oecd_rep}b and \ref{oecd_rep}c plot the representation of the topics shown in the map.
 Figure \ref{oecd_rep}c shows that topics more commonly cited by IPCC working group I are older and largely better represented in IPCC reports.
-It makes intuitive sense that these topics, for example on ozone, oceans, clouds, aerosols and sea levels, are older, predominantly cited by WG I, and well cited by IPCC reports, as these are some of the core topics of the physical science of climate change.
+It makes intuitive sense that these topics, for example \textbf{ozone}, \textbf{oceans}, \textbf{clouds}, \textbf{aerosols} and \textbf{sea levels}, are older, predominantly cited by WG I, and well cited by IPCC reports, as these are some of the core topics of the physical science of climate change.
 
@@
 They are the topics that could be seen as potential gaps in the IPCC's coverage of the science.
-These topics are primarily in working group III, on the mitigation of climate change, with the exception of adsorption, CLC and hydrogen which are primarily of relevance to WG III but are miscategorised due to the low number of citations of relevant documents \footnote{For example, the word ``capacity" is relevant to the adsorption topic, so documents talking about adaptive capacity receive a low relevance score for that topic.
+Because they are new areas of knowledge, they may be highly salient in a periodic assessment process.
+These topics are primarily in working group III (mitigation), with the exception of adsorption, CLC and hydrogen which are primarily of relevance to WG III but are miscategorised due to the low number of citations of relevant documents and citations of tangentially relevant documents by other working groups \footnote{For example, the word ``capacity" is relevant to the adsorption topic, so documents talking about adaptive capacity receive a low relevance score for that topic.
 Because only very few documents highly relevant to the adsorption topic (in that they talk about adsorption or adsorptive capacity) are cited by the IPCC, and many of the weakly relevant documents are cited by the IPCC, the sum of the topic scores of the weakly relevant WG II documents outweighs the sum of the topic scores of the strongly relevant WG III documents}.
-and citations of tangentially relevant documents by other working groups
 
-Although it is not surprising that these newer topics are less well represented than the older topics that make up the core of the physical science research on climate change, the difference between these new topics and other new topics that are better represented is intriguing.
+Although it is perhaps not surprising that these newer topics are less well represented than the older topics that make up the core of the physical science research on climate change, the difference between these new topics and other new topics that are better represented is intriguing.
 This difference is visible in figure \ref{evolution-map}, where the fastest growing topics in each period are labelled, and the documents are coloured according to the working group, if any, which cites them.
@@
 Within WG III topics, those that are well represented contain a greater proportion of social science research (figure \ref{oecd_rep}b).
-Topics on countries, policy, and prices are close to a proportional representation and are made up of around 30\% social science research.
-Waste, biochar, cement and coal, are more than 3 times more prevalent in the wider literature than in the literature cited by the IPCC, and are made up of around 5\% social science research.
+The topics \textbf{countries}, \textbf{policy}, and \textbf{prices} are close to a proportional representation and are made up of around 30\% social science research.
+\textbf{Waste}, \textbf{biochar}, \textbf{cement} and \textbf{coal}, are more than 3 times more prevalent in the wider literature than in the literature cited by the IPCC, and are made up of around 5\% social science research.
 This pattern is not visible in other working groups (see Figure \ref{socsci-wgs}), and complicates the perception of the under-representation of the social sciences.
@@
 All are arguably related to climate solutions.
-However, while policymakers' demands for solutions-oriented knowledge were rather about policy options, these under-represented new topics deal with more technical solutions.
+However, while policymakers' demands for solutions-oriented knowledge were rather about policy options, these under-represented new topics deal with more technical solutions and are found rather in technical disciplines within engineering \& technology and the agricultural sciences.
 
@@
 The desire for more social science research in IPCC reports may imply, given the evidence here, that more social science research on climate change needs to be produced and funded, rather than that the IPCC should cite more of what already exists.
-Or, one could argue that, in light of the evidence that there is little social science research on solutions-relevant, under-represented topics, that the social sciences could do more to address more technical or specific solutions topics such as negative emissions, green concrete, or waste and recycling.
+Or, one could argue that, in light of the evidence that there is little social science research on solutions-relevant, under-represented topics, that the social sciences could do more to address technical or specific solutions such as negative emissions, green concrete, or waste and recycling.
 
@@
 The analysis excludes studies about climate change that do not match our query, studies relevant to tackling climate change that do not mention it specifically, studies written in languages other than English (unless the abstract has been translated), studies not indexed in the Web of Science, and reports published outside peer reviewed journals, not to mention Indigenous knowledge \cite{Ford2016b}.
-Despite this, unless the social science literature in the above categories is systematically less often cited by the IPCC than the social science literature that was analysed in this study, or the solutions-relevant literature in the above categories is systematically more cited by the IPCC, then the two main conclusions of this study hold.
+Despite this, unless the social science literature in the above categories is cited systematically less often  by the IPCC than the social science literature that was analysed in this study, then the main conclusions of this study hold.
+Topic models also carry limitations, and do not present the \textit{objective} truth about a corpus, given that they can be sensitive to modeller choices, such as the number of topics.
+However, the observations about the under-representation of solutions-relevant topics are robust across a broad range of topic numbers \ref{top-rep-ks}.
 
-Ultimately, computers can only \textit{assist} humans in understanding a climate change literature which is produced by human individuals and institutions.
+Computational methods then, provide \textit{assistance} to humans in understanding a climate change literature that is produced by human individuals and institutions.
 As in other areas of machine learning \cite{Barocas2016}, computational assessments of the literature run the risk of reproducing biases or gaps in the training data.
 However, just as with other applications of machine learning, machine-reading the science of climate change can provide information that helps us to understand gaps in what we have knowledge about, and potential biases, or options for emphasis, in how we represent that knowledge in the IPCC.
+In this way, we can more effectively meet the challenges posed by Big Literature to global environmental assessments.
 %Machine learning approaches to understanding scientific literature are already latently present in our engagement with  when we use academic search engines or are recommended articles
@@
 \linespread{1}
-%\bibliography{Mendeley}
-\begin{thebibliography}{10}
-
-	\bibitem{Bjurström2011}
-	Andreas Bjurstr{\"{o}}m and Merritt Polk.
-	\newblock {Physical and economic bias in climate change research: A
-		scientometric study of IPCC Third Assessment Report}.
-	\newblock {\em Climatic Change}, 108(1):1--22, 2011.
-
-	\bibitem{Grieneisen2011}
-	Michael Grieneisen and Minghua Zhang.
-	\newblock {The Current Status of Climate Change Research}.
-	\newblock {\em Nature Climate Change}, 1:72--73, 2011.
-
-	\bibitem{Haunschild2016}
-	Robin Haunschild, Lutz Bornmann, and Werner Marx.
-	\newblock {Climate Change Research in View of Bibliometrics}.
-	\newblock {\em PLoS ONE}, 11(7):1--19, 2016.
-
-	\bibitem{Minx2017l}
-	Jan~C. Minx, Max Callaghan, William~F. Lamb, Jennifer Garard, and Ottmar
-	Edenhofer.
-	\newblock {Learning about climate change solutions in the IPCC and beyond}.
-	\newblock {\em Environmental Science {\&} Policy}, 2017.
-
-	\bibitem{Kowarsch2017}
-	Martin Kowarsch, Jason Jabbour, Christian Flachsland, Marcel T.~J. Kok, Robert
-	Watson, Peter~M. Haas, Jan~C. Minx, Joseph Alcamo, Jennifer Garard, Pauline
-	Riousset, L{\'{a}}szl{\'{o}} Pint{\'{e}}r, Cameron Langford, Yulia Yamineva,
-	Christoph von Stechow, Jessica O'Reilly, and Ottmar Edenhofer.
-	\newblock {A road map for global environmental assessments}.
-	\newblock {\em Nature Climate Change}, 7(6):379--382, 2017.
-
-	\bibitem{Victor2015}
-	{David G. Victor}.
-	\newblock {Embed the social sciences in climate policy - David Victor}.
-	\newblock {\em Nature}, 520:7--9, 2015.
-
-	\bibitem{Barnes2013}
-	Jessica Barnes, Michael Dove, Myanna Lahsen, Andrew Mathews, Pamela McElwee,
-	Roderick McIntosh, Frances Moore, Jessica O'Reilly, Ben Orlove, Rajindra
-	Puri, Harvey Weiss, and Karina Yager.
-	\newblock {Contribution of anthropology to the study of climate change}.
-	\newblock {\em Nature Climate Change}, 3(6):541--544, 2013.
-
-	\bibitem{Hulme2010}
-	Mike Hulme and Martin Mahony.
-	\newblock {Climate change: What do we know about the IPCC?}
-	\newblock {\em Progress in Physical Geography}, 34(5):705--718, 2010.
-
-	\bibitem{Blei2012}
-	David Blei, Lawrence Carin, and David Dunson.
-	\newblock {Probabilistic topic models}.
-	\newblock {\em Communications of the ACM}, 55(4):77--84, 2012.
-
-	\bibitem{vandermaaten2008}
-	Laurens van~der Maaten and Geoffrey Hinton.
-	\newblock {Visualizing Data using t-SNE}.
-	\newblock {\em Journal of Machine Learning Research}, 9:2579--2605, 2008.
-
-	\bibitem{Edenhofer2015}
-	Ottmar Edenhofer and Martin Kowarsch.
-	\newblock {Cartography of pathways: A new model for environmental policy
-		assessments}.
-	\newblock {\em Environmental Science and Policy}, 51:56--64, 2015.
-
-	\bibitem{McKinnon2015}
-	Madeleine~C McKinnon, Samantha~H Cheng, Ruth Garside, Yuta~J Masuda, and
-	Daniel~C Miller.
-	\newblock {Sustainability: Map the evidence}.
-	\newblock {\em Nature}, 528(7581):185--187, 2015.
-
-	\bibitem{James2016}
-	Katy~L. James, Nicola~P. Randall, and Neal~R. Haddaway.
-	\newblock {A methodology for systematic mapping in environmental sciences}.
-	\newblock {\em Environmental Evidence}, 5(1):1--13, 2016.
-
-	\bibitem{Corbera2016}
-	Esteve Corbera, Laura Calvet-Mir, Hannah Hughes, and Matthew Paterson.
-	\newblock {Patterns of authorship in the IPCC Working Group III report}.
-	\newblock {\em Nature Climate Change}, 6(1):94--99, 2016.
-
-	\bibitem{Nunez-Mir2016}
-	Gabriela~C. Nunez-Mir, Basil~V. Iannone, Bryan~C. Pijanowski, Ningning Kong,
-	Songlin Fei, and Richard Fitzjohn.
-	\newblock {Automated content analysis: addressing the big literature challenge
-		in ecology and evolution}.
-	\newblock {\em Methods in Ecology and Evolution}, 7(11):1262--1272, 2016.
-
-	\bibitem{Ford2016b}
-	James~D. Ford, Laura Cameron, Jennifer Rubis, Michelle Maillet, Douglas
-	Nakashima, Ashlee~Cunsolo Willox, and Tristan Pearce.
-	\newblock {Including indigenous knowledge and experience in IPCC assessment
-		reports}.
-	\newblock {\em Nature Climate Change}, 6(4):349--353, 2016.
-
-	\bibitem{Barocas2016}
-	Solon Barocas and Andrew~D Selbst.
-	\newblock {Big Data's Disparate Impact}.
-	\newblock {\em California Law Review}, 104:671--732, 2016.
-
-\end{thebibliography}
+\bibliography{Mendeley}
 \bibliographystyle{unsrt}
 
-%\include{methods}
+\include{methods}
 

### 2019-06-26 main.tex
jan's edits

@@
 \author[1,2]{Max Callaghan}
+\author[1,2]{Jan Minx}
+\author[2]{Piers M. Forster}
 
 \affil[1]{Mercator Research Institute on Global Commons and Climate Change, Torgauer Straße, 10829 Berlin, Germany}
-\affil[2]{School of Earth and Environment, University of Leeds, Leeds LS2 9JT, United Kingdom}
+\affil[2]{Priestley International Centre for Climate, University of Leeds, Leeds LS2 9JT, United Kingdom}
 
@@
 		\noindent We live in an age of ``Big Literature'' 
-\cite{Nunez-Mir2016}, where the science of climate change is expanding rapidly \cite{Grieneisen2011, Haunschild2016}.
-In the five years since the publication of the last IPCC assessment report \cite{IPCC2014c}, 201,606 papers were published (see Table \ref{tab}).
+		\cite{Nunez-Mir2016, Minx2017}, where the science of climate change is expanding exponentially \cite{Grieneisen2011, Haunschild2016}.
+For example, in the five years since the publication of the last IPCC assessment report \cite{IPCC2014c}, 201,606 papers were published in WoS (see Table \ref{tab}).
 This is almost as much as the 204,585 papers published during the first five assessment periods, a period of nearly 30 years.
-The vocabulary of the literature has also expanded - from 2,000 unique words in AR1 to 94,746 words so far in AR6 - indicating that the field has incorporated new content.
+A total of about 350,000 new publications can be expected for the current sixth assessment cycle of the IPCC.
+If we assume that WOS contains roughly about 41\% of the entire climate change literature (Khabasa), this yields a total number of new publications of around 850,000 for this assessment cycle.
+But the literature has also become more diverse.
+This is, for example, reflected in the expansion of vocabulary in this literature - from 2,000 unique words in AR1 to 94,746 words so far in AR6 - indicating that the field has incorporated new content.
 For example, the zika virus, which was mentioned in 182 articles from 2014-2018, had never before been discussed in the titles or abstracts of articles relating to climate change.
@@
 Similar rapid emergences can be seen for [Intended] Nationally Determined Contributions ([I]NDCs) and Sustainable Development Goals (SDGs) in AR6, and Biochar and REDD (The United Nations Collaborative Programme on Reducing Emissions from Deforestation and Forest Degradation in Developing Countries) in AR5, among others.
-This large and rapidly evolving literature demands innovative machine-reading methods to enable understanding of the field at scale.
 
@@
 
-Research synthesis offers structured methodologies for integrating knowledge from bodies of evidence \cite{Chalmers2002}.
-Systematic reviews, which are common in the health sciences, collect all literature relevant to a specific question, in order to establish whether findings are consistent and generalisable \cite{Mulrow597}.
-Already in 1994, systematic review was being proposed as an answer to the ``small mountain of information'' presented by two million annual publications in biomedical literature \cite{Mulrow597}.
-Although climate change faces a similar scale problem, systematic review is little used in the field \cite{Berrang-Ford2015}.
-Systematic maps are a more recent methodological development, which show the state of the evidence in a broad subject area \cite{James2016}.
-There have been high profile calls to broaden the applications of evidence mapping in sustainable development \cite{McKinnon2015}, and they are similar underused in climate change, with only 25 of the more than 400,000 relevant papers containing the phrase "systematic map" in the abstract or title.
+		Big literature poses at least three challenges for scientific policy advice and its underlying science: \emph{First}, established procedures in scientific assessments like those conducted by the IPCC fail to address the exploding literature base.
+For example, the ratio of studies cited in IPCC reports to the number or relevant studies has declined from 60\% to 20\%  \cite{Minx2017l} and poses a rapidly growing risk of selection bias.
+More generally, the provision of comprehensive, objective, open and transparent assessments of the available scientific literature as often mandated is no longer possible for authors or author teams by traditional means.
+Machine reading and learning methods as well as other data science applications are required to enable an understanding of the field of climate change research at scale (REFs).
+\emph{Second}, evidence synthesis - the enterprise of reviewing the literature based on a formal and systematic set of methods (REFs) - becomes increasingly important for aggregating and consolidating the rapidly emerging knowledge and enabling scientific assessments to do their job.
+Yet, traditional methods of evidence synthesis themselves are pushed to their limits by the large amount of scientific publications, whilst the field of evidence synthesis technology that tries to streamline human tasks through  at the different stages of the review process is still in its infancy (REFs).
+\emph{Finally}, overwhelming amounts of literature may be a major reasons why assessments of scientific assessments (REFs) do not offer robust quantifications, for example, between report citations and the underlying literature.
+This may substantially bias some of the findings.
 
-In the research synthesis field, researchers are introducing new methods from natural language processing and machine-learning to scale up synthesis work \cite{OMara-Eves2015, Westgate2018a}.
-In the same way, this study uses topic modelling \cite{Blei2010} to map out the vast body of evidence on climate change.
+		This study uses topic modelling \cite{Blei2010} to map out the vast body of evidence on climate change.
 Topic modelling is an unsupervised machine-learning technique, where patterns of word co-occurrences in documents are used to learn a set of topics which can be used to describe the corpus.
@@
 Such a systematic engagement with the thematic content of the climate science is missing from the literature so far.%To our knowledge, this is the first
+		We apply this map in a second step to understand how the IPCC reports have represented the available climate change literature and re-evaluate claims of bias based on a comprehensive understanding of the available climate science.
 
-Systematic maps can have several uses: from the identification of knowledge gaps and gluts to the can identification of authors or institutions with expertise on a subject.
-The map in this paper also has several potential uses, but we focus here on using the map to understand the evolution of relationship between the five IPCC assessment reports and the wider literature on climate change.
-Big Literature in climate change poses a great challenge to the IPCC, who's mandate is to comprehensively assess the science of climate change \cite{IPCC2013}.
-The ratio of studies cited in IPCC reports to the number or relevant studies has declined from 60\% to 20\%  \cite{Minx2017l}, thus increasing the risk of a lack of comprehensiveness, or even bias.
+		\subsection{Mapping out the landscape of climate change literature}
 
-What gets included in IPCC reports is also much discussed.
-Policymakers demand more solution-oriented knowledge \cite{Kowarsch2017}, and there have been calls for the inclusion of more knowledge from the social sciences \cite{Victor2015}.
-But what we say about the literature cited in the IPCC has often been limited by a failure to consider the context of the wider literature.
-A scientometric study from 2011 claimed that the IPCC gave a greater \textit{emphasis} to natural sciences and, within the social sciences, to economics \cite{Bjurström2011}.
-This claim has subsequently been interpreted as a disciplinary bias by the IPCC \cite{Hulme2010, Corbera2016} towards the natural sciences, but the study operationalised disciplinary emphasis as simply the share of citations from each field, and was based on analysis of the Third Assessment report, published in 2001.
-In the following sections, we compare distributions of literature in the subset that is cited by the IPCC and the wider corpora, to analyse the \textit{representation}, proportional or otherwise, of scientific fields, as well as of topics.
+		\begin{itemize}
+			\item There is a broad and diverse range of topics
+			\item The climate change literature is dominated by the Natural Sciences, but there is a range of interdisciplinary topics. Few topics are dominated by other discisplines.
+			\item Topic growth within the landscape is dynamic. While most topics exist from the beginning, they show distinct patterhs of growth.
+		\end{itemize}
+
+		\subsection{Research representation in IPCC reports}
+
+		\subsection{Discussion}
+
+		\begin{itemize}
+			\item Focus of our search - not a full representation - this may bias some of our results
+			\item There is a much wider range of applications for this type of research
+		\end{itemize}
 
@@
 In this way, we can more effectively meet the challenges posed by Big Literature to global environmental assessments.
-%Machine learning approaches to understanding scientific literature are already latently present in our engagement with  when we use academic search engines or are recommended articles
 
@@
 	\linespread{1}
-\bibliography{Mendeley}
+	%\bibliography{Mendeley}
+	\begin{thebibliography}{10}
+
+		\bibitem{Bjurström2011}
+		Andreas Bjurstr{\"{o}}m and Merritt Polk.
+		\newblock {Physical and economic bias in climate change research: A
+			scientometric study of IPCC Third Assessment Report}.
+		\newblock {\em Climatic Change}, 108(1):1--22, 2011.
+
+		\bibitem{Nunez-Mir2016}
+		Gabriela~C Nunez-Mir, Basil~V Iannone, Bryan~C Pijanowski, Ningning Kong,
+		Songlin Fei, and Richard Fitzjohn.
+		\newblock {Automated content analysis: addressing the big literature challenge
+			in ecology and evolution}.
+		\newblock {\em Methods in Ecology and Evolution}, 7(11):1262--1272, 2016.
+
+		\bibitem{Grieneisen2011}
+		Michael Grieneisen and Minghua Zhang.
+		\newblock {The Current Status of Climate Change Research}.
+		\newblock {\em Nature Climate Change}, 1:72--73, 2011.
+
+		\bibitem{Haunschild2016}
+		Robin Haunschild, Lutz Bornmann, and Werner Marx.
+		\newblock {Climate Change Research in View of Bibliometrics}.
+		\newblock {\em PLoS ONE}, 11(7):1--19, 2016.
+
+		\bibitem{IPCC2014c}
+		IPCC.
+		\newblock {\em {Climate Change 2014: Synthesis Report. Contribution of Working
+				Groups I, II and III to the Fifth Assessment Report of the Intergovernmental
+				Panel on Climate Change}}.
+		\newblock IPCC, Geneva, Switzerland, 2014.
+
+		\bibitem{Rao2019}
+		V.~Brahmananda Rao, K.~Maneesha, Panangipalli Sravya, Sergio~H. Franchito,
+		Hariprasad Dasari, and Manoel~A. Gan.
+		\newblock {Future increase in extreme El Nino events under greenhouse warming
+			increases Zika virus incidence in South America}.
+		\newblock {\em npj Climate and Atmospheric Science}, 2(1):2--8, 2019.
+
+		\bibitem{Chalmers2002}
+		Iain Chalmers, Larry~V Hedges, and Harris Cooper.
+		\newblock {A Brief History of Research Synthesis}.
+		\newblock {\em Evaluation {\&} The Health Professions}, 25(1):12--37, 2002.
+
+		\bibitem{Mulrow597}
+		C~D Mulrow.
+		\newblock {Systematic Reviews: Rationale for systematic reviews}.
+		\newblock {\em BMJ}, 309(6954):597--599, 1994.
+
+		\bibitem{Berrang-Ford2015}
+		Lea Berrang-Ford, Tristan Pearce, and James~D. Ford.
+		\newblock {Systematic review approaches for climate change adaptation
+			research}.
+		\newblock {\em Regional Environmental Change}, 15(5):755--769, 2015.
+
+		\bibitem{James2016}
+		Katy~L. James, Nicola~P. Randall, and Neal~R. Haddaway.
+		\newblock {A methodology for systematic mapping in environmental sciences}.
+		\newblock {\em Environmental Evidence}, 5(1):1--13, 2016.
+
+		\bibitem{McKinnon2015}
+		Madeleine~C. McKinnon, Samantha~H. Cheng, Ruth Garside, Yuta~J. Masuda, and
+		Daniel~C. Miller.
+		\newblock {Sustainability: Map the evidence}.
+		\newblock {\em Nature}, 528(7581):185--187, 2015.
+
+		\bibitem{OMara-Eves2015}
+		Alison O'Mara-Eves, James Thomas, John McNaught, Makoto Miwa, and Sophia
+		Ananiadou.
+		\newblock {Using text mining for study identification in systematic reviews: A
+			systematic review of current approaches}.
+		\newblock {\em Systematic Reviews}, 4(1):1--22, 2015.
+
+		\bibitem{Westgate2018a}
+		Martin~J. Westgate, Neal~R. Haddaway, Samantha~H. Cheng, Emma~J. McIntosh,
+		Chris Marshall, and David~B. Lindenmayer.
+		\newblock {Software support for environmental evidence synthesis}.
+		\newblock {\em Nature Ecology and Evolution}, 2(4):588--590, 2018.
+
+		\bibitem{Blei2010}
+		David Blei, Lawrence Carin, and David Dunson.
+		\newblock {Probabilistic topic models}.
+		\newblock {\em IEEE Signal Processing Magazine}, 2010.
+
+		\bibitem{IPCC2013}
+		IPCC.
+		\newblock {Principles governing IPCC work}, 2013.
+
+		\bibitem{Minx2017l}
+		Jan~C. Minx, Max Callaghan, William~F. Lamb, Jennifer Garard, and Ottmar
+		Edenhofer.
+		\newblock {Learning about climate change solutions in the IPCC and beyond}.
+		\newblock {\em Environmental Science {\&} Policy}, 2017.
+
+		\bibitem{Kowarsch2017}
+		Martin Kowarsch, Jason Jabbour, Christian Flachsland, Marcel T.~J. Kok, Robert
+		Watson, Peter~M. Haas, Jan~C. Minx, Joseph Alcamo, Jennifer Garard, Pauline
+		Riousset, L{\'{a}}szl{\'{o}} Pint{\'{e}}r, Cameron Langford, Yulia Yamineva,
+		Christoph von Stechow, Jessica O'Reilly, and Ottmar Edenhofer.
+		\newblock {A road map for global environmental assessments}.
+		\newblock {\em Nature Climate Change}, 7(6):379--382, 2017.
+
+		\bibitem{Victor2015}
+		{David G. Victor}.
+		\newblock {Embed the social sciences in climate policy - David Victor}.
+		\newblock {\em Nature}, 520:7--9, 2015.
+
+		\bibitem{Hulme2010}
+		Mike Hulme and Martin Mahony.
+		\newblock {Climate change: What do we know about the IPCC?}
+		\newblock {\em Progress in Physical Geography}, 34(5):705--718, 2010.
+
+		\bibitem{Corbera2016}
+		Esteve Corbera, Laura Calvet-Mir, Hannah Hughes, and Matthew Paterson.
+		\newblock {Patterns of authorship in the IPCC Working Group III report}.
+		\newblock {\em Nature Climate Change}, 6(1):94--99, 2016.
+
+		\bibitem{Ford2016b}
+		James~D. Ford, Laura Cameron, Jennifer Rubis, Michelle Maillet, Douglas
+		Nakashima, Ashlee~Cunsolo Willox, and Tristan Pearce.
+		\newblock {Including indigenous knowledge and experience in IPCC assessment
+			reports}.
+		\newblock {\em Nature Climate Change}, 6(4):349--353, 2016.
+
+		\bibitem{Barocas2016}
+		Solon Barocas and Andrew~D Selbst.
+		\newblock {Big Data's Disparate Impact}.
+		\newblock {\em California Law Review}, 104:671--732, 2016.
+
+	\end{thebibliography}
 	\bibliographystyle{unsrt}

### 2019-07-10 coverletter.tex
piers edits

\documentclass{letter}
\usepackage{letterbib}
\usepackage{natbib}
\usepackage{geometry}

\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{fancyhdr}
\pagestyle{fancy}

\usepackage{tikzpagenodes}
\geometry{
	a4paper,
	left=20mm,
	right=60mm,
	marginparwidth=50mm,
	top=30mm,
}

\def\myyshifttop{0}
\def\mypagetop{0}

\newcommand{\marpartop}[1]% content, color
{   \begin{tikzpicture}[remember picture, overlay]
	\ifthenelse{\thepage=\mypagetop}{}{\xdef\myyshifttop{0}}        
	\xdef\mypagetop{\thepage}
	\node[below right, yshift=\myyshifttop, text width=\marginparwidth-4pt, inner sep=2pt] (tempnode) at (current page marginpar area.north west) {#1};
	\path (current page marginpar area.north west);
	\pgfgetlastxy{\tempxone}{\tempyone}
	\path (tempnode.south west);
	\pgfgetlastxy{\tempxtwo}{\tempytwo}
	\pgfmathsetmacro{\diffy}{(\tempytwo-\tempyone)}
	\xdef\myyshifttop{\diffy}
	\end{tikzpicture}
}

\def\myyshiftbot{0}
\def\mypagebot{0}

\newcommand{\marparbot}[1]% content, color
{   \begin{tikzpicture}[remember picture, overlay]
	\ifthenelse{\thepage=\mypagebot}{}{\xdef\myyshiftbot{0}}        
	\xdef\mypagebot{\thepage}
	\node[above right, yshift=\myyshiftbot, text width=\marginparwidth-4pt, inner sep=2pt] (tempnode) at (current page marginpar area.south west) {#1};
	\path (current page marginpar area.south west);
	\pgfgetlastxy{\tempxone}{\tempyone}
	\path (tempnode.north west);
	\pgfgetlastxy{\tempxtwo}{\tempytwo}
	\pgfmathsetmacro{\diffy}{(\tempytwo-\tempyone)}
	\xdef\myyshiftbot{\diffy}
	\end{tikzpicture}
}

\signature{Max Callaghan}

\begin{document}

	\begin{letter}{Bronwyn Wake \\ Chief Editor \\ \textit{Nature Climate Change}}

		\begin{tikzpicture}[remember picture, overlay]
		\node [anchor=north west, shift={(-1mm,0mm)}]  at (current page text area.north west) {\footnotesize\textbf{MCC} Torgauer Str. 12-15 \textbar\ 10829 Berlin \textbar\  Germany
		};
		\end{tikzpicture}

		\begin{tikzpicture}[remember picture, overlay]
		\node [anchor=south, shift={(-1mm,5mm)}]  at (current page text area.north east) {\includegraphics[width=4cm]{pres/MCC_Logo_RZ_rgb.jpg}
		};
		\end{tikzpicture}

		\marpartop{\textcolor[HTML]{0067a1}{\footnotesize\textsf{Mercator Research Institute on Global Commons and Climate Change (MCC) gemeinnützige GmbH}\\ \bigskip}%
			\par\textsf{\textbf{Max W. Callaghan}}%
			\par\textsf{PhD Candidate}%
			\par\textsf{Applied Sustainability Science}%
			\par\textsf{Torgauer Str. 12-15}
			\par\textsf{10829 Berlin | Germany}
			\par\textsf{tel +49 (0) 30 338 55 27 - 245}
			\par\textsf{fax +49 (0) 30 338 55 37 - 102}
			\par\textsf{mail callaghan@mcc-berlin.net}
			\par\textsf{web www.mcc-berlin.net}
		}

		\marparbot{
			\footnotesize
			Director \\
			Prof. Dr. Ottmar Edenhofer \\
			\medskip
			Bank Account \\
			Sparkasse Berlin \\
			iban DE58 1005 0000 0190 1246 36 \\
			bic  BELADEBEXXX \\
			\medskip
			Amtsgericht Charlottenburg \\
			HRB 142902 B \\
			\medskip
			MCC was founded jointly by the Stiftung Mercator and the Potsdam Institute for Climate Impact Research
		}

		\date{}

   \opening{\today \\ \\ Dear Bronwyn Wake,}

   I herewith submit on behalf of my co-authors the manuscript ``A Topography of Climate Change Litereature'' for consideration as a letter in Nature Climate Change.

We believe this letter addresses a crucial challenge affecting the broad climate change community: namely, the field's rapidly expanding literature. This phenomenon - there are more than 45,000 papers published on climate change each year - means understanding the field in its entirety is more difficult than ever. 
This is particularly relevant for the IPCC, given their mandate of providing comprehensive, objective and transparent assessments of he literature.

Moreover, this challenge has also hampered how we have attempted to understand how the IPCC engages with the literature. Such attempts \cite{Bjurström2011, Hulme2010, Victor2015, Corbera2016, Kowarsch2017} have often been based on qualitiative perceptions, or out of date data with insufficient methodological sophistication to contrast patterns in IPCC citations with patterns in the wider literature.

Our study has two innovations which allow us advance the current state of knowledge on the the IPCC and the field it is tasked with assessing. First, we set the complete set of IPCC citations into the context of the wider literature, allowing us to show which disciplines have been over or under-represented.  Contrary to previous claims, the social sciences are over-represented in IPCC reports. This is because the proportion of social science articles among publications cited by the IPCC is higher than the proportion of social science articles among all publications on climate change. 
Second, our use of topic modelling allows us to dig down into the content of articles more or less represented in the IPCC. This provides the basis for our second main conclusion, that literature on technical solutions (such as negative emissions, buildings or cities) is growing fast and, even compared to other fast-growing literatures, has been under-represented in IPCC reports.

These insights have several implications across the community, and we further point out how the map we produce can enhance our understanding of the field and contribute to improving processes involved in the production of global environmental assessments.

\closing{Yours Sincerely,}

\bibliography{Mendeley}
\bibliographystyle{unsrt}

\end{letter}
\end{document}

### 2019-07-10 main.tex
piers edits

@@
 		\noindent We live in an age of ``Big Literature'' 
-		\cite{Nunez-Mir2016, Minx2017}, where the science of climate change is expanding exponentially \cite{Grieneisen2011, Haunschild2016}.
-For example, in the five years since the publication of the last IPCC assessment report \cite{IPCC2014c}, 201,606 papers were published in WoS (see Table \ref{tab}).
+		\cite{Nunez-Mir2016, Minx2017l}, where the science of climate change is expanding exponentially \cite{Grieneisen2011, Haunschild2016}.
+In the five years since the publication of the last IPCC assessment report \cite{IPCC2014c}, 201,606 papers were published in the Web of Science (WoS) (see Table \ref{tab}).
 This is almost as much as the 204,585 papers published during the first five assessment periods, a period of nearly 30 years.
-A total of about 350,000 new publications can be expected for the current sixth assessment cycle of the IPCC.
-If we assume that WOS contains roughly about 41\% of the entire climate change literature (Khabasa), this yields a total number of new publications of around 850,000 for this assessment cycle.
-But the literature has also become more diverse.
-This is, for example, reflected in the expansion of vocabulary in this literature - from 2,000 unique words in AR1 to 94,746 words so far in AR6 - indicating that the field has incorporated new content.
+A total of around 350,000 new publications can be expected for the current sixth assessment cycle of the IPCC, based on current growth patterns.
+Moreover, the literature has also become more diverse.
+This is reflected in the expansion of the literature's vocabulary - from 2,000 unique words in the first assessment period to 94,746 words so far in the sixth - indicating that the field has incorporated new content.
 For example, the zika virus, which was mentioned in 182 articles from 2014-2018, had never before been discussed in the titles or abstracts of articles relating to climate change.
 Yet it has emerged as a topic of high relevance: the incidence of the virus, the outbreak of which in Brazil in 2016 was declared a public health emergency by the WHO, is set to increase under rising global temperatures \cite{Rao2019}.
-Similar rapid emergences can be seen for [Intended] Nationally Determined Contributions ([I]NDCs) and Sustainable Development Goals (SDGs) in AR6, and Biochar and REDD (The United Nations Collaborative Programme on Reducing Emissions from Deforestation and Forest Degradation in Developing Countries) in AR5, among others.
+Similar rapid emergence patterns can be seen for [Intended] Nationally Determined Contributions ([I]NDCs) and Sustainable Development Goals (SDGs) in AR6, and Biochar and REDD (The United Nations Collaborative Programme on Reducing Emissions from Deforestation and Forest Degradation in Developing Countries) in AR5, among others.
 
@@
 
-		Big literature poses at least three challenges for scientific policy advice and its underlying science: \emph{First}, established procedures in scientific assessments like those conducted by the IPCC fail to address the exploding literature base.
-For example, the ratio of studies cited in IPCC reports to the number or relevant studies has declined from 60\% to 20\%  \cite{Minx2017l} and poses a rapidly growing risk of selection bias.
-More generally, the provision of comprehensive, objective, open and transparent assessments of the available scientific literature as often mandated is no longer possible for authors or author teams by traditional means.
+		Big literature poses at least three challenges for scientific policy advice and science itself: \emph{First}, established procedures in scientific assessments like those conducted by the IPCC fail to address the exploding literature base.
+For example, the ratio of studies cited in IPCC reports to the number or relevant studies has declined from 60\% to 20\%  \cite{Minx2017l}, posing a rapidly growing risk of selection bias.
+More generally, the provision of comprehensive, objective, open and transparent assessments of the available scientific literature, as defined in the principles governing IPCC work \cite{IPCC2013}, is no longer possible for authors or author teams by traditional means.
 Machine reading and learning methods as well as other data science applications are required to enable an understanding of the field of climate change research at scale (REFs).
-\emph{Second}, evidence synthesis - the enterprise of reviewing the literature based on a formal and systematic set of methods (REFs) - becomes increasingly important for aggregating and consolidating the rapidly emerging knowledge and enabling scientific assessments to do their job.
-Yet, traditional methods of evidence synthesis themselves are pushed to their limits by the large amount of scientific publications, whilst the field of evidence synthesis technology that tries to streamline human tasks through  at the different stages of the review process is still in its infancy (REFs).
-\emph{Finally}, overwhelming amounts of literature may be a major reasons why assessments of scientific assessments (REFs) do not offer robust quantifications, for example, between report citations and the underlying literature.
-This may substantially bias some of the findings.
+\emph{Second}, evidence synthesis - the enterprise of reviewing the literature based on a formal and systematic set of methods \cite{Chalmers2002} - becomes increasingly important for aggregating and consolidating the rapidly emerging knowledge and enabling scientific assessments to do their job.
+Yet, traditional methods of evidence synthesis themselves are pushed to their limits by the large amount of scientific publications.
+Whilst the field of evidence synthesis technology that tries to streamline human tasks through machine learning at the different stages of the review process is still in its infancy \cite{Beller2018}.
+\emph{Finally}, overwhelming amounts of literature may be a major reasons why assessments of scientific assessments \cite{Bjurström2011, Hulme2010, Victor2015, Corbera2016} do not offer robust quantifications, for example, for claims about the relationship between report citations and the underlying literature.
+This may substantially affect findings.
 
@@
 Such a systematic engagement with the thematic content of the climate science is missing from the literature so far.%To our knowledge, this is the first
-		We apply this map in a second step to understand how the IPCC reports have represented the available climate change literature and re-evaluate claims of bias based on a comprehensive understanding of the available climate science.
+		We apply this map in a second step to understand how the IPCC reports have represented the available climate change literature and re-evaluate claims of bias based on a more comprehensive understanding of the available climate science, and enrich the discussion of representation in the literature to include topics as well as disciplines.
 
-		\subsection{Mapping out the landscape of climate change literature}
+		\subsection*{Mapping out the landscape of climate change literature}
 
-		\begin{itemize}
-			\item There is a broad and diverse range of topics
-			\item The climate change literature is dominated by the Natural Sciences, but there is a range of interdisciplinary topics. Few topics are dominated by other discisplines.
-			\item Topic growth within the landscape is dynamic. While most topics exist from the beginning, they show distinct patterhs of growth.
-		\end{itemize}
-
-		\subsection{Research representation in IPCC reports}
-
-		\subsection{Discussion}
-
-		\begin{itemize}
-			\item Focus of our search - not a full representation - this may bias some of our results
-			\item There is a much wider range of applications for this type of research
-		\end{itemize}
-
-		\subsection*{Proportionality in IPCC citations}
-
-		Figure \ref{oecd_rep}.a shows that the social sciences were indeed under-represented in the third assessment report, but by the fifth assessment report were over-represented.
-Likewise, other social sciences than economics have become better represented since AR3  (see figure \ref{subfield}f) with social \& economic geography (4.3\% of the literature), political science (1.0\%), and sociology (0.8\%) showing improved representation in AR5 compared to AR3, and Social and economic geography, political science, and other social sciences better represented than economics when taking into account the distribution of studies in the literature.
-
-		This challenges what we think we know about the IPCC.
-The social sciences, by now, are actually the best represented field, with a share in the literature cited by IPCC reports [1.5] times as high as in the literature at large.
-On the other hand the Agricultural Sciences and Engineering \& Technology have been consistently under-represented, with [2.5] and [3.5] times the share of studies in the wider literature than in the literature cited by the IPCC in AR5 respectively.
-% (Humanities are also underrepresented, but making up only 0.9\% of the wider literature, the proportionality is particularly sensitive).
+		Figure \ref{oecd_topic_map} shows a \emph{thematic} or \emph{topopographic map} of the 400,000 publications on climate change in our dataset with a total number of 140 topics.
+The number of topics must be defined exogenously, but the results are robust to different specifications (see methods for examples and a thorough explanation of model selection).
+Using non-negative matrix factoriziation \cite{Lee1999}, the topics are machine-learned from the papers' abstracts (see methods for details).
 
@@
 
-		%\subsection*{A Topography of Climate Change Research}
+		The map shown covers a broad range of topics that occur in meaningful clusters.
+In general, topics related to climate science and impacts are in the West, while solution-oriented topics are in the East.
+More fine-grained research areas can also be distinguished.
+For example, publications related to urban infrastructure (buildings, energy, cement, waste) are located in the East (), physical climate impacts such as sea-level rise (), heat waves (), droughts () or crop yield (losses) () are in the South-West and energy systems are in North-East ().
+There are larger groups of documents at the fringes of the map that relate mainly to one or two specific topics such as biochar, corals, soil organic carbon, clouds and aerosols, diseases, membranes, absorption or adsorption or CO2 storage.
+Interestingly, scenarios feature centrally in the map, at the interface between different scientific communities.
+This corresponds to their integrative nature in IPCC reports (REF).
+This depiction of the thematic structure of the literature, and its ordering and categorising thereby could be useful for individual communities or for climate change assessments \footnote{We include the list of topic-document combinations in the supplementary materials}.
 
-		Figure \ref{oecd_topic_map} shows the 400,000 documents on climate change in our dataset in a dimensionality reduction enabled representation of their topic structure, with topic labels placed near clusters of documents highly relevant to each topic.
-The map shows the high proportion of the natural sciences in climate change research, and the large proportion of the topic space dominated by natural science publications.
-These two features of the landscape account for the proportionally high share of natural science publications in IPCC citations.
+		The disciplinary composition of this research topography indicated by the different colours in Figure \ref{oecd_topic_map} highlights the dominance of natural sciences in climate change research.
+More than 60\% of the literature is published in natural science journals.
+Similarly, only in X out of 140 topics do publications from another field make up the majority of documents, in Y cases the contribution of publications in natural science journals make more than 50\%.
+We calculate disciplinary entropy of topics as a measure of their degree of interdisciplinarity (see Figure \ref{dis-entropy} and methods for details).
+While research on health, food, or policy comes from a range of disciplines, research on ice and oceans comes almost exclusively from the natural sciences).
 
-		The thematic structure of the literature also maps well to the disciplinary structure, with clusters of social science topics, such as \textbf{policy}, \textbf{research}, \textbf{sector} and \textbf{growth} in the centre right of the graph, and natural sciences on the left.
-With reference to figure \ref{dis-entropy}, we can identify the topics which are more or less distributed across disciplines.
-\textbf{Coral}, for example, is almost exclusively discussed in the natural sciences, while papers on socio-economic issues are discussed in a variety of disciplines.
-Further, by using the topographical map, we can dig down further into the subject matter that is more or less proportionately represented, within and across disciplines.
+		\begin{figure}
+			\begin{center}
+				\includegraphics[width=180mm]{plots_pub/topic_evolution_4.png}
+				\caption{Evolution of the landscape of climate change literature.
+In each period, the 10 fastest growing topics are labelled.
+Where documents could be matched to IPCC citations, they are coloured by the working group citing them.}
+				\label{evolution-map}
+			\end{center}
+		\end{figure}
+
+		Finally, the topography shows the thematic evolution of the literature, with topics exhibiting distinct patterns of growth.
+Fast-growing topics in the last three assessment periods have included, among others, coral, risks, adaptation, hydrogen, buildings, CO2 removal, networks and biochar.
+Biochar is particularly remarkable in that the sizeable literature which emerged in AR5 was completely absent from the climate change literature beforehand.
+		The identification of new topics as they emerge, particularly as these are discovered without prior knowledge of the literature, can help researchers and assesment-makers to keep abreast of a quickly evolving field.
+
+		\subsection*{Research representation in IPCC reports}
+		We apply our topic map to understand the representation of science in IPCC assesssments and how it manages to respond to demands for more solution-oriented knowledge \cite{Kowarsch2017}.
+Several studies have identified, made, or repeated claims of a disciplinary bias of IPCC assessments towards the natural sciences, and within the social sciences towards economics \cite{Bjurström2011, Victor2015, Hulme2010, Corbera2016}.
+Where these claims were based on an analysis of IPCC citations \cite{Bjurström2011}, they fail to assess this claim against a reasonable, measurable benchmark.
+We argue here that the composition of the climate change literature as a whole provides such a benchmark, in view of the organisation's mandate to provide ``comprehensive, objective, open and transparent'' assessment of the available science \cite{IPCC2013}.
+Our comprehensive database allows us to study representation with such a benchmark, and over time rather than for single assessment cycles.
+
+		Figure \ref{oecd_rep}.a shows that the social sciences were indeed under-represented in the third assessment report, but by the fifth assessment report were over-represented.
+Likewise, other social sciences than economics have become better represented since AR3  (see figure \ref{subfield}f) with social \& economic geography (4.3\% of the literature), political science (1.0\%), and sociology (0.8\%) showing improved representation in AR5 compared to AR3, and social and economic geography, political science, and other social sciences better represented than economics when taking into account the distribution of studies in the literature.
+
+		This challenges what we think we know about the IPCC.
+The social sciences, by now, are actually the best represented field, with a share in the literature cited by IPCC reports [1.5] times as high as in the literature at large.
+On the other hand the Agricultural Sciences and Engineering \& Technology have been consistently under-represented, with [2.5] and [3.5] times the share of studies in the wider literature than in the literature cited by the IPCC in AR5 respectively.
+
+		The topography allows us to delve deeper into the subject matter that receives more or less attention in the IPCC.
+Figures \ref{oecd_rep}b and \ref{oecd_rep}c plot the representation of the topics shown in the map.
+Figure \ref{oecd_rep}c shows that topics more commonly cited by IPCC working group I are older and largely better represented in IPCC reports.
+These topics, for example \textbf{ozone}, \textbf{oceans}, \textbf{clouds}, \textbf{aerosols} and \textbf{sea levels}, are older, predominantly cited by WG I, and well cited by IPCC reports.
+They make up some of the core topics of the physical science of climate change.
+
+		The topics in the lower right of the graph are the most pertinent to the question of whether the IPCC is well representing knowledge on climate change.
+These topics are newer and until now have been under-represented in IPCC reports.
+They are the topics that could be seen as potential gaps in the IPCC's coverage of the science.
+Because they are new areas of knowledge, they may be highly salient in a periodic assessment process.
+These topics are primarily in working group III, on mitigation (see methods section [] for a discussion of the categorisation of topics, including CLC, adsorption and hydrogen, which may more properly be of relevance to WGIII).
+
+		The difference between these under-represented new topics and other new topics that are better represented is intriguing.
+This difference is visible in figure \ref{evolution-map}, where In AR5, the clusters of documents around the \textbf{adsorption}, \textbf{buildings}, and \textbf{biochar} topics contain few IPCC citations, whereas the clusters around \textbf{food}, \textbf{health}, \textbf{adaptation}, and \textbf{GHGs} contain more.
+As shown in figure \ref{oecd_rep}c, adsorption buildings and biochar are [4, 3.5 and 3.8] times more prevalent in the literature than in IPCC citations, while food is [0.3] times more prevalent in the literature and health and adaptation are [0.1] and [2,5] times more prevalent in IPCC citations respectively.
+The IPCC, then, has been better at integrating new knowledge from these topics, and in general better at integrating new knowledge from WG II  than WG III topics.
+
+		Further, within WG III topics, those that are well represented contain a greater proportion of social science research (figure \ref{oecd_rep}b).
+The topics \textbf{countries}, \textbf{policy}, and \textbf{prices} are close to a proportional representation and are made up of around 30\% social science research.
+\textbf{Waste}, \textbf{biochar}, \textbf{cement} and \textbf{coal}, are more than 3 times more prevalent in the wider literature than in the literature cited by the IPCC, and are made up of around 5\% social science research.
+This pattern is not visible in other working groups (see Figure \ref{socsci-wgs}), and complicates the perception of the under-representation of the social sciences.
+
+		Recalling policymakers' demands for more solution-oriented assessments \cite{Kowarsch2017}, we could also interpret the topics that are newer and under-represented as ``solutions-relevant''.
+Many deal with negative emissions, or with mitigation (or to a lesser extent adaptation) options in the transport, buildings and power sectors.
+All are arguably related to climate solutions.
+However, while policymakers' demands for solutions-oriented knowledge were rather about policy options, these under-represented new topics deal with more technical solutions and are found rather in technical disciplines within engineering \& technology and the agricultural sciences.
 
@@
 
-		%, and to further investigate the content of the documents that are more less proportionately represented in the IPCC.
+		\subsection*{Machine-learning for climate change assessments}%, evidence synthesis and science of science} % needs to be reviewed
+		Keeping track of developments in the scientific literature is becoming increasingly difficult in the age of big literature.
+This is becoming a central challenge for global environmental assessments such as those conducted by the IPCC \cite{Minx2017l, Kowarsch2017}, as well as for science of science research (\cite{Zeng2017}), the provision of thorough and comprehensive reviews in specific fields, and the efficient allocation of research funding where it is needed.
+Ultimately it is a challenge for sound, evidence-based scientific policy advice (\cite{White2019}).
+Systematic maps and evidence gap maps (\cite{James2016}, \cite{McKinnon2015}) provide crucial tools for tracing the literature, but current approaches are constrained by available resources to answering very specific questions, or are limited by a lack of suitable literature.
+On the other hand, current scientometric and research weaving approaches (\cite{Nakagawa2019}) can capture a broader landscape of research, but are too unspecific with regard to the thematic content of literature.
 
-		\begin{figure}
-			\begin{center}
-				\includegraphics[width=180mm]{plots_pub/topic_evolution_4.png}
-				\caption{Evolution of the landscape of climate change literature}
-				\label{evolution-map}
-			\end{center}
-		\end{figure}
+		Elsewhere, we show how machine learning can accelerate the provision of traditional maps of evidence with thousands rather than hundreds of data points (\cite{Lamb2018d}).
+Here we extend this analysis to vast bodies of literature with hundreds of thousands of publications and show how ``topopgraphic maps'' provide an efficient visualisation of these.
 
-		\subsection*{Supply and demand for solutions-oriented knowledge}
+		We acknowledge that the climate change topography presented here is not fully comprehensive.
+The WoS  covers a substantive, yet by no means exhaustive set of publications.
+Grey literature, some smaller journals and books, not to mention indigenous knowledge \cite{Ford2016b}, are not covered.
+Similarly, our query (see methods) requires that the keywords, title or abstract of a publication mentions climate change or a synonym or related term.
+Whilst this is a reasonable system boundary definition, and follows \cite{Grieneisen2011} exactly, we acknowledge the existence of directly relevant studies for climate change research - for example on energy technologies, energy policies or - that may not meet our criteria and remain outside the scope of our analysis.
+Yet our decisions are driven by data availability and requirements for a clean, climate-changed focused dataset.
+Given the large size of our sample (400,000+ publications), we argue that our topography provides a reasonable representation of the research landscape on climate change.
+Furthermore, unless IPCC citation patterns systematically differ in the not included parts of the literature, the main conclusions of this study are unaffected.
 
-		Figures \ref{oecd_rep}b and \ref{oecd_rep}c plot the representation of the topics shown in the map.
-Figure \ref{oecd_rep}c shows that topics more commonly cited by IPCC working group I are older and largely better represented in IPCC reports.
-It makes intuitive sense that these topics, for example \textbf{ozone}, \textbf{oceans}, \textbf{clouds}, \textbf{aerosols} and \textbf{sea levels}, are older, predominantly cited by WG I, and well cited by IPCC reports, as these are some of the core topics of the physical science of climate change.
+		In addition, our analysis is based on a topic model of publication abstracts.
+Though it is reasonable to assume that abstracts reflect the themes of the papers they describe, this depends on the quality of the abstracts, and thematic features of the underlying texts may not be adequately represented.
+In the absence of comprehensive full-text access and remaining, non-trivial challenges in text extraction from PDFs, we argue that abstracts provide a reasonable unit of analysis.
 
-		The topics in the lower right of the graph are the most pertinent to the question of whether the IPCC is well representing knowledge on climate change.
-These topics are newer and until now have been under-represented in IPCC reports.
-They are the topics that could be seen as potential gaps in the IPCC's coverage of the science.
-Because they are new areas of knowledge, they may be highly salient in a periodic assessment process.
-These topics are primarily in working group III (mitigation), with the exception of adsorption, CLC and hydrogen which are primarily of relevance to WG III but are miscategorised due to the low number of citations of relevant documents and citations of tangentially relevant documents by other working groups \footnote{For example, the word ``capacity" is relevant to the adsorption topic, so documents talking about adaptive capacity receive a low relevance score for that topic.
-Because only very few documents highly relevant to the adsorption topic (in that they talk about adsorption or adsorptive capacity) are cited by the IPCC, and many of the weakly relevant documents are cited by the IPCC, the sum of the topic scores of the weakly relevant WG II documents outweighs the sum of the topic scores of the strongly relevant WG III documents}.
+		We apply our map of the climate change literature to understand the representativeness of IPCC citations and argue that answering related questions requires a clear benchmark.
+We show that applying this benchmark challenges and confirms some prominent findings around disciplinary representation in and solution-orientation of IPCC assessments.
 
-		Although it is perhaps not surprising that these newer topics are less well represented than the older topics that make up the core of the physical science research on climate change, the difference between these new topics and other new topics that are better represented is intriguing.
-This difference is visible in figure \ref{evolution-map}, where the fastest growing topics in each period are labelled, and the documents are coloured according to the working group, if any, which cites them.
-In AR5, the clusters of documents around the \textbf{adsorption}, \textbf{buildings}, and \textbf{biochar} topics contain few IPCC citations, whereas the clusters around \textbf{food}, \textbf{health}, \textbf{adaptation}, and \textbf{GHGs} contain more.
-This is also evident in figure \ref{oecd_rep}c, where these topics display corresponding representation values.
-The IPCC, then, has been better at integrating new knowledge from these topics, and in general better at integrating new knowledge from WG II  than WG III topics.
+		While proportional representation of all topics and all disciplines may not be desirable, the analysis presented here can help the IPCC to make quantitatively informed decisions about what to represent.
+The claim that the IPCC needs to incorporate more social science research may indeed be well-founded, but, in light of the fact shown here that the IPCC over-represents the social science literature that is published, this would imply increases in funding for climate change research in the social sciences.
+While some might argue that engineering or agricultural research on solutions related topics may be too technical and less relevant to IPCC assessments, in light of the size of the literature in these areas relative to that which is cited by the IPCC it would follow that more social science research needs to be carried out that deals with these topics and produces assessment-ready knowledge.
 
-		Within WG III topics, those that are well represented contain a greater proportion of social science research (figure \ref{oecd_rep}b).
-The topics \textbf{countries}, \textbf{policy}, and \textbf{prices} are close to a proportional representation and are made up of around 30\% social science research.
-\textbf{Waste}, \textbf{biochar}, \textbf{cement} and \textbf{coal}, are more than 3 times more prevalent in the wider literature than in the literature cited by the IPCC, and are made up of around 5\% social science research.
-This pattern is not visible in other working groups (see Figure \ref{socsci-wgs}), and complicates the perception of the under-representation of the social sciences.
+		We highlight that there are a variety of other immediate applications for such comprehensive topic maps and their rich, underlying data.
+Rapid, comprehensive maps could make a contribution to making climate change assessment processes in various places more efficient.
+For example, they could inform the scoping of scientific assessment reports to make sure that reports keep abreast of developments in the literature and remain policy relevant.
+What's more, they could help in the efficient identification of the best subject area experts across regions, sectors and genders (REFs) and directly increase the transparency with regard to the availability and selection of citations.
+Beyond the organisation of global environmental assessments, such maps can inform research funding decisions, and help individual researchers identi Future research can explore how further methods, and more comprehensive data, can help drive forward these applications.
 
-		Recalling policymakers' demands for more solution-oriented assessments \cite{Kowarsch2017}, we could also interpret the topics that are newer and under-represented as ``solutions-relevant''.
-Many deal with negative emissions, or with mitigation (or to a lesser extent adaptation) options in the transport, buildings and power sectors.
-All are arguably related to climate solutions.
-However, while policymakers' demands for solutions-oriented knowledge were rather about policy options, these under-represented new topics deal with more technical solutions and are found rather in technical disciplines within engineering \& technology and the agricultural sciences.
-
-		\subsection*{The IPCC as an informed decision-maker on topical representation}
-
-		Deciding on the optimal proportion of each topic's literature to be cited by the IPCC is not a trivial task.
-A perfectly proportional representation of each topic is almost certainly not optimal, and as such, decisions about which topics to over-, or under- represent are best made by experts, not by a computer.
-Indeed, the IPCC itself is the best-placed institution to make these decisions.
-But in the age of ``Big Literature'' \cite{Nunez-Mir2016}, these decision should at best be underpinned by systematic knowledge of the landscape of the literature, and made in discussion with the wider research community, funders, policymakers and other stakeholders.
-
-		The analysis in this study provide a useful input to this discussion.
-It could be argued that the under-represented technical literature on specific technological or sectoral solutions is not relevant to policymakers, and that working group III should give more weight to evidence about general policy instruments such as carbon taxes.
-Conversely, one could argue that establishing a technical understanding of specific climate solutions is as important a task as establishing a technical understanding of the physical science of climate change.
-The desire for more social science research in IPCC reports may imply, given the evidence here, that more social science research on climate change needs to be produced and funded, rather than that the IPCC should cite more of what already exists.
-Or, one could argue that, in light of the evidence that there is little social science research on solutions-relevant, under-represented topics, that the social sciences could do more to address technical or specific solutions such as negative emissions, green concrete, or waste and recycling.
-
-		An understanding of the topography of the literature helps bring these arguments to the foreground, and allows them to be made in an informed way.
-Machine reading the literature in this way is not without its limitations though, and indeed many are apparent in this analysis.
-The corpus of potentially relevant literature is of course much wider than what is included in this study.
-The analysis excludes studies about climate change that do not match our query, studies relevant to tackling climate change that do not mention it specifically, studies written in languages other than English (unless the abstract has been translated), studies not indexed in the Web of Science, and reports published outside peer reviewed journals, not to mention Indigenous knowledge \cite{Ford2016b}.
-Despite this, unless the social science literature in the above categories is cited systematically less often  by the IPCC than the social science literature that was analysed in this study, then the main conclusions of this study hold.
-Topic models also carry limitations, and do not present the \textit{objective} truth about a corpus, given that they can be sensitive to modeller choices, such as the number of topics.
-However, the observations about the under-representation of solutions-relevant topics are robust across a broad range of topic numbers \ref{top-rep-ks}.
-
-		Computational methods then, provide \textit{assistance} to humans in understanding a climate change literature that is produced by human individuals and institutions.
-As in other areas of machine learning \cite{Barocas2016}, computational assessments of the literature run the risk of reproducing biases or gaps in the training data.
-However, just as with other applications of machine learning, machine-reading the science of climate change can provide information that helps us to understand gaps in what we have knowledge about, and potential biases, or options for emphasis, in how we represent that knowledge in the IPCC.
-In this way, we can more effectively meet the challenges posed by Big Literature to global environmental assessments.
+		While the size and variety of the literature on climate change presents challenges to global environmental assessments, it represents a wealth of knowledge on vital climate solutions.
+By shedding light on new and under-reported subjects and by providing quantifications of what we think we know about how assessments and their relationship to the literature, computational mapping can help ensure that this knowledge is made use of efficiently.
+Topographic maps  can become part of a toolbox which helps the IPCC continue to be able to fulfil its mandate of providing comprehensive, objective and transparent assessments of an expanding literature.
 
@@
 
+		\bibitem{Minx2017l}
+		Jan~C. Minx, Max Callaghan, William~F. Lamb, Jennifer Garard, and Ottmar
+		Edenhofer.
+		\newblock {Learning about climate change solutions in the IPCC and beyond}.
+		\newblock {\em Environmental Science {\&} Policy}, 2017.
+
+		\bibitem{IPCC2013}
+		IPCC.
+		\newblock {Principles governing IPCC work}, 2013.
+
 		\bibitem{Chalmers2002}
@@
 
-		\bibitem{Mulrow597}
-		C~D Mulrow.
-		\newblock {Systematic Reviews: Rationale for systematic reviews}.
-		\newblock {\em BMJ}, 309(6954):597--599, 1994.
+		\bibitem{Beller2018}
+		Elaine Beller, Justin Clark, Guy Tsafnat, Clive Adams, Heinz Diehl, Hans Lund,
+		Mourad Ouzzani, Kristina Thayer, James Thomas, Tari Turner, Jun Xia, Karen
+		Robinson, Paul Glasziou, and {On behalf of the founding members of the ICASR
+			group}.
+		\newblock {Making progress with the automation of systematic reviews:
+			principles of the International Collaboration for the Automation of
+			Systematic Reviews (ICASR)}.
+		\newblock {\em Systematic Reviews}, 7(1):1--7, 2018.
 
-		\bibitem{Berrang-Ford2015}
-		Lea Berrang-Ford, Tristan Pearce, and James~D. Ford.
-		\newblock {Systematic review approaches for climate change adaptation
-			research}.
-		\newblock {\em Regional Environmental Change}, 15(5):755--769, 2015.
+		\bibitem{Hulme2010}
+		Mike Hulme and Martin Mahony.
+		\newblock {Climate change: What do we know about the IPCC?}
+		\newblock {\em Progress in Physical Geography}, 34(5):705--718, 2010.
+
+		\bibitem{Victor2015}
+		{David G. Victor}.
+		\newblock {Embed the social sciences in climate policy - David Victor}.
+		\newblock {\em Nature}, 520:7--9, 2015.
+
+		\bibitem{Corbera2016}
+		Esteve Corbera, Laura Calvet-Mir, Hannah Hughes, and Matthew Paterson.
+		\newblock {Patterns of authorship in the IPCC Working Group III report}.
+		\newblock {\em Nature Climate Change}, 6(1):94--99, 2016.
+
+		\bibitem{Blei2010}
+		David Blei, Lawrence Carin, and David Dunson.
+		\newblock {Probabilistic topic models}.
+		\newblock {\em IEEE Signal Processing Magazine}, 2010.
+
+		\bibitem{Lee1999}
+		D~D Lee and H~S Seung.
+		\newblock {Learning the parts of objects by non-negative matrix factorization.}
+		\newblock {\em Nature}, 401(6755):788--791, 1999.
+
+		\bibitem{Kowarsch2017}
+		Martin Kowarsch, Jason Jabbour, Christian Flachsland, Marcel T.~J. Kok, Robert
+		Watson, Peter~M. Haas, Jan~C. Minx, Joseph Alcamo, Jennifer Garard, Pauline
+		Riousset, L{\'{a}}szl{\'{o}} Pint{\'{e}}r, Cameron Langford, Yulia Yamineva,
+		Christoph von Stechow, Jessica O'Reilly, and Ottmar Edenhofer.
+		\newblock {A road map for global environmental assessments}.
+		\newblock {\em Nature Climate Change}, 7(6):379--382, 2017.
+
+		\bibitem{Zeng2017}
+		An~Zeng, Zhesi Shen, Jianlin Zhou, Jinshan Wu, Ying Fan, Yougui Wang, and
+		H.~Eugene Stanley.
+		\newblock {The science of science: From the perspective of complex systems}.
+		\newblock {\em Physics Reports}, 714-715:1--73, 2017.
+
+		\bibitem{White2019}
+		Howard White.
+		\newblock {The twenty-first century experimenting society: the four waves of
+			the evidence revolution}.
+		\newblock {\em Palgrave Communications}, 5(1):1--7, 2019.
 
@@
 
-		\bibitem{OMara-Eves2015}
-		Alison O'Mara-Eves, James Thomas, John McNaught, Makoto Miwa, and Sophia
-		Ananiadou.
-		\newblock {Using text mining for study identification in systematic reviews: A
-			systematic review of current approaches}.
-		\newblock {\em Systematic Reviews}, 4(1):1--22, 2015.
+		\bibitem{Nakagawa2019}
+		Shinichi Nakagawa, Gihan Samarasinghe, Neal~R. Haddaway, Martin~J. Westgate,
+		Rose~E. O'Dea, Daniel~W.A. Noble, and Malgorzata Lagisz.
+		\newblock {Research Weaving: Visualizing the Future of Research Synthesis}.
+		\newblock {\em Trends in Ecology and Evolution}, 34(3):224--238, 2019.
 
-		\bibitem{Westgate2018a}
-		Martin~J. Westgate, Neal~R. Haddaway, Samantha~H. Cheng, Emma~J. McIntosh,
-		Chris Marshall, and David~B. Lindenmayer.
-		\newblock {Software support for environmental evidence synthesis}.
-		\newblock {\em Nature Ecology and Evolution}, 2(4):588--590, 2018.
-
-		\bibitem{Blei2010}
-		David Blei, Lawrence Carin, and David Dunson.
-		\newblock {Probabilistic topic models}.
-		\newblock {\em IEEE Signal Processing Magazine}, 2010.
-
-		\bibitem{IPCC2013}
-		IPCC.
-		\newblock {Principles governing IPCC work}, 2013.
-
-		\bibitem{Minx2017l}
-		Jan~C. Minx, Max Callaghan, William~F. Lamb, Jennifer Garard, and Ottmar
-		Edenhofer.
-		\newblock {Learning about climate change solutions in the IPCC and beyond}.
-		\newblock {\em Environmental Science {\&} Policy}, 2017.
-
-		\bibitem{Kowarsch2017}
-		Martin Kowarsch, Jason Jabbour, Christian Flachsland, Marcel T.~J. Kok, Robert
-		Watson, Peter~M. Haas, Jan~C. Minx, Joseph Alcamo, Jennifer Garard, Pauline
-		Riousset, L{\'{a}}szl{\'{o}} Pint{\'{e}}r, Cameron Langford, Yulia Yamineva,
-		Christoph von Stechow, Jessica O'Reilly, and Ottmar Edenhofer.
-		\newblock {A road map for global environmental assessments}.
-		\newblock {\em Nature Climate Change}, 7(6):379--382, 2017.
-
-		\bibitem{Victor2015}
-		{David G. Victor}.
-		\newblock {Embed the social sciences in climate policy - David Victor}.
-		\newblock {\em Nature}, 520:7--9, 2015.
-
-		\bibitem{Hulme2010}
-		Mike Hulme and Martin Mahony.
-		\newblock {Climate change: What do we know about the IPCC?}
-		\newblock {\em Progress in Physical Geography}, 34(5):705--718, 2010.
-
-		\bibitem{Corbera2016}
-		Esteve Corbera, Laura Calvet-Mir, Hannah Hughes, and Matthew Paterson.
-		\newblock {Patterns of authorship in the IPCC Working Group III report}.
-		\newblock {\em Nature Climate Change}, 6(1):94--99, 2016.
+		\bibitem{Lamb2018d}
+		William~F. Lamb, Felix Creutzig, Max~W. Callaghan, and Jan~C. Minx.
+		\newblock {Learning about urban climate solutions}.
+		\newblock {\em Nature Climate Change}, 9(4):279--287, 2018.
 
@@
 
-		\bibitem{Barocas2016}
-		Solon Barocas and Andrew~D Selbst.
-		\newblock {Big Data's Disparate Impact}.
-		\newblock {\em California Law Review}, 104:671--732, 2016.
-
 	\end{thebibliography}

### 2019-07-10 methods.tex
draft 1
piers edits

--- 2019-06-12 methods.tex
@@
 	This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on the Web of Science core collection.
-Though not exhaustive, the Web of Science gives a good coverage of the literature in major peer-reviewed journals.	Each document is assigned to an assessment period according to the timeline shown in table 1.
+Though not exhaustive, the Web of Science gives a good coverage of the literature in major peer-reviewed journals.
+The Web of Science data gives us a disciplinary classification (based on the journal) and publication year, among other metadata, for each document.	Each document is assigned to an assessment period according to the timeline shown in table 1.
 
-	We use the references scraped from IPCC assessment reports from \citep{Minx2017l}, and attempt to match these with the results from the web of science.
-Table \todo{}[x] shows the percentage of IPCC citations matched in each working group for each assessment report.
+	We use the references scraped from IPCC assessment reports from \citep{Minx2017l}, and attempt to match these with the results from the Web of Science.
+We use doc2vec similarity scores \cite{Le2014} to identify the 500 most similar titles for each reference, and count the document as a match if the jaccard similarity score of the two word shingles of the reference title and the document title is greater than 0.5 \cite{Khabsa2014}.
+Table \ref{ipcc-matching} shows the percentage of IPCC citations matched in each working group for each assessment report.
+This is significantly lower in earlier periods, as data coverage and quality of citation databases is lower for earlier periods.
+Matching in WG III is also lower, suggesting a greater share of non-peer review literature, or literature not directly mentioning climate change, but related to it's mitigation (for example on energy policy).
+
+		\begin{table}[htp]
+			\begin{center}
+		\input{tables/ipcc_matching.tex}
+	\caption{IPCC matching}
+	\label{ipcc-matching}
+	\end{center}
+\end{table}
 
@@
 	Data quality in earlier Web of Science results is poorer, and some documents have missing abstracts.
-In the quantification of the size of the literature and its vocabulary in table [], titles are substituted for abstracts where they are not available.
-The words of the documents are lemmatized/stemmed, replacing different forms of the same word (i.e.
+In the quantification of the size of the literature and its vocabulary in table \ref{tab}, titles are substituted for abstracts where they are not available.
+The words of the documents are lemmatized, replacing different forms of the same word (i.e.
 word/words) with a single instance.
-Commonly occuring words, or ``stopwords'' are removed, as are all words shorter than 3 characters, and all words containing only punctuation or numbers.
+Commonly occurring words, or ``stopwords'' are removed, as are all words shorter than 3 characters, and all words containing only punctuation or numbers.
 
@@
 	For the calculation of the topic model, documents with missing abstracts are ignored, and the document term matrix is transformed into a document
-	frequency-inverse document frequency (tf-idf) matrix, where scores are scaled according to the frequency of their occurence in the corpus.
+	frequency-inverse document frequency (tf-idf) matrix, where scores are scaled according to the frequency of their occurrence in the corpus.
 This gives more weight to terms which appear in few documents, and less weight to those which appear in many.
@@
 
-	Topic models are calculated for 70, 80, 90, 100, 110, 120, 130 and 140 topics.
+	Topic models are calculated for 70, 80, 90, 100, 110, 120, 130, 140 and 150 topics.
+The run with 150 topics was discarded as it contained a topic to which no terms or documents were assigned.
 The relative usefulness of each model was assessed subjectively by the authors, based on inspection of the online visualisation tool, and the spreadsheet \textbf{topic\_comparison.xlsx} accompanying the supporting information.
@@
 	\end{equation}
+
+	\subsubsection*{Topic Map}
+	The topic model gives us the location of each document in a 140 dimensional topic space, with each dimension corresponding to a that document's \textit{topic-ness} in a given topic.
+t-Distributed Stochastic Neighbour Embedding (t-SNE) is a dimensionality reduction technique which we use to represent each document's topic scores in 2 dimensions \cite{vandermaaten2008}.
 
@@
 		\label{socsci-wgs}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=1\linewidth]{plots_pub/topic_rep_ks.pdf}
+		\caption{Topic representation over different values of K (number of topics). Topics in the upper or lower 6.66th percentile of either dimension are labelled}
+		\label{top-rep-ks}
 	\end{center}
@@
 \linespread{1}
+
 %\bibliography{Mendeley}
 
-\begin{thebibliography}{1}
+\begin{thebibliography}{10}
 
@@
 
+	\bibitem{Le2014}
+	Quoc~V. Le and Tomas Mikolov.
+	\newblock {Distributed Representations of Sentences and Documents}.
+	\newblock {\em ICML}, 32, 2014.
+
+	\bibitem{Khabsa2014}
+	Madian Khabsa and C~Lee Giles.
+	\newblock {The number of scholarly documents on the public web}.
+	\newblock {\em PLoS ONE}, 9(5), 2014.
+
 	\bibitem{Lee1999}
@@
 	\newblock {Learning the parts of objects by non-negative matrix factorization.}
-	\newblock {\em Nature}, 401(6755):788--91, 1999.
+	\newblock {\em Nature}, 401(6755):788--791, 1999.
 
@@
 
+	\bibitem{vandermaaten2008}
+	Laurens van~der Maaten and Geoffrey Hinton.
+	\newblock {Visualizing Data using t-SNE}.
+	\newblock {\em Journal of Machine Learning Research}, 9:2579--2605, 2008.
+
 	\bibitem{Meehl2007}

### 2019-07-10 tables/growth_table_large.tex
comma table

@@
 &\textbf{AR1} & \textbf{AR2} & \textbf{AR3} & \textbf{AR4} & \textbf{AR5} & \textbf{AR6}\\ \hline\textbf{Documents} &1167 & 8539 & 21716 & 38750 & 134413 & 201606\\ 
-\textbf{Words} &2000 & 12480 & 23346 & 34637 & 71867 & 94746\\ 
-\textbf{New words} & change (560) & oil (287) & downscaling (217) & sres (234) & biochar (1791) & mmms (313)\\ & climate (428) & deltac (283) & degreesc (187) & petm (95) & redd (1113) & cop21 (234)\\ & co2 (318) & whole (256) & ncep (130) & amf (88) & cmip5 (679) & c3n4 (214)\\ & climatic (289) & tax (254) & fco (107) & sf5cf3 (86) & cmip3 (587) & sdg (187)\\ & model (288) & landscape (249) & pfc (98) & clc (81) & mofs (299) & zika (182)\\ & atmospheric (281) & alternative (243) & otcs (98) & embankment (81) & sdm (297) & ndcs (168)\\ & effect (280) & availability (242) & dtr (95) & cwd (79) & mof (275) & indc (164)\\ & global (224) & life (239) & nee (89) & etm (75) & biochars (252) & indcs (134)
+\textbf{Words} &2,000 & 12,480 & 23,346 & 34,637 & 71,867 & 94,746\\ 
+\textbf{New words} & change (560) & oil (287) & downscaling (217) & sres (234) & biochar (1,791) & mmms (313)\\ & climate (428) & deltac (283) & degreesc (187) & petm (95) & redd (1,113) & cop21 (234)\\ & co2 (318) & whole (256) & ncep (130) & amf (88) & cmip5 (679) & c3n4 (214)\\ & climatic (289) & tax (254) & fco (107) & sf5cf3 (86) & cmip3 (587) & sdg (187)\\ & model (288) & landscape (249) & pfc (98) & clc (81) & mofs (299) & zika (182)\\ & atmospheric (281) & alternative (243) & otcs (98) & embankment (81) & sdm (297) & ndcs (168)\\ & effect (280) & availability (242) & dtr (95) & cwd (79) & mof (275) & indc (164)\\ & global (224) & life (239) & nee (89) & etm (75) & biochars (252) & indcs (134)
 \end{tabular}

### 2019-07-12 tables/growth_table.tex
produce docs table

--- 2019-04-24 tables/growth_table.tex
@@
-\begin{tabular}{l p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm}} 
-&\textbf{AR1} & \textbf{AR2} & \textbf{AR3} & \textbf{AR4} & \textbf{AR5} & \textbf{AR6}\\ \hline\textbf{Documents} &1167 & 8539 & 21716 & 38750 & 134413 & 201606\\ 
-\textbf{Words} &2000 & 12480 & 23346 & 34637 & 71867 & 94746\\ 
-\textbf{New words} & change (560) & oil (287) & downscaling (217) & sres (234) & biochar (1791) & mmms (313)\\ & climate (428) & deltac (283) & degreesc (187) & petm (95) & redd (1113) & cop21 (234)\\ & co2 (318) & whole (256) & ncep (130) & amf (88) & cmip5 (679) & c3n4 (214)\\ & climatic (289) & tax (254) & fco (107) & sf5cf3 (86) & cmip3 (587) & sdg (187)\\ & model (288) & landscape (249) & pfc (98) & clc (81) & mofs (299) & zika (182)\\ & atmospheric (281) & alternative (243) & otcs (98) & embankment (81) & sdm (297) & ndcs (168)\\ & effect (280) & availability (242) & dtr (95) & cwd (79) & mof (275) & indc (164)\\ & global (224) & life (239) & nee (89) & etm (75) & biochars (252) & indcs (134)
+\begin{tabular}{|l |p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm} p{1.8cm}|} 
+\hline 
+&\textbf{AR1} & \textbf{AR2} & \textbf{AR3} & \textbf{AR4} & \textbf{AR5} & \textbf{AR6}\\ \hline\textbf{Years} &1986-1989 & 1990-1994 & 1995-2000 & 2001-2006 & 2007-2013 & 2014-\\ 
+\textbf{Documents} &1,167 & 8,539 & 21,716 & 38,750 & 134,413 & 201,606\\ 
+\textbf{Unique words} &2,000 & 12,480 & 23,346 & 34,637 & 71,867 & 94,746\\ 
+\textbf{New words} & change (560) & oil (287) & downscaling (217) & sres (234) & biochar (1,791) & mmms (313)\\ & climate (428) & deltac (283) & degreesc (187) & petm (95) & redd (1,113) & cop21 (234)\\ & co2 (318) & whole (256) & ncep (130) & amf (88) & cmip5 (679) & c3n4 (214)\\ & climatic (289) & tax (254) & fco (107) & sf5cf3 (86) & cmip3 (587) & sdg (187)\\ & model (288) & landscape (249) & pfc (98) & clc (81) & mofs (299) & zika (182)\\ & atmospheric (281) & alternative (243) & otcs (98) & embankment (81) & sdm (297) & ndcs (168)\\ & effect (280) & availability (242) & dtr (95) & cwd (79) & mof (275) & indc (164)\\ & global (224) & life (239) & nee (89) & etm (75) & biochars (252) & indcs (134) \\ \hline
 \end{tabular}

### 2019-07-12 coverletter.tex
before merging in overleaf

@@
 \usepackage{tikz}
-\usepackage{fancyhdr}
-\pagestyle{fancy}
+\usepackage{url}
+\usepackage{xifthen}
 
@@
 			\par\textsf{mail callaghan@mcc-berlin.net}
-			\par\textsf{web www.mcc-berlin.net}
+			\par\textsf{web \url{www.mcc-berlin.net}}
 		}
@@
 
-We believe this letter addresses a crucial challenge affecting the broad climate change community: namely, the field's rapidly expanding literature.
-This phenomenon - there are more than 45,000 papers published on climate change each year - means understanding the field in its entirety is more difficult than ever.
-This is particularly relevant for the IPCC, given their mandate of providing comprehensive, objective and transparent assessments of he literature.
+``Big literature'' - dealing with a vast and rapidly expanding body of publications - poses new, and largely neglected challenges for climate change assessments and how we understand them.
+For example, we estimate a total of 350,000 new publications on climate change to emerge (only) in the Web of Science during the Sixth Assessment Cycle of the Intergovernmental Panel on Climate Change spanning from 2015 to 2022.
+Big data and machine learning methods need to be applied for keeping an overview of developments in the scientific landscape and to analyse how past IPCC assessments have engaged with the avaailable literature.
+So far, attempts \cite{Bjurström2011, Hulme2010, Victor2015, Corbera2016, Kowarsch2017} have often been based on qualitiative perceptions, or incomplete data with insufficient methodological sophistication.
 
-Moreover, this challenge has also hampered how we have attempted to understand how the IPCC engages with the literature.
-Such attempts \cite{Bjurström2011, Hulme2010, Victor2015, Corbera2016, Kowarsch2017} have often been based on qualitiative perceptions, or out of date data with insufficient methodological sophistication to contrast patterns in IPCC citations with patterns in the wider literature.
-
-Our study has two innovations which allow us advance the current state of knowledge on the the IPCC and the field it is tasked with assessing.
-First, we set the complete set of IPCC citations into the context of the wider literature, allowing us to show which disciplines have been over or under-represented.
-Contrary to previous claims, the social sciences are over-represented in IPCC reports.
-This is because the proportion of social science articles among publications cited by the IPCC is higher than the proportion of social science articles among all publications on climate change.
-Second, our use of topic modelling allows us to dig down into the content of articles more or less represented in the IPCC.
-This provides the basis for our second main conclusion, that literature on technical solutions (such as negative emissions, buildings or cities) is growing fast and, even compared to other fast-growing literatures, has been under-represented in IPCC reports.
-
-These insights have several implications across the community, and we further point out how the map we produce can enhance our understanding of the field and contribute to improving processes involved in the production of global environmental assessments.
+In this study we use machine-learning to provide a comprehensive, thematic map of the more than 400,000 articles on climate change published in the Web of Science to date.
+We perceive two innovations that allow us advance the current state of knowledge on the IPCC and the field it is tasked with assessing.
+First, our thematic map allows us to situate a complete set of IPCC citations into the context of the wider literature and analyse disciplinary representation adequately.
+We find that contrary to previous claims, the social sciences are over-represented in IPCC reports.Second, the use of machine learning methods in creating the map allows us to analyse the content of publications more or less represented in the IPCC.
+We find that literature on technical solutions (such as negative emissions, buildings or cities) is growing fast and, even compared to other fast-growing literatures, has been under-represented in IPCC reports.
+We point towards a variety of other applications of such a comprehensive, thematic literature map within global environmetal assessments as well as the broad field of research synthesis.
+Our findings have direct implications for addressing growing demands for more solution-oriented climate change assessments that are also more firmly rooted in the social sciences.
 

### 2019-07-12 main.tex
before merging in overleaf

@@
 \usepackage{standalone}
+\usepackage{xr}
+\externaldocument{methods}
 
@@
 \title{A Topography of Climate Change Research}
-\author[1,2]{Max Callaghan}
+\author[1,2]{Max Callaghan*}
 \author[1,2]{Jan Minx}
@@
 		\cite{Nunez-Mir2016, Minx2017l}, where the science of climate change is expanding exponentially \cite{Grieneisen2011, Haunschild2016}.
-In the five years since the publication of the last IPCC assessment report \cite{IPCC2014c}, 201,606 papers were published in the Web of Science (WoS) (see Table \ref{tab}).
-This is almost as much as the 204,585 papers published during the first five assessment periods, a period of nearly 30 years.
-A total of around 350,000 new publications can be expected for the current sixth assessment cycle of the IPCC, based on current growth patterns.
+In the five years since the publication of the last IPCC assessment report \cite{IPCC2014c}, 202,000 papers were published in the Web of Science (WoS) (see Table \ref{tab}).
+This is almost as much as the 205,000 papers published during the first five assessment periods; a period of nearly 30 years.
+A total of around 350,000 new publications can be expected for the current sixth assessment cycle of the IPCC, based on current growth patterns (Figure \ref{pub-growth}.
 Moreover, the literature has also become more diverse.
-This is reflected in the expansion of the literature's vocabulary - from 2,000 unique words in the first assessment period to 94,746 words so far in the sixth - indicating that the field has incorporated new content.
+This is reflected in the expansion of the literature's vocabulary - from 2,000 unique words in the first assessment period to 95,000 words so far in the sixth - indicating that the field has incorporated new content.
 For example, the zika virus, which was mentioned in 182 articles from 2014-2018, had never before been discussed in the titles or abstracts of articles relating to climate change.
 Yet it has emerged as a topic of high relevance: the incidence of the virus, the outbreak of which in Brazil in 2016 was declared a public health emergency by the WHO, is set to increase under rising global temperatures \cite{Rao2019}.
-Similar rapid emergence patterns can be seen for [Intended] Nationally Determined Contributions ([I]NDCs) and Sustainable Development Goals (SDGs) in AR6, and Biochar and REDD (The United Nations Collaborative Programme on Reducing Emissions from Deforestation and Forest Degradation in Developing Countries) in AR5, among others.
+Similar rapid emergence patterns can be seen for INDCs and SDGs in AR6, and Biochar and REDD in AR5, among others\footnote{The glossary in SI contains a complete list of the acronyms shown in the table}.
+
+		\begin{figure}[htp]
+			\begin{center}
+				\includegraphics[width=180mm]{plots_pub/pubs_time_wgb.pdf}
+				\caption{ The number of climate change documents in the Web of Science in each year.
+For 2019-21 we project the number of papers assuming there is no more growth, and assuming that growth continues at the same rate as over the past five years}
+				\label{pub-growth}
+			\end{center}
+		\end{figure}
 
@@
 Whilst the field of evidence synthesis technology that tries to streamline human tasks through machine learning at the different stages of the review process is still in its infancy \cite{Beller2018}.
-\emph{Finally}, overwhelming amounts of literature may be a major reasons why assessments of scientific assessments \cite{Bjurström2011, Hulme2010, Victor2015, Corbera2016} do not offer robust quantifications, for example, for claims about the relationship between report citations and the underlying literature.
-This may substantially affect findings.
+\emph{Finally}, overwhelming amounts of literature may be a major reason why studies of scientific assessments \cite{Bjurström2011, Hulme2010, Victor2015, Corbera2016} do not offer robust quantifications, for claims about the relationship between report citations and the underlying literature.
 
@@
 The word topic derives from the Greek word for place (topos), and by \textit{situating} the documents in a reduced-form projection of their thematic content (see Figure \ref{oecd_topic_map}), we create a \textit{topographic map} of the literature on climate change.
-Such a systematic engagement with the thematic content of the climate science is missing from the literature so far.%To our knowledge, this is the first
-		We apply this map in a second step to understand how the IPCC reports have represented the available climate change literature and re-evaluate claims of bias based on a more comprehensive understanding of the available climate science, and enrich the discussion of representation in the literature to include topics as well as disciplines.
+Such a systematic engagement with the thematic content of the climate science is missing from the literature so far.
+		We apply this map in a second step to understand how the IPCC reports have represented the available climate change literature and re-evaluate claims of bias based on a more comprehensive understanding of the available climate science.
+We enrich the discussion of representation in the literature by discussing topics as well as disciplines.
 
@@
 		Figure \ref{oecd_topic_map} shows a \emph{thematic} or \emph{topopographic map} of the 400,000 publications on climate change in our dataset with a total number of 140 topics.
-The number of topics must be defined exogenously, but the results are robust to different specifications (see methods for examples and a thorough explanation of model selection).
-Using non-negative matrix factoriziation \cite{Lee1999}, the topics are machine-learned from the papers' abstracts (see methods for details).
+The number of topics must be defined exogenously, but the results are robust to different specifications.
+Using non-negative matrix factoriziation \cite{Lee1999}, the topics are machine-learned from the papers' abstracts (see methods for details, examples of different model specifications, and a thorough explanation of model selection), and the topic scores of each document are reduced to the two dimensions shown through t-distributed stochastic neighbour embedding \cite{vandermaaten2008}.
+\footnote{A full list of topics and related words, and a list of documents and related topics are given in the SI}.
 
@@
 
-		The map shown covers a broad range of topics that occur in meaningful clusters.
+		The map shown covers a broad range of topics, with related topics shown in clusters.
 In general, topics related to climate science and impacts are in the West, while solution-oriented topics are in the East.
 More fine-grained research areas can also be distinguished.
-For example, publications related to urban infrastructure (buildings, energy, cement, waste) are located in the East (), physical climate impacts such as sea-level rise (), heat waves (), droughts () or crop yield (losses) () are in the South-West and energy systems are in North-East ().
-There are larger groups of documents at the fringes of the map that relate mainly to one or two specific topics such as biochar, corals, soil organic carbon, clouds and aerosols, diseases, membranes, absorption or adsorption or CO2 storage.
+For example, publications related to urban infrastructure (\textbf{buildings}, \textbf{energy}, \textbf{cement}, \textbf{waste}) are located in the East, physical climate impacts such as \textbf{sea-level}, \textbf{droughts}  or [crop] \textbf{yield} are in the South-West and energy systems are in North-East.
+There are larger groups of documents at the fringes of the map that relate mainly to one or two specific topics such as \textbf{biochar}, \textbf{coral}, or \textbf{CO2 storage}.
 Interestingly, scenarios feature centrally in the map, at the interface between different scientific communities.
 This corresponds to their integrative nature in IPCC reports (REF).
-This depiction of the thematic structure of the literature, and its ordering and categorising thereby could be useful for individual communities or for climate change assessments \footnote{We include the list of topic-document combinations in the supplementary materials}.
+This map of the thematic structure of the literature could be useful for individual communities or for climate change assessments.
 
@@
 More than 60\% of the literature is published in natural science journals.
-Similarly, only in X out of 140 topics do publications from another field make up the majority of documents, in Y cases the contribution of publications in natural science journals make more than 50\%.
+Similarly, in 115 out of 140 topics the contribution of publications in natural science journals is greater than any other discipline.
 We calculate disciplinary entropy of topics as a measure of their degree of interdisciplinarity (see Figure \ref{dis-entropy} and methods for details).
-While research on health, food, or policy comes from a range of disciplines, research on ice and oceans comes almost exclusively from the natural sciences).
+This shows how research on health, food, or policy comes from a range of disciplines, while research on ice and oceans comes almost exclusively from the natural sciences).
 
@@
 		Finally, the topography shows the thematic evolution of the literature, with topics exhibiting distinct patterns of growth.
-Fast-growing topics in the last three assessment periods have included, among others, coral, risks, adaptation, hydrogen, buildings, CO2 removal, networks and biochar.
-Biochar is particularly remarkable in that the sizeable literature which emerged in AR5 was completely absent from the climate change literature beforehand.
-		The identification of new topics as they emerge, particularly as these are discovered without prior knowledge of the literature, can help researchers and assesment-makers to keep abreast of a quickly evolving field.
+Fast-growing topics in the last three assessment periods have included, among others, \textbf{coral}, \textbf{risks}, \textbf{adaptation}, \textbf{hydrogen}, \textbf{buildings}, \textbf{CO2 removal}, \textbf{networks} and \textbf{biochar}.
+\textbf{Biochar} is particularly remarkable in that the sizeable literature which emerged in AR5 was completely absent from the climate change literature beforehand.
+		The identification of new topics as they emerge, particularly as these are identified without prior knowledge of the literature, can help researchers and assessment-makers to keep abreast of a quickly evolving field.
 
@@
 		Figure \ref{oecd_rep}.a shows that the social sciences were indeed under-represented in the third assessment report, but by the fifth assessment report were over-represented.
-Likewise, other social sciences than economics have become better represented since AR3  (see figure \ref{subfield}f) with social \& economic geography (4.3\% of the literature), political science (1.0\%), and sociology (0.8\%) showing improved representation in AR5 compared to AR3, and social and economic geography, political science, and other social sciences better represented than economics when taking into account the distribution of studies in the literature.
+Likewise, other social sciences than economics have become better represented since AR3  (see figure \ref{subfield}f) with social \& economic geography (4.3\% of the literature), political science (1.0\%), and sociology (0.8\%) showing improved representation in AR5 compared to AR3, and social and economic geography, political science, and other social sciences better represented than economics.
 
 		This challenges what we think we know about the IPCC.
-The social sciences, by now, are actually the best represented field, with a share in the literature cited by IPCC reports [1.5] times as high as in the literature at large.
-On the other hand the Agricultural Sciences and Engineering \& Technology have been consistently under-represented, with [2.5] and [3.5] times the share of studies in the wider literature than in the literature cited by the IPCC in AR5 respectively.
+The social sciences, by now, are actually the best represented field, with a share in the literature cited by IPCC reports 1.32 times as high as in the literature at large.
+On the other hand the Agricultural Sciences and Engineering \& Technology have been consistently under-represented, with 2.27 and 3.49 times the share of studies in the wider literature than in the literature cited by the IPCC in AR5 respectively.
 
@@
 Figure \ref{oecd_rep}c shows that topics more commonly cited by IPCC working group I are older and largely better represented in IPCC reports.
-These topics, for example \textbf{ozone}, \textbf{oceans}, \textbf{clouds}, \textbf{aerosols} and \textbf{sea levels}, are older, predominantly cited by WG I, and well cited by IPCC reports.
-They make up some of the core topics of the physical science of climate change.
+These topics, for example \textbf{ozone}, \textbf{oceans}, \textbf{clouds}, \textbf{aerosols} and \textbf{sea levels} make up some of the core topics of the physical science of climate change.
 
@@
 These topics are newer and until now have been under-represented in IPCC reports.
-They are the topics that could be seen as potential gaps in the IPCC's coverage of the science.
 Because they are new areas of knowledge, they may be highly salient in a periodic assessment process.
-These topics are primarily in working group III, on mitigation (see methods section [] for a discussion of the categorisation of topics, including CLC, adsorption and hydrogen, which may more properly be of relevance to WGIII).
+These topics are primarily in working group III, on mitigation \footnote{see methods for a discussion of the categorisation of topics, including CLC, adsorption and hydrogen, which may more properly be described as relevant to WGIII}.
 
 		The difference between these under-represented new topics and other new topics that are better represented is intriguing.
-This difference is visible in figure \ref{evolution-map}, where In AR5, the clusters of documents around the \textbf{adsorption}, \textbf{buildings}, and \textbf{biochar} topics contain few IPCC citations, whereas the clusters around \textbf{food}, \textbf{health}, \textbf{adaptation}, and \textbf{GHGs} contain more.
-As shown in figure \ref{oecd_rep}c, adsorption buildings and biochar are [4, 3.5 and 3.8] times more prevalent in the literature than in IPCC citations, while food is [0.3] times more prevalent in the literature and health and adaptation are [0.1] and [2,5] times more prevalent in IPCC citations respectively.
-The IPCC, then, has been better at integrating new knowledge from these topics, and in general better at integrating new knowledge from WG II  than WG III topics.
+This difference is visible in figure \ref{evolution-map}, where in AR5, the clusters of documents around the \textbf{adsorption}, \textbf{buildings}, and \textbf{biochar} topics contain few IPCC citations, whereas the clusters around \textbf{food}, \textbf{health}, \textbf{adaptation}, and \textbf{GHGs} contain more.
+As shown in figure \ref{oecd_rep}c, \textbf{adsorption}, \textbf{buildings} and \textbf{biochar} are 4.08, 3.34 and 3.61] times more prevalent in the literature than in IPCC citations, while food is 1.22 times more prevalent in the literature and health and adaptation are 1.02 and 2.22 times more prevalent in IPCC citations respectively.
+The IPCC, has been better at integrating new knowledge from these topics, and in general better at integrating new knowledge from WG II  than WG III topics.
 
@@
 		Recalling policymakers' demands for more solution-oriented assessments \cite{Kowarsch2017}, we could also interpret the topics that are newer and under-represented as ``solutions-relevant''.
-Many deal with negative emissions, or with mitigation (or to a lesser extent adaptation) options in the transport, buildings and power sectors.
-All are arguably related to climate solutions.
 However, while policymakers' demands for solutions-oriented knowledge were rather about policy options, these under-represented new topics deal with more technical solutions and are found rather in technical disciplines within engineering \& technology and the agricultural sciences.
@@
 
-		\subsection*{Machine-learning for climate change assessments}%, evidence synthesis and science of science} % needs to be reviewed
-		Keeping track of developments in the scientific literature is becoming increasingly difficult in the age of big literature.
-This is becoming a central challenge for global environmental assessments such as those conducted by the IPCC \cite{Minx2017l, Kowarsch2017}, as well as for science of science research (\cite{Zeng2017}), the provision of thorough and comprehensive reviews in specific fields, and the efficient allocation of research funding where it is needed.
-Ultimately it is a challenge for sound, evidence-based scientific policy advice (\cite{White2019}).
-Systematic maps and evidence gap maps (\cite{James2016}, \cite{McKinnon2015}) provide crucial tools for tracing the literature, but current approaches are constrained by available resources to answering very specific questions, or are limited by a lack of suitable literature.
-On the other hand, current scientometric and research weaving approaches (\cite{Nakagawa2019}) can capture a broader landscape of research, but are too unspecific with regard to the thematic content of literature.
+		\subsection*{Machine-learning for climate change assessments}
 
-		Elsewhere, we show how machine learning can accelerate the provision of traditional maps of evidence with thousands rather than hundreds of data points (\cite{Lamb2018d}).
-Here we extend this analysis to vast bodies of literature with hundreds of thousands of publications and show how ``topopgraphic maps'' provide an efficient visualisation of these.
+		We have shown that social science literature about climate change is over-represented in the IPCC, while technical literature on solutions is under-represented.
+		A perfectly proportional representation of every part of the literature is of course not optimal, yet these two features represent new knowledge about the interaction between the IPCC and the literature, and have important implications for the community.
+		The over-representation of the social sciences, combined with the perception that the IPCC needs to include more social science knowledge \cite{Victor2015}, suggests that doing so must involve the funding and production of more social science literature on climate change, not just greater efforts by the IPCC to include it.
+		Moreover, the fact that solutions-relevant topics are under-represented - while policymakers demand more solutions-oriented assessments - and that these topics contain little social science research, suggests areas where social science research may be usefully conducted.
+Further, this fact can open a debate about the extent to which the IPCC should include more technical knowledge on solutions from disciplines within engineering and the agricultural sciences.
 
-		We acknowledge that the climate change topography presented here is not fully comprehensive.
-The WoS  covers a substantive, yet by no means exhaustive set of publications.
-Grey literature, some smaller journals and books, not to mention indigenous knowledge \cite{Ford2016b}, are not covered.
-Similarly, our query (see methods) requires that the keywords, title or abstract of a publication mentions climate change or a synonym or related term.
-Whilst this is a reasonable system boundary definition, and follows \cite{Grieneisen2011} exactly, we acknowledge the existence of directly relevant studies for climate change research - for example on energy technologies, energy policies or - that may not meet our criteria and remain outside the scope of our analysis.
-Yet our decisions are driven by data availability and requirements for a clean, climate-changed focused dataset.
-Given the large size of our sample (400,000+ publications), we argue that our topography provides a reasonable representation of the research landscape on climate change.
-Furthermore, unless IPCC citation patterns systematically differ in the not included parts of the literature, the main conclusions of this study are unaffected.
+		The map can also serve as a guide to future assessments, to ensure that decisions about how different areas of the literature are represented are well-informed. 
+		The map can contribute to these decisions as they are made from the scoping process, through to the selection by authors of individual studies.
+		Beyond this, the methods shown here could aid other processes in the production of IPCC reports, such as the identification of potential authors to acheive a better balance across sectors, regions and genders \cite{Corbera2016}.
+		Outside of the IPCC, this approach is part of ongoing attempts to make use of machine-learning within evidence synthesis.
+The topographic map presented is a new approach to rapidly mapping very large literatures.
 
-		In addition, our analysis is based on a topic model of publication abstracts.
-Though it is reasonable to assume that abstracts reflect the themes of the papers they describe, this depends on the quality of the abstracts, and thematic features of the underlying texts may not be adequately represented.
-In the absence of comprehensive full-text access and remaining, non-trivial challenges in text extraction from PDFs, we argue that abstracts provide a reasonable unit of analysis.
-
-		We apply our map of the climate change literature to understand the representativeness of IPCC citations and argue that answering related questions requires a clear benchmark.
-We show that applying this benchmark challenges and confirms some prominent findings around disciplinary representation in and solution-orientation of IPCC assessments.
-
-		While proportional representation of all topics and all disciplines may not be desirable, the analysis presented here can help the IPCC to make quantitatively informed decisions about what to represent.
-The claim that the IPCC needs to incorporate more social science research may indeed be well-founded, but, in light of the fact shown here that the IPCC over-represents the social science literature that is published, this would imply increases in funding for climate change research in the social sciences.
-While some might argue that engineering or agricultural research on solutions related topics may be too technical and less relevant to IPCC assessments, in light of the size of the literature in these areas relative to that which is cited by the IPCC it would follow that more social science research needs to be carried out that deals with these topics and produces assessment-ready knowledge.
-
-		We highlight that there are a variety of other immediate applications for such comprehensive topic maps and their rich, underlying data.
-Rapid, comprehensive maps could make a contribution to making climate change assessment processes in various places more efficient.
-For example, they could inform the scoping of scientific assessment reports to make sure that reports keep abreast of developments in the literature and remain policy relevant.
-What's more, they could help in the efficient identification of the best subject area experts across regions, sectors and genders (REFs) and directly increase the transparency with regard to the availability and selection of citations.
-Beyond the organisation of global environmental assessments, such maps can inform research funding decisions, and help individual researchers identi Future research can explore how further methods, and more comprehensive data, can help drive forward these applications.
-
-		While the size and variety of the literature on climate change presents challenges to global environmental assessments, it represents a wealth of knowledge on vital climate solutions.
-By shedding light on new and under-reported subjects and by providing quantifications of what we think we know about how assessments and their relationship to the literature, computational mapping can help ensure that this knowledge is made use of efficiently.
-Topographic maps  can become part of a toolbox which helps the IPCC continue to be able to fulfil its mandate of providing comprehensive, objective and transparent assessments of an expanding literature.
+		The more than 400,000 publications we deal with here represent a wealth of knowledge on climate change and climate solutions.
+However, we acknowledge that our dataset is by no means exhaustive.
+We repeat an established query \cite{Haunschild2016}, granting that it may have imperfections.
+Beyond this we miss publications not in the Web of Science (some small journals, some books, and most grey literature, not to mention indigenous knowledge \cite{Ford2016b}); and studies relevant for the work of the IPCC, but that do not directly mention climate change (for example on energy policy).
+We argue that this remains a reasonable system boundary given data availabilty, and stress that the documents not included in our study alter our findings only if they have systematically different patterns of citation by the IPCC.
+In the future, making use of more sources climate change knowledge, and extracting and classifying information from full texts (here we only use abstracts), could improve the granularity of this topography.
+Most importantly, machine learning applications should be explored that support IPCC authors in assessing the literature.
+This would prepare IPCC assessments for the age of big literature.
 
@@
 	%\bibliography{Mendeley}
+
 \begin{thebibliography}{10}
@@
 	\bibitem{Nunez-Mir2016}
-		Gabriela~C Nunez-Mir, Basil~V Iannone, Bryan~C Pijanowski, Ningning Kong,
+	Gabriela~C. Nunez-Mir, Basil~V. Iannone, Bryan~C. Pijanowski, Ningning Kong,
 	Songlin Fei, and Richard Fitzjohn.
@@
 	\newblock {\em Methods in Ecology and Evolution}, 7(11):1262--1272, 2016.
+
+	\bibitem{Minx2017l}
+	Jan~C. Minx, Max Callaghan, William~F. Lamb, Jennifer Garard, and Ottmar
+	Edenhofer.
+	\newblock {Learning about climate change solutions in the IPCC and beyond}.
+	\newblock {\em Environmental Science {\&} Policy}, 2017.
 
@@
 	\newblock {\em npj Climate and Atmospheric Science}, 2(1):2--8, 2019.
-
-		\bibitem{Minx2017l}
-		Jan~C. Minx, Max Callaghan, William~F. Lamb, Jennifer Garard, and Ottmar
-		Edenhofer.
-		\newblock {Learning about climate change solutions in the IPCC and beyond}.
-		\newblock {\em Environmental Science {\&} Policy}, 2017.
 
@@
 	\newblock {Learning the parts of objects by non-negative matrix factorization.}
-		\newblock {\em Nature}, 401(6755):788--791, 1999.
+	\newblock {\em Nature}, 401(6755):788--91, 1999.
+
+	\bibitem{vandermaaten2008}
+	Laurens van~der Maaten and Geoffrey Hinton.
+	\newblock {Visualizing Data using t-SNE}.
+	\newblock {\em Journal of Machine Learning Research}, 9:2579--2605, 2008.
+
+	\bibitem{Moss2010}
+	Richard~H. Moss, Jae~A. Edmonds, Kathy~A. Hibbard, Martin~R. Manning, Steven~K.
+	Rose, Detlef~P. {Van Vuuren}, Timothy~R. Carter, Seita Emori, Mikiko Kainuma,
+	Tom Kram, Gerald~A. Meehl, John~F.B. Mitchell, Nebojsa Nakicenovic, Keywan
+	Riahi, Steven~J. Smith, Ronald~J. Stouffer, Allison~M. Thomson, John~P.
+	Weyant, and Thomas~J. Wilbanks.
+	\newblock {The next generation of scenarios for climate change research and
+		assessment}.
+	\newblock {\em Nature}, 463(7282):747--756, 2010.
 
@@
 
-		\bibitem{Zeng2017}
-		An~Zeng, Zhesi Shen, Jianlin Zhou, Jinshan Wu, Ying Fan, Yougui Wang, and
-		H.~Eugene Stanley.
-		\newblock {The science of science: From the perspective of complex systems}.
-		\newblock {\em Physics Reports}, 714-715:1--73, 2017.
-
-		\bibitem{White2019}
-		Howard White.
-		\newblock {The twenty-first century experimenting society: the four waves of
-			the evidence revolution}.
-		\newblock {\em Palgrave Communications}, 5(1):1--7, 2019.
-
-		\bibitem{James2016}
-		Katy~L. James, Nicola~P. Randall, and Neal~R. Haddaway.
-		\newblock {A methodology for systematic mapping in environmental sciences}.
-		\newblock {\em Environmental Evidence}, 5(1):1--13, 2016.
-
-		\bibitem{McKinnon2015}
-		Madeleine~C. McKinnon, Samantha~H. Cheng, Ruth Garside, Yuta~J. Masuda, and
-		Daniel~C. Miller.
-		\newblock {Sustainability: Map the evidence}.
-		\newblock {\em Nature}, 528(7581):185--187, 2015.
-
-		\bibitem{Nakagawa2019}
-		Shinichi Nakagawa, Gihan Samarasinghe, Neal~R. Haddaway, Martin~J. Westgate,
-		Rose~E. O'Dea, Daniel~W.A. Noble, and Malgorzata Lagisz.
-		\newblock {Research Weaving: Visualizing the Future of Research Synthesis}.
-		\newblock {\em Trends in Ecology and Evolution}, 34(3):224--238, 2019.
-
-		\bibitem{Lamb2018d}
-		William~F. Lamb, Felix Creutzig, Max~W. Callaghan, and Jan~C. Minx.
-		\newblock {Learning about urban climate solutions}.
-		\newblock {\em Nature Climate Change}, 9(4):279--287, 2018.
-
 	\bibitem{Ford2016b}
@@
 \end{thebibliography}
+
 	\bibliographystyle{unsrt}
 
-	\include{methods}
+	%	\include{methods}
 

### 2019-07-12 methods.tex
before merging in overleaf

@@
 \usepackage[section]{placeins}
+\usepackage{xr}
+\externaldocument{main}
 
@@
 	\author[1,2]{Max Callaghan}
+	\author[1,2]{Jan Minx}
+	\author[2]{Piers M. Forster}
 
 	\affil[1]{Mercator Research Institute on Global Commons and Climate Change, Torgauer Straße, 10829 Berlin, Germany}
-	\affil[2]{School of Earth and Environment, University of Leeds, Leeds LS2 9JT, United Kingdom}
+	\affil[2]{Priestley International Centre for Climate, University of Leeds, Leeds LS2 9JT, United Kingdom}
+
 	\maketitle
@@
 		\input{tables/ipcc_matching.tex}
-	\caption{IPCC matching}
+	\caption{The proportion of citations in each report that could be matched with a document from the Web of Science}
 	\label{ipcc-matching}
@@
 This helps authors to find an appropriate level of granularity for the analysis.
+
+	\subsubsection*{Topic assignment to working groups}
+	\label{topic-wg}
+	A topic's score for each working group is calculated by summing the document-topic scores for all documents cited by that working group.
+We call the topic's primary working group that working group for which the above sum is the highest, but in some cases, where there are very few IPCC citations of documents related to a topic this can be misleading .
+For example, the word ``capacity" is relevant to the adsorption topic, so documents talking about adaptive capacity receive a low score for the topic.
+Because only very few documents highly relevant to the topic (in that they talk about adsorption or adsorptive capacity) are cited by the IPCC, and many of the weakly relevant documents are cited by the IPCC, the sum of the topic scores of the weakly relevant documents outweighs the sum of the topic scores of the strongly relevant documents, meaning that the topic is mistakenly assigned to working group II when it is more properly relevant to working group III.
 

### 2019-07-12 code/assemble_pubs.sh

@@ -9,3 +9,16 @@ cp tsne_results/plots/run_$1_s_0_p$2_all_topic_words_oecds.pdf plots_pub/all_top
 
 cp tsne_results/plots/run_$1_s_0_p$2_evolution_4.png plots_pub/topic_evolution_4.png
 cp tsne_results/plots/run_$1_s_0_p$2_evolution_4.pdf plots_pub/topic_evolution_4.pdf
+
+
+cp plots_pub/topic_oecd_entropy.pdf plots_pub/upload_figures/Figure_SI_1.pdf
+cp plots_pub/single_doc_3_536594_1861.pdf plots_pub/upload_figures/Figure_SI_2.pdf
+cp plots_pub/ipcc_rep_wcs_simplified.pdf plots_pub/upload_figures/Figure_SI_3.pdf
+cp plots_pub/wgs_socsci.pdf plots_pub/upload_figures/Figure_SI_4.pdf
+cp plots_pub/topic_rep_ks.pdf plots_pub/upload_figures/Figure_SI_5.pdf
+cp plots_pub/pubs_time_wgb.pdf plots_pub/upload_figures/Figure_1.pdf
+cp plots_pub/all_topic_words_oecds.png plots_pub/upload_figures/Figure_2.png
+cp plots_pub/all_topic_words_oecds.pdf plots_pub/upload_figures/Figure_2_hq.pdf
+cp plots_pub/topic_evolution_4.png plots_pub/upload_figures/Figure_3.png
+cp plots_pub/topic_evolution_4.pdf plots_pub/upload_figures/Figure_3_hq.pdf
+cp plots_pub/big_panel_representation.pdf plots_pub/upload_figures/Figure_4.pdf

### 2019-07-12 main.tex
submission

@@
 \title{A Topography of Climate Change Research}
-\author[1,2]{Max Callaghan*}
+\author[1,2]{Max Callaghan}
 \author[1,2]{Jan Minx}
@@
 This is almost as much as the 205,000 papers published during the first five assessment periods; a period of nearly 30 years.
-A total of around 350,000 new publications can be expected for the current sixth assessment cycle of the IPCC, based on current growth patterns (Figure \ref{pub-growth}.
+A total of around 350,000 new publications can be expected for the current sixth assessment cycle of the IPCC, based on current growth patterns (Figure \ref{pub-growth}).
 Moreover, the literature has also become more diverse.
@@
 		\begin{table}[htp]
+			\begin{center}
 				{\scriptsize
@@
 				\label{tab}
+			\end{center}
 		\end{table}
@@
 More generally, the provision of comprehensive, objective, open and transparent assessments of the available scientific literature, as defined in the principles governing IPCC work \cite{IPCC2013}, is no longer possible for authors or author teams by traditional means.
-Machine reading and learning methods as well as other data science applications are required to enable an understanding of the field of climate change research at scale (REFs).
+		Machine reading and learning methods as well as other data science applications are required to enable an understanding of the field of climate change research at scale. 
 		\emph{Second}, evidence synthesis - the enterprise of reviewing the literature based on a formal and systematic set of methods \cite{Chalmers2002} - becomes increasingly important for aggregating and consolidating the rapidly emerging knowledge and enabling scientific assessments to do their job.
-Yet, traditional methods of evidence synthesis themselves are pushed to their limits by the large amount of scientific publications.
-Whilst the field of evidence synthesis technology that tries to streamline human tasks through machine learning at the different stages of the review process is still in its infancy \cite{Beller2018}.
-\emph{Finally}, overwhelming amounts of literature may be a major reason why studies of scientific assessments \cite{Bjurström2011, Hulme2010, Victor2015, Corbera2016} do not offer robust quantifications, for claims about the relationship between report citations and the underlying literature.
+		Yet traditional methods of evidence synthesis themselves are pushed to their limits by the large amount of scientific publications.
+The field of evidence synthesis technology, which tries to streamline human tasks through machine learning at the different stages of the review process, is still in its infancy \cite{Beller2018}.
+\emph{Finally}, overwhelming amounts of literature may be a major reason why studies of scientific assessments \cite{Bjurström2011, Hulme2010, Victor2015} do not offer robust quantifications, for claims about the relationship between report citations and the underlying literature.
 
@@
 The number of topics must be defined exogenously, but the results are robust to different specifications.
-Using non-negative matrix factoriziation \cite{Lee1999}, the topics are machine-learned from the papers' abstracts (see methods for details, examples of different model specifications, and a thorough explanation of model selection), and the topic scores of each document are reduced to the two dimensions shown through t-distributed stochastic neighbour embedding \cite{vandermaaten2008}.
-\footnote{A full list of topics and related words, and a list of documents and related topics are given in the SI}.
+Using non-negative matrix factoriziation \cite{Lee1999}, the topics are machine-learned from the papers' abstracts (see methods for details, examples of different model specifications, and a thorough explanation of model selection), and the topic scores of each document are reduced to the two dimensions shown through t-distributed stochastic neighbour embedding \cite{vandermaaten2008} \footnote{A full list of topics and related words, and a list of documents, their positions on the map, and their related topics are given in the SI}.
 
@@
 Interestingly, scenarios feature centrally in the map, at the interface between different scientific communities.
-This corresponds to their integrative nature in IPCC reports (REF).
+This corresponds to their integrative nature in IPCC reports \cite{Moss2010}.
 This map of the thematic structure of the literature could be useful for individual communities or for climate change assessments.
@@
 We calculate disciplinary entropy of topics as a measure of their degree of interdisciplinarity (see Figure \ref{dis-entropy} and methods for details).
-This shows how research on health, food, or policy comes from a range of disciplines, while research on ice and oceans comes almost exclusively from the natural sciences).
+This shows how research on \textbf{health}, \textbf{food}, or \textbf{policy} comes from a range of disciplines, while research on \textbf{ice} and \textbf{oceans} comes almost exclusively from the natural sciences).
 
@@
 
-		Finally, the topography shows the thematic evolution of the literature, with topics exhibiting distinct patterns of growth.
+		Finally, the topography shows the thematic evolution of the literature (Figure \ref{evolution-map}), with topics exhibiting distinct patterns of growth.
 Fast-growing topics in the last three assessment periods have included, among others, \textbf{coral}, \textbf{risks}, \textbf{adaptation}, \textbf{hydrogen}, \textbf{buildings}, \textbf{CO2 removal}, \textbf{networks} and \textbf{biochar}.
@@
 Several studies have identified, made, or repeated claims of a disciplinary bias of IPCC assessments towards the natural sciences, and within the social sciences towards economics \cite{Bjurström2011, Victor2015, Hulme2010, Corbera2016}.
-Where these claims were based on an analysis of IPCC citations \cite{Bjurström2011}, they fail to assess this claim against a reasonable, measurable benchmark.
+Where these claims were based on an analysis of IPCC citations \cite{Bjurström2011}, they fail to assess this claim against a measurable benchmark.
 We argue here that the composition of the climate change literature as a whole provides such a benchmark, in view of the organisation's mandate to provide ``comprehensive, objective, open and transparent'' assessment of the available science \cite{IPCC2013}.
-Our comprehensive database allows us to study representation with such a benchmark, and over time rather than for single assessment cycles.
+Our database of publications allows us to study representation with such a benchmark, and over time rather than for single assessment cycles.
 
@@
 On the other hand the Agricultural Sciences and Engineering \& Technology have been consistently under-represented, with 2.27 and 3.49 times the share of studies in the wider literature than in the literature cited by the IPCC in AR5 respectively.
+Humanities are also under-represented, although they make up a very small proportion of the total literature.
 
@@
 This difference is visible in figure \ref{evolution-map}, where in AR5, the clusters of documents around the \textbf{adsorption}, \textbf{buildings}, and \textbf{biochar} topics contain few IPCC citations, whereas the clusters around \textbf{food}, \textbf{health}, \textbf{adaptation}, and \textbf{GHGs} contain more.
-As shown in figure \ref{oecd_rep}c, \textbf{adsorption}, \textbf{buildings} and \textbf{biochar} are 4.08, 3.34 and 3.61] times more prevalent in the literature than in IPCC citations, while food is 1.22 times more prevalent in the literature and health and adaptation are 1.02 and 2.22 times more prevalent in IPCC citations respectively.
+As shown in figure \ref{oecd_rep}c, \textbf{adsorption}, \textbf{buildings} and \textbf{biochar} are 4.08, 3.34 and 3.61 times more prevalent in the literature than in IPCC citations, while \textbf{food} is 1.22 times more prevalent in the literature and \textbf{health} and \textbf{adaptation} are 1.02 and 2.22 times more prevalent in IPCC citations respectively.
 The IPCC, has been better at integrating new knowledge from these topics, and in general better at integrating new knowledge from WG II than WG III topics.
@@
 Representation is the share of the subset of documents being cited by the IPCC divided by the share of the subset in the whole literature.
-The log is taken so that 0 is equal to perfectly proportional representation, and -1 and 1 are equally under and over represented.}
+We plot on a log scale so that 0.5 is equally distant to 1 as 2; plot labels show real values.}
 				\label{oecd_rep}
@@
 We argue that this remains a reasonable system boundary given data availabilty, and stress that the documents not included in our study alter our findings only if they have systematically different patterns of citation by the IPCC.
-In the future, making use of more sources climate change knowledge, and extracting and classifying information from full texts (here we only use abstracts), could improve the granularity of this topography.
+In the future, making use of more sources climate change knowledge, and extracting and classifying information from full texts, could improve the granularity of this topography.
 Most importantly, machine learning applications should be explored that support IPCC authors in assessing the literature.
@@
 	\linespread{1}
-	%\bibliography{Mendeley}
-
-\begin{thebibliography}{10}
-
-	\bibitem{Bjurström2011}
-	Andreas Bjurstr{\"{o}}m and Merritt Polk.
-	\newblock {Physical and economic bias in climate change research: A
-		scientometric study of IPCC Third Assessment Report}.
-	\newblock {\em Climatic Change}, 108(1):1--22, 2011.
-
-	\bibitem{Nunez-Mir2016}
-	Gabriela~C. Nunez-Mir, Basil~V. Iannone, Bryan~C. Pijanowski, Ningning Kong,
-	Songlin Fei, and Richard Fitzjohn.
-	\newblock {Automated content analysis: addressing the big literature challenge
-		in ecology and evolution}.
-	\newblock {\em Methods in Ecology and Evolution}, 7(11):1262--1272, 2016.
-
-	\bibitem{Minx2017l}
-	Jan~C. Minx, Max Callaghan, William~F. Lamb, Jennifer Garard, and Ottmar
-	Edenhofer.
-	\newblock {Learning about climate change solutions in the IPCC and beyond}.
-	\newblock {\em Environmental Science {\&} Policy}, 2017.
-
-	\bibitem{Grieneisen2011}
-	Michael Grieneisen and Minghua Zhang.
-	\newblock {The Current Status of Climate Change Research}.
-	\newblock {\em Nature Climate Change}, 1:72--73, 2011.
-
-	\bibitem{Haunschild2016}
-	Robin Haunschild, Lutz Bornmann, and Werner Marx.
-	\newblock {Climate Change Research in View of Bibliometrics}.
-	\newblock {\em PLoS ONE}, 11(7):1--19, 2016.
-
-	\bibitem{IPCC2014c}
-	IPCC.
-	\newblock {\em {Climate Change 2014: Synthesis Report. Contribution of Working
-			Groups I, II and III to the Fifth Assessment Report of the Intergovernmental
-			Panel on Climate Change}}.
-	\newblock IPCC, Geneva, Switzerland, 2014.
-
-	\bibitem{Rao2019}
-	V.~Brahmananda Rao, K.~Maneesha, Panangipalli Sravya, Sergio~H. Franchito,
-	Hariprasad Dasari, and Manoel~A. Gan.
-	\newblock {Future increase in extreme El Nino events under greenhouse warming
-		increases Zika virus incidence in South America}.
-	\newblock {\em npj Climate and Atmospheric Science}, 2(1):2--8, 2019.
-
-	\bibitem{IPCC2013}
-	IPCC.
-	\newblock {Principles governing IPCC work}, 2013.
-
-	\bibitem{Chalmers2002}
-	Iain Chalmers, Larry~V Hedges, and Harris Cooper.
-	\newblock {A Brief History of Research Synthesis}.
-	\newblock {\em Evaluation {\&} The Health Professions}, 25(1):12--37, 2002.
-
-	\bibitem{Beller2018}
-	Elaine Beller, Justin Clark, Guy Tsafnat, Clive Adams, Heinz Diehl, Hans Lund,
-	Mourad Ouzzani, Kristina Thayer, James Thomas, Tari Turner, Jun Xia, Karen
-	Robinson, Paul Glasziou, and {On behalf of the founding members of the ICASR
-		group}.
-	\newblock {Making progress with the automation of systematic reviews:
-		principles of the International Collaboration for the Automation of
-		Systematic Reviews (ICASR)}.
-	\newblock {\em Systematic Reviews}, 7(1):1--7, 2018.
-
-	\bibitem{Hulme2010}
-	Mike Hulme and Martin Mahony.
-	\newblock {Climate change: What do we know about the IPCC?}
-	\newblock {\em Progress in Physical Geography}, 34(5):705--718, 2010.
-
-	\bibitem{Victor2015}
-	{David G. Victor}.
-	\newblock {Embed the social sciences in climate policy - David Victor}.
-	\newblock {\em Nature}, 520:7--9, 2015.
-
-	\bibitem{Corbera2016}
-	Esteve Corbera, Laura Calvet-Mir, Hannah Hughes, and Matthew Paterson.
-	\newblock {Patterns of authorship in the IPCC Working Group III report}.
-	\newblock {\em Nature Climate Change}, 6(1):94--99, 2016.
-
-	\bibitem{Blei2010}
-	David Blei, Lawrence Carin, and David Dunson.
-	\newblock {Probabilistic topic models}.
-	\newblock {\em IEEE Signal Processing Magazine}, 2010.
-
-	\bibitem{Lee1999}
-	D~D Lee and H~S Seung.
-	\newblock {Learning the parts of objects by non-negative matrix factorization.}
-	\newblock {\em Nature}, 401(6755):788--91, 1999.
-
-	\bibitem{vandermaaten2008}
-	Laurens van~der Maaten and Geoffrey Hinton.
-	\newblock {Visualizing Data using t-SNE}.
-	\newblock {\em Journal of Machine Learning Research}, 9:2579--2605, 2008.
-
-	\bibitem{Moss2010}
-	Richard~H. Moss, Jae~A. Edmonds, Kathy~A. Hibbard, Martin~R. Manning, Steven~K.
-	Rose, Detlef~P. {Van Vuuren}, Timothy~R. Carter, Seita Emori, Mikiko Kainuma,
-	Tom Kram, Gerald~A. Meehl, John~F.B. Mitchell, Nebojsa Nakicenovic, Keywan
-	Riahi, Steven~J. Smith, Ronald~J. Stouffer, Allison~M. Thomson, John~P.
-	Weyant, and Thomas~J. Wilbanks.
-	\newblock {The next generation of scenarios for climate change research and
-		assessment}.
-	\newblock {\em Nature}, 463(7282):747--756, 2010.
-
-	\bibitem{Kowarsch2017}
-	Martin Kowarsch, Jason Jabbour, Christian Flachsland, Marcel T.~J. Kok, Robert
-	Watson, Peter~M. Haas, Jan~C. Minx, Joseph Alcamo, Jennifer Garard, Pauline
-	Riousset, L{\'{a}}szl{\'{o}} Pint{\'{e}}r, Cameron Langford, Yulia Yamineva,
-	Christoph von Stechow, Jessica O'Reilly, and Ottmar Edenhofer.
-	\newblock {A road map for global environmental assessments}.
-	\newblock {\em Nature Climate Change}, 7(6):379--382, 2017.
-
-	\bibitem{Ford2016b}
-	James~D. Ford, Laura Cameron, Jennifer Rubis, Michelle Maillet, Douglas
-	Nakashima, Ashlee~Cunsolo Willox, and Tristan Pearce.
-	\newblock {Including indigenous knowledge and experience in IPCC assessment
-		reports}.
-	\newblock {\em Nature Climate Change}, 6(4):349--353, 2016.
-
-\end{thebibliography}
+	\bibliography{Mendeley}
 

### 2019-07-12 methods.tex
submission

@@
 \usepackage[section]{placeins}
+
 \usepackage{xr}
@@
 
-		{\large{Draft current \@date}}
+		{\large{ \@date}}
 
@@
 	\title{Words, words, words: Mapping the Matter of Climate Change Literature}
-	\title{A Topography of Climate Change Research - Methods}
-	\author[1,2]{Max Callaghan}
+	\title{A Topography of Climate Change Research}
+
+\author[1,2]{Max Callaghan*}
 \author[1,2]{Jan Minx}
@@
 \affil[2]{Priestley International Centre for Climate, University of Leeds, Leeds LS2 9JT, United Kingdom}
-
 	\maketitle
@@
 
-	\setcounter{figure}{0}
-	\renewcommand\thefigure{SI.\arabic{figure}}
+		\section*{Methods}
+
+					\setcounter{table}{0}
+		\renewcommand\thetable{SI.\arabic{table}}
 
@@
 
+		We also tested the query documented in \cite{Haunschild2016}, by checking a random sample of documents exclusive to it.
+We found that the majority of additional documents were not relevant, and decided to use only the query from \cite{Grieneisen2011}.
+
 		We use the references scraped from IPCC assessment reports from \citep{Minx2017l}, and attempt to match these with the results from the Web of Science.
@@
 This is significantly lower in earlier periods, as data coverage and quality of citation databases is lower for earlier periods.
-Matching in WG III is also lower, suggesting a greater share of non-peer review literature, or literature not directly mentioning climate change, but related to it's mitigation (for example on energy policy).
+Matching in WG III is also lower, suggesting a greater share of non-peer review literature, or literature not directly mentioning climate change, but related to its mitigation (for example on energy policy).
 
@@
 		As demonstrated in Figure \ref{doc-topic}, each topic is represented as a set of word scores, and each document a set of topic scores.
-The combination of the two give the word scores in the document.
+The combination of the two approach the word scores in the document.
 For clarity in the figure, these are shown as simple counts, but in the model these are scaled according to each term's frequency within the corpus as explained above.
@@
 This helps authors to find an appropriate level of granularity for the analysis.
+Statistical methods for the selection of topic model parameters are available but they do not necessarily align with human perceptions of topic model quality \cite{Chang2009}.
+We make a judgement based on subjective criteria, but for transparency publish the results of the analysis for different numbers of topics in figure \ref{top-rep-ks}.
+The main conclusions drawn about the rapid growth and under-representation of solutions-relevant topics are stable across models.
 
@@
 Because only very few documents highly relevant to the topic (in that they talk about adsorption or adsorptive capacity) are cited by the IPCC, and many of the weakly relevant documents are cited by the IPCC, the sum of the topic scores of the weakly relevant documents outweighs the sum of the topic scores of the strongly relevant documents, meaning that the topic is mistakenly assigned to working group II when it is more properly relevant to working group III.
+We point out that topics are in any case mixtures of documents cited by different working groups, and stress that the colouring of the topics by working group is merely illustrative.
 
@@
 
-	To calculate topic representation in IPCC reports we divide each topic's share in the subsample of documents cited by IPCC reports by its share in the whole corpus.
+		To calculate topic representation in IPCC reports we divide each topic's share in the subsample of documents cited by IPCC reports by its share in the whole corpus (excluding documents published after the last assessment report).
+Disciplinary representation is calculated in the same way.
 
@@
 
+		It is an indication of the diversity of disciplines within the set of documents related to a topic.
+
 		\subsubsection*{Topic Map}
@@
 t-Distributed Stochastic Neighbour Embedding (t-SNE) is a dimensionality reduction technique which we use to represent each document's topic scores in 2 dimensions \cite{vandermaaten2008}.
-
-	\begin{figure}
-		\begin{center}
-			\includegraphics[width=1\linewidth]{plots_pub/topic_oecd_entropy.pdf}
-			\caption{SI Disciplinary Entropy}
-			\label{dis-entropy}
-		\end{center}
-	\end{figure}
-
-	\begin{figure}
-		\begin{center}
-			\includegraphics[width=1\linewidth]{plots_pub/single_doc_3_536594_1861.pdf}
-			\caption{SI Topic make up of a single document}
-			\label{doc-topic}
-		\end{center}
-	\end{figure}
-
-	\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots_pub/ipcc_rep_wcs_simplified.pdf}
-		\caption{SI Representation by subfield}
-		\label{subfield}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots_pub/wgs_socsci.pdf}
-		\caption{SI Social science \& representation in topics across working groups}
-		\label{socsci-wgs}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=1\linewidth]{plots_pub/topic_rep_ks.pdf}
-		\caption{Topic representation over different values of K (number of topics). Topics in the upper or lower 6.66th percentile of either dimension are labelled}
-		\label{top-rep-ks}
-	\end{center}
-\end{figure}
+Documents are placed on the map such that documents with similar combinations of topics are close together.
 
@@
 
-%\bibliography{Mendeley}
+	\section*{Supplementary Files}
 
-\begin{thebibliography}{10}
+	\texttt{docs.csv} contains a list of the documents considered in this study, along with basic metadata and their position on the map
 
-	\bibitem{Grieneisen2011}
-	Michael Grieneisen and Minghua Zhang.
-	\newblock {The Current Status of Climate Change Research}.
-	\newblock {\em Nature Climate Change}, 1:72--73, 2011.
+	\medskip\noindent
+	\texttt{topics.csv} Contains a list of the topics, along with their features discussed in this paper. The top 10 words associated with each topic are also shown
 
-	\bibitem{Minx2017l}
-	Jan~C. Minx, Max Callaghan, William~F. Lamb, Jennifer Garard, and Ottmar
-	Edenhofer.
-	\newblock {Learning about climate change solutions in the IPCC and beyond}.
-	\newblock {\em Environmental Science {\&} Policy}, 2017.
+\medskip\noindent
+	\texttt{doctopics.csv} Contains a list of document-topic scores, which can be cross-referenced with the document and topic ids in \texttt{docs.csv} and \texttt{topics.csv}.
 
-	\bibitem{Le2014}
-	Quoc~V. Le and Tomas Mikolov.
-	\newblock {Distributed Representations of Sentences and Documents}.
-	\newblock {\em ICML}, 32, 2014.
+	\section*{Supplementary Figures}
 
-	\bibitem{Khabsa2014}
-	Madian Khabsa and C~Lee Giles.
-	\newblock {The number of scholarly documents on the public web}.
-	\newblock {\em PLoS ONE}, 9(5), 2014.
+			\setcounter{figure}{0}
+	\renewcommand\thefigure{SI.\arabic{figure}}
 
-	\bibitem{Lee1999}
-	D~D Lee and H~S Seung.
-	\newblock {Learning the parts of objects by non-negative matrix factorization.}
-	\newblock {\em Nature}, 401(6755):788--791, 1999.
+	\begin{figure}
+		\begin{center}
+			\includegraphics[width=1\linewidth]{plots_pub/topic_oecd_entropy.pdf}
+			\caption{SI Disciplinary Entropy}
+			\label{dis-entropy}
+		\end{center}
+	\end{figure}
 
-	\bibitem{Pedregosa2011}
-	Fabian Pedregosa, Ga{\"{e}}l Varoquaux, Alexandre Gramfort, Vincent Michel,
-	Bertrand Thirion, Olivier Grisel, Mathieu Blondel, Peter Prettenhofer, Ron
-	Weiss, Vincent Dubourg, Jake Vanderplas, Alexandre Passos, David Cournapeau,
-	Matthieu Brucher, Mattheiu Perrot, and {\'{E}}douard Duchesnay.
-	\newblock {Scikit-learn: Machine Learning in Python Fabian}.
-	\newblock {\em Journal of Machine Learning Research}, 12:2825--2830, 2011.
+	\begin{figure}
+		\begin{center}
+			\includegraphics[width=1\linewidth]{plots_pub/single_doc_3_536594_1861.pdf}
+			\caption{SI Topic make up of a single document}
+			\label{doc-topic}
+		\end{center}
+	\end{figure}
 
-	\bibitem{Chaney2012}
-	Allison J~B Chaney and David~M. Blei.
-	\newblock {Visualizing Topic Models}.
-	\newblock {\em Icwsm}, pages 419--422, 2012.
+	\begin{figure}
+		\begin{center}
+			\includegraphics[width=1\linewidth]{plots_pub/ipcc_rep_wcs_simplified.pdf}
+			\caption{SI Representation by subfield}
+			\label{subfield}
+		\end{center}
+	\end{figure}
 
-	\bibitem{Hall2008}
-	David Hall, Daniel Jurafsky, and Christopher~D. Manning.
-	\newblock {Studying the history of ideas using topic models}.
-	\newblock {\em Proceedings of the Conference on Empirical Methods in Natural
-		Language Processing - EMNLP '08}, pages 363--371, 2008.
+	\begin{figure}
+		\begin{center}
+			\includegraphics[width=1\linewidth]{plots_pub/wgs_socsci.pdf}
+			\caption{SI Social science \& representation in topics across working groups}
+			\label{socsci-wgs}
+		\end{center}
+	\end{figure}
 
-	\bibitem{vandermaaten2008}
-	Laurens van~der Maaten and Geoffrey Hinton.
-	\newblock {Visualizing Data using t-SNE}.
-	\newblock {\em Journal of Machine Learning Research}, 9:2579--2605, 2008.
-
-	\bibitem{Meehl2007}
-	Gerald~A. Meehl, Curt Covey, Thomas Delworth, Mojib Latif, Bryant McAvaney,
-	John~F.B. Mitchell, Ronald~J. Stouffer, and Karl~E. Taylor.
-	\newblock {The WCRP CMIP3 multimodel dataset: A new era in climatic change
-		research}.
-	\newblock {\em Bulletin of the American Meteorological Society},
-	88(9):1383--1394, 2007.
-
-\end{thebibliography}
+	\begin{figure}
+		\begin{center}
+			\includegraphics[width=1\linewidth]{plots_pub/topic_rep_ks.pdf}
+			\caption{Topic representation over different values of K (number of topics). Topics in the upper or lower 6.66th percentile of either dimension are labelled}
+			\label{top-rep-ks}
+		\end{center}
+	\end{figure}
+	\bibliography{Mendeley}
 

### 2019-07-24 manuscript/coverletter.tex
repository tidied for paper submission

--- 2019-07-12 coverletter.tex
@@
 
-``Big literature'' - dealing with a vast and rapidly expanding body of publications - poses new, and largely neglected challenges for climate change assessments and how we understand them.
+``Big literature'' - the vast and rapidly expanding body of publications - poses new, and largely neglected challenges for climate change assessments and how we understand them.
 For example, we estimate a total of 350,000 new publications on climate change to emerge (only) in the Web of Science during the Sixth Assessment Cycle of the Intergovernmental Panel on Climate Change spanning from 2015 to 2022.
-Big data and machine learning methods need to be applied for keeping an overview of developments in the scientific landscape and to analyse how past IPCC assessments have engaged with the avaailable literature.
-So far, attempts \cite{Bjurström2011, Hulme2010, Victor2015, Corbera2016, Kowarsch2017} have often been based on qualitiative perceptions, or incomplete data with insufficient methodological sophistication.
+Big data and machine learning methods need to be applied to maintain an overview of developments in the scientific landscape and to analyse how past IPCC assessments have engaged with the available literature.
+So far, attempts \cite{Bjurström2011, Hulme2010, Victor2015, Kowarsch2017} have often been based on qualitative perceptions, or incomplete data with insufficient methodological sophistication.
 
@@
 First, our thematic map allows us to situate a complete set of IPCC citations into the context of the wider literature and analyse disciplinary representation adequately.
-We find that contrary to previous claims, the social sciences are over-represented in IPCC reports.Second, the use of machine learning methods in creating the map allows us to analyse the content of publications more or less represented in the IPCC.
+We find that contrary to previous claims, the social sciences are over-represented in IPCC reports.
+Second, the use of machine learning methods in creating the map allows us to analyse the content of publications more or less represented in the IPCC.
 We find that literature on technical solutions (such as negative emissions, buildings or cities) is growing fast and, even compared to other fast-growing literatures, has been under-represented in IPCC reports.

### 2019-07-24 manuscript/methods.tex
repository tidied for paper submission

--- 2019-07-12 methods.tex
@@
 			\begin{center}
-				\input{tables/ipcc_matching.tex}
+				\input{../tables/ipcc_matching.tex}
 				\caption{The proportion of citations in each report that could be matched with a document from the Web of Science}
@@
 
-	\section*{Supplementary Files}
+	\section*{Supplementary Figures}
 
-	\texttt{docs.csv} contains a list of the documents considered in this study, along with basic metadata and their position on the map
+			\setcounter{figure}{0}
+	\renewcommand\thefigure{SI.\arabic{figure}}
+
+	\begin{figure}
+		\begin{center}
+			\includegraphics[width=1\linewidth]{../plots_pub/topic_oecd_entropy.pdf}
+			\caption{SI Disciplinary Entropy}
+			\label{dis-entropy}
+		\end{center}
+	\end{figure}
+
+	\begin{figure}
+		\begin{center}
+			\includegraphics[width=1\linewidth]{../plots_pub/single_doc_3_536594_1861.pdf}
+			\caption{SI Topic make up of a single document}
+			\label{doc-topic}
+		\end{center}
+	\end{figure}
+
+	\begin{figure}
+		\begin{center}
+			\includegraphics[width=1\linewidth]{../plots_pub/ipcc_rep_wcs_simplified.pdf}
+			\caption{SI Representation by subfield}
+			\label{subfield}
+		\end{center}
+	\end{figure}
+
+	\begin{figure}
+		\begin{center}
+			\includegraphics[width=1\linewidth]{../plots_pub/wgs_socsci.pdf}
+			\caption{SI Social science \& representation in topics across working groups}
+			\label{socsci-wgs}
+		\end{center}
+	\end{figure}
+
+	\begin{figure}
+		\begin{center}
+			\includegraphics[width=1\linewidth]{../plots_pub/topic_rep_ks.pdf}
+			\caption{Topic representation over different values of K (number of topics). Topics in the upper or lower 6.66th percentile of either dimension are labelled}
+			\label{top-rep-ks}
+		\end{center}
+	\end{figure}
+
+	\section*{Data Availability}
+
+	Three datasets from this study are available at \url{https://doi.org/10.6084/m9.figshare.9009665}
+
+	\medskip\noindent
+	\texttt{docs.csv} contains a list of the documents considered in this study, along with basic metadata and their position on the map.
+For copyright reasons, the full metadata from Web of Science can not be published.
+To reproduce the analysis, it would be necessary to download the abstracts for the papers shown, either using the Web of Science IDs provided, or the query documented in \cite{Grieneisen2011}.
 
@@
 
-	\section*{Supplementary Figures}
+	\medskip\noindent
+	\texttt{topic\_comparison.xlsx} shows models with different numbers of topics. It was used to select the topic model used for analysis in this paper.
 
-			\setcounter{figure}{0}
-	\renewcommand\thefigure{SI.\arabic{figure}}
+	\section*{Code Availability}
 
-	\begin{figure}
-		\begin{center}
-			\includegraphics[width=1\linewidth]{plots_pub/topic_oecd_entropy.pdf}
-			\caption{SI Disciplinary Entropy}
-			\label{dis-entropy}
-		\end{center}
-	\end{figure}
+	The code used to produce this paper is available at https://github.com/mcallaghan/cc-topography
 
-	\begin{figure}
-		\begin{center}
-			\includegraphics[width=1\linewidth]{plots_pub/single_doc_3_536594_1861.pdf}
-			\caption{SI Topic make up of a single document}
-			\label{doc-topic}
-		\end{center}
-	\end{figure}
-
-	\begin{figure}
-		\begin{center}
-			\includegraphics[width=1\linewidth]{plots_pub/ipcc_rep_wcs_simplified.pdf}
-			\caption{SI Representation by subfield}
-			\label{subfield}
-		\end{center}
-	\end{figure}
-
-	\begin{figure}
-		\begin{center}
-			\includegraphics[width=1\linewidth]{plots_pub/wgs_socsci.pdf}
-			\caption{SI Social science \& representation in topics across working groups}
-			\label{socsci-wgs}
-		\end{center}
-	\end{figure}
-
-	\begin{figure}
-		\begin{center}
-			\includegraphics[width=1\linewidth]{plots_pub/topic_rep_ks.pdf}
-			\caption{Topic representation over different values of K (number of topics). Topics in the upper or lower 6.66th percentile of either dimension are labelled}
-			\label{top-rep-ks}
-		\end{center}
-	\end{figure}
 	\bibliography{Mendeley}
-
 	\bibliographystyle{unsrt}

### 2019-07-24 code/do_nmf.py

@@ -1,28 +1,0 @@
-import sys
-import django
-import os
-# import file for easy access to browser database
-sys.path.append('/home/galm/software/django/tmv/BasicBrowser/')
-os.environ.setdefault("DJANGO_SETTINGS_MODULE", "BasicBrowser.settings")
-django.setup()
-
-from tmv_app.models import *
-from scoping.models import *
-from tmv_app.tasks import *
-
-K = int(sys.argv[1])
-
-q = Query.objects.get(pk=2355)
-
-stat = RunStats(
-    query=q,
-    K=K,
-    min_freq=5,
-    method='NM',
-    citations=True,
-    max_iterations=500
-)
-
-stat.save()
-
-do_nmf(stat.pk)

### 2019-07-24 code/do_runs.sh

@@ -1,25 +1,0 @@
-
-features=(10000 50000 100000)
-ngrams=(1 2)
-
-#python3 /home/galm/software/django/tmv/BasicBrowser/manage.py nmf --alpha 0.1 365 100
-
-#python dynamic_nmf0.py 3769 80
-
-python dynamic_nmf0.py 6018 100
-
-#python dynamic_nmf0.py 3769 120
-
-#python3 /home/galm/software/django/tmv/BasicBrowser/manage.py nmf --alpha 0.05 365 120
-
-#python3 /home/galm/software/django/tmv/BasicBrowser/manage.py nmf --alpha 0.05 365 80
-
-  # for f in "${features[@]}"
-  # do
-  #   :
-  #   for n in "${ngrams[@]}"
-  #   do
-  #     :
-  #     python3 /home/galm/projects/cc-topography/code/nmf_multi.py 20 $n $f
-  #   done
-  # done

### 2019-07-24 code/dynamic_nmf.py

@@ -1,389 +1,0 @@
-import pickle, string, numpy, getopt, sys, random, time, re, pprint, gc, resource
-import pandas as pd
-import onlineldavb, scrapeWoS, gensim, nltk, subprocess, psycopg2
-from nltk.stem import SnowballStemmer
-from nltk import word_tokenize
-from multiprocess import Pool
-import django
-from functools import partial
-from sklearn.feature_extraction.text import TfidfVectorizer, CountVectorizer
-from sklearn.decomposition import NMF, LatentDirichletAllocation
-from time import time
-from django.utils import timezone
-from scipy.sparse import csr_matrix, find
-import numpy as np
-
-
-sys.stdout.flush()
-
-# import file for easy access to browser database
-sys.path.append('/home/galm/software/tmv/BasicBrowser/')
-
-# sys.path.append('/home/max/Desktop/django/BasicBrowser/')
-import db as db
-from tmv_app.models import *
-from scoping.models import Doc, Query
-from django.db import connection, transaction
-cursor = connection.cursor()
-
-def flatten(container):
-    for i in container:
-        if isinstance(i, (list,tuple)):
-            for j in flatten(i):
-                yield j
-        else:
-            yield i
-
-def f_gamma(docs,gamma,docsizes,docUTset,topic_ids):
-    dts = []
-    for d in docs:
-        if gamma[2][d] > 0.005:
-            dt = DocTopic(
-                doc_id = docUTset[gamma[0][d]],
-                topic_id = topic_ids[gamma[1][d]],
-                score = gamma[2][d],
-                scaled_score = gamma[2][d] / docsizes[gamma[0][d]],
-                run_id_id=run_id
-            )
-        dts.append(dt)
-    return dts
-
-def f_gamma2(docs,gamma,docsizes,docUTset,topic_ids):
-    vl = []
-    for d in docs:
-        if gamma[2][d] > 0.001:
-            dt = (
-                docUTset[gamma[0][d]],
-                topic_ids[gamma[1][d]],
-                gamma[2][d],
-                gamma[2][d] / docsizes[gamma[0][d]],
-                run_id
-            )
-            vl.append(dt)
-    return vl
-
-def f_lambda(t,m,v_ids,t_ids):
-    tt = TopicTerm(
-        term_id = v_ids[m[1][t]],
-        topic_id = t_ids[m[0][t]],
-        score = m[2][t],
-        run_id = run_id
-    )
-    return tt
-
[…]

### 2019-07-24 code/dynamic_nmf0.py

@@ -1,514 +1,0 @@
-import pickle, string, numpy, getopt, sys, random, time, re, pprint, gc, resource
-import pandas as pd
-import nltk, subprocess, psycopg2, math
-from nltk.stem import SnowballStemmer
-from nltk import word_tokenize
-from multiprocess import Pool
-import django
-from functools import partial
-from sklearn.feature_extraction.text import TfidfVectorizer, CountVectorizer
-from sklearn.decomposition import NMF, LatentDirichletAllocation
-from time import time
-from django.utils import timezone
-from scipy.sparse import csr_matrix, find
-import numpy as np
-from django.core import management
-import os
-
-
-
-sys.stdout.flush()
-
-# import file for easy access to browser database
-sys.path.append('/home/galm/software/django/tmv/BasicBrowser')
-os.environ.setdefault("DJANGO_SETTINGS_MODULE", "BasicBrowser.settings")
-django.setup()
-
-# sys.path.append('/home/max/Desktop/django/BasicBrowser/')
-import utils.db as db
-from tmv_app.models import *
-from scoping.models import *
-from django.db import connection, transaction
-from django.db.models import Count, Sum
-from utils.text import *
-cursor = connection.cursor()
-
-def flatten(container):
-    for i in container:
-        if isinstance(i, (list,tuple)):
-            for j in flatten(i):
-                yield j
-        else:
-            yield i
-
-def f_gamma(docs,gamma,docsizes,docUTset,topic_ids):
-    dts = []
-    for d in docs:
-        if gamma[2][d] > 0:
-            dt = DocTopic(
-                doc_id = docUTset[gamma[0][d]],
-                topic_id = topic_ids[gamma[1][d]],
-                score = gamma[2][d],
-                scaled_score = gamma[2][d] / docsizes[gamma[0][d]],
-                run_id_id=run_id
-            )
-        dts.append(dt)
-    return dts
-
-def f_gamma2(docs,gamma,docsizes,docUTset,topic_ids):
-    vl = []
-    for d in docs:
-        if gamma[2][d] > 0.001:
-            dt = (
-                docUTset[gamma[0][d]],
-                topic_ids[gamma[1][d]],
-                gamma[2][d],
-                gamma[2][d] / docsizes[gamma[0][d]],
-                run_id
-            )
-            vl.append(dt)
-    return vl
-
-def f_lambda(t,m,v_ids,t_ids):
-    tt = TopicTerm(
[…]

### 2019-07-24 code/merge_scopus.py

@@ -1,151 +1,0 @@
-import os, sys, time, resource, re, gc, shutil
-from multiprocess import Pool
-from functools import partial
-from mongoengine import *
-from urllib.parse import urlparse, parse_qsl
-connect('mongoengine_documents')
-import matplotlib.pyplot as plt
-import numpy as np
-import pandas as pd
-from mongoengine.queryset.visitor import Q
-import django
-sys.path.append('/home/galm/software/tmv/BasicBrowser/')
-os.environ.setdefault("DJANGO_SETTINGS_MODULE", "BasicBrowser.settings")
-django.setup()
-from monary import Monary
-mon = Monary()
-
-from scoping.models import *
-
-class scopus_doc(DynamicDocument):
-    scopus_id = StringField(required=True, max_length=50, unique=True)
-    PY = IntField(required=True)
-
-class scopus_ref(Document):
-    text = StringField(required=True, unique=True)
-    ti = StringField()
-    PY = IntField()
-    extra = StringField()
-    doi = StringField()
-    url = URLField()
-
-class similarity(Document):
-    wos_ut = StringField(required=True, max_length=50)
-    scopus_id = StringField(required=True, max_length=50,unique_with='wos_ut')
-    scopus_do = BooleanField(required=True, max_length=50)
-    wos_do = BooleanField(required=True, max_length=50)
-    do_match = BooleanField()
-    t_match = BooleanField()
-    jaccard = FloatField()
-    py_diff = IntField()
-    wc_diff = IntField()
-    wc = IntField()
-
-class match(Document):
-    scopus_id = StringField(required=True, max_length=50,unique_with='wos_ut')
-    wos_ut = StringField(required=True, max_length=50)
-    py_diff = IntField()
-    jaccard = FloatField()
-    wc_diff = IntField()
-
-def get(r, k):
-    try:
-        x = r[k]
-    except:
-        x = ""
-    return(x)
-
-def add_doc(r):
-    scopus2WoSFields = {
-        'TY': 'dt',
-        'TI': 'ti',
-        'T2': '',
-        'C3': '',
-        'J2': 'so',
-        'VL': 'vl',
-        'IS': '',
-        'SP': 'bp',
-        'EP': 'ep',
-        'PY': 'py',
-        'DO': 'di',
-        'SN': 'sn',
-        'AU': 'au',
-        'AD': 'ad',
-        'AB': 'ab',
-        'KW': 'kwp',
-        'Y2': '',
-        'CY': '',
[…]

### 2019-07-24 code/nmf.py

@@ -1,336 +1,0 @@
-import pickle, string, numpy, getopt, sys, random, time, re, pprint, gc, resource
-import pandas as pd
-import scrapeWoS
-import gensim
-import nltk
-from nltk.stem import SnowballStemmer
-from nltk import word_tokenize
-import sys
-import time
-from multiprocess import Pool
-import django
-from functools import partial
-from sklearn.feature_extraction.text import TfidfVectorizer, CountVectorizer
-from sklearn.decomposition import NMF, LatentDirichletAllocation
-from time import time
-from django.utils import timezone
-from scipy.sparse import csr_matrix, find
-import numpy as np
-import psycopg2
-
-#conn = psycopg2.connect("dbname=tmv_app user=tmv password=topicmodels")
-
-sys.stdout.flush()
-
-# import file for easy access to browser database
-sys.path.append('/home/galm/software/django/tmv/BasicBrowser/')
-
-# sys.path.append('/home/max/Desktop/django/BasicBrowser/')
-import db as db
-from tmv_app.models import *
-from scoping.models import Doc
-from django.db import connection, transaction
-cursor = connection.cursor()
-
-def flatten(container):
-    for i in container:
-        if isinstance(i, (list,tuple)):
-            for j in flatten(i):
-                yield j
-        else:
-            yield i
-
-def f_gamma(docs,gamma,docsizes,docUTset,topic_ids):
-    dts = []
-    for d in docs:
-        dt = DocTopic(
-            doc_id = docUTset[gamma[0][d]],
-            topic_id = topic_ids[gamma[1][d]],
-            score = gamma[2][d],
-            scaled_score = gamma[2][d] / docsizes[gamma[0][d]],
-            run_id=run_id
-        )
-        dts.append(dt)
-    return dts
-
-def f_gamma2(docs,gamma,docsizes,docUTset,topic_ids):
-    vl = []
-    for d in docs:
-        dt = (
-            docUTset[gamma[0][d]],
-            topic_ids[gamma[1][d]],
-            gamma[2][d],
-            gamma[2][d] / docsizes[gamma[0][d]],
-            run_id
-        )
-        vl.append(dt)
-    return vl
-
-def f_lambda(t,m,v_ids,t_ids):
-    tt = TopicTerm(
-        term_id = v_ids[m[1][t]],
-        topic_id = t_ids[m[0][t]],
-        score = m[2][t],
-        run_id = run_id
-    )
-    return tt
-
[…]

### 2019-07-24 code/nmf_copy.py

@@ -1,380 +1,0 @@
-#!/usr/bin/env python3
-
-# onlinewikipedia.py: Demonstrates the use of online VB for LDA to
-# analyze a bunch of random Wikipedia articles.
-#
-# Copyright (C) 2010  Matthew D. Hoffman
-#
-# This program is free software: you can redistribute it and/or modify
-# it under the terms of the GNU General Public License as published by
-# the Free Software Foundation, either version 3 of the License, or
-# (at your option) any later version.
-#
-# This program is distributed in the hope that it will be useful,
-# but WITHOUT ANY WARRANTY; without even the implied warranty of
-# MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-# GNU General Public License for more details.
-#
-# You should have received a copy of the GNU General Public License
-# along with this program.  If not, see <http://www.gnu.org/licenses/>.
-
-import pickle, string, numpy, getopt, sys, random, time, re, pprint, gc, resource
-import pandas as pd
-import onlineldavb
-import scrapeWoS
-import gensim
-import nltk
-from nltk.stem import SnowballStemmer
-from nltk import word_tokenize
-import sys
-import time
-from multiprocess import Pool
-import django
-from functools import partial
-from sklearn.feature_extraction.text import TfidfVectorizer, CountVectorizer
-from sklearn.decomposition import NMF, LatentDirichletAllocation
-from time import time
-from django.utils import timezone
-from scipy.sparse import csr_matrix, find
-import numpy as np
-import psycopg2
-
-#conn = psycopg2.connect("dbname=tmv_app user=tmv password=topicmodels")
-
-sys.stdout.flush()
-
-# import file for easy access to browser database
-sys.path.append('/home/galm/software/tmv/BasicBrowser/')
-
-# sys.path.append('/home/max/Desktop/django/BasicBrowser/')
-import db as db
-from tmv_app.models import *
-from scoping.models import Doc
-from django.db import connection, transaction
-cursor = connection.cursor()
-
-def flatten(container):
-    for i in container:
-        if isinstance(i, (list,tuple)):
-            for j in flatten(i):
-                yield j
-        else:
-            yield i
-
-# def f_gamma(d,gamma,docsizes,docUTset,topic_ids):
-#     dts = []
[…]

### 2019-08-21 manuscript/abstract.tex

\documentclass{article}

\begin{document}
   The massive expansion of scientific literature on climate change poses challenges for global environmental assessments and how we
understand them. 
Big data and machine learning can help us deal 
with the large collections of text represented by scientific fields.
Such methods help make the production of assessments
more tractable, and give us better insights about how past assessments  have engaged with the literature as it has evolved.
We use topic modelling to identify the thematic structure and draw a comprehensive topic map, or topography, of over 400,000 scientific publications from the Web of Science on climate change. 
We update current knowledge on the IPCC, showing that the social sciences are in fact over-represented in recent assessment reports, and that
technical, solutions-relevant knowledge - especially in the agricultural and engineering sciences - are under-represented.
We point to a variety of other applications of such maps, and our findings have direct implications for addressing growing demands for more solution-oriented climate change assessments that are also more firmly rooted in the social sciences.
\end{document}

### 2019-08-21 manuscript/main.tex

--- 2019-07-12 main.tex
@@
 			\begin{center}
-				\includegraphics[width=180mm]{plots_pub/pubs_time_wgb.pdf}
+				\includegraphics[width=180mm]{../plots_pub/pubs_time_wgb.pdf}
 				\caption{ The number of climate change documents in the Web of Science in each year.
@@
 				{\scriptsize
-					\input{tables/growth_table.tex}}
+					\input{../tables/growth_table.tex}}
 				\caption{Growth of Literature on Climate Change. A glossary of acronyms is provided in SI}
@@
 			\begin{center}
-				\includegraphics[width=180mm]{plots_pub/all_topic_words_oecds.png}
+				\includegraphics[width=180mm]{../plots_pub/all_topic_words_oecds.png}
 				\caption{A map of the literature on climate change.
@@
 			\begin{center}
-				\includegraphics[width=180mm]{plots_pub/topic_evolution_4.png}
+				\includegraphics[width=180mm]{../plots_pub/topic_evolution_4.png}
 				\caption{Evolution of the landscape of climate change literature.
@@
 			\begin{center}
-				\includegraphics[width=180mm]{plots_pub/big_panel_representation.pdf}
+				\includegraphics[width=180mm]{../plots_pub/big_panel_representation.pdf}
 				\caption{Representation in IPCC reports: \textbf{a)} by discipline, \textbf{b)} by social science proportion of WG 3 topics, \textbf{c)} and novelty of all topics, where topics in the highest and lowest 10\% of either axis are labelled.

### 2019-08-21 tables/growth_table.tex
lp

@@
 \hline 
-&\textbf{AR1} & \textbf{AR2} & \textbf{AR3} & \textbf{AR4} & \textbf{AR5} & \textbf{AR6}\\ \hline\textbf{Years} &1986-1989 & 1990-1994 & 1995-2000 & 2001-2006 & 2007-2013 & 2014-\\ 
-\textbf{Documents} &1,167 & 8,539 & 21,716 & 38,750 & 134,413 & 201,606\\ 
-\textbf{Unique words} &2,000 & 12,480 & 23,346 & 34,637 & 71,867 & 94,746\\ 
-\textbf{New words} & change (560) & oil (287) & downscaling (217) & sres (234) & biochar (1,791) & mmms (313)\\ & climate (428) & deltac (283) & degreesc (187) & petm (95) & redd (1,113) & cop21 (234)\\ & co2 (318) & whole (256) & ncep (130) & amf (88) & cmip5 (679) & c3n4 (214)\\ & climatic (289) & tax (254) & fco (107) & sf5cf3 (86) & cmip3 (587) & sdg (187)\\ & model (288) & landscape (249) & pfc (98) & clc (81) & mofs (299) & zika (182)\\ & atmospheric (281) & alternative (243) & otcs (98) & embankment (81) & sdm (297) & ndcs (168)\\ & effect (280) & availability (242) & dtr (95) & cwd (79) & mof (275) & indc (164)\\ & global (224) & life (239) & nee (89) & etm (75) & biochars (252) & indcs (134) \\ \hline
-\end{tabular}
+&\textbf{AR1} & \textbf{AR2} & \textbf{AR3} & \textbf{AR4} & \textbf{AR5} & \textbf{AR6}\\ \hline

### 2019-10-01 tables/ipcc_matching_sample.tex
new plots after revisions

@@
 \midrule
- 2 &  2 &  Landfill gas: working with Gaia. Biodeterioration Extracts no. 4, Energy Technology Support Unit, Harwell Laboratory, Oxfordshire, UK.  &  Richards, K.M. &  1989 \\
- 1 &  1 &  Longwave cloud radiative forcing as determined from Nimbus-7 observations J Cltm , 2, 766 799  &  Ardanuy, P E , L L Stowe, A Gruber, M Weiss and C S Long &  1989 \\
- 3 &  2 &  Climate change: overview and implications   for wildlife.
-In: Wildlife Responses to Climate Change: North American Case   Studies [Schneider, S.H.
-and T.L.
-Root (eds.)].
-Island Press, Washington, DC,   USA, (in press).
-&  Root, T.L.
-and S.H.
-Schneider &  2001 \\
- 2 &  3 &  The impact ol' global wanning on the United States: A survey of recent literature, mimco. Institute lor Interna-tional Economics, Washington, DC (April).  &  Cline, W.R. &  1993 \\
- 3 &  2 &  Population-environment   relations at the forested frontier of Nepal. Applied Geography, 20, 221-242. &  Conway, D., K. Bhattarai, and N.R. Shrestha &  2000 \\
- 3 &  2 &  The Cities Project. Australian Geological Survey Organisation,   Australia. Available online at http://www.agso.gov.au/geohazards/grm/cities2.html. &  AGSO &  1999 \\
- 4 &  1 &  CLIMBER-2: A climate system model of intermediate complexity. Part I: Model description and performance for present climate.  &  Petoukhov, V., et al. &  2000 \\
- 5 &  1 &  A skill-score based evaluation of simulated Australian climate. Australian Meteorol. Oceanogr &  Watterson, I., A. C. Hirst, and L. D. Rotstayn &  2013 \\
- 5 &  1 &  Enhanced aerosol backscatter adjacent to tropical trade wind clouds revealed by satellite-based lidar. Geophys. Res &  Tackett, J. L., and L. Di Girolamo &  2009 \\
- 5 &  3 &  Promoting long-term invest-ments by institutional investors. OECD Journal: Financial Market Trends 1, 145 – 164 &  Della Croce R, F Stewart, and J Yermo &  2011 \\
+ 3 &  1 &  The IIASA Database for Mean Monthly   Values of Temperature, Precipitation and Cloudiness on a Global Terrestrial   Grid.
+IIASA Report RR-91-18, Laxenburg, 63 pp.
+&  Leemans, R.
+and W.
+Cramer &  1991 \\
+ 2 &  2 &  Rischi connessi con la dinámica glaciale nelle Alpi ItaUane. Geografía Física e Dinámica Quatemaría, 15, 85-99.  &  Dutto, F. and G. Mortara &  1992 \\
+ 3 &  1 &  Specification   of eddy transfer coefficients in coarse-resolution ocean circulation models.   J. Phys. Oceanogr., 27, 381-402. &  Visbeck, M., J. Marshall, T. Haine and M. Spall &  1997 \\
+ 3 &  2 &  A koala (Phascolartos   cinereus Goldfuss) population crash during drought and heatwave conditions in   south-western Queensland.
+Australian Journal of Ecology, 13, 451-461.
+&  Gordon, G., A.S.
+Brown, and T.
+Pulsford &  1988 \\
+ 4 &  2 &  Climate change and land resources of Russia. &  Isaev, A., V. Stolbovoi, V. Kotlyakov, S. Nilsson and I. McCallum &  2004 \\
+ 4 &  3 &  Generation technology choices: near and long term. US DOE/EPRI Annual Energy Outlook Conference, Washington D.C., www.eia.doe.gov/oiaf/archive/aeo04/conf/pdf/gehl.pdf  &  Gehl, S &  2004 \\
+ 4 &  3 &  Climate Change and the European Countryside: Impacts on Land Management and Response Strategies &  Viner, D., M. Sayer, M. Uyarra, and N. Hodgson &  2006 \\
+ 5 &  2 &  Adaptation to climate change in the context ofsustainable development and equity &  Smit, B. and O. Pilifosova &  2001 \\
+ 5 &  3 &  Copenhagen City of Cyclists: Bicycle Account 2010. City of Copenha-gen, The Technical and Environmental Administration. Available at: http: / / www. cycling-embassy &  COP &  2010 \\
+ 5 &  3 &  Uncertainty analysis of the IEA / ORAU CO2 emissions model. The Energy Journal 8, 1 – 29 &  Reilly J M, J A Edmonds, R H Gardner, and A L Brenkert &  1987 \\
 \bottomrule

### 2019-10-01 code/check_ipccmatches.py

@@ -1,0 +1,75 @@
+
+import os, sys, time, resource, re, gc, shutil
+import argparse
+import pandas as pd
+
+import django
+
+sys.path.append('/home/galm/software/django/tmv/BasicBrowser/')
+os.environ.setdefault("DJANGO_SETTINGS_MODULE", "BasicBrowser.settings")
+django.setup()
+
+from scoping.models import *
+
+parser = argparse.ArgumentParser(description='Check unmatched IPCC References')
+parser.add_argument('sample_size', type=int)
+
+args = parser.parse_args()
+
+already_rated = IPCCRef.objects.filter(match_status__gt=0)
+
+if already_rated.count() < args.sample_size:
+
+    qdocs = set(IPCCRef.objects.filter(doc__query=6187).values_list('pk',flat=True))
+
+    unmatched = list(IPCCRef.objects.exclude(id__in=qdocs).values_list('pk',flat=True))
+
+    def random_list(l,n):
+        return [ l[i] for i in sorted(random.sample(range(len(l)), n)) ]
+
+    already_rated = IPCCRef.objects.filter(pk__in=unmatched, match_status__gt=0)
+
+    docs_left = args.sample_size-already_rated.count()
+
+    print(docs_left)
+
+    if docs_left > 0:
+
+        ir_sample = IPCCRef.objects.filter(id__in=random_list(unmatched, docs_left))
+
+        for i,ir in enumerate(ir_sample):
+            if ir.doc:
+                ir.match_status=2
+                ir.save()
+            else:
+                print(f"\n{docs_left-i} docs left!")
+                print(f"\n{ir.text} - {ir.year} - {ir.authors}")
+                ms = input("\nis this 1 - in the query; 2 - in the WoS; 3 - not in WoS: \n")
+                ir.match_status=ms
+                ir.save()
+
+        already_rated = IPCCRef.objects.filter(pk__in=unmatched, match_status__gt=0)
+
+results = []
+for r in already_rated:
+    results.append({
+        "wgs": "; ".join([wg.__str__() for wg in r.wg.all()]),
+        "text":  f"{r.text} - {r.year} - {r.authors}",
+        "match_status": r.get_match_status_display()
+    })
+
+df = pd.DataFrame.from_dict(
+    results
+)
+
+df.to_csv("../tables/ipcc_ref_matching.csv", index=False)
+
+for s in IPCCRef.MATCH_STATUS:
[…]

### 2019-10-02 manuscript/abstract.tex
revisions, too many words

@@
 \begin{document}
-   The massive expansion of scientific literature on climate change poses challenges for global environmental assessments and how we
-understand them. 
+	The massive expansion of scientific literature on climate change poses challenges for global environmental assessments and our understanding of how these assessments work. 
 	Big data and machine learning can help us deal 
@@
 	more tractable, and give us better insights about how past assessments  have engaged with the literature as it has evolved.
-We use topic modelling to identify the thematic structure and draw a comprehensive topic map, or topography, of over 400,000 scientific publications from the Web of Science on climate change. 
-We update current knowledge on the IPCC, showing that the social sciences are in fact over-represented in recent assessment reports, and that
+	We use topic modelling to identify the thematic structure and draw a comprehensive topic map, or topography, of over 400,000 scientific publications from the Web of Science (WoS) on climate change. 
+	We update current knowledge on the Intergovernmental Panel on Climate Change (IPCC), showing that, at least when compared to the baseline of the literature identified in the WoS,  the social sciences are in fact over-represented in recent assessment reports, and that
 	technical, solutions-relevant knowledge - especially in the agricultural and engineering sciences - are under-represented.
 	We point to a variety of other applications of such maps, and our findings have direct implications for addressing growing demands for more solution-oriented climate change assessments that are also more firmly rooted in the social sciences.
+	We highlight fast-growing topics on solutions that could be better integrated into future IPCC reports. 
+	The perceived lack of social science knowledge in solutions-relevant IPCC reports does not necessarily imply a bias towards the natural sciences. 
+	It rather suggests a need for more social science research with a focus on ``technical'' topics related to climate solutions. 
 \end{document}

### 2019-10-02 manuscript/coverletter.tex
revisions, too many words

@@
 
-   \opening{\today \\ \\ Dear Bronwyn Wake,}
+   \opening{\today \\ \\ Dear Adam Yeeles,}
 
-   I herewith submit on behalf of my co-authors the manuscript ``A Topography of Climate Change Litereature'' for consideration as a letter in Nature Climate Change.
+   I herewith resubmit on behalf of my co-authors the manuscript ``A Topography of Climate Change Literature'' for consideration as a letter in Nature Climate Change.
+
+   The letter makes use of topic modelling in order to reassess claims made in the literature about how the IPCC has represented scientific knowledge about climate change.
+We do this in the context of Big Literature - the hundreds of thousands of papers published on climate change which it is the IPCC's job to assess.
+Big Literature poses a challenge to the provision of comprehensive assessments, but has also challenged scholars who have attempted
 

### 2019-10-02 manuscript/main.tex
revisions, too many words

@@
 
-\newcommand{\multicollinenumbers}{
-	\linenumbers
-	\def\makeLineNumber{\docolaction
-		{\makeLineNumberLeft}
-		{}
-		{\makeLineNumberRight}
-	}
-}
-
-\newenvironment{figurehere}
-{\def\@captype{figure}}
-{}
-
 % Title
@@
 		\cite{Nunez-Mir2016, Minx2017l}, where the science of climate change is expanding exponentially \cite{Grieneisen2011, Haunschild2016}.
-In the five years since the publication of the last IPCC assessment report \cite{IPCC2014c}, 202,000 papers were published in the Web of Science (WoS) (see Table \ref{tab}).
-This is almost as much as the 205,000 papers published during the first five assessment periods; a period of nearly 30 years.
-A total of around 350,000 new publications can be expected for the current sixth assessment cycle of the IPCC, based on current growth patterns (Figure \ref{pub-growth}).
+In the five years since the publication of the last IPCC assessment report \cite{IPCC2014c}, 202,000 papers on climate change were published in the Web of Science (WoS) (see Table \ref{tab}).
+This is almost as much as the 205,000 papers identified in the same query \cite{Grieneisen2011} during the first five assessment periods; a period of nearly 30 years.
+A total of around 350,000 new publications can be expected for before the sixth assessment report (AR6) of the Intergovernmental Panel on Climate Change (IPCC), based on current growth patterns (Figure \ref{pub-growth}).
 Moreover, the literature has also become more diverse.
-This is reflected in the expansion of the literature's vocabulary - from 2,000 unique words in the first assessment period to 95,000 words so far in the sixth - indicating that the field has incorporated new content.
+This is reflected in the expansion of the literature's vocabulary (see methods) - from 2,000 unique words in the first assessment period to 95,000 words so far in the sixth - indicating that the field has incorporated new content.
 For example, the zika virus, which was mentioned in 182 articles from 2014-2018, had never before been discussed in the titles or abstracts of articles relating to climate change.
-Yet it has emerged as a topic of high relevance: the incidence of the virus, the outbreak of which in Brazil in 2016 was declared a public health emergency by the WHO, is set to increase under rising global temperatures \cite{Rao2019}.
-Similar rapid emergence patterns can be seen for INDCs and SDGs in AR6, and Biochar and REDD in AR5, among others\footnote{The glossary in SI contains a complete list of the acronyms shown in the table}.
+Yet it has emerged as a topic of high relevance: the incidence of the virus, the outbreak of which in Brazil in 2016 was declared a public health emergency by the World Health Organization, is set to increase under rising global temperatures \cite{Rao2019}.
+Similar rapid emergence patterns can be seen for Intended Nationally Determined Contributions (INDCs) and Sustainable Development Goals (SDGs) in AR6, and Biochar and the UN forest protection programme REDD in AR5, among others\footnote{The glossary in SI contains a complete list of the acronyms shown in the table}.
 
@@
 				\caption{ The number of climate change documents in the Web of Science in each year.
+A total of 406,191 documents were published until the end of 2018.
+The number of publications in each assessment period is shown in square brackets.
 For 2019-21 we project the number of papers assuming there is no more growth, and assuming that growth continues at the same rate as over the past five years}
@@
 
-		Big literature poses at least three challenges for scientific policy advice and science itself: \emph{First}, established procedures in scientific assessments like those conducted by the IPCC fail to address the exploding literature base.
-For example, the ratio of studies cited in IPCC reports to the number or relevant studies has declined from 60\% to 20\%  \cite{Minx2017l}, posing a rapidly growing risk of selection bias.
-More generally, the provision of comprehensive, objective, open and transparent assessments of the available scientific literature, as defined in the principles governing IPCC work \cite{IPCC2013}, is no longer possible for authors or author teams by traditional means.
+		Big literature poses at least three challenges for scientific policy advice and science itself: \emph{First}, established procedures in scientific assessments like those conducted by the IPCC struggle to address the exploding literature base.
+For example, the ratio of studies cited in IPCC reports to the number of studies on climate change in the WoS has declined from 60\% to 20\%  \cite{Minx2017l}, posing a rapidly growing risk of selection bias.
+More generally, the exponential increase in the volume of literature means that the provision of comprehensive, objective, open and transparent assessments of the available scientific literature, as defined in the principles governing IPCC work \cite{IPCC2013}, is no longer possible for authors or author teams by traditional means.
 		Machine reading and learning methods as well as other data science applications are required to enable an understanding of the field of climate change research at scale. 
@@
 The field of evidence synthesis technology, which tries to streamline human tasks through machine learning at the different stages of the review process, is still in its infancy \cite{Beller2018}.
-\emph{Finally}, overwhelming amounts of literature may be a major reason why studies of scientific assessments \cite{Bjurström2011, Hulme2010, Victor2015} do not offer robust quantifications, for claims about the relationship between report citations and the underlying literature.
+\emph{Finally}, overwhelming amounts of literature may be a major reason why studies of scientific assessments \cite{Bjurström2011, Hulme2010, Victor2015} do not offer robust quantification for their claims about the relationship between report citations and the underlying literature.
 
@@
 		We apply this map in a second step to understand how the IPCC reports have represented the available climate change literature and re-evaluate claims of bias based on a more comprehensive understanding of the available climate science.
-We enrich the discussion of representation in the literature by discussing topics as well as disciplines.
+We enrich the discussion on representation in the literature by discussing topics as well as disciplines.
 
@@
 
-		Figure \ref{oecd_topic_map} shows a \emph{thematic} or \emph{topopographic map} of the 400,000 publications on climate change in our dataset with a total number of 140 topics.
+		Figure \ref{oecd_topic_map} shows a \emph{thematic} or \emph{topographic map} of the 378,000 publications on climate change in our dataset that had abstracts with a total number of 140 topics.
 The number of topics must be defined exogenously, but the results are robust to different specifications.
-Using non-negative matrix factoriziation \cite{Lee1999}, the topics are machine-learned from the papers' abstracts (see methods for details, examples of different model specifications, and a thorough explanation of model selection), and the topic scores of each document are reduced to the two dimensions shown through t-distributed stochastic neighbour embedding \cite{vandermaaten2008} \footnote{A full list of topics and related words, and a list of documents, their positions on the map, and their related topics are given in the SI}.
+Using non-negative matrix factorization \cite{Lee1999}, the topics, which are groups of words that describe groups of documents, are machine-learned from the papers' abstracts (see methods for details, examples of different model specifications, and a thorough explanation of model selection).
+The topic scores of each document are reduced to the two dimensions shown through t-distributed stochastic neighbour embedding (t-SNE) \cite{vandermaaten2008}.
+\footnote{A full list of topics and related words, and a list of documents, their positions on the map, and their related topics are given in the SI}.
+The two dimensions represent a projection of the 140-dimensional topic scores of each document that seeks to preserve small distances between similar documents.
 
@@
 				\caption{A map of the literature on climate change.
-Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by web of science discipline category.
+Document positions are obtained by reducing the topic scores to two dimensions via t-SNE (see methods for further details).
+The two axes therefore have no direct interpretation, but represent a reduced version of similarities between documents across 140 topics.
+Documents are coloured by web of science discipline category.
 Topic labels are placed in the center of each of the large clusters of documents associated with each topic.
@@
 		The map shown covers a broad range of topics, with related topics shown in clusters.
-In general, topics related to climate science and impacts are in the West, while solution-oriented topics are in the East.
+In general, topics related to climate science and impacts are on the left, while solution-oriented topics are on the right.
 More fine-grained research areas can also be distinguished.
-For example, publications related to urban infrastructure (\textbf{buildings}, \textbf{energy}, \textbf{cement}, \textbf{waste}) are located in the East, physical climate impacts such as \textbf{sea-level}, \textbf{droughts}  or [crop] \textbf{yield} are in the South-West and energy systems are in North-East.
+For example, publications related to urban infrastructure (\textbf{buildings}, \textbf{energy}, \textbf{cement}, \textbf{waste}) are located on the right, physical climate impacts such as \textbf{sea-level}, \textbf{droughts}  or [crop] \textbf{yield} are in the lower left and energy systems are in upper right.
 There are larger groups of documents at the fringes of the map that relate mainly to one or two specific topics such as \textbf{biochar}, \textbf{coral}, or \textbf{CO2 storage}.
@@
 This corresponds to their integrative nature in IPCC reports \cite{Moss2010}.
-This map of the thematic structure of the literature could be useful for individual communities or for climate change assessments.
+This map of the thematic structure of the literature could be useful for individual scientific communities or for climate change assessments.
 
@@
 		\subsection*{Research representation in IPCC reports}
-		We apply our topic map to understand the representation of science in IPCC assesssments and how it manages to respond to demands for more solution-oriented knowledge \cite{Kowarsch2017}.
+		We apply our topic map to understand the representation of science in IPCC assesssments and how they manage to respond to demands for more solution-oriented knowledge \cite{Kowarsch2017}.
 Several studies have identified, made, or repeated claims of a disciplinary bias of IPCC assessments towards the natural sciences, and within the social sciences towards economics \cite{Bjurström2011, Victor2015, Hulme2010, Corbera2016}.
-Where these claims were based on an analysis of IPCC citations \cite{Bjurström2011}, they fail to assess this claim against a measurable benchmark.
-We argue here that the composition of the climate change literature as a whole provides such a benchmark, in view of the organisation's mandate to provide ``comprehensive, objective, open and transparent'' assessment of the available science \cite{IPCC2013}.
-Our database of publications allows us to study representation with such a benchmark, and over time rather than for single assessment cycles.
+Where these claims were based on an analysis of IPCC citations \cite{Bjurström2011}, they fail to assess this claim against a measurable baseline.
+We argue here that this can be provided by the composition of the climate change literature as a whole.
+Although, as we discuss in the concluding section, it is in many ways imperfect, in view of the organisation's mandate to provide ``comprehensive, objective, open and transparent'' assessment of the available science \cite{IPCC2013}, our dataset of publications allows us to study representation with a meaningful baseline, and over time rather than for single assessment cycles.
+As such it forms a starting point for informed discussion about how to represent the literature according to the IPCC's priorities.
+By matching the documents in our dataset to a set of references scraped from all published IPCC reports \cite{Minx2017l}, we can assess the representation of a group of studies by comparing the group's share in the subset of studies cited by the IPCC with it's share in the dataset of WoS studies on climate change (see methods for further details).
 
 		Figure \ref{oecd_rep}.a shows that the social sciences were indeed under-represented in the third assessment report, but by the fifth assessment report were over-represented.
-Likewise, other social sciences than economics have become better represented since AR3  (see figure \ref{subfield}f) with social \& economic geography (4.3\% of the literature), political science (1.0\%), and sociology (0.8\%) showing improved representation in AR5 compared to AR3, and social and economic geography, political science, and other social sciences better represented than economics.
+Likewise, social sciences other than economics have become better represented since AR3  (see figure \ref{subfield}f) with social \& economic geography (4.3\% of the literature), political science (1.0\%), and sociology (0.8\%) showing improved representation in AR5 compared to AR3, and social and economic geography, political science, and other social sciences better represented than economics.
 
 		This challenges what we think we know about the IPCC.
-The social sciences, by now, are actually the best represented field, with a share in the literature cited by IPCC reports 1.32 times as high as in the literature at large.
+The social sciences, by now, are actually the best represented field, with a share in the literature cited by IPCC reports 1.32 times higher than in the literature at large.
 On the other hand the Agricultural Sciences and Engineering \& Technology have been consistently under-represented, with 2.27 and 3.49 times the share of studies in the wider literature than in the literature cited by the IPCC in AR5 respectively.
@@
 Figures \ref{oecd_rep}b and \ref{oecd_rep}c plot the representation of the topics shown in the map.
-Figure \ref{oecd_rep}c shows that topics more commonly cited by IPCC working group I are older and largely better represented in IPCC reports.
+Figure \ref{oecd_rep}c shows that topics more commonly cited by IPCC working group I (WGI - the physical science basis) are older and largely better represented in IPCC reports.
 These topics, for example \textbf{ozone}, \textbf{oceans}, \textbf{clouds}, \textbf{aerosols} and \textbf{sea levels} make up some of the core topics of the physical science of climate change.
@@
 Because they are new areas of knowledge, they may be highly salient in a periodic assessment process.
-These topics are primarily in working group III, on mitigation \footnote{see methods for a discussion of the categorisation of topics, including CLC, adsorption and hydrogen, which may more properly be described as relevant to WGIII}.
+These topics are primarily in working group III, on mitigation \footnote{see methods for a discussion of the categorisation of topics, including adsorption, and membranes, which may more properly be described as relevant to WGIII}.
 
@@
 				\includegraphics[width=180mm]{../plots_pub/big_panel_representation.pdf}
-				\caption{Representation in IPCC reports: \textbf{a)} by discipline, \textbf{b)} by social science proportion of WG 3 topics, \textbf{c)} and novelty of all topics, where topics in the highest and lowest 10\% of either axis are labelled.
+				\caption{Representation in IPCC reports: \textbf{a)} by discipline, \textbf{b)} by social science proportion of WG III topics, \textbf{c)} and novelty of all topics, where topics in the highest and lowest 10\% of either axis are labelled.
 Topics are coloured according to the working group from which they receive the most citations.
 Representation is the share of the subset of documents being cited by the IPCC divided by the share of the subset in the whole literature.
-We plot on a log scale so that 0.5 is equally distant to 1 as 2; plot labels show real values.}
+We plot on a log scale so that 0.5 is equally distant to 1 as 2; plot labels show real values.
+Assessment period occurrence refers to the center of a topic's distribution across assessment periods (see methods for further details).}
 				\label{oecd_rep}
@@
 		We have shown that social science literature about climate change is over-represented in the IPCC, while technical literature on solutions is under-represented.
-		A perfectly proportional representation of every part of the literature is of course not optimal, yet these two features represent new knowledge about the interaction between the IPCC and the literature, and have important implications for the community.
+		A perfectly proportional representation of every part of the literature is of course not optimal, and a recommendation that the IPCC cite more of one part of the literature or less of another is by no means the goal of such an analysis.
+Indeed, the community of scientific experts made up by the IPCC is vastly better placed to decide on what is relevant, of high quality, and should be included in each report than any algorithm.
+		As with many machine learning applications, we should be mindful of David Hume's is-ought problem. 
+		Machine learning can help us to more efficiently understand and describe the landscape of climate change literature, but we should be careful about what we interpret as a recommendation.
+In this light the two main results described here represent new knowledge about the interaction between the IPCC and the literature, which can have a variety of important implications.
 		The over-representation of the social sciences, combined with the perception that the IPCC needs to include more social science knowledge \cite{Victor2015}, suggests that doing so must involve the funding and production of more social science literature on climate change, not just greater efforts by the IPCC to include it.
-		Moreover, the fact that solutions-relevant topics are under-represented - while policymakers demand more solutions-oriented assessments - and that these topics contain little social science research, suggests areas where social science research may be usefully conducted.
+		Moreover, the fact that solutions-relevant topics are under-represented - while policymakers demand more solutions-oriented assessments - and that these topics contain little social science research, suggests areas where social science research may be usefully conducted, as well as opportunities for particularly fruitful interdisciplinary collaboration.
 Further, this fact can open a debate about the extent to which the IPCC should include more technical knowledge on solutions from disciplines within engineering and the agricultural sciences.
@@
 		The map can contribute to these decisions as they are made from the scoping process, through to the selection by authors of individual studies.
+		The advantage of topic modelling is that the outcome is not determined by any categorisation scheme imposed by the modeller, which facilitates the discovery of ``unsearched'' for topics.
+Highlighting recent research on, for example, membranes, biochar or e-vehicles, could prompt discussion in the scoping process about the extent to which each of these topics are relevant and should be included.
+		This mode of discovery can act as a complement to human expertise, which may be better at identifying under-researched niches, existing biases or knowledge requirements.
 		Beyond this, the methods shown here could aid other processes in the production of IPCC reports, such as the identification of potential authors to acheive a better balance across sectors, regions and genders \cite{Corbera2016}.
+The possible contribution of, or drawbacks to data science methods for IPCC processes is an important area for future research.
 		Outside of the IPCC, this approach is part of ongoing attempts to make use of machine-learning within evidence synthesis.
@@
 Beyond this we miss publications not in the Web of Science (some small journals, some books, and most grey literature, not to mention indigenous knowledge \cite{Ford2016b}); and studies relevant for the work of the IPCC, but that do not directly mention climate change (for example on energy policy).
-We argue that this remains a reasonable system boundary given data availabilty, and stress that the documents not included in our study alter our findings only if they have systematically different patterns of citation by the IPCC.
-In the future, making use of more sources climate change knowledge, and extracting and classifying information from full texts, could improve the granularity of this topography.
+We argue that this remains a reasonable system boundary given data availability, and stress that the documents not included in our study alter our findings only if they have systematically different patterns of citation by the IPCC.
+In the future, making use of more sources of climate change knowledge, extracting and classifying information from full texts, or exploring author networks and interdisciplinarity, could improve the usefulness of this topography.
 Most importantly, machine learning applications should be explored that support IPCC authors in assessing the literature.

### 2019-10-02 manuscript/methods.tex
revisions, too many words

@@
 		This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on the Web of Science core collection.
+We downloaded the results of the query on March 19, 2019.
 Though not exhaustive, the Web of Science gives a good coverage of the literature in major peer-reviewed journals.
@@
 
+		We analysed by hand a sample of 100 IPCC references which could not be matched and found that 46\% of these references were not in the Web of Science at all, 53\% were in the Web of Science but not in our query, and 1 document was in our query but had mistakenly been identified as not being so.
+This was due a different version of the title appearing in the IPCC citation and the Web of Science record.
+
 		\begin{table}[htp]
@@
 				\input{../tables/ipcc_matching.tex}
-				\caption{The proportion of citations in each report that could be matched with a document from the Web of Science}
+				\caption{The proportion of citations in each report that could be matched with a document in our query from the Web of Science}
 				\label{ipcc-matching}
@@
 
+		\noindent\textbf{co2:} Carbon Dioxide
+
 		\noindent\textbf{ncep:} National Centers for Environmental Protection
@@
 
-		\noindent\textbf{indc:} Intended Nationally Determined Contributions
+		\noindent\textbf{(i)ndc:} (Intended) Nationally Determined Contributions
 
@@
 			\includegraphics[width=1\linewidth]{../plots_pub/topic_oecd_entropy.pdf}
-			\caption{SI Disciplinary Entropy}
+			\caption{Disciplinary Entropy of Topics.
+Coloured bars show the proportion of each topic made up of papers from each disciplinary category.
+Crosses show the Disciplinary Entropy of each topic (see methods for details).}
 			\label{dis-entropy}
@@
 			\includegraphics[width=1\linewidth]{../plots_pub/single_doc_3_536594_1861.pdf}
-			\caption{SI Topic make up of a single document}
+			\caption{Topic make up of a single document.
+The Doc Term Matrix shows the number of occurrences of each term in the document.
+The Topic Term Matrix shows the topic score of each term-topic combination.
+The Doc Topic Matrix shows the document-topic score for each topic.
+This topic makeup of the document shown is illustrated by the bars in the top left.
+Words highly associated with each topic that occur in the document are highlighted.
+All values are real, although the doc-term matrix is scaled by the inverse-document frequency before being used in the model.}
 			\label{doc-topic}
@@
 			\includegraphics[width=1\linewidth]{../plots_pub/ipcc_rep_wcs_simplified.pdf}
-			\caption{SI Representation by subfield}
+			\caption{IPCC Representation by subfield.
+Representation is the share of the subset of documents being cited by the IPCC divided by the share of the subset in the whole literature.
+We plot on a log scale so that 0.5 is equally distant to 1 as 2; plot labels show real values.}
 			\label{subfield}
@@
 			\includegraphics[width=1\linewidth]{../plots_pub/wgs_socsci.pdf}
-			\caption{SI Social science \& representation in topics across working groups}
+			\caption{SI Social science \& representation in topics across working groups.
+Representation is the share of the subset of documents being cited by the IPCC divided by the share of the subset in the whole literature.
+Social science proportion shows the proportion of the total document-topic score coming from documents in the social sciences.}
 			\label{socsci-wgs}
@@
 			\includegraphics[width=1\linewidth]{../plots_pub/topic_rep_ks.pdf}
-			\caption{Topic representation over different values of K (number of topics). Topics in the upper or lower 6.66th percentile of either dimension are labelled}
+			\caption{Topic representation over different values of K (number of topics).
+Topics in the upper or lower 6.66th percentile of either dimension are labelled.
+Representation is the share of the subset of documents being cited by the IPCC divided by the share of the subset in the whole literature.
+Assessment period occurrence refers to the center of a topic's distribution across assessment periods (see methods for further details).}
 			\label{top-rep-ks}

### 2019-10-14 manuscript/main.tex
resubmission

@@
 This is almost as much as the 205,000 papers identified in the same query \cite{Grieneisen2011} during the first five assessment periods; a period of nearly 30 years.
-A total of around 350,000 new publications can be expected for before the sixth assessment report (AR6) of the Intergovernmental Panel on Climate Change (IPCC), based on current growth patterns (Figure \ref{pub-growth}).
-Moreover, the literature has also become more diverse.
-This is reflected in the expansion of the literature's vocabulary (see methods) - from 2,000 unique words in the first assessment period to 95,000 words so far in the sixth - indicating that the field has incorporated new content.
-For example, the zika virus, which was mentioned in 182 articles from 2014-2018, had never before been discussed in the titles or abstracts of articles relating to climate change.
-Yet it has emerged as a topic of high relevance: the incidence of the virus, the outbreak of which in Brazil in 2016 was declared a public health emergency by the World Health Organization, is set to increase under rising global temperatures \cite{Rao2019}.
-Similar rapid emergence patterns can be seen for Intended Nationally Determined Contributions (INDCs) and Sustainable Development Goals (SDGs) in AR6, and Biochar and the UN forest protection programme REDD in AR5, among others\footnote{The glossary in SI contains a complete list of the acronyms shown in the table}.
+Around 350,000 new publications can be expected for before the sixth assessment report (AR6) of the Intergovernmental Panel on Climate Change (IPCC), based on current growth patterns (Figure \ref{pub-growth}).
+Moreover, from the expansion of the literature's vocabulary (see methods) - from 2,000 unique words in the first assessment period to 95,000 words so far in the sixth - we can observe the literature's increasing diversity of content.
+For example, the zika virus, mentioned in 182 articles from 2014-2018, had never before been discussed in the titles or abstracts of articles relating to climate change.
+Yet it has emerged as a topic of high relevance: the incidence of the virus, whose outbreak in Brazil in 2016 was declared a public health emergency by the World Health Organization, is set to increase under rising global temperatures \cite{Rao2019}.
+Similar rapid emergence patterns can be seen for Intended Nationally Determined Contributions (INDCs) in AR6, and Biochar in AR5, among others\footnote{The glossary in SI contains a complete list of the acronyms shown in the table}.
 
@@
 For example, the ratio of studies cited in IPCC reports to the number of studies on climate change in the WoS has declined from 60\% to 20\%  \cite{Minx2017l}, posing a rapidly growing risk of selection bias.
-More generally, the exponential increase in the volume of literature means that the provision of comprehensive, objective, open and transparent assessments of the available scientific literature, as defined in the principles governing IPCC work \cite{IPCC2013}, is no longer possible for authors or author teams by traditional means.
-		Machine reading and learning methods as well as other data science applications are required to enable an understanding of the field of climate change research at scale. 
-		\emph{Second}, evidence synthesis - the enterprise of reviewing the literature based on a formal and systematic set of methods \cite{Chalmers2002} - becomes increasingly important for aggregating and consolidating the rapidly emerging knowledge and enabling scientific assessments to do their job.
+The exponentially increasing volume of literature means that the provision of ``comprehensive, objective, open and transparent'' assessments of the available scientific literature, as defined in the principles governing IPCC work \cite{IPCC2013}, is no longer possible by traditional means.
+		Machine reading and learning methods, among other data science applications, are required to enable an understanding of the field of climate change research at scale. 
+		\emph{Second}, evidence synthesis - the enterprise of reviewing the literature based on a formal and systematic set of methods \cite{Chalmers2002} - becomes increasingly important for aggregating and consolidating rapidly emerging knowledge and enabling scientific assessments to do their job.
 		Yet traditional methods of evidence synthesis themselves are pushed to their limits by the large amount of scientific publications.
 The field of evidence synthesis technology, which tries to streamline human tasks through machine learning at the different stages of the review process, is still in its infancy \cite{Beller2018}.
-\emph{Finally}, overwhelming amounts of literature may be a major reason why studies of scientific assessments \cite{Bjurström2011, Hulme2010, Victor2015} do not offer robust quantification for their claims about the relationship between report citations and the underlying literature.
+\emph{Finally}, overwhelming amounts of literature may be a major reason why studies of scientific assessments \cite{Bjurström2011} do not offer robust quantification for their claims about the relationship between report citations and the underlying literature.
 
-		This study uses topic modelling \cite{Blei2010} to map out the vast body of evidence on climate change.
-Topic modelling is an unsupervised machine-learning technique, where patterns of word co-occurrences in documents are used to learn a set of topics which can be used to describe the corpus.
-The word topic derives from the Greek word for place (topos), and by \textit{situating} the documents in a reduced-form projection of their thematic content (see Figure \ref{oecd_topic_map}), we create a \textit{topographic map} of the literature on climate change.
+		This study uses topic modelling \cite{Blei2010} to map the vast body of evidence on climate change.
+Topic modelling is an unsupervised machine-learning technique, where patterns of word co-occurrences are used to learn a set of topics, groups of words, which describe the corpus.
+		The word topic derives from the Greek word for place (topos), and by \textit{situating} the documents in a reduced-form projection of their thematic content (Figure \ref{oecd_topic_map}), we create a \textit{topographic map} of the literature on climate change.
 Such a systematic engagement with the thematic content of the climate science is missing from the literature so far.
-		We apply this map in a second step to understand how the IPCC reports have represented the available climate change literature and re-evaluate claims of bias based on a more comprehensive understanding of the available climate science.
-We enrich the discussion on representation in the literature by discussing topics as well as disciplines.
+		We then use this map to understand how IPCC reports have represented the available climate change literature and re-evaluate claims of bias based on a more comprehensive understanding of the available climate science.
+		We enrich the discussion on representation by discussing topics as well as disciplines.
 
-		\subsection*{Mapping out the landscape of climate change literature}
+		\subsection*{Mapping the landscape of climate change literature}
 
-		Figure \ref{oecd_topic_map} shows a \emph{thematic} or \emph{topographic map} of the 378,000 publications on climate change in our dataset that had abstracts with a total number of 140 topics.
-The number of topics must be defined exogenously, but the results are robust to different specifications.
-Using non-negative matrix factorization \cite{Lee1999}, the topics, which are groups of words that describe groups of documents, are machine-learned from the papers' abstracts (see methods for details, examples of different model specifications, and a thorough explanation of model selection).
+		Figure \ref{oecd_topic_map} shows a \emph{thematic} or \emph{topographic map} of the 378,000 publications on climate change in our dataset with abstracts.
+Using non-negative matrix factorization \cite{Lee1999}, the 140 topics are machine-learned from the papers' abstracts (see methods for details).
 The topic scores of each document are reduced to the two dimensions shown through t-distributed stochastic neighbour embedding (t-SNE) \cite{vandermaaten2008}.
 \footnote{A full list of topics and related words, and a list of documents, their positions on the map, and their related topics are given in the SI}.
-The two dimensions represent a projection of the 140-dimensional topic scores of each document that seeks to preserve small distances between similar documents.
+The two dimensions represent a projection of the 140-dimensional topic scores of each document that seeks to preserve small distances between topically similar documents.
 
@@
 
-		The map shown covers a broad range of topics, with related topics shown in clusters.
-In general, topics related to climate science and impacts are on the left, while solution-oriented topics are on the right.
+		Our map covers a broad range of topics, with related topics in clusters.
+Generally, topics related to climate science and impacts are on the left, while solution-oriented topics are on the right.
 More fine-grained research areas can also be distinguished.
-For example, publications related to urban infrastructure (\textbf{buildings}, \textbf{energy}, \textbf{cement}, \textbf{waste}) are located on the right, physical climate impacts such as \textbf{sea-level}, \textbf{droughts}  or [crop] \textbf{yield} are in the lower left and energy systems are in upper right.
-There are larger groups of documents at the fringes of the map that relate mainly to one or two specific topics such as \textbf{biochar}, \textbf{coral}, or \textbf{CO2 storage}.
+For example, publications related to urban infrastructure (\textbf{buildings}, \textbf{cement}, \textbf{waste}) are located on the right, physical climate impacts (\textbf{sea-level}, \textbf{droughts}  or [crop] \textbf{yield}) are in the lower left and energy systems are in upper right.
+Larger groups of documents at the fringes of the map relate mainly to one or two specific topics like \textbf{biochar} or \textbf{coral}.
 Interestingly, scenarios feature centrally in the map, at the interface between different scientific communities.
 This corresponds to their integrative nature in IPCC reports \cite{Moss2010}.
-This map of the thematic structure of the literature could be useful for individual scientific communities or for climate change assessments.
+%This map of the thematic structure of the literature could be useful for individual scientific communities or for climate change assessments.
 
@@
 More than 60\% of the literature is published in natural science journals.
-Similarly, in 115 out of 140 topics the contribution of publications in natural science journals is greater than any other discipline.
-We calculate disciplinary entropy of topics as a measure of their degree of interdisciplinarity (see Figure \ref{dis-entropy} and methods for details).
-This shows how research on \textbf{health}, \textbf{food}, or \textbf{policy} comes from a range of disciplines, while research on \textbf{ice} and \textbf{oceans} comes almost exclusively from the natural sciences).
+Similarly, 115 of 140 topics contain a greater share of publications from natural science journals than any other discipline.
+We calculate disciplinary entropy of topics as a measure of their degree of interdisciplinarity (Figure \ref{dis-entropy} and methods for details).
+This shows how research on \textbf{health}, \textbf{food}, or \textbf{policy} comes from a range of disciplines, while research on \textbf{ice} or \textbf{oceans} comes almost exclusively from the natural sciences).
 
@@
 		\subsection*{Research representation in IPCC reports}
-		We apply our topic map to understand the representation of science in IPCC assesssments and how they manage to respond to demands for more solution-oriented knowledge \cite{Kowarsch2017}.
+		We apply our topic map to understand how IPCC assessments represent the science and respond to policymakers' and consulted experts' demands for more solution-oriented knowledge \cite{Kowarsch2017}.
 Several studies have identified, made, or repeated claims of a disciplinary bias of IPCC assessments towards the natural sciences, and within the social sciences towards economics \cite{Bjurström2011, Victor2015, Hulme2010, Corbera2016}.
-Where these claims were based on an analysis of IPCC citations \cite{Bjurström2011}, they fail to assess this claim against a measurable baseline.
-We argue here that this can be provided by the composition of the climate change literature as a whole.
-Although, as we discuss in the concluding section, it is in many ways imperfect, in view of the organisation's mandate to provide ``comprehensive, objective, open and transparent'' assessment of the available science \cite{IPCC2013}, our dataset of publications allows us to study representation with a meaningful baseline, and over time rather than for single assessment cycles.
-As such it forms a starting point for informed discussion about how to represent the literature according to the IPCC's priorities.
-By matching the documents in our dataset to a set of references scraped from all published IPCC reports \cite{Minx2017l}, we can assess the representation of a group of studies by comparing the group's share in the subset of studies cited by the IPCC with it's share in the dataset of WoS studies on climate change (see methods for further details).
+Where these claims were based on an analysis of IPCC citations \cite{Bjurström2011}, they assess this without measurable baseline.
+		In view of the organisation's mandate to provide ``comprehensive, objective, open and transparent'' assessments of the available science \cite{IPCC2013}, our dataset of publications allows us - albeit imperfectly, as discussed in the concluding section - to study representation with a meaningful baseline.
+Further we provide an update to the last quantitative assessment of IPCC citations \cite{Bjurström2011}, which looked only at AR3.
+		This baseline forms a starting point for informed discussion about how to represent the literature according to the IPCC's priorities.
 
-		Figure \ref{oecd_rep}.a shows that the social sciences were indeed under-represented in the third assessment report, but by the fifth assessment report were over-represented.
-Likewise, social sciences other than economics have become better represented since AR3  (see figure \ref{subfield}f) with social \& economic geography (4.3\% of the literature), political science (1.0\%), and sociology (0.8\%) showing improved representation in AR5 compared to AR3, and social and economic geography, political science, and other social sciences better represented than economics.
+		By matching the documents in our dataset to a set of references scraped from all published IPCC reports \cite{Minx2017l}, we assess the representation of a group of studies by comparing its share in IPCC citations with its share in the dataset of WoS studies on climate change (see methods).
+		Figure \ref{oecd_rep}.a shows that social science documents (as identified by WoS) were indeed under-represented in AR3, but by AR5 were the most over-represented discipline, with a share in the literature cited by IPCC reports 1.32 times higher than their share in our WoS dataset.
+Likewise, social \& economic geography, political science, and "Other social sciences" were better represented in AR5 than economics.
+		This challenges what we think we know about the IPCC. 
+		Instead of under-representing the social sciences, the IPCC has been under-representing the Agricultural Sciences and Engineering \& Technology.
+		%Humanities are also under-represented, although they make up a very small proportion of the total literature.
 
-		This challenges what we think we know about the IPCC.
-The social sciences, by now, are actually the best represented field, with a share in the literature cited by IPCC reports 1.32 times higher than in the literature at large.
-On the other hand the Agricultural Sciences and Engineering \& Technology have been consistently under-represented, with 2.27 and 3.49 times the share of studies in the wider literature than in the literature cited by the IPCC in AR5 respectively.
-Humanities are also under-represented, although they make up a very small proportion of the total literature.
-
-		The topography allows us to delve deeper into the subject matter that receives more or less attention in the IPCC.
-Figures \ref{oecd_rep}b and \ref{oecd_rep}c plot the representation of the topics shown in the map.
-Figure \ref{oecd_rep}c shows that topics more commonly cited by IPCC working group I (WGI - the physical science basis) are older and largely better represented in IPCC reports.
-These topics, for example \textbf{ozone}, \textbf{oceans}, \textbf{clouds}, \textbf{aerosols} and \textbf{sea levels} make up some of the core topics of the physical science of climate change.
+		The topography allows us to delve deeper into subjects that receive more or less attention in the IPCC. 
+		%Figures \ref{oecd_rep}b and \ref{oecd_rep}c plot topic representation. 
+		Figure \ref{oecd_rep}c shows that topics more commonly cited by IPCC working group I (WGI) are older and largely better represented in IPCC reports.
+These topics, for example \textbf{ozone}, \textbf{oceans}, and \textbf{aerosols}, are core topics for WGI, which addresses the physical science of climate change.
 
 		The topics in the lower right of the graph are the most pertinent to the question of whether the IPCC is well representing knowledge on climate change.
-These topics are newer and until now have been under-represented in IPCC reports.
-Because they are new areas of knowledge, they may be highly salient in a periodic assessment process.
-These topics are primarily in working group III, on mitigation \footnote{see methods for a discussion of the categorisation of topics, including adsorption, and membranes, which may more properly be described as relevant to WGIII}.
+They are newer and until now have been under-represented in IPCC reports.
+Their novelty may be highly salient in a periodic assessment process.
+These topics are primarily in working group III, on mitigation and are ``solutions-relevant''.
+But while policymakers' demands for solutions-oriented IPCC assessments were often focussed on policy options, these under-represented new topics deal with more technical solutions and are found in technical disciplines within engineering \& technology and the agricultural sciences.
 
-		The difference between these under-represented new topics and other new topics that are better represented is intriguing.
-This difference is visible in figure \ref{evolution-map}, where in AR5, the clusters of documents around the \textbf{adsorption}, \textbf{buildings}, and \textbf{biochar} topics contain few IPCC citations, whereas the clusters around \textbf{food}, \textbf{health}, \textbf{adaptation}, and \textbf{GHGs} contain more.
-As shown in figure \ref{oecd_rep}c, \textbf{adsorption}, \textbf{buildings} and \textbf{biochar} are 4.08, 3.34 and 3.61 times more prevalent in the literature than in IPCC citations, while \textbf{food} is 1.22 times more prevalent in the literature and \textbf{health} and \textbf{adaptation} are 1.02 and 2.22 times more prevalent in IPCC citations respectively.
-The IPCC, has been better at integrating new knowledge from these topics, and in general better at integrating new knowledge from WG II than WG III topics.
+		Further, WGIII topics that are well represented contain a greater proportion of social science research (figure \ref{oecd_rep}b).
+The topics \textbf{countries}, \textbf{policy}, and \textbf{prices} are close to a proportional representation and are made up of around 30\% social science research.
+\textbf{Waste}, \textbf{biochar}, and \textbf{cement}, are more than 3 times more prevalent in the wider literature than in the literature cited by the IPCC, and are made up of around 5\% social science research.
+This pattern is not visible in other working groups (Figure \ref{socsci-wgs}).
 
-		Further, within WG III topics, those that are well represented contain a greater proportion of social science research (figure \ref{oecd_rep}b).
-The topics \textbf{countries}, \textbf{policy}, and \textbf{prices} are close to a proportional representation and are made up of around 30\% social science research.
-\textbf{Waste}, \textbf{biochar}, \textbf{cement} and \textbf{coal}, are more than 3 times more prevalent in the wider literature than in the literature cited by the IPCC, and are made up of around 5\% social science research.
-This pattern is not visible in other working groups (see Figure \ref{socsci-wgs}), and complicates the perception of the under-representation of the social sciences.
-
-		Recalling policymakers' demands for more solution-oriented assessments \cite{Kowarsch2017}, we could also interpret the topics that are newer and under-represented as ``solutions-relevant''.
-However, while policymakers' demands for solutions-oriented knowledge were rather about policy options, these under-represented new topics deal with more technical solutions and are found rather in technical disciplines within engineering \& technology and the agricultural sciences.
+		The difference between under-represented new topics and new topics that are better represented is intriguing.
+This is visible in figure \ref{evolution-map}, where in AR5, the clusters of documents around the, \textbf{buildings} and \textbf{biochar} topics contain few IPCC citations, whereas the clusters around, \textbf{adaptation} and \textbf{food} contain more.
+As shown in figure \ref{oecd_rep}c, \textbf{buildings} and \textbf{biochar} are 3.34 and 3.61 times more prevalent in the literature than in IPCC citations, while \textbf{food} is 1.22 times more prevalent in the literature and \textbf{adaptation} is 2.22 times more prevalent in IPCC citations respectively.
+%The IPCC, has been better at integrating new knowledge from these topics, and in general better at integrating new knowledge from WGII than WGIII topics.
 
@@
 				\includegraphics[width=180mm]{../plots_pub/big_panel_representation.pdf}
-				\caption{Representation in IPCC reports: \textbf{a)} by discipline, \textbf{b)} by social science proportion of WG III topics, \textbf{c)} and novelty of all topics, where topics in the highest and lowest 10\% of either axis are labelled.
-Topics are coloured according to the working group from which they receive the most citations.
+				\caption{Representation in IPCC reports: \textbf{a)} by discipline, \textbf{b)} by social science proportion of WGIII topics, \textbf{c)} and novelty of all topics, where topics in the highest and lowest 10\% of either axis are labelled.
+Topics are coloured according to the working group from which they receive the most citations, although infrequently cited topics may not correspond to the relevant working group (see methods).
 Representation is the share of the subset of documents being cited by the IPCC divided by the share of the subset in the whole literature.
@@
 
-		We have shown that social science literature about climate change is over-represented in the IPCC, while technical literature on solutions is under-represented.
-		A perfectly proportional representation of every part of the literature is of course not optimal, and a recommendation that the IPCC cite more of one part of the literature or less of another is by no means the goal of such an analysis.
-Indeed, the community of scientific experts made up by the IPCC is vastly better placed to decide on what is relevant, of high quality, and should be included in each report than any algorithm.
+		Notwithstanding the over-representation of social science and under-representation of technical solutions in the IPCC with respect to the WoS, a
+		 perfectly proportional representation of the literature is of course not optimal.
+A recommendation that the IPCC cite more or less of any part of the literature is by no means the goal of such an analysis.
+The IPCC, as a community of scientific experts, is vastly better placed to decide what is relevant than any algorithm.
 		As with many machine learning applications, we should be mindful of David Hume's is-ought problem. 
-		Machine learning can help us to more efficiently understand and describe the landscape of climate change literature, but we should be careful about what we interpret as a recommendation.
-In this light the two main results described here represent new knowledge about the interaction between the IPCC and the literature, which can have a variety of important implications.
-		The over-representation of the social sciences, combined with the perception that the IPCC needs to include more social science knowledge \cite{Victor2015}, suggests that doing so must involve the funding and production of more social science literature on climate change, not just greater efforts by the IPCC to include it.
-		Moreover, the fact that solutions-relevant topics are under-represented - while policymakers demand more solutions-oriented assessments - and that these topics contain little social science research, suggests areas where social science research may be usefully conducted, as well as opportunities for particularly fruitful interdisciplinary collaboration.
-Further, this fact can open a debate about the extent to which the IPCC should include more technical knowledge on solutions from disciplines within engineering and the agricultural sciences.
+		Machine learning can help us to more efficiently understand and describe the landscape of climate change literature, but cannot tell us how things should be. 
+		The results represent new knowledge about the interaction between the IPCC and the literature, which can have a variety of implications. 
+		If the IPCC needs to include more social science knowledge \cite{Victor2015}, our analysis suggests that this is a result of insufficient production or funding of social science research on climate, rather than IPCC bias.
+		The under-representation of solutions-relevant topics (despite calls for solutions-oriented assessments), and the small proportion of social science research within these topics,  suggests areas for future highly relevant social science research, as well as opportunities for particularly fruitful interdisciplinary collaboration.
 
-		The map can also serve as a guide to future assessments, to ensure that decisions about how different areas of the literature are represented are well-informed. 
-		The map can contribute to these decisions as they are made from the scoping process, through to the selection by authors of individual studies.
-		The advantage of topic modelling is that the outcome is not determined by any categorisation scheme imposed by the modeller, which facilitates the discovery of ``unsearched'' for topics.
-Highlighting recent research on, for example, membranes, biochar or e-vehicles, could prompt discussion in the scoping process about the extent to which each of these topics are relevant and should be included.
+		As a guide for future assessments, the map could facilitate well informed decisions about the representation of different areas of climate literature, from the early scoping process, through to selection by authors of individual studies.
+		One advantage of topic modelling is that outcomes are not determined by any categorisation scheme imposed by the modeller, facilitating the discovery of ``unsearched'' for topics. 
+		Highlighting recent research on, for example, membranes, biochar or e-vehicles, could prompt discussion in the scoping process about their inclusion in chapter outlines.
 		This mode of discovery can act as a complement to human expertise, which may be better at identifying under-researched niches, existing biases or knowledge requirements.
-		Beyond this, the methods shown here could aid other processes in the production of IPCC reports, such as the identification of potential authors to acheive a better balance across sectors, regions and genders \cite{Corbera2016}.
-The possible contribution of, or drawbacks to data science methods for IPCC processes is an important area for future research.
-		Outside of the IPCC, this approach is part of ongoing attempts to make use of machine-learning within evidence synthesis.
-The topographic map presented is a new approach to rapidly mapping very large literatures.
+		The methods shown here could also aid other processes in the production of IPCC reports, such as the identification of potential authors to achieve a better balance across sectors, regions and genders \cite{Corbera2016}.
+The possible benefits or risks of using data science methods for IPCC processes constitutes an important area for future research.
+		Outside of the IPCC, this approach is part of ongoing attempts to make use of machine learning within evidence synthesis.
+This topographic map is a new approach to rapidly mapping very large literatures.
 
-		The more than 400,000 publications we deal with here represent a wealth of knowledge on climate change and climate solutions.
-However, we acknowledge that our dataset is by no means exhaustive.
+		Our dataset of more than 400,000 publications represents a wealth of knowledge on climate change and climate solutions, but is by no means exhaustive.
 We repeat an established query \cite{Haunschild2016}, granting that it may have imperfections.
-Beyond this we miss publications not in the Web of Science (some small journals, some books, and most grey literature, not to mention indigenous knowledge \cite{Ford2016b}); and studies relevant for the work of the IPCC, but that do not directly mention climate change (for example on energy policy).
-We argue that this remains a reasonable system boundary given data availability, and stress that the documents not included in our study alter our findings only if they have systematically different patterns of citation by the IPCC.
-In the future, making use of more sources of climate change knowledge, extracting and classifying information from full texts, or exploring author networks and interdisciplinarity, could improve the usefulness of this topography.
-Most importantly, machine learning applications should be explored that support IPCC authors in assessing the literature.
-This would prepare IPCC assessments for the age of big literature.
+Furthermore, we miss publications not in WoS  (some small journals, some books, and most grey literature, not to mention indigenous knowledge \cite{Ford2016b}); and studies relevant for the work of the IPCC, that do not directly mention climate change (for example on energy policy).
+We argue that this remains a reasonable system boundary given data availability, and stress that documents not included in our study alter our findings only if they have systematically different patterns of citation by the IPCC.
+		A future topography could be improved by making use of more sources of climate change knowledge, extracting and classifying information from full texts, or exploring author networks and interdisciplinarity.
+		Most importantly, exploring machine learning applications that support IPCC authors in their assessments would prepare the IPCC for the age of big literature.
 

### 2019-12-13 manuscript/coverletter.tex

--- 2019-07-24 manuscript/coverletter.tex
@@
 
-	\begin{letter}{Bronwyn Wake \\ Chief Editor \\ \textit{Nature Climate Change}}
+	\begin{letter}{Adam Yeeles \\ Editor \\ \textit{Nature Climate Change}}
 
@@
 		\begin{tikzpicture}[remember picture, overlay]
-		\node [anchor=south, shift={(-1mm,5mm)}]  at (current page text area.north east) {\includegraphics[width=4cm]{pres/MCC_Logo_RZ_rgb.jpg}
+		\node [anchor=south, shift={(-1mm,5mm)}]  at (current page text area.north east) {\includegraphics[width=4cm]{../pres/MCC_Logo_RZ_rgb.jpg}
 		};
@@
 
-   \opening{\today \\ \\ Dear Bronwyn Wake,}
+   \opening{\today \\ \\ Dear Adam Yeeles,}
 
-   I herewith submit on behalf of my co-authors the manuscript ``A Topography of Climate Change Litereature'' for consideration as a letter in Nature Climate Change.
+   I herewith resubmit on behalf of my co-authors the Letter ``A Topography of Climate Change Literature'' (NCLIM-19071401).
 
-``Big literature'' - the vast and rapidly expanding body of publications - poses new, and largely neglected challenges for climate change assessments and how we understand them.
-For example, we estimate a total of 350,000 new publications on climate change to emerge (only) in the Web of Science during the Sixth Assessment Cycle of the Intergovernmental Panel on Climate Change spanning from 2015 to 2022.
-Big data and machine learning methods need to be applied to maintain an overview of developments in the scientific landscape and to analyse how past IPCC assessments have engaged with the available literature.
-So far, attempts \cite{Bjurström2011, Hulme2010, Victor2015, Kowarsch2017} have often been based on qualitative perceptions, or incomplete data with insufficient methodological sophistication.
+   The letter made use of topic modelling in order to reassess claims made in the literature about how the IPCC has represented scientific knowledge about climate change.
+This in the context of Big Literature - the hundreds of thousands of papers published on climate change which it is the IPCC's job to assess.
 
-In this study we use machine-learning to provide a comprehensive, thematic map of the more than 400,000 articles on climate change published in the Web of Science to date.
-We perceive two innovations that allow us advance the current state of knowledge on the IPCC and the field it is tasked with assessing.
-First, our thematic map allows us to situate a complete set of IPCC citations into the context of the wider literature and analyse disciplinary representation adequately.
-We find that contrary to previous claims, the social sciences are over-represented in IPCC reports.
-Second, the use of machine learning methods in creating the map allows us to analyse the content of publications more or less represented in the IPCC.
-We find that literature on technical solutions (such as negative emissions, buildings or cities) is growing fast and, even compared to other fast-growing literatures, has been under-represented in IPCC reports.
-We point towards a variety of other applications of such a comprehensive, thematic literature map within global environmetal assessments as well as the broad field of research synthesis.
-Our findings have direct implications for addressing growing demands for more solution-oriented climate change assessments that are also more firmly rooted in the social sciences.
+   We express our gratitude for the handling of our manuscript, and for the comments received from the reviewers.
+We have edited our manuscript accordingly and attach a point by point response to all comments.
+   The comments received were clear and along similar lines. Broadly speaking, we 
+   \begin{itemize}
+   	\item Improved the clarity of our description of our methods in the main text so that they could be understood by a non-specialist audience.
+   	\item Added significant nuance to the interpretation of our results.
+We have been more explicit about what can and can't be drawn as recommendations from our analysis, given its advantages and drawbacks.
+This has led in turn to a more interesting discussion about how the methods we propose could be used in further IPCC assessments.
+   \end{itemize}
+
+	We are confident that this re-submission addresses all of the concerns raised by the reviewers.
 
@@
 
-\bibliography{Mendeley}
-\bibliographystyle{unsrt}
+\section{Manuscript details}
+
+\begin{tabular}{l r r}
+
+	 & \textbf{Main text} & \textbf{SI \& Methods} \\
+	 \textbf{Words} & 2196 & 1584 \\
+	 \textbf{Figures} & 4 & 5 \\
+	 \textbf{Tables} & 1 & 1 \\
+	 \textbf{References} & 19 & 12
+
+\end{tabular} 
+%\bibliography{Mendeley}
+%\bibliographystyle{unsrt}
 

### 2019-12-13 manuscript/main.tex
final submission ready

@@
 \usepackage{url}
-\usepackage{natbib}
+%\usepackage{natbib}
 \usepackage{todonotes}
@@
 \usepackage{xr}
-\externaldocument{methods}
+
+\externaldocument{extended_figures}
 
 \usepackage[section]{placeins}
+
+%\setcitestyle{square, citesep={,}}
 
@@
 
-		\bigskip
-
-		{\large{Draft current \@date}}
-
 	\end{flushleft}\egroup
@@
 % Title
-\title{A Topic Model of Climate Change Literature}
-\title{Words, words, words: Mapping the Matter of Climate Change Literature}
 \title{A Topography of Climate Change Research}
@@
 Yet it has emerged as a topic of high relevance: the incidence of the virus, whose outbreak in Brazil in 2016 was declared a public health emergency by the World Health Organization, is set to increase under rising global temperatures \cite{Rao2019}.
-Similar rapid emergence patterns can be seen for Intended Nationally Determined Contributions (INDCs) in AR6, and Biochar in AR5, among others\footnote{The glossary in SI contains a complete list of the acronyms shown in the table}.
+Similar rapid emergence patterns can be seen for Intended Nationally Determined Contributions (INDCs) in AR6, and Biochar in AR5, among others.
 
@@
 					\input{../tables/growth_table.tex}}
-				\caption{Growth of Literature on Climate Change. A glossary of acronyms is provided in SI}
+				\caption{Growth of Literature on Climate Change. A glossary of acronyms is provided in the note below}
 				\label{tab}
@@
 
-		Big literature poses at least three challenges for scientific policy advice and science itself: \emph{First}, established procedures in scientific assessments like those conducted by the IPCC struggle to address the exploding literature base.
+		\section*{}
+		\textbf{Note - definition of acronyms}: 		\textbf{co2:} Carbon Dioxide, 	
+		\textbf{ncep:} National Centers for Environmental Protection,
+		\textbf{fco:} Fugacity of Carbon Dioxide,
+		\textbf{pfc:} Perflourocompound
+		\textbf{otcs:} Open Top Chambers
+		\textbf{dtr:} Diurnal Temperature Range
+		\textbf{sres:} Special Report on Emissions Scenarios (200)
+		\textbf{petm:} Paleocene Eocene Thermal Maximum
+		\textbf{amf:}  Arbuscular Mycorrhizal Fungal
+		\textbf{sf5cf3:} trifluoromethyl sulfur pentafluoride (A Potent Greenhouse Gas Identified in the Atmosphere, 2000)
+		\textbf{clc:} Chemical Looping Combustion
+		\textbf{cwd:} Coarse woody debris
+		\textbf{etm:} Enhanced Thematic Mapper (NASA satellite sensor)
+		\textbf{cmip5:} Coupled Model Intercomparison Project 5 (Starting 2008)
+		\textbf{cmip3:} Coupled Model Intercomparison Project phase 3 (first published 2007 \cite{Meehl2007})
+		\textbf{mofs:} metal-organic frameworks (for CO2 storage)
+		\textbf{sdm:} statistical-dynamical model
+		\textbf{mmms:} Mixed Matrix Membranes (for CO2 capture)
+		\textbf{cop21:} 21st Conference of Parties (Paris 2015) 
+		\textbf{c3n4:} Carbon nitride (a synthetic nanomaterial used for hydrogen production)
+		\textbf{sdg:} Sustainable Development Goals
+		\textbf{(i)ndc:} (Intended) Nationally Determined Contributions
+
+		\section*{}
+
+		Big literature poses at least three challenges for scientific policy advice and science itself: First, established procedures in scientific assessments like those conducted by the IPCC struggle to address the exploding literature base.
 For example, the ratio of studies cited in IPCC reports to the number of studies on climate change in the WoS has declined from 60\% to 20\%  \cite{Minx2017l}, posing a rapidly growing risk of selection bias.
@@
 		Machine reading and learning methods, among other data science applications, are required to enable an understanding of the field of climate change research at scale. 
-		\emph{Second}, evidence synthesis - the enterprise of reviewing the literature based on a formal and systematic set of methods \cite{Chalmers2002} - becomes increasingly important for aggregating and consolidating rapidly emerging knowledge and enabling scientific assessments to do their job.
+		Second, evidence synthesis - the enterprise of reviewing the literature based on a formal and systematic set of methods \cite{Chalmers2002} - becomes increasingly important for aggregating and consolidating rapidly emerging knowledge and enabling scientific assessments to do their job.
 		Yet traditional methods of evidence synthesis themselves are pushed to their limits by the large amount of scientific publications.
 The field of evidence synthesis technology, which tries to streamline human tasks through machine learning at the different stages of the review process, is still in its infancy \cite{Beller2018}.
-\emph{Finally}, overwhelming amounts of literature may be a major reason why studies of scientific assessments \cite{Bjurström2011} do not offer robust quantification for their claims about the relationship between report citations and the underlying literature.
+Finally, overwhelming amounts of literature may be a major reason why studies of scientific assessments \cite{Bjurstroem2011} do not offer robust quantification for their claims about the relationship between report citations and the underlying literature.
 
@@
 Topic modelling is an unsupervised machine-learning technique, where patterns of word co-occurrences are used to learn a set of topics, groups of words, which describe the corpus.
-		The word topic derives from the Greek word for place (topos), and by \textit{situating} the documents in a reduced-form projection of their thematic content (Figure \ref{oecd_topic_map}), we create a \textit{topographic map} of the literature on climate change.
+		The word topic derives from the Greek word for place (topos), and by situating the documents in a reduced-form projection of their thematic content (Figure \ref{oecd_topic_map}), we create a topographic map of the literature on climate change.
 Such a systematic engagement with the thematic content of the climate science is missing from the literature so far.
@@
 
-		\subsection*{Mapping the landscape of climate change literature}
+		%\subsection*{Mapping the landscape of climate change literature}
 
-		Figure \ref{oecd_topic_map} shows a \emph{thematic} or \emph{topographic map} of the 378,000 publications on climate change in our dataset with abstracts.
+		Figure \ref{oecd_topic_map} shows a thematic or topographic map of the 378,000 publications on climate change in our dataset with abstracts.
 Using non-negative matrix factorization \cite{Lee1999}, the 140 topics are machine-learned from the papers' abstracts (see methods for details).
-The topic scores of each document are reduced to the two dimensions shown through t-distributed stochastic neighbour embedding (t-SNE) \cite{vandermaaten2008}.
-\footnote{A full list of topics and related words, and a list of documents, their positions on the map, and their related topics are given in the SI}.
+The topic scores of each document are reduced to the two dimensions shown through t-distributed stochastic neighbour embedding (t-SNE) \cite{vandermaaten2008} (a full list of topics and related words, and a list of documents, their positions on the map, and their related topics are given in the supplementary material).
 The two dimensions represent a projection of the 140-dimensional topic scores of each document that seeks to preserve small distances between topically similar documents.
@@
 Similarly, 115 of 140 topics contain a greater share of publications from natural science journals than any other discipline.
-We calculate disciplinary entropy of topics as a measure of their degree of interdisciplinarity (Figure \ref{dis-entropy} and methods for details).
+We calculate disciplinary entropy of topics as a measure of their degree of interdisciplinarity (Extended Data Figure \ref{dis-entropy} and methods for details).
 This shows how research on \textbf{health}, \textbf{food}, or \textbf{policy} comes from a range of disciplines, while research on \textbf{ice} or \textbf{oceans} comes almost exclusively from the natural sciences).
@@
 In each period, the 10 fastest growing topics are labelled.
-Where documents could be matched to IPCC citations, they are coloured by the working group citing them.}
+Where documents could be matched to IPCC citations, they are coloured by the working group citing them.
+Panel a) shows documents from assessment periods 1-3, b) shows documents from assessment period 4, c) shows documents from assessment period 5, and d) shows documents published during assessment period 6.}
 				\label{evolution-map}
@@
 
-		\subsection*{Research representation in IPCC reports}
+		%\subsection*{Research representation in IPCC reports}
 		We apply our topic map to understand how IPCC assessments represent the science and respond to policymakers' and consulted experts' demands for more solution-oriented knowledge \cite{Kowarsch2017}.
-Several studies have identified, made, or repeated claims of a disciplinary bias of IPCC assessments towards the natural sciences, and within the social sciences towards economics \cite{Bjurström2011, Victor2015, Hulme2010, Corbera2016}.
-Where these claims were based on an analysis of IPCC citations \cite{Bjurström2011}, they assess this without measurable baseline.
+Several studies have identified, made, or repeated claims of a disciplinary bias of IPCC assessments towards the natural sciences, and within the social sciences towards economics \cite{Bjurstroem2011, Victor2015, Hulme2010, Corbera2016}.
+Where these claims were based on an analysis of IPCC citations \cite{Bjurstroem2011}, they assess this without measurable baseline.
 		In view of the organisation's mandate to provide ``comprehensive, objective, open and transparent'' assessments of the available science \cite{IPCC2013}, our dataset of publications allows us - albeit imperfectly, as discussed in the concluding section - to study representation with a meaningful baseline.
-Further we provide an update to the last quantitative assessment of IPCC citations \cite{Bjurström2011}, which looked only at AR3.
+Further we provide an update to the last quantitative assessment of IPCC citations \cite{Bjurstroem2011}, which looked only at AR3.
 		This baseline forms a starting point for informed discussion about how to represent the literature according to the IPCC's priorities.
@@
 \textbf{Waste}, \textbf{biochar}, and \textbf{cement}, are more than 3 times more prevalent in the wider literature than in the literature cited by the IPCC, and are made up of around 5\% social science research.
-This pattern is not visible in other working groups (Figure \ref{socsci-wgs}).
+This pattern is not visible in other working groups (Extended Data Figure \ref{socsci-wgs}).
 
@@
 
-		\subsection*{Machine-learning for climate change assessments}
+		%\subsection*{Machine-learning for climate change assessments}
 
@@
 		This mode of discovery can act as a complement to human expertise, which may be better at identifying under-researched niches, existing biases or knowledge requirements.
-		The methods shown here could also aid other processes in the production of IPCC reports, such as the identification of potential authors to achieve a better balance across sectors, regions and genders \cite{Corbera2016}.
+		The methods shown here could also be extended to aid other processes in the production of IPCC reports, such as the identification of potential authors to achieve a better balance across sectors and regions \cite{Corbera2016}.
 The possible benefits or risks of using data science methods for IPCC processes constitutes an important area for future research.
@@
 
+		\section*{Methods}
+
+		\subsection*{Data}
+
+		This study reproduces the query developed by Grieneisen and Zhang \cite{Grieneisen2011}, which is carried out on the Web of Science core collection.
+We downloaded the results of the query on March 19, 2019.
+Though not exhaustive, the Web of Science gives a good coverage of the literature in major peer-reviewed journals.
+The Web of Science data gives us a disciplinary classification (based on the journal) and publication year, among other metadata, for each document.	Each document is assigned to an assessment period according to the timeline shown in table 1.
+
+		We also tested the query documented in \cite{Haunschild2016}, by checking a random sample of documents exclusive to it.
+We found that the majority of additional documents were not relevant, and decided to use only the query from \cite{Grieneisen2011}.
+
+		We use the references scraped from IPCC assessment reports from Minx et al.
+\cite{Minx2017l}, and attempt to match these with the results from the Web of Science.
+We use doc2vec similarity scores \cite{Le2014} to identify the 500 most similar titles for each reference, and count the document as a match if the jaccard similarity score of the two word shingles of the reference title and the document title is greater than 0.5 \cite{Khabsa2014}.
+Extended Data Table \ref{ipcc-matching} shows the percentage of IPCC citations matched in each working group for each assessment report.
+This is significantly lower in earlier periods, as data coverage and quality of citation databases is lower for earlier periods.
+Matching in WG III is also lower, suggesting a greater share of non-peer review literature, or literature not directly mentioning climate change, but related to its mitigation (for example on energy policy).
+
+		We analysed by hand a sample of 100 IPCC references which could not be matched and found that 46\% of these references were not in the Web of Science at all, 53\% were in the Web of Science but not in our query, and 1 document was in our query but had mistakenly been identified as not being so.
+This was due a different version of the title appearing in the IPCC citation and the Web of Science record.
+
+		\begin{table}[htp]
+			\begin{center}
+				\input{../tables/ipcc_matching.tex}
+				\caption{The proportion of citations in each report that could be matched with a document in our query from the Web of Science}
+				\label{ipcc-matching}
+			\end{center}
+		\end{table}
+
+		\subsection*{Pre-processing}
+
+		Data quality in earlier Web of Science results is poorer, and some documents have missing abstracts.
+In the quantification of the size of the literature and its vocabulary in table \ref{tab}, titles are substituted for abstracts where they are not available.
+The words of the documents are lemmatized, replacing different forms of the same word (i.e.
+word/words) with a single instance.
+Commonly occurring words, or ``stopwords'' are removed, as are all words shorter than 3 characters, and all words containing only punctuation or numbers.
+
+		The documents are transformed into a document-term matrix, where each row represents a document, and each column represents a unique word.
+Each cell contains the number of that column's terms in that document.
+Only terms which occur more than once are considered.
+
+		For the calculation of the topic model, documents with missing abstracts are ignored, and the document term matrix is transformed into a document
+		frequency-inverse document frequency (tf-idf) matrix, where scores are scaled according to the frequency of their occurrence in the corpus.
+This gives more weight to terms which appear in few documents, and less weight to those which appear in many.
+
+		\begin{equation}
+		tf(t,d) = f_{t,d} \mathrm{,}\quad idf(t,D) = \log\frac{N}{|\{d \in D:t \in d\}|}
+		\end{equation}
+
+		\subsection*{Topic Model}
+
+		We use non-negative Matrix Factorisation (NMF) \cite{Lee1999}, an approach to topic modelling which factorises the term-frequency-inverse document frequency matrix \( V \) into the matrices \(W\), the topic-term matrix, and \( H \) the document-topic matrix, whose product approximates \(V\):
+
+		\begin{equation}
+		V_{i\mu} \approx (WH)_{i\mu} = \sum_{a=1}^{r}W_{ia}H_{a\mu}
+		\end{equation}
+
+		As demonstrated in Extended Data Figure \ref{doc-topic}, each topic is represented as a set of word scores, and each document a set of topic scores.
+The combination of the two approach the word scores in the document.
+For clarity in the figure, these are shown as simple counts, but in the model these are scaled according to each term's frequency within the corpus as explained above.
+
+		Topics are calculated using the scikitlearn library \cite{Pedregosa2011}, and are saved in a database and topic visualisation system based on that developed by Chaney and Blei \cite{Chaney2012}.
+The system adds new functionality to and combines it with a system for managing sets of documents and queries.
+The code and additional information is published online at \url{https://github.com/mcallaghan/tmv}.
+
+		\subsubsection*{Model selection}
+
+		Topic models are calculated for 70, 80, 90, 100, 110, 120, 130, 140 and 150 topics.
+The run with 150 topics was discarded as it contained a topic to which no terms or documents were assigned.
+The relative usefulness of each model was assessed subjectively by the authors, based on inspection of the online visualisation tool, and the spreadsheet \textbf{topic\_comparison.xlsx} accompanying the supporting information.
+The spreadsheet shows each set of topics in adjacent columns.
+Topics from each model are placed next to the topics with the largest number of each topic's 10 highest scoring words in common.
+This helps authors to find an appropriate level of granularity for the analysis.
+Statistical methods for the selection of topic model parameters are available but they do not necessarily align with human perceptions of topic model quality \cite{Chang2009}.
+We make a judgement based on subjective criteria, but for transparency publish the results of the analysis for different numbers of topics in Extended Data Figure \ref{top-rep-ks}.
+The main conclusions drawn about the rapid growth and under-representation of solutions-relevant topics are stable across models.
+
+		\subsubsection*{Topic assignment to working groups}
+		\label{topic-wg}
+		A topic's score for each working group is calculated by summing the document-topic scores for all documents cited by that working group.
+We call the topic's primary working group that working group for which the above sum is the highest, but in some cases, where there are very few IPCC citations of documents related to a topic this can be misleading .
+For example, the word ``capacity" is relevant to the adsorption topic, so documents talking about adaptive capacity receive a low score for the topic.
+Because only very few documents highly relevant to the topic (in that they talk about adsorption or adsorptive capacity) are cited by the IPCC, and many of the weakly relevant documents are cited by the IPCC, the sum of the topic scores of the weakly relevant documents outweighs the sum of the topic scores of the strongly relevant documents, meaning that the topic is mistakenly assigned to working group II when it is more properly relevant to working group III.
+We point out that topics are in any case mixtures of documents cited by different working groups, and stress that the colouring of the topics by working group is merely illustrative.
+
+		\subsubsection*{Topic Representation and Newness}
+
+		To calculate topic representation in IPCC reports we divide each topic's share in the subsample of documents cited by IPCC reports by its share in the whole corpus (excluding documents published after the last assessment report).
+Disciplinary representation is calculated in the same way.
+
+		We calculate a topic's total score as the sum of document-topic scores.
+A topic's window score is the sum of document-topic scores considering only documents in the given time window.
+To represent a topic's newness, we multiply each assessment period number by the share of it's total score occurring in that window, and take the mean of these scores.
+A topic in which 100\% of documents which make it up occurred in assessment period 1 (6) would thereby receive a score of 1 (6), while a topic evenly distributed across all assessment periods would receive a score of 3.5.
+
+		\subsubsection*{Disciplinary Entropy}
+
+		Disciplinary Entropy inverts the measurement of a conference's topical diversity suggested in \cite{Hall2008}, by measuring a topic \(z\)'s entropy \(H\), where
+
+		\begin{equation}
+		H(f|z) = -\sum_{i=1}^K \hat{p}(f|z) \log \hat{p}(f|z) 
+		\end{equation}
+
+		based on the empirical distribution of a field \(f\) in the documents \(d\) in each topic:
+
+		\begin{equation}
+		\hat{p}(f|z) = \sum_{d:z_d=z} \hat{p} (f|d) \hat{p} (d|z)
+		\end{equation}
+
+		It is an indication of the diversity of disciplines within the set of documents related to a topic.
+
+		\subsubsection*{Topic Map}
+		The topic model gives us the location of each document in a 140 dimensional topic space, with each dimension corresponding to a that document's ``topic-ness'' in a given topic.
+t-Distributed Stochastic Neighbour Embedding (t-SNE) is a dimensionality reduction technique which we use to represent each document's topic scores in 2 dimensions \cite{vandermaaten2008}.
+Documents are placed on the map such that documents with similar combinations of topics are close together.
+
+		Datasets showing the documents considered, the topics, and the associations between topics and documents are are published alongside this piece \cite{Callaghan2019}
+
 	\end{linenumbers}
 
-	\appendix
+	\section*{Author Information}
+
+	\subsection*{Author Contribution Statement}
+	M.C. and J.M. designed the research. M.C. performed the analysis. M.C., J.M. and P.M.F analysed the results. M.C. wrote the manuscript with contributions from all authors.
+
+	\subsection*{Corresponding Author}
+	Correspondence to Max Callaghan
+
+	\section*{Acknowledgements}
+	Max Callaghan is supported by a PhD stipend from the Heinrich Böll Stiftung.
+Jan Minx acknowledges funding from the German Federal Ministry of Research and Education within the PEGASOS project (grant reference: 01LA1826A)
+
+	\section*{Data Availability}
+
+	Three datasets from this study are available at \url{https://doi.org/10.6084/m9.figshare.9009665}
+
+	\medskip\noindent
+	\texttt{docs.csv} contains a list of the documents considered in this study, along with basic metadata and their position on the map.
+For copyright reasons, the full metadata from Web of Science can not be published.
+To reproduce the analysis, it would be necessary to download the abstracts for the papers shown, either using the Web of Science IDs provided, or the query documented in \cite{Grieneisen2011}.
+
+	\medskip\noindent
+	\texttt{topics.csv} Contains a list of the topics, along with their features discussed in this paper. The top 10 words associated with each topic are also shown
+
+	\medskip\noindent
+	\texttt{doctopics.csv} Contains a list of document-topic scores, which can be cross-referenced with the document and topic ids in \texttt{docs.csv} and \texttt{topics.csv}.
+
+	\medskip\noindent
+	\texttt{topic\_comparison.xlsx} shows models with different numbers of topics. It was used to select the topic model used for analysis in this paper.
+
+	\section*{Code Availability}
+
+	The code used to produce this paper is available at https://github.com/mcallaghan/cc-topography
+
+	\section*{Ethics Declarations}
+
+	\subsection*{Competing Interests}
+	The authors declare no competing interests.
 
@@
 
-	\bibliographystyle{unsrt}
+	\bibliographystyle{natunsrt}
 

### 2019-12-13 pres/2019_11_dzhw.tex
final submission ready

\documentclass[9pt, aspectratio=169]{beamer}
\mode<presentation>
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{tikz}
\usepackage{pgfplots}
\usetikzlibrary{spy,calc}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{appendixnumberbeamer}

\usepackage{tcolorbox}

\usetheme{Boadilla}

\definecolor{mcctext}{HTML}{0d77b0}
\definecolor{mcclogo}{HTML}{0067a1}
\definecolor{mcclight}{HTML}{D9E8F1}

\usecolortheme[named=mcclogo]{structure}

\usefonttheme{professionalfonts}

\title[Big Literature]{A Topography of Climate Change Research}
\subtitle{}
\author{Max Callaghan }
\institute[MCC]{
	{\footnotesize with Jan Minx, Piers Forster} \\ \medskip
	\includegraphics[height=1cm,width=2cm]{MCC_Logo_RZ_rgb.jpg} \hspace{3em}
	\includegraphics[height=1cm]{University-of-Leeds-logo.png}
}
\date{September 26, 2019}

\newtheorem*{remark}{}

\bibliographystyle{apalike}

\newif\ifblackandwhitecycle
\gdef\patternnumber{0}

\pgfkeys{/tikz/.cd,
	zoombox paths/.style={
		draw=orange,
		very thick
	},
	black and white/.is choice,
	black and white/.default=static,
	black and white/static/.style={ 
		draw=white,   
		zoombox paths/.append style={
			draw=white,
			postaction={
				draw=black,
				loosely dashed
			}
		}
	},
	black and white/static/.code={
		\gdef\patternnumber{1}
	},
	black and white/cycle/.code={
		\blackandwhitecycletrue
		\gdef\patternnumber{1}
	},
	black and white pattern/.is choice,
	black and white pattern/0/.style={},
	black and white pattern/1/.style={    
		draw=white,
		postaction={
			draw=black,
			dash pattern=on 2pt off 2pt
		}
	},
	black and white pattern/2/.style={    
		draw=white,
		postaction={
			draw=black,
			dash pattern=on 4pt off 4pt
		}
	},
	black and white pattern/3/.style={    
		draw=white,
		postaction={
			draw=black,
			dash pattern=on 4pt off 4pt on 1pt off 4pt
		}
	},
	black and white pattern/4/.style={    
		draw=white,
		postaction={
			draw=black,
			dash pattern=on 4pt off 2pt on 2 pt off 2pt on 2 pt off 2pt
		}
	},
	zoomboxarray inner gap/.initial=5pt,
	zoomboxarray columns/.initial=2,
	zoomboxarray rows/.initial=2,
	subfigurename/.initial={},
	figurename/.initial={zoombox},
	zoomboxarray/.style={
		execute at begin picture={
			\begin{scope}[
				spy using outlines={%
					zoombox paths,
					width=\imagewidth / \pgfkeysvalueof{/tikz/zoomboxarray columns} - (\pgfkeysvalueof{/tikz/zoomboxarray columns} - 1) / \pgfkeysvalueof{/tikz/zoomboxarray columns} * \pgfkeysvalueof{/tikz/zoomboxarray inner gap} -\pgflinewidth,
					height=\imageheight / \pgfkeysvalueof{/tikz/zoomboxarray rows} - (\pgfkeysvalueof{/tikz/zoomboxarray rows} - 1) / \pgfkeysvalueof{/tikz/zoomboxarray rows} * \pgfkeysvalueof{/tikz/zoomboxarray inner gap}-\pgflinewidth,
					magnification=3,
					every spy on node/.style={
						zoombox paths
					},
					every spy in node/.style={
						zoombox paths
					}
				}
				]
			},
			execute at end picture={
			\end{scope}
			\node at (image.north) [anchor=north,inner sep=0pt] {\subcaptionbox{\label{\pgfkeysvalueof{/tikz/figurename}-image}}{\phantomimage}};
			\node at (zoomboxes container.north) [anchor=north,inner sep=0pt] {\subcaptionbox{\label{\pgfkeysvalueof{/tikz/figurename}-zoom}}{\phantomimage}};
			\gdef\patternnumber{0}
		},
		spymargin/.initial=0.5em,
		zoomboxes xshift/.initial=1,
		zoomboxes right/.code=\pgfkeys{/tikz/zoomboxes xshift=1},
		zoomboxes left/.code=\pgfkeys{/tikz/zoomboxes xshift=-1},
		zoomboxes yshift/.initial=0,
		zoomboxes above/.code={
			\pgfkeys{/tikz/zoomboxes yshift=1},
			\pgfkeys{/tikz/zoomboxes xshift=0}
		},
		zoomboxes below/.code={
			\pgfkeys{/tikz/zoomboxes yshift=-1},
			\pgfkeys{/tikz/zoomboxes xshift=0}
		},
		caption margin/.initial=4ex,
	},
	adjust caption spacing/.code={},
	image container/.style={
		inner sep=0pt,
		at=(image.north),
		anchor=north,
		adjust caption spacing
	},
	zoomboxes container/.style={
		inner sep=0pt,
		at=(image.north),
		anchor=north,
		name=zoomboxes container,
		xshift=\pgfkeysvalueof{/tikz/zoomboxes xshift}*(\imagewidth+\pgfkeysvalueof{/tikz/spymargin}),
		yshift=\pgfkeysvalueof{/tikz/zoomboxes yshift}*(\imageheight+\pgfkeysvalueof{/tikz/spymargin}+\pgfkeysvalueof{/tikz/caption margin}),
		adjust caption spacing
	},
	calculate dimensions/.code={
		\pgfpointdiff{\pgfpointanchor{image}{south west} }{\pgfpointanchor{image}{north east} }
		\pgfgetlastxy{\imagewidth}{\imageheight}
		\global\let\imagewidth=\imagewidth
		\global\let\imageheight=\imageheight
		\gdef\columncount{1}
		\gdef\rowcount{1}
		\gdef\zoomboxcount{1}
	},
	image node/.style={
		inner sep=0pt,
		name=image,
		anchor=south west,
		append after command={
			[calculate dimensions]
			node [image container,subfigurename=\pgfkeysvalueof{/tikz/figurename}-image] {\phantomimage}
			node [zoomboxes container,subfigurename=\pgfkeysvalueof{/tikz/figurename}-zoom] {\phantomimage}
		}
	},
	color code/.style={
		zoombox paths/.append style={draw=#1}
	},
	connect zoomboxes/.style={
		spy connection path={\draw[draw=none,zoombox paths] (tikzspyonnode) -- (tikzspyinnode);}
	},
	help grid code/.code={
		\begin{scope}[
			x={(image.south east)},
			y={(image.north west)},
			font=\footnotesize,
			help lines,
			overlay
			]
			\foreach \x in {0,1,...,9} { 
				\draw(\x/10,0) -- (\x/10,1);
				\node [anchor=north] at (\x/10,0) {0.\x};
			}
			\foreach \y in {0,1,...,9} {
				\draw(0,\y/10) -- (1,\y/10);                        \node [anchor=east] at (0,\y/10) {0.\y};
			}
		\end{scope}    
	},
	help grid/.style={
		append after command={
			[help grid code]
		}
	},
}

\newcommand\phantomimage{%
	\phantom{%
		\rule{\imagewidth}{\imageheight}%
	}%
}
\newcommand\zoombox[2][]{
	\begin{scope}[zoombox paths]
		\pgfmathsetmacro\xpos{
			(\columncount-1)*(\imagewidth / \pgfkeysvalueof{/tikz/zoomboxarray columns} + \pgfkeysvalueof{/tikz/zoomboxarray inner gap} / \pgfkeysvalueof{/tikz/zoomboxarray columns} ) + \pgflinewidth
		}
		\pgfmathsetmacro\ypos{
			(\rowcount-1)*( \imageheight / \pgfkeysvalueof{/tikz/zoomboxarray rows} + \pgfkeysvalueof{/tikz/zoomboxarray inner gap} / \pgfkeysvalueof{/tikz/zoomboxarray rows} ) + 0.5*\pgflinewidth
		}
		\edef\dospy{\noexpand\spy [
			#1,
			zoombox paths/.append style={
				black and white pattern=\patternnumber
			},
			every spy on node/.append style={#1},
			x=\imagewidth,
			y=\imageheight
			] on (#2) in node [anchor=north west] at ($(zoomboxes container.north west)+(\xpos pt,-\ypos pt)$);}
		\dospy
		\pgfmathtruncatemacro\pgfmathresult{ifthenelse(\columncount==\pgfkeysvalueof{/tikz/zoomboxarray columns},\rowcount+1,\rowcount)}
		\global\let\rowcount=\pgfmathresult
		\pgfmathtruncatemacro\pgfmathresult{ifthenelse(\columncount==\pgfkeysvalueof{/tikz/zoomboxarray columns},1,\columncount+1)}
		\global\let\columncount=\pgfmathresult
		\ifblackandwhitecycle
		\pgfmathtruncatemacro{\newpatternnumber}{\patternnumber+1}
		\global\edef\patternnumber{\newpatternnumber}
		\fi
	\end{scope}
}

\begin{document}

\begin{frame}
	\titlepage
\end{frame}

\addtobeamertemplate{frametitle}{}{
	\begin{tikzpicture}[remember picture,overlay]
	\node[anchor=north east,yshift=2pt] at (current page.north east) {\includegraphics[height=0.6cm]{MCC_Logo_RZ_rgb.jpg}};
	\end{tikzpicture}}

\begin{frame}{Introduction}
\begin{columns}[T]
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{figure}
				\includegraphics[width=1\linewidth]{../plots/Hondius_Portrait_of_map-makers}
				\caption{Portrait of map-makers, Gerardus Mercator and Jodocus Hondius (Jodocus Hondius) source: Wikipedia Commons}
			\end{figure}
		\end{center}
	\end{column}
	\begin{column}{0.6\linewidth}
		%\begin{minipage}{0.9\linewidth}
			\begin{columns}[t]
				\begin{column}{0.45\linewidth}<2->
					\begin{figure}
						\includegraphics[width=0.6\linewidth]{syrcover}
					\end{figure}
				\end{column}
				\begin{column}{0.45\linewidth}<2->
					\begin{itemize}
						\item<2-> The IPCC has a \textit{cartographic} role at the science policy interface \citep{Edenhofer2014, Edenhofer2015}
						\item<3-> It is much studied in STS \citep{Hulme2010}
					\end{itemize}
				\end{column}
			\end{columns}
		%\end{minipage}
		\bigskip
		\begin{center}
			\begin{itemize}
				\item<4-> A topography is a description of a landscape
				\item<5-> Topics (from the Greek ``topos'', place) can describe the features of a body of text
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}
\end{frame}

\begin{frame}{Outline}
\tableofcontents
\end{frame}

\section{Motivation}
\frame{\tableofcontents[currentsection]}

\begin{frame}{Context - Big Literature}
\begin{columns}
	\begin{column}{0.618\linewidth} % Golden ratio columns
		\begin{figure}
			\includegraphics[width=\linewidth]{../plots/literature_size/pubs_time_wgb_lp.pdf}
			\caption{Articles on climate change in the Web of Science}
		\end{figure}
	\end{column}
	\begin{column}{0.382\linewidth}
		A challenge for
		\begin{itemize}
			\item Global environmental assessments
			\item Our understanding of global environmental assessments
			\item Evidence synthesis more generally
		\end{itemize}
	\end{column}
\end{columns}
\end{frame}

\begin{frame}{The IPCC in the age of Big Literature}

\begin{columns}
	\begin{column}{0.382\linewidth}
		\begin{itemize}
			\item<1->We entrust the IPCC with providing a \textit{comprehensive} and \textit{transparent} assessment of the literature 
			\item<2->Although IPCC reports cite ever greater numbers of papers, this number decreases in proportion to the number of papers in literature

		\end{itemize}
	\end{column}
	\begin{column}{0.618\linewidth}<2->
		\begin{figure}
			\includegraphics[width=\linewidth]{wos_IPCC_shares.png}
			\caption{\citep{Minx2017l}}
		\end{figure}
	\end{column}
\end{columns}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{What Do We Know About the IPCC?}
\begin{columns}
	\begin{column}{0.618\linewidth}
		\begin{itemize}
			\item<2-> The social sciences are seen as under-represented in IPCC reports
			\item<3-> \citep{Bjurström2011} are often cited as evidence of this under-representation, e.g. as demonstrating ``a powerful bias to the natural sicences in the construction of `IPCC knowledge' '' \cite{Hulme2010}
			\item<4-> The evidence is simply the relative shares of the different disciplines in IPCC citations

		\end{itemize}
	\end{column}
	\begin{column}{0.382\linewidth}<2->
		\begin{figure}[h!]
			\begin{center}
				\includegraphics[width=0.85\linewidth]{../plots/victor.png}
				\caption{\citep{Victor2015}}
			\end{center}
		\end{figure}
	\end{column}
\end{columns}
\end{frame}

\begin{frame}{The Age of Climate Solutions? }
\begin{columns}

	\begin{column}{0.618\linewidth}<1->
		\begin{figure}[h!]
			\begin{center}
				\includegraphics[width=\linewidth]{../plots/kowarsch-solutions.png}
				\caption{\citep{Kowarsch2017}}
			\end{center}
		\end{figure}

	\end{column}
	\begin{column}{0.382\linewidth}
		\begin{itemize}
			\item<1-> Demand for solutions is increasing
			\item<2-> We know little about the supply of solutions in the literature

		\end{itemize}
	\end{column}
\end{columns}
\end{frame}

\section{Methods}
\frame{\tableofcontents[currentsection]}

\begin{frame}{Investigating bibliometric and text data}

To understand the representation of social science and solutions relevant knowledge in IPCC reports, we look at journal classification and document abstracts

\bigskip

\textbf{Data:}

400,000 papers on climate change from the Web of Science (query following \cite{Grieneisen2011}), matched with 70,000 IPCC citations (Using Doc2Vec)

\bigskip

\textbf{Topic modelling:}

We use topic modelling (with NMF \citep{Lee1999}) to understand the thematic content of papers

\bigskip

\textbf{Topographic mapping:}

We project the documents' topical locations into 2 dimensions using t-SNE \citep{vandermaaten2008}

\bigskip

\textbf{Measuring representation:}

We compare the proportions of categories of documents in the whole of the literature with the subset of the literature that is cited by the IPCC

\end{frame}

\begin{frame}{Words, words, words}

\begin{table}[h]
	\begin{adjustbox}{width=0.8\linewidth}
		\input{../tables/growth_table.tex}
	\end{adjustbox}			
	\caption{Growth in climate change literature}
	\label{growthtable}
\end{table}

%		\begin{itemize}
%			\item bla
%			
%		\end{itemize}

Data from WoS Core Collection, query following \citet{Grieneisen2011}

\end{frame}

\begin{frame}{Approach - What is the matter?}

\begin{columns}
	\begin{column}{0.382\linewidth}
		\begin{itemize}
			\item<1-> Topic modelling \citep{Blei2012} describes a suite of algorithms to discover the latent semantic content of documents
			\item<2-> NMF \citep{Lee1999} is a dimensionality reduction technique that can be used for topic modelling
			\item<3-> Topics are distributions of words. They describe documents.
			\item<4-> A document's topic scores describe its association with each topic

		\end{itemize}
	\end{column}
	\begin{column}{0.618\linewidth}<2->
		\only<2->{\(V_{i\mu} \) is a term frequency-inverse document frequency matrix of \textit{stemmed} terms} 
		\only<2->{\[V_{i\mu} \approx (WH)_{i\mu} = \sum_{a=1}^{r}W_{ia}H_{a\mu} \] \(V\) is approximated by the product of \(W\) and \(H\)}

		\begin{figure}
			\includegraphics[width=\linewidth]{../plots/VWH.png}
		\end{figure}
	\end{column}

\end{columns}

\end{frame}

\begin{frame}{Doc Topic Example}
\begin{figure}
	\includegraphics[width=0.8\linewidth]{../plots/single_doc_3_536594.pdf}
\end{figure}

\end{frame}

\section{Results}
\frame{\tableofcontents[currentsection]}

\begin{frame}[plain]{A Topography of Climate Change Literature}

\vspace{-0.5cm}

\begin{columns}
	\begin{column}{0.6\linewidth}<1->
		\begin{center}
			%\hspace{-1.3cm}
			\includegraphics[width=0.9\linewidth]{../tsne_results/plots/run_1861_s_0_p100_all_topic_words_oecds_lp.png}
		\end{center}

	\end{column}

	\begin{column}{0.4\linewidth}
		\begin{itemize}
			\item<1-> We use t-distributed stochastic neighbour embedding \citep{vandermaaten2008}
			to reduce documents' topic vectors to 2 dimensions  
			\item<2-> Each dot is a document, and documents with similar topic vectors are close together in the 2-dimensional space
			\item<3-> We can see the preponderance of natural sciences, and the greater or lesser clustering of disciplines in certain topic areas

		\end{itemize}
	\end{column}
\end{columns}

\end{frame}

\begin{frame}

\begin{figure}\centering
	\begin{tikzpicture}[zoomboxarray]
	\node [image node] { \includegraphics[width=0.45\textwidth]{../tsne_results/plots/run_1861_s_0_p100_all_topic_words_oecds_lp.png} };
	\zoombox[magnification=2.5]{0.35,0.7}
	\zoombox[magnification=2]{0.65,0.65}
	\zoombox[magnification=3]{0.15,0.4}
	\zoombox[magnification=3]{0.85,0.5}
	\end{tikzpicture}
\end{figure}

\end{frame}

\begin{frame}{The Social Sciences are No Longer Under-Represented in IPCC reports}
\begin{columns}

	\begin{column}{0.382\linewidth}
		\begin{itemize}
			\item<1-> The social sciences were under-represented in AR3, but by AR5 are over-represented
			\item<2-> The share of natural science documents in IPCC citations is similar to the share in the wider literature
			\item<3-> Agricultural sciences and engineering \& technology are under-represented		
		\end{itemize}
	\end{column}

	\begin{column}{0.618\linewidth}<1->
		\begin{figure}[h!]
			\begin{center}
				\includegraphics[width=\linewidth]{../plots_pub/ipcc_rep_oecds_simplified_lp.pdf}
			\end{center}
		\end{figure}
	\end{column}
\end{columns}
\end{frame}

\begin{frame}{Topics on solutions are newer and under-represented}

\vspace{-0.5cm}

\begin{columns}

	\begin{column}{0.618\linewidth}<1->
		\begin{figure}[h!]
			\begin{center}
				\includegraphics[width=\linewidth]{../plots_pub/rep_time_lp.pdf}
			\end{center}
		\end{figure}

	\end{column}
	\begin{column}{0.382\linewidth}
		\begin{itemize}
			\item<1-> The physical science of climate change is older and better covered
			\item<2-> Topics on ``solutions'' (although rather technical than policy) are newer and under-represented
			\item<3-> Newer WGII topics are better covered than newer WGIII topics

		\end{itemize}
	\end{column}
\end{columns}
\end{frame}

\begin{frame}{Topics on solutions are newer and under-represented}

\vspace{-0.5cm}

\begin{columns}

	\begin{column}{0.618\linewidth}<1->
		\begin{figure}[h!]
			\begin{center}
				\includegraphics[width=\linewidth]{../plots/run_1861_wg3_socsci.pdf}
			\end{center}
		\end{figure}

	\end{column}
	\begin{column}{0.382\linewidth}
		\begin{itemize}
			\item<1-> Technical solutions topics in WGIII contain little social science research and are under-represented

		\end{itemize}
	\end{column}
\end{columns}
\end{frame}

\begin{frame}{Conclusions}
\begin{columns}[t]
	\begin{column}{0.618\linewidth}
		\begin{itemize}
			\item<1-> Lack of social science knowledge in IPCC $ \neq $ IPCC natural science bias
			\item<2-> If there is a lack, we need to produce more social science knowledge, particularly on technical solutions
			\item<3-> There is a vast technical literature on solutions which is relatively untapped
		\end{itemize}
	\end{column}
	\begin{column}{0.382\linewidth}<4->
		\textbf{But,}
		\begin{itemize}
			\item<4-> Literature here is not all relevant climate knowledge (only WoS, only directly on climate change)
			\item<5-> Relative representation of different parts of the literature is job of IPCC to decide, not a computer
		\end{itemize}
		\only<6->{\textbf{Nevertheless,}}
		\begin{itemize}
			\item<6-> Computer assisted methods can help the IPCC make its decisions on how to represent the literature from a more solid basis, and efficiently point to areas of growth or of under-representation
		\end{itemize}
	\end{column}
\end{columns}
\end{frame}

\begin{frame}{Bibliography}
\scriptsize
\bibliography{../manuscript/Mendeley}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix

\begin{frame}{n Topics}
\vspace{-0.4cm}
\begin{figure}
	\includegraphics[width=1\linewidth]{../plots_pub/topic_rep_ks_wide.pdf}
\end{figure}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

\end{document}

### 2019-12-24 manuscript/abstract.tex

--- 2019-08-21 manuscript/abstract.tex
@@
 \begin{document}
-   The massive expansion of scientific literature on climate change poses challenges for global environmental assessments and how we
-understand them. 
-Big data and machine learning can help us deal 
-with the large collections of text represented by scientific fields.
-Such methods help make the production of assessments
-more tractable, and give us better insights about how past assessments  have engaged with the literature as it has evolved.
-We use topic modelling to identify the thematic structure and draw a comprehensive topic map, or topography, of over 400,000 scientific publications from the Web of Science on climate change. 
-We update current knowledge on the IPCC, showing that the social sciences are in fact over-represented in recent assessment reports, and that
-technical, solutions-relevant knowledge - especially in the agricultural and engineering sciences - are under-represented.
-We point to a variety of other applications of such maps, and our findings have direct implications for addressing growing demands for more solution-oriented climate change assessments that are also more firmly rooted in the social sciences.
+	The massive expansion of scientific literature on climate change \cite{Minx2017l} poses challenges for global environmental assessments and our understanding of how these assessments work. 
+	Big data and machine learning can help us deal with large collections of scientific text, making the production of assessments
+	more tractable, and giving us better insights about how past assessments  have engaged with the literature.
+	We use topic modelling to draw a topic map, or topography, of over 400,000 publications from the Web of Science (WoS) on climate change. 
+	We update current knowledge on the Intergovernmental Panel on Climate Change (IPCC), showing that, when compared to the baseline of the literature identified,  the social sciences are in fact over-represented in recent assessment reports.
+Technical, solutions-relevant knowledge - especially in agriculture and engineering - is under-represented.
+	We suggest a variety of other applications of such maps, and our findings have direct implications for addressing growing demands for more solution-oriented climate change assessments that are also more firmly rooted in the social sciences \cite{Kowarsch2017, Victor2015}.
+	The perceived lack of social science knowledge in assessment reports does not necessarily imply a IPCC bias, but rather suggests a need for more social science research with a focus on ``technical'' topics on climate solutions.
 \end{document}

### 2019-12-24 manuscript/extended_figures.tex

--- 2019-10-02 manuscript/methods.tex
@@
 	\maketitle
-	\begin{linenumbers}
-
-		\section*{Methods}
-
-					\setcounter{table}{0}
-		\renewcommand\thetable{SI.\arabic{table}}
-
-		\subsection*{Data}
-
-		This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on the Web of Science core collection.
-We downloaded the results of the query on March 19, 2019.
-Though not exhaustive, the Web of Science gives a good coverage of the literature in major peer-reviewed journals.
-The Web of Science data gives us a disciplinary classification (based on the journal) and publication year, among other metadata, for each document.	Each document is assigned to an assessment period according to the timeline shown in table 1.
-
-		We also tested the query documented in \cite{Haunschild2016}, by checking a random sample of documents exclusive to it.
-We found that the majority of additional documents were not relevant, and decided to use only the query from \cite{Grieneisen2011}.
-
-		We use the references scraped from IPCC assessment reports from \citep{Minx2017l}, and attempt to match these with the results from the Web of Science.
-We use doc2vec similarity scores \cite{Le2014} to identify the 500 most similar titles for each reference, and count the document as a match if the jaccard similarity score of the two word shingles of the reference title and the document title is greater than 0.5 \cite{Khabsa2014}.
-Table \ref{ipcc-matching} shows the percentage of IPCC citations matched in each working group for each assessment report.
-This is significantly lower in earlier periods, as data coverage and quality of citation databases is lower for earlier periods.
-Matching in WG III is also lower, suggesting a greater share of non-peer review literature, or literature not directly mentioning climate change, but related to its mitigation (for example on energy policy).
-
-		We analysed by hand a sample of 100 IPCC references which could not be matched and found that 46\% of these references were not in the Web of Science at all, 53\% were in the Web of Science but not in our query, and 1 document was in our query but had mistakenly been identified as not being so.
-This was due a different version of the title appearing in the IPCC citation and the Web of Science record.
-
-		\begin{table}[htp]
-			\begin{center}
-				\input{../tables/ipcc_matching.tex}
-				\caption{The proportion of citations in each report that could be matched with a document in our query from the Web of Science}
-				\label{ipcc-matching}
-			\end{center}
-		\end{table}
-
-		\subsection*{Pre-processing}
-
-		Data quality in earlier Web of Science results is poorer, and some documents have missing abstracts.
-In the quantification of the size of the literature and its vocabulary in table \ref{tab}, titles are substituted for abstracts where they are not available.
-The words of the documents are lemmatized, replacing different forms of the same word (i.e.
-word/words) with a single instance.
-Commonly occurring words, or ``stopwords'' are removed, as are all words shorter than 3 characters, and all words containing only punctuation or numbers.
-
-		The documents are transformed into a document-term matrix, where each row represents a document, and each column represents a unique word.
-Each cell contains the number of that column's terms in that document.
-Only terms which occur more than once are considered.
-
-		For the calculation of the topic model, documents with missing abstracts are ignored, and the document term matrix is transformed into a document
-		frequency-inverse document frequency (tf-idf) matrix, where scores are scaled according to the frequency of their occurrence in the corpus.
-This gives more weight to terms which appear in few documents, and less weight to those which appear in many.
-
-		\begin{equation}
-		tf(t,d) = f_{t,d} \mathrm{,}\quad idf(t,D) = \log\frac{N}{|\{d \in D:t \in d\}|}
-		\end{equation}
-
-		\subsection*{Topic Model}
-
-		We use non-negative Matrix Factorisation (NMF) \cite{Lee1999}, an approach to topic modelling which factorises the term-frequency-inverse document frequency matrix \( V \) into the matrices \(W\), the topic-term matrix, and \( H \) the document-topic matrix, whose product approximates \(V\):
-
-		\begin{equation}
-		V_{i\mu} \approx (WH)_{i\mu} = \sum_{a=1}^{r}W_{ia}H_{a\mu}
-		\end{equation}
-
-		As demonstrated in Figure \ref{doc-topic}, each topic is represented as a set of word scores, and each document a set of topic scores.
-The combination of the two approach the word scores in the document.
-For clarity in the figure, these are shown as simple counts, but in the model these are scaled according to each term's frequency within the corpus as explained above.
-
-		Topics are calculated using the scikitlearn library \cite{Pedregosa2011}, and are saved in a database and topic visualisation system based on \cite{Chaney2012} \footnote{The system adds new functionality to \cite{Chaney2012} and combines it with a system for managing sets of documents and queries.
-The code and additional information is published online at \url{https://github.com/mcallaghan/tmv}}.
-
-		\subsubsection*{Model selection}
-
-		Topic models are calculated for 70, 80, 90, 100, 110, 120, 130, 140 and 150 topics.
-The run with 150 topics was discarded as it contained a topic to which no terms or documents were assigned.
-The relative usefulness of each model was assessed subjectively by the authors, based on inspection of the online visualisation tool, and the spreadsheet \textbf{topic\_comparison.xlsx} accompanying the supporting information.
-The spreadsheet shows each set of topics in adjacent columns.
-Topics from each model are placed next to the topics with the largest number of each topic's 10 highest scoring words in common.
-This helps authors to find an appropriate level of granularity for the analysis.
-Statistical methods for the selection of topic model parameters are available but they do not necessarily align with human perceptions of topic model quality \cite{Chang2009}.
-We make a judgement based on subjective criteria, but for transparency publish the results of the analysis for different numbers of topics in figure \ref{top-rep-ks}.
-The main conclusions drawn about the rapid growth and under-representation of solutions-relevant topics are stable across models.
-
-		\subsubsection*{Topic assignment to working groups}
-		\label{topic-wg}
-		A topic's score for each working group is calculated by summing the document-topic scores for all documents cited by that working group.
-We call the topic's primary working group that working group for which the above sum is the highest, but in some cases, where there are very few IPCC citations of documents related to a topic this can be misleading .
-For example, the word ``capacity" is relevant to the adsorption topic, so documents talking about adaptive capacity receive a low score for the topic.
-Because only very few documents highly relevant to the topic (in that they talk about adsorption or adsorptive capacity) are cited by the IPCC, and many of the weakly relevant documents are cited by the IPCC, the sum of the topic scores of the weakly relevant documents outweighs the sum of the topic scores of the strongly relevant documents, meaning that the topic is mistakenly assigned to working group II when it is more properly relevant to working group III.
-We point out that topics are in any case mixtures of documents cited by different working groups, and stress that the colouring of the topics by working group is merely illustrative.
-
-		\subsubsection*{Topic Representation and Newness}
-
-		To calculate topic representation in IPCC reports we divide each topic's share in the subsample of documents cited by IPCC reports by its share in the whole corpus (excluding documents published after the last assessment report).
-Disciplinary representation is calculated in the same way.
-
-		We calculate a topic's total score as the sum of document-topic scores.
-A topic's window score is the sum of document-topic scores considering only documents in the given time window.
-To represent a topic's newness, we multiply each assessment period number by the share of it's total score occurring in that window, and take the mean of these scores.
-A topic in which 100\% of documents which make it up occurred in assessment period 1 (6) would thereby receive a score of 1 (6), while a topic evenly distributed across all assessment periods would receive a score of 3.5.
-
-		\subsubsection*{Disciplinary Entropy}
-
-		Disciplinary Entropy inverts the measurement of a conference's topical diversity suggested in \cite{Hall2008}, by measuring a topic \(z\)'s entropy \(H\), where
-
-		\begin{equation}
-		H(f|z) = -\sum_{i=1}^K \hat{p}(f|z) \log \hat{p}(f|z) 
-		\end{equation}
-
-		based on the empirical distribution of a field \(f\) in the documents \(d\) in each topic:
-
-		\begin{equation}
-		\hat{p}(f|z) = \sum_{d:z_d=z} \hat{p} (f|d) \hat{p} (d|z)
-		\end{equation}
-
-		It is an indication of the diversity of disciplines within the set of documents related to a topic.
-
-		\subsubsection*{Topic Map}
-		The topic model gives us the location of each document in a 140 dimensional topic space, with each dimension corresponding to a that document's \textit{topic-ness} in a given topic.
-t-Distributed Stochastic Neighbour Embedding (t-SNE) is a dimensionality reduction technique which we use to represent each document's topic scores in 2 dimensions \cite{vandermaaten2008}.
-Documents are placed on the map such that documents with similar combinations of topics are close together.
-
-		\subsection*{Glossary}
-
-		\noindent\textbf{co2:} Carbon Dioxide
-
-		\noindent\textbf{ncep:} National Centers for Environmental Protection
-
-		\noindent\textbf{fco:} Fugacity of Carbon Dioxide
-
-		\noindent\textbf{pfc:} Perflourocompound
-
-		\noindent\textbf{otcs:} Open Top Chambers
-
-		\noindent\textbf{dtr:} Diurnal Temperature Range
-
-		\noindent\textbf{sres:} Special Report on Emissions Scenarios (200)
-
-		\noindent\textbf{petm:} Paleocene Eocene Thermal Maximum
-
-		\noindent\textbf{amf:}  Arbuscular Mycorrhizal Fungal
-
-		\noindent\textbf{sf5cf3:} trifluoromethyl sulfur pentafluoride (A Potent Greenhouse Gas Identified in the Atmosphere, 2000)
-
-		\noindent\textbf{clc:} Chemical Looping Combustion
-
-		\noindent\textbf{cwd:} Coarse woody debris
-
-		\noindent\textbf{etm:} Enhanced Thematic Mapper (NASA satellite sensor)
-
-		\noindent\textbf{cmip5:} Coupled Model Intercomparison Project 5 (Starting 2008)
-
-		\noindent\textbf{cmip3:} Coupled Model Intercomparison Project phase 3 (first published 2007 \cite{Meehl2007})
-
-		\noindent\textbf{mofs:} metal-organic frameworks (for CO2 storage)
-
-		\noindent\textbf{sdm:} statistical-dynamical model
-
-		\noindent\textbf{mmms:} Mixed Matrix Membranes (for CO2 capture)
-
-		\noindent\textbf{cop21:} 21st Conference of Parties (Paris 2015)
-
-		\noindent\textbf{c3n4:} Carbon nitride (a synthetic nanomaterial used for hydrogen production)
-
-		\noindent\textbf{sdg:} Sustainable Development Goals
-
-		\noindent\textbf{(i)ndc:} (Intended) Nationally Determined Contributions
-
-	\end{linenumbers}
-
-	\linespread{1}
-
-	\section*{Supplementary Figures}
-
+	\section*{Extended Figures}
 			\setcounter{figure}{0}
-	\renewcommand\thefigure{SI.\arabic{figure}}
 
@@
 
-	\section*{Data Availability}
-
-	Three datasets from this study are available at \url{https://doi.org/10.6084/m9.figshare.9009665}
-
-	\medskip\noindent
-	\texttt{docs.csv} contains a list of the documents considered in this study, along with basic metadata and their position on the map.
-For copyright reasons, the full metadata from Web of Science can not be published.
-To reproduce the analysis, it would be necessary to download the abstracts for the papers shown, either using the Web of Science IDs provided, or the query documented in \cite{Grieneisen2011}.
-
-	\medskip\noindent
-	\texttt{topics.csv} Contains a list of the topics, along with their features discussed in this paper. The top 10 words associated with each topic are also shown
-
-	\medskip\noindent
-	\texttt{doctopics.csv} Contains a list of document-topic scores, which can be cross-referenced with the document and topic ids in \texttt{docs.csv} and \texttt{topics.csv}.
-
-	\medskip\noindent
-	\texttt{topic\_comparison.xlsx} shows models with different numbers of topics. It was used to select the topic model used for analysis in this paper.
-
-	\section*{Code Availability}
-
-	The code used to produce this paper is available at https://github.com/mcallaghan/cc-topography
-
-	\bibliography{Mendeley}
-	\bibliographystyle{unsrt}
-
 \end{document}

### 2020-01-31 manuscript/supplementary_information.tex
amld pres

--- 2019-10-14 manuscript/main.tex
@@
 \usepackage[a4paper, total={180mm, 260mm}]{geometry}
+\usepackage[english]{babel}
 \usepackage{graphicx}
 \usepackage{url}
-\usepackage{natbib}
-\usepackage{todonotes}
 \usepackage{booktabs}
@@
 \usepackage{color}
-%\usepackage{auto-pst-pdf}
-\usepackage[colaction]{multicol}
 \usepackage{caption}
-\usepackage{svg}
 \usepackage{authblk}
-\usepackage{standalone}
-\usepackage{xr}
-\externaldocument{methods}
-
-\usepackage[section]{placeins}
-
-\linespread{1.5}
 
@@
 % Title
-\title{A Topic Model of Climate Change Literature}
-\title{Words, words, words: Mapping the Matter of Climate Change Literature}
-\title{A Topography of Climate Change Research}
+\title{A Topography of Climate Change Research - Supplementary Information}
 \author[1,2]{Max Callaghan}
@@
 
-	\begin{linenumbers}
-
-		\noindent\textbf{\input{abstract.tex}}
-
-		\bigskip
-
-		\noindent We live in an age of ``Big Literature'' 
-		\cite{Nunez-Mir2016, Minx2017l}, where the science of climate change is expanding exponentially \cite{Grieneisen2011, Haunschild2016}.
-In the five years since the publication of the last IPCC assessment report \cite{IPCC2014c}, 202,000 papers on climate change were published in the Web of Science (WoS) (see Table \ref{tab}).
-This is almost as much as the 205,000 papers identified in the same query \cite{Grieneisen2011} during the first five assessment periods; a period of nearly 30 years.
-Around 350,000 new publications can be expected for before the sixth assessment report (AR6) of the Intergovernmental Panel on Climate Change (IPCC), based on current growth patterns (Figure \ref{pub-growth}).
-Moreover, from the expansion of the literature's vocabulary (see methods) - from 2,000 unique words in the first assessment period to 95,000 words so far in the sixth - we can observe the literature's increasing diversity of content.
-For example, the zika virus, mentioned in 182 articles from 2014-2018, had never before been discussed in the titles or abstracts of articles relating to climate change.
-Yet it has emerged as a topic of high relevance: the incidence of the virus, whose outbreak in Brazil in 2016 was declared a public health emergency by the World Health Organization, is set to increase under rising global temperatures \cite{Rao2019}.
-Similar rapid emergence patterns can be seen for Intended Nationally Determined Contributions (INDCs) in AR6, and Biochar in AR5, among others\footnote{The glossary in SI contains a complete list of the acronyms shown in the table}.
-
-		\begin{figure}[htp]
-			\begin{center}
-				\includegraphics[width=180mm]{../plots_pub/pubs_time_wgb.pdf}
-				\caption{ The number of climate change documents in the Web of Science in each year.
-A total of 406,191 documents were published until the end of 2018.
-The number of publications in each assessment period is shown in square brackets.
-For 2019-21 we project the number of papers assuming there is no more growth, and assuming that growth continues at the same rate as over the past five years}
-				\label{pub-growth}
-			\end{center}
-		\end{figure}
+	\renewcommand\thetable{Supplementary .\arabic{table}}
 
@@
 			\begin{center}
-				{\scriptsize
-					\input{../tables/growth_table.tex}}
-				\caption{Growth of Literature on Climate Change. A glossary of acronyms is provided in SI}
-				\label{tab}
+				\begin{tabular}{lrrrrr}
+					\toprule
+					AR &  1 &   2 &   3 &   4 &   5 \\
+					WG &    &     &     &     &     \\
+					\midrule
+					1  & 8\% & 25\% & 37\% & 47\% & 58\% \\
+					2  & 6\% & 12\% & 30\% & 38\% & 47\% \\
+					3  & 3\% &  9\% & 15\% & 22\% & 35\% \\
+					\bottomrule
+				\end{tabular}
+
+				\caption*{Supplementary Table 1: The proportion of citations in each report that could be matched with a document in our query from the Web of Science}
+				\label{ipcc-matching}
 			\end{center}
@@
 
-		Big literature poses at least three challenges for scientific policy advice and science itself: \emph{First}, established procedures in scientific assessments like those conducted by the IPCC struggle to address the exploding literature base.
-For example, the ratio of studies cited in IPCC reports to the number of studies on climate change in the WoS has declined from 60\% to 20\%  \cite{Minx2017l}, posing a rapidly growing risk of selection bias.
-The exponentially increasing volume of literature means that the provision of ``comprehensive, objective, open and transparent'' assessments of the available scientific literature, as defined in the principles governing IPCC work \cite{IPCC2013}, is no longer possible by traditional means.
-		Machine reading and learning methods, among other data science applications, are required to enable an understanding of the field of climate change research at scale. 
-		\emph{Second}, evidence synthesis - the enterprise of reviewing the literature based on a formal and systematic set of methods \cite{Chalmers2002} - becomes increasingly important for aggregating and consolidating rapidly emerging knowledge and enabling scientific assessments to do their job.
-		Yet traditional methods of evidence synthesis themselves are pushed to their limits by the large amount of scientific publications.
-The field of evidence synthesis technology, which tries to streamline human tasks through machine learning at the different stages of the review process, is still in its infancy \cite{Beller2018}.
-\emph{Finally}, overwhelming amounts of literature may be a major reason why studies of scientific assessments \cite{Bjurström2011} do not offer robust quantification for their claims about the relationship between report citations and the underlying literature.
-
-		This study uses topic modelling \cite{Blei2010} to map the vast body of evidence on climate change.
-Topic modelling is an unsupervised machine-learning technique, where patterns of word co-occurrences are used to learn a set of topics, groups of words, which describe the corpus.
-		The word topic derives from the Greek word for place (topos), and by \textit{situating} the documents in a reduced-form projection of their thematic content (Figure \ref{oecd_topic_map}), we create a \textit{topographic map} of the literature on climate change.
-Such a systematic engagement with the thematic content of the climate science is missing from the literature so far.
-		We then use this map to understand how IPCC reports have represented the available climate change literature and re-evaluate claims of bias based on a more comprehensive understanding of the available climate science.
-		We enrich the discussion on representation by discussing topics as well as disciplines.
-
-		\subsection*{Mapping the landscape of climate change literature}
-
-		Figure \ref{oecd_topic_map} shows a \emph{thematic} or \emph{topographic map} of the 378,000 publications on climate change in our dataset with abstracts.
-Using non-negative matrix factorization \cite{Lee1999}, the 140 topics are machine-learned from the papers' abstracts (see methods for details).
-The topic scores of each document are reduced to the two dimensions shown through t-distributed stochastic neighbour embedding (t-SNE) \cite{vandermaaten2008}.
-\footnote{A full list of topics and related words, and a list of documents, their positions on the map, and their related topics are given in the SI}.
-The two dimensions represent a projection of the 140-dimensional topic scores of each document that seeks to preserve small distances between topically similar documents.
-
-		\begin{figure}[htp]
-			\begin{center}
-				\includegraphics[width=180mm]{../plots_pub/all_topic_words_oecds.png}
-				\caption{A map of the literature on climate change.
-Document positions are obtained by reducing the topic scores to two dimensions via t-SNE (see methods for further details).
-The two axes therefore have no direct interpretation, but represent a reduced version of similarities between documents across 140 topics.
-Documents are coloured by web of science discipline category.
-Topic labels are placed in the center of each of the large clusters of documents associated with each topic.
-}
-				\label{oecd_topic_map}
-			\end{center}
-		\end{figure}
-
-		Our map covers a broad range of topics, with related topics in clusters.
-Generally, topics related to climate science and impacts are on the left, while solution-oriented topics are on the right.
-More fine-grained research areas can also be distinguished.
-For example, publications related to urban infrastructure (\textbf{buildings}, \textbf{cement}, \textbf{waste}) are located on the right, physical climate impacts (\textbf{sea-level}, \textbf{droughts}  or [crop] \textbf{yield}) are in the lower left and energy systems are in upper right.
-Larger groups of documents at the fringes of the map relate mainly to one or two specific topics like \textbf{biochar} or \textbf{coral}.
-Interestingly, scenarios feature centrally in the map, at the interface between different scientific communities.
-This corresponds to their integrative nature in IPCC reports \cite{Moss2010}.
-%This map of the thematic structure of the literature could be useful for individual scientific communities or for climate change assessments.
-
-		The disciplinary composition of this research topography indicated by the different colours in Figure \ref{oecd_topic_map} highlights the dominance of natural sciences in climate change research.
-More than 60\% of the literature is published in natural science journals.
-Similarly, 115 of 140 topics contain a greater share of publications from natural science journals than any other discipline.
-We calculate disciplinary entropy of topics as a measure of their degree of interdisciplinarity (Figure \ref{dis-entropy} and methods for details).
-This shows how research on \textbf{health}, \textbf{food}, or \textbf{policy} comes from a range of disciplines, while research on \textbf{ice} or \textbf{oceans} comes almost exclusively from the natural sciences).
-
-		\begin{figure}
-			\begin{center}
-				\includegraphics[width=180mm]{../plots_pub/topic_evolution_4.png}
-				\caption{Evolution of the landscape of climate change literature.
-In each period, the 10 fastest growing topics are labelled.
-Where documents could be matched to IPCC citations, they are coloured by the working group citing them.}
-				\label{evolution-map}
-			\end{center}
-		\end{figure}
-
-		Finally, the topography shows the thematic evolution of the literature (Figure \ref{evolution-map}), with topics exhibiting distinct patterns of growth.
-Fast-growing topics in the last three assessment periods have included, among others, \textbf{coral}, \textbf{risks}, \textbf{adaptation}, \textbf{hydrogen}, \textbf{buildings}, \textbf{CO2 removal}, \textbf{networks} and \textbf{biochar}.
-\textbf{Biochar} is particularly remarkable in that the sizeable literature which emerged in AR5 was completely absent from the climate change literature beforehand.
-		The identification of new topics as they emerge, particularly as these are identified without prior knowledge of the literature, can help researchers and assessment-makers to keep abreast of a quickly evolving field.
-
-		\subsection*{Research representation in IPCC reports}
-		We apply our topic map to understand how IPCC assessments represent the science and respond to policymakers' and consulted experts' demands for more solution-oriented knowledge \cite{Kowarsch2017}.
-Several studies have identified, made, or repeated claims of a disciplinary bias of IPCC assessments towards the natural sciences, and within the social sciences towards economics \cite{Bjurström2011, Victor2015, Hulme2010, Corbera2016}.
-Where these claims were based on an analysis of IPCC citations \cite{Bjurström2011}, they assess this without measurable baseline.
-		In view of the organisation's mandate to provide ``comprehensive, objective, open and transparent'' assessments of the available science \cite{IPCC2013}, our dataset of publications allows us - albeit imperfectly, as discussed in the concluding section - to study representation with a meaningful baseline.
-Further we provide an update to the last quantitative assessment of IPCC citations \cite{Bjurström2011}, which looked only at AR3.
-		This baseline forms a starting point for informed discussion about how to represent the literature according to the IPCC's priorities.
-
-		By matching the documents in our dataset to a set of references scraped from all published IPCC reports \cite{Minx2017l}, we assess the representation of a group of studies by comparing its share in IPCC citations with its share in the dataset of WoS studies on climate change (see methods).
-		Figure \ref{oecd_rep}.a shows that social science documents (as identified by WoS) were indeed under-represented in AR3, but by AR5 were the most over-represented discipline, with a share in the literature cited by IPCC reports 1.32 times higher than their share in our WoS dataset.
-Likewise, social \& economic geography, political science, and "Other social sciences" were better represented in AR5 than economics.
-		This challenges what we think we know about the IPCC. 
-		Instead of under-representing the social sciences, the IPCC has been under-representing the Agricultural Sciences and Engineering \& Technology.
-		%Humanities are also under-represented, although they make up a very small proportion of the total literature.
-
-		The topography allows us to delve deeper into subjects that receive more or less attention in the IPCC. 
-		%Figures \ref{oecd_rep}b and \ref{oecd_rep}c plot topic representation. 
-		Figure \ref{oecd_rep}c shows that topics more commonly cited by IPCC working group I (WGI) are older and largely better represented in IPCC reports.
-These topics, for example \textbf{ozone}, \textbf{oceans}, and \textbf{aerosols}, are core topics for WGI, which addresses the physical science of climate change.
-
-		The topics in the lower right of the graph are the most pertinent to the question of whether the IPCC is well representing knowledge on climate change.
-They are newer and until now have been under-represented in IPCC reports.
-Their novelty may be highly salient in a periodic assessment process.
-These topics are primarily in working group III, on mitigation and are ``solutions-relevant''.
-But while policymakers' demands for solutions-oriented IPCC assessments were often focussed on policy options, these under-represented new topics deal with more technical solutions and are found in technical disciplines within engineering \& technology and the agricultural sciences.
-
-		Further, WGIII topics that are well represented contain a greater proportion of social science research (figure \ref{oecd_rep}b).
-The topics \textbf{countries}, \textbf{policy}, and \textbf{prices} are close to a proportional representation and are made up of around 30\% social science research.
-\textbf{Waste}, \textbf{biochar}, and \textbf{cement}, are more than 3 times more prevalent in the wider literature than in the literature cited by the IPCC, and are made up of around 5\% social science research.
-This pattern is not visible in other working groups (Figure \ref{socsci-wgs}).
-
-		The difference between under-represented new topics and new topics that are better represented is intriguing.
-This is visible in figure \ref{evolution-map}, where in AR5, the clusters of documents around the, \textbf{buildings} and \textbf{biochar} topics contain few IPCC citations, whereas the clusters around, \textbf{adaptation} and \textbf{food} contain more.
-As shown in figure \ref{oecd_rep}c, \textbf{buildings} and \textbf{biochar} are 3.34 and 3.61 times more prevalent in the literature than in IPCC citations, while \textbf{food} is 1.22 times more prevalent in the literature and \textbf{adaptation} is 2.22 times more prevalent in IPCC citations respectively.
-%The IPCC, has been better at integrating new knowledge from these topics, and in general better at integrating new knowledge from WGII than WGIII topics.
-
-		\begin{figure}[htp]
-			\begin{center}
-				\includegraphics[width=180mm]{../plots_pub/big_panel_representation.pdf}
-				\caption{Representation in IPCC reports: \textbf{a)} by discipline, \textbf{b)} by social science proportion of WGIII topics, \textbf{c)} and novelty of all topics, where topics in the highest and lowest 10\% of either axis are labelled.
-Topics are coloured according to the working group from which they receive the most citations, although infrequently cited topics may not correspond to the relevant working group (see methods).
-Representation is the share of the subset of documents being cited by the IPCC divided by the share of the subset in the whole literature.
-We plot on a log scale so that 0.5 is equally distant to 1 as 2; plot labels show real values.
-Assessment period occurrence refers to the center of a topic's distribution across assessment periods (see methods for further details).}
-				\label{oecd_rep}
-			\end{center}
-		\end{figure}
-
-		\subsection*{Machine-learning for climate change assessments}
-
-		Notwithstanding the over-representation of social science and under-representation of technical solutions in the IPCC with respect to the WoS, a
-		 perfectly proportional representation of the literature is of course not optimal.
-A recommendation that the IPCC cite more or less of any part of the literature is by no means the goal of such an analysis.
-The IPCC, as a community of scientific experts, is vastly better placed to decide what is relevant than any algorithm.
-		As with many machine learning applications, we should be mindful of David Hume's is-ought problem. 
-		Machine learning can help us to more efficiently understand and describe the landscape of climate change literature, but cannot tell us how things should be. 
-		The results represent new knowledge about the interaction between the IPCC and the literature, which can have a variety of implications. 
-		If the IPCC needs to include more social science knowledge \cite{Victor2015}, our analysis suggests that this is a result of insufficient production or funding of social science research on climate, rather than IPCC bias.
-		The under-representation of solutions-relevant topics (despite calls for solutions-oriented assessments), and the small proportion of social science research within these topics,  suggests areas for future highly relevant social science research, as well as opportunities for particularly fruitful interdisciplinary collaboration.
-
-		As a guide for future assessments, the map could facilitate well informed decisions about the representation of different areas of climate literature, from the early scoping process, through to selection by authors of individual studies.
-		One advantage of topic modelling is that outcomes are not determined by any categorisation scheme imposed by the modeller, facilitating the discovery of ``unsearched'' for topics. 
-		Highlighting recent research on, for example, membranes, biochar or e-vehicles, could prompt discussion in the scoping process about their inclusion in chapter outlines.
-		This mode of discovery can act as a complement to human expertise, which may be better at identifying under-researched niches, existing biases or knowledge requirements.
-		The methods shown here could also aid other processes in the production of IPCC reports, such as the identification of potential authors to achieve a better balance across sectors, regions and genders \cite{Corbera2016}.
-The possible benefits or risks of using data science methods for IPCC processes constitutes an important area for future research.
-		Outside of the IPCC, this approach is part of ongoing attempts to make use of machine learning within evidence synthesis.
-This topographic map is a new approach to rapidly mapping very large literatures.
-
-		Our dataset of more than 400,000 publications represents a wealth of knowledge on climate change and climate solutions, but is by no means exhaustive.
-We repeat an established query \cite{Haunschild2016}, granting that it may have imperfections.
-Furthermore, we miss publications not in WoS  (some small journals, some books, and most grey literature, not to mention indigenous knowledge \cite{Ford2016b}); and studies relevant for the work of the IPCC, that do not directly mention climate change (for example on energy policy).
-We argue that this remains a reasonable system boundary given data availability, and stress that documents not included in our study alter our findings only if they have systematically different patterns of citation by the IPCC.
-		A future topography could be improved by making use of more sources of climate change knowledge, extracting and classifying information from full texts, or exploring author networks and interdisciplinarity.
-		Most importantly, exploring machine learning applications that support IPCC authors in their assessments would prepare the IPCC for the age of big literature.
-
-	\end{linenumbers}
-
-	\appendix
-
-	%\listoffigures
-	\linespread{1}
-	\bibliography{Mendeley}
-
-	\bibliographystyle{unsrt}
-
-	%	\include{methods}
-
 \end{document}

### 2020-01-31 poster/poster_amld_2020.tex
amld pres

--- 2019-05-22 poster/baposter.tex
@@
 \usepackage{epstopdf}	% Included EPS files automatically converted to PDF to include with pdflatex
-
+\usepackage{moresize}
 \usepackage{multicol}
@@
 \definecolor{headerfontcol}{RGB}{0,0,0}
-\definecolor{boxcolor}{HTML}{f0f0f0}
+\definecolor{boxcolor}{HTML}{ffffff}
 
@@
 {\sf\bf
-	A Topography of Climate Change Literature
+	A Topography of Climate Change Research
 }
@@
 {
-	\vspace{0.8em} Max Callaghan\\
+	\vspace{0.4em} \url{https://dx.doi.org/10.1038/s41558-019-0684-5}\\
+	Max Callaghan\\
 	{\smaller callaghan@mcc-berlin.net}
@@
 
-\includegraphics[width=\linewidth]{../plots/literature_size/pubs_time}
+\includegraphics[width=\linewidth]{../plots/literature_size/pubs_time_wgb_lp.pdf}
 
@@
 \begin{center}
-	\includegraphics[width=0.98\linewidth]{../plots/ipcc_representation/ipcc_rep_oecds_simplified_short.pdf}
+	\includegraphics[width=0.98\linewidth]{../plots_pub/ipcc_rep_oecds_simplified_lp.pdf}
+
 \end{center}
 \vspace{-1.4em} 
-Contrary to suggestions/previously \cite{Victor2015, Bjurström2011}, the social sciences are over-represented in IPCC reports, engineering/agricultural sciences are under-represented
+Contrary to suggestions/previously \cite{Victor2015, Bjurstroem2011}, the social sciences are over-represented in IPCC reports, engineering/agricultural sciences are under-represented
 }
@@
 \begin{center}
-	\includegraphics[width=0.98\linewidth]{../plots/ipcc_representation/ipcc_rep_new1771_all.pdf}
+	\includegraphics[width=0.98\linewidth]{../plots_pub/rep_time_lp.pdf}
 \end{center}
+
+\vspace{-1.4em}
 
@@
 \headerbox{New Concepts}{name=concepts,span=2,column=1,row=0}{
-	{\scriptsize
-	\input{../tables/growth_table.tex}}
+	{\scriptsize\resizebox{\textwidth}{!}{
+	\input{../tables/growth_table.tex}}}
 
@@
 	\begin{center}
-	\includegraphics[width=1\linewidth]{../tsne_results/plots/run_1771_s_0_p200_all_topic_words_oecds_big.png}
+	\includegraphics[width=1\linewidth]{../plots_pub/all_topic_words_oecds.png}
 	\end{center}
@@
 \begin{center}
-	\includegraphics[width=0.98\linewidth]{../tsne_results/plots/run_1771_s_0_p200_evolution_4.png}
+	\includegraphics[width=0.98\linewidth]{../plots_pub/topic_evolution_4.png}
 \end{center}
@@
 	\begin{center}
-		\includegraphics[width=0.98\linewidth]{../plots/run_1771_wg3_socsci.pdf}
+		\includegraphics[width=0.98\linewidth]{../plots/run_1861_wg3_socsci_lp.pdf}
 	\end{center}
@@
 
-Quantification of knowledge transfer pyramid.
-
-Tools/methodologies for computer assisted evidence synthesis.
+Robust Statistical Stopping Criteria for Automated
+Screening in Systematic Reviews
 

### 2020-01-31 pres/2020_01_amld.tex
amld pres

--- 2019-12-13 pres/2019_11_dzhw.tex
@@
 }
-\date{September 26, 2019}
+\date{January 26, 2019}
 
@@
 			\item<2-> The social sciences are seen as under-represented in IPCC reports
-			\item<3-> \citep{Bjurström2011} are often cited as evidence of this under-representation, e.g.
+			\item<3-> \citep{Bjurstroem2011} are often cited as evidence of this under-representation, e.g.
 as demonstrating ``a powerful bias to the natural sicences in the construction of `IPCC knowledge' '' \cite{Hulme2010}
@@
 			\begin{center}
-				\includegraphics[width=\linewidth]{../plots/run_1861_wg3_socsci.pdf}
+				\includegraphics[width=\linewidth]{../plots/run_1861_wg3_socsci_lp.pdf}
 			\end{center}
@@
 		\end{itemize}
+
+		\bigskip
+		\bigskip
+		\only<7->{
+		\hrule
+		\bigskip
+		\bigskip
+		\hspace{2em}A Topography of Climate Change Research
+		\bigskip
+
+		\hspace{2em}\url{https://dx.doi.org/10.1038/s41558-019-0684-5}
+
+		\bigskip
+		\hspace{2em}\url{callaghan@mcc-berlin.net}
+		}
 	\end{column}
@@
 \begin{frame}{n Topics}
-\vspace{-0.4cm}
+\vspace{-0.4cm}September
 \begin{figure}

### 2020-01-31 pres/AMLD2020_AI&Climate Change_MaxCallaghan_V1.tex
amld pres

--- 2020-01-31 pres/2020_01_amld.tex
@@
 	\includegraphics[height=1cm,width=2cm]{MCC_Logo_RZ_rgb.jpg} \hspace{3em}
-	\includegraphics[height=1cm]{University-of-Leeds-logo.png}
+	\includegraphics[height=1cm]{University-of-Leeds-logo.png} \hspace{3em}
+	\includegraphics[height=1cm]{logo_hbs.jpg}
 }
-\date{January 26, 2019}
+\date{January 27, 2019}
 
@@
 
-\begin{frame}{Topics on solutions are newer and under-represented}
+\begin{frame}{WGIII topics with little social science are under-represented}
 
@@
 
+\begin{frame}{Topic disciplinary entropy and subdiscipline representation}
+\vspace{-0.4cm}
+\begin{columns}
+\begin{column}{0.5\linewidth}
+\begin{figure}
+	\includegraphics[width=1\linewidth]{../plots_pub/upload_figures/Figure_SI_1.pdf}
+\end{figure}
+\end{column}
+
+\begin{column}{0.5\linewidth}
+	\begin{figure}
+		\includegraphics[width=1\linewidth]{../plots_pub/upload_figures/Figure_SI_3.pdf}
+	\end{figure}
+\end{column}
+
+\end{columns}
+\end{frame}
+
+\begin{frame}{Topic growth}
+\vspace{-0.4cm}
+\begin{figure}
+	\includegraphics[width=0.5\linewidth]{../tsne_results/plots/run_1861_s_0_p100_evolution_4.pdf}
+\end{figure}
+
+\end{frame}
+
+\begin{frame}{Social sciences and topic representation}
+\vspace{-0.4cm}
+\begin{figure}
+	\includegraphics[width=0.5\linewidth]{../plots_pub/upload_figures/Figure_SI_4.pdf}
+\end{figure}
+
+\end{frame}
+
 \begin{frame}{n Topics}
-\vspace{-0.4cm}September
+\vspace{-0.4cm}
 \begin{figure}

### 2020-01-31 pres/AMLD2020_AI&Climate Change_MaxCallaghan_V3.tex
amld pres

--- 2020-01-31 pres/AMLD2020_AI&Climate Change_MaxCallaghan_V1.tex
@@
 						\item<2-> The IPCC has a \textit{cartographic} role at the science policy interface \citep{Edenhofer2014, Edenhofer2015}
-						\item<3-> It is much studied in STS \citep{Hulme2010}
 					\end{itemize}
@@
 			\begin{itemize}
-				\item<4-> A topography is a description of a landscape
-				\item<5-> Topics (from the Greek ``topos'', place) can describe the features of a body of text
+				\item<3-> A topography is a description of a landscape
+				\item<4-> Topics (from the Greek ``topos'', place) can describe the features of a body of text
 			\end{itemize}
@@
 			\item<2-> NMF \citep{Lee1999} is a dimensionality reduction technique that can be used for topic modelling
-			\item<3-> Topics are distributions of words. They describe documents.
-			\item<4-> A document's topic scores describe its association with each topic
+			\item<2-> Topics are distributions of words. They describe documents.
+			\item<2-> A document's topic scores describe its association with each topic
 
@@
 			\item<1-> The physical science of climate change is older and better covered
-			\item<2-> Topics on ``solutions'' (although rather technical than policy) are newer and under-represented
-			\item<3-> Newer WGII topics are better covered than newer WGIII topics
+			\item<1-> Topics on ``solutions'' (although rather technical than policy) are newer and under-represented
+			\item<1-> Newer WGII topics are better covered than newer WGIII topics
 

### 2020-01-31 code/run_id.py
cleanup on publication

@@ -1,1 +1,0 @@
-run_id = 386

### 2020-01-31 manuscript/main.tex
png figures for github

--- 2019-10-02 manuscript/main.tex
@@
 
-		{\large{Draft current \@date}}
+		{\large{Draft current July 24, 2019}}
 
@@
 \makeatother
+
+\newcommand{\multicollinenumbers}{
+	\linenumbers
+	\def\makeLineNumber{\docolaction
+		{\makeLineNumberLeft}
+		{}
+		{\makeLineNumberRight}
+	}
+}
+
+\newenvironment{figurehere}
+{\def\@captype{figure}}
+{}
 
@@
 		\cite{Nunez-Mir2016, Minx2017l}, where the science of climate change is expanding exponentially \cite{Grieneisen2011, Haunschild2016}.
-In the five years since the publication of the last IPCC assessment report \cite{IPCC2014c}, 202,000 papers on climate change were published in the Web of Science (WoS) (see Table \ref{tab}).
-This is almost as much as the 205,000 papers identified in the same query \cite{Grieneisen2011} during the first five assessment periods; a period of nearly 30 years.
-A total of around 350,000 new publications can be expected for before the sixth assessment report (AR6) of the Intergovernmental Panel on Climate Change (IPCC), based on current growth patterns (Figure \ref{pub-growth}).
+In the five years since the publication of the last IPCC assessment report \cite{IPCC2014c}, 202,000 papers were published in the Web of Science (WoS) (see Table \ref{tab}).
+This is almost as much as the 205,000 papers published during the first five assessment periods; a period of nearly 30 years.
+A total of around 350,000 new publications can be expected for the current sixth assessment cycle of the IPCC, based on current growth patterns (Figure \ref{pub-growth}).
 Moreover, the literature has also become more diverse.
-This is reflected in the expansion of the literature's vocabulary (see methods) - from 2,000 unique words in the first assessment period to 95,000 words so far in the sixth - indicating that the field has incorporated new content.
+This is reflected in the expansion of the literature's vocabulary - from 2,000 unique words in the first assessment period to 95,000 words so far in the sixth - indicating that the field has incorporated new content.
 For example, the zika virus, which was mentioned in 182 articles from 2014-2018, had never before been discussed in the titles or abstracts of articles relating to climate change.
-Yet it has emerged as a topic of high relevance: the incidence of the virus, the outbreak of which in Brazil in 2016 was declared a public health emergency by the World Health Organization, is set to increase under rising global temperatures \cite{Rao2019}.
-Similar rapid emergence patterns can be seen for Intended Nationally Determined Contributions (INDCs) and Sustainable Development Goals (SDGs) in AR6, and Biochar and the UN forest protection programme REDD in AR5, among others\footnote{The glossary in SI contains a complete list of the acronyms shown in the table}.
+Yet it has emerged as a topic of high relevance: the incidence of the virus, the outbreak of which in Brazil in 2016 was declared a public health emergency by the WHO, is set to increase under rising global temperatures \cite{Rao2019}.
+Similar rapid emergence patterns can be seen for INDCs and SDGs in AR6, and Biochar and REDD in AR5, among others\footnote{The glossary in SI contains a complete list of the acronyms shown in the table}.
 
@@
 				\caption{ The number of climate change documents in the Web of Science in each year.
-A total of 406,191 documents were published until the end of 2018.
-The number of publications in each assessment period is shown in square brackets.
 For 2019-21 we project the number of papers assuming there is no more growth, and assuming that growth continues at the same rate as over the past five years}
@@
 
-		Big literature poses at least three challenges for scientific policy advice and science itself: \emph{First}, established procedures in scientific assessments like those conducted by the IPCC struggle to address the exploding literature base.
-For example, the ratio of studies cited in IPCC reports to the number of studies on climate change in the WoS has declined from 60\% to 20\%  \cite{Minx2017l}, posing a rapidly growing risk of selection bias.
-More generally, the exponential increase in the volume of literature means that the provision of comprehensive, objective, open and transparent assessments of the available scientific literature, as defined in the principles governing IPCC work \cite{IPCC2013}, is no longer possible for authors or author teams by traditional means.
+		Big literature poses at least three challenges for scientific policy advice and science itself: \emph{First}, established procedures in scientific assessments like those conducted by the IPCC fail to address the exploding literature base.
+For example, the ratio of studies cited in IPCC reports to the number or relevant studies has declined from 60\% to 20\%  \cite{Minx2017l}, posing a rapidly growing risk of selection bias.
+More generally, the provision of comprehensive, objective, open and transparent assessments of the available scientific literature, as defined in the principles governing IPCC work \cite{IPCC2013}, is no longer possible for authors or author teams by traditional means.
 		Machine reading and learning methods as well as other data science applications are required to enable an understanding of the field of climate change research at scale. 
@@
 The field of evidence synthesis technology, which tries to streamline human tasks through machine learning at the different stages of the review process, is still in its infancy \cite{Beller2018}.
-\emph{Finally}, overwhelming amounts of literature may be a major reason why studies of scientific assessments \cite{Bjurström2011, Hulme2010, Victor2015} do not offer robust quantification for their claims about the relationship between report citations and the underlying literature.
+\emph{Finally}, overwhelming amounts of literature may be a major reason why studies of scientific assessments \cite{Bjurström2011, Hulme2010, Victor2015} do not offer robust quantifications, for claims about the relationship between report citations and the underlying literature.
 
@@
 		We apply this map in a second step to understand how the IPCC reports have represented the available climate change literature and re-evaluate claims of bias based on a more comprehensive understanding of the available climate science.
-We enrich the discussion on representation in the literature by discussing topics as well as disciplines.
+We enrich the discussion of representation in the literature by discussing topics as well as disciplines.
 
@@
 
-		Figure \ref{oecd_topic_map} shows a \emph{thematic} or \emph{topographic map} of the 378,000 publications on climate change in our dataset that had abstracts with a total number of 140 topics.
+		Figure \ref{oecd_topic_map} shows a \emph{thematic} or \emph{topopographic map} of the 400,000 publications on climate change in our dataset with a total number of 140 topics.
 The number of topics must be defined exogenously, but the results are robust to different specifications.
-Using non-negative matrix factorization \cite{Lee1999}, the topics, which are groups of words that describe groups of documents, are machine-learned from the papers' abstracts (see methods for details, examples of different model specifications, and a thorough explanation of model selection).
-The topic scores of each document are reduced to the two dimensions shown through t-distributed stochastic neighbour embedding (t-SNE) \cite{vandermaaten2008}.
-\footnote{A full list of topics and related words, and a list of documents, their positions on the map, and their related topics are given in the SI}.
-The two dimensions represent a projection of the 140-dimensional topic scores of each document that seeks to preserve small distances between similar documents.
+Using non-negative matrix factoriziation \cite{Lee1999}, the topics are machine-learned from the papers' abstracts (see methods for details, examples of different model specifications, and a thorough explanation of model selection), and the topic scores of each document are reduced to the two dimensions shown through t-distributed stochastic neighbour embedding \cite{vandermaaten2008} \footnote{A full list of topics and related words, and a list of documents, their positions on the map, and their related topics are given in the SI}.
 
@@
 				\caption{A map of the literature on climate change.
-Document positions are obtained by reducing the topic scores to two dimensions via t-SNE (see methods for further details).
-The two axes therefore have no direct interpretation, but represent a reduced version of similarities between documents across 140 topics.
-Documents are coloured by web of science discipline category.
+Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by web of science discipline category.
 Topic labels are placed in the center of each of the large clusters of documents associated with each topic.
@@
 		The map shown covers a broad range of topics, with related topics shown in clusters.
-In general, topics related to climate science and impacts are on the left, while solution-oriented topics are on the right.
+In general, topics related to climate science and impacts are in the West, while solution-oriented topics are in the East.
 More fine-grained research areas can also be distinguished.
-For example, publications related to urban infrastructure (\textbf{buildings}, \textbf{energy}, \textbf{cement}, \textbf{waste}) are located on the right, physical climate impacts such as \textbf{sea-level}, \textbf{droughts}  or [crop] \textbf{yield} are in the lower left and energy systems are in upper right.
+For example, publications related to urban infrastructure (\textbf{buildings}, \textbf{energy}, \textbf{cement}, \textbf{waste}) are located in the East, physical climate impacts such as \textbf{sea-level}, \textbf{droughts}  or [crop] \textbf{yield} are in the South-West and energy systems are in North-East.
 There are larger groups of documents at the fringes of the map that relate mainly to one or two specific topics such as \textbf{biochar}, \textbf{coral}, or \textbf{CO2 storage}.
@@
 This corresponds to their integrative nature in IPCC reports \cite{Moss2010}.
-This map of the thematic structure of the literature could be useful for individual scientific communities or for climate change assessments.
+This map of the thematic structure of the literature could be useful for individual communities or for climate change assessments.
 
@@
 		\subsection*{Research representation in IPCC reports}
-		We apply our topic map to understand the representation of science in IPCC assesssments and how they manage to respond to demands for more solution-oriented knowledge \cite{Kowarsch2017}.
+		We apply our topic map to understand the representation of science in IPCC assesssments and how it manages to respond to demands for more solution-oriented knowledge \cite{Kowarsch2017}.
 Several studies have identified, made, or repeated claims of a disciplinary bias of IPCC assessments towards the natural sciences, and within the social sciences towards economics \cite{Bjurström2011, Victor2015, Hulme2010, Corbera2016}.
-Where these claims were based on an analysis of IPCC citations \cite{Bjurström2011}, they fail to assess this claim against a measurable baseline.
-We argue here that this can be provided by the composition of the climate change literature as a whole.
-Although, as we discuss in the concluding section, it is in many ways imperfect, in view of the organisation's mandate to provide ``comprehensive, objective, open and transparent'' assessment of the available science \cite{IPCC2013}, our dataset of publications allows us to study representation with a meaningful baseline, and over time rather than for single assessment cycles.
-As such it forms a starting point for informed discussion about how to represent the literature according to the IPCC's priorities.
-By matching the documents in our dataset to a set of references scraped from all published IPCC reports \cite{Minx2017l}, we can assess the representation of a group of studies by comparing the group's share in the subset of studies cited by the IPCC with it's share in the dataset of WoS studies on climate change (see methods for further details).
+Where these claims were based on an analysis of IPCC citations \cite{Bjurström2011}, they fail to assess this claim against a measurable benchmark.
+We argue here that the composition of the climate change literature as a whole provides such a benchmark, in view of the organisation's mandate to provide ``comprehensive, objective, open and transparent'' assessment of the available science \cite{IPCC2013}.
+Our database of publications allows us to study representation with such a benchmark, and over time rather than for single assessment cycles.
 
 		Figure \ref{oecd_rep}.a shows that the social sciences were indeed under-represented in the third assessment report, but by the fifth assessment report were over-represented.
-Likewise, social sciences other than economics have become better represented since AR3  (see figure \ref{subfield}f) with social \& economic geography (4.3\% of the literature), political science (1.0\%), and sociology (0.8\%) showing improved representation in AR5 compared to AR3, and social and economic geography, political science, and other social sciences better represented than economics.
+Likewise, other social sciences than economics have become better represented since AR3  (see figure \ref{subfield}f) with social \& economic geography (4.3\% of the literature), political science (1.0\%), and sociology (0.8\%) showing improved representation in AR5 compared to AR3, and social and economic geography, political science, and other social sciences better represented than economics.
 
 		This challenges what we think we know about the IPCC.
-The social sciences, by now, are actually the best represented field, with a share in the literature cited by IPCC reports 1.32 times higher than in the literature at large.
+The social sciences, by now, are actually the best represented field, with a share in the literature cited by IPCC reports 1.32 times as high as in the literature at large.
 On the other hand the Agricultural Sciences and Engineering \& Technology have been consistently under-represented, with 2.27 and 3.49 times the share of studies in the wider literature than in the literature cited by the IPCC in AR5 respectively.
@@
 Figures \ref{oecd_rep}b and \ref{oecd_rep}c plot the representation of the topics shown in the map.
-Figure \ref{oecd_rep}c shows that topics more commonly cited by IPCC working group I (WGI - the physical science basis) are older and largely better represented in IPCC reports.
+Figure \ref{oecd_rep}c shows that topics more commonly cited by IPCC working group I are older and largely better represented in IPCC reports.
 These topics, for example \textbf{ozone}, \textbf{oceans}, \textbf{clouds}, \textbf{aerosols} and \textbf{sea levels} make up some of the core topics of the physical science of climate change.
@@
 Because they are new areas of knowledge, they may be highly salient in a periodic assessment process.
-These topics are primarily in working group III, on mitigation \footnote{see methods for a discussion of the categorisation of topics, including adsorption, and membranes, which may more properly be described as relevant to WGIII}.
+These topics are primarily in working group III, on mitigation \footnote{see methods for a discussion of the categorisation of topics, including CLC, adsorption and hydrogen, which may more properly be described as relevant to WGIII}.
 
@@
 				\includegraphics[width=180mm]{../plots_pub/big_panel_representation.pdf}
-				\caption{Representation in IPCC reports: \textbf{a)} by discipline, \textbf{b)} by social science proportion of WG III topics, \textbf{c)} and novelty of all topics, where topics in the highest and lowest 10\% of either axis are labelled.
+				\caption{Representation in IPCC reports: \textbf{a)} by discipline, \textbf{b)} by social science proportion of WG 3 topics, \textbf{c)} and novelty of all topics, where topics in the highest and lowest 10\% of either axis are labelled.
 Topics are coloured according to the working group from which they receive the most citations.
 Representation is the share of the subset of documents being cited by the IPCC divided by the share of the subset in the whole literature.
-We plot on a log scale so that 0.5 is equally distant to 1 as 2; plot labels show real values.
-Assessment period occurrence refers to the center of a topic's distribution across assessment periods (see methods for further details).}
+We plot on a log scale so that 0.5 is equally distant to 1 as 2; plot labels show real values.}
 				\label{oecd_rep}
@@
 		We have shown that social science literature about climate change is over-represented in the IPCC, while technical literature on solutions is under-represented.
-		A perfectly proportional representation of every part of the literature is of course not optimal, and a recommendation that the IPCC cite more of one part of the literature or less of another is by no means the goal of such an analysis.
-Indeed, the community of scientific experts made up by the IPCC is vastly better placed to decide on what is relevant, of high quality, and should be included in each report than any algorithm.
-		As with many machine learning applications, we should be mindful of David Hume's is-ought problem. 
-		Machine learning can help us to more efficiently understand and describe the landscape of climate change literature, but we should be careful about what we interpret as a recommendation.
-In this light the two main results described here represent new knowledge about the interaction between the IPCC and the literature, which can have a variety of important implications.
+		A perfectly proportional representation of every part of the literature is of course not optimal, yet these two features represent new knowledge about the interaction between the IPCC and the literature, and have important implications for the community.
 		The over-representation of the social sciences, combined with the perception that the IPCC needs to include more social science knowledge \cite{Victor2015}, suggests that doing so must involve the funding and production of more social science literature on climate change, not just greater efforts by the IPCC to include it.
-		Moreover, the fact that solutions-relevant topics are under-represented - while policymakers demand more solutions-oriented assessments - and that these topics contain little social science research, suggests areas where social science research may be usefully conducted, as well as opportunities for particularly fruitful interdisciplinary collaboration.
+		Moreover, the fact that solutions-relevant topics are under-represented - while policymakers demand more solutions-oriented assessments - and that these topics contain little social science research, suggests areas where social science research may be usefully conducted.
 Further, this fact can open a debate about the extent to which the IPCC should include more technical knowledge on solutions from disciplines within engineering and the agricultural sciences.
@@
 		The map can contribute to these decisions as they are made from the scoping process, through to the selection by authors of individual studies.
-		The advantage of topic modelling is that the outcome is not determined by any categorisation scheme imposed by the modeller, which facilitates the discovery of ``unsearched'' for topics.
-Highlighting recent research on, for example, membranes, biochar or e-vehicles, could prompt discussion in the scoping process about the extent to which each of these topics are relevant and should be included.
-		This mode of discovery can act as a complement to human expertise, which may be better at identifying under-researched niches, existing biases or knowledge requirements.
 		Beyond this, the methods shown here could aid other processes in the production of IPCC reports, such as the identification of potential authors to acheive a better balance across sectors, regions and genders \cite{Corbera2016}.
-The possible contribution of, or drawbacks to data science methods for IPCC processes is an important area for future research.
 		Outside of the IPCC, this approach is part of ongoing attempts to make use of machine-learning within evidence synthesis.
@@
 Beyond this we miss publications not in the Web of Science (some small journals, some books, and most grey literature, not to mention indigenous knowledge \cite{Ford2016b}); and studies relevant for the work of the IPCC, but that do not directly mention climate change (for example on energy policy).
-We argue that this remains a reasonable system boundary given data availability, and stress that the documents not included in our study alter our findings only if they have systematically different patterns of citation by the IPCC.
-In the future, making use of more sources of climate change knowledge, extracting and classifying information from full texts, or exploring author networks and interdisciplinarity, could improve the usefulness of this topography.
+We argue that this remains a reasonable system boundary given data availabilty, and stress that the documents not included in our study alter our findings only if they have systematically different patterns of citation by the IPCC.
+In the future, making use of more sources climate change knowledge, and extracting and classifying information from full texts, could improve the granularity of this topography.
 Most importantly, machine learning applications should be explored that support IPCC authors in assessing the literature.

### 2020-01-31 code/run_models.py

@@ -21,8 +21,7 @@ sw.add('copyright')
 q = Query.objects.get(pk=6187)
 for m in ["NM","LD"]:
     for a in [0.01,0.05,0.1]:
-        #for k in [80,90,100,110,120,130,140,150]:
-        for k in [150]:
+        for k in [80,90,100,110,120,130,140,150]:
             if m=="LD":
                 alpha=a*10
             else:

### 2020-01-31 code/tsne_runs.py

@@ -96,8 +96,7 @@ def draw_simple(results,r_ind,fname=None):
         plt.savefig(fname)
         plt.close()
 
-for run_id in [1861]:#,758]:
-    #for s_size in [10000,20000,50000,100000,0]:
+for run_id in [1861]:
     for s_size in [0]:
         print(s_size)
         m, c_ind, r_ind = get_matrix(run_id,s_size)
